### 2021-11-15 inst/main/linear_test.Rmd
All files
files

---
title: "linear_test"
author: "Anubhav Gupta"
date: "16/12/2020"
output: html_document
---

```{r message=FALSE}

library(dplyr)
library(ggplot2)

set.seed(123)
m <- 4
c <- 5
npoints <- 3001
x <- seq(0, 300, length.out = npoints)
epsilon <- rnorm(npoints, mean = 0, sd = 50)
y <- m * x + c + epsilon

dd_raw <- data.frame(x = x, y = y)
ggplot(dd_raw) +
  geom_point(aes(x = x, y = y)) +
  geom_vline(xintercept = c(100, 200), color = "red")

dd_lower <- dd_raw %>%
  filter(x <= 100)

dd_mid <- dd_raw %>%
  filter(x >= 100 & x <= 200)

dd_upper <- dd_raw %>%
  filter(x >= 200 & x <= 300)

lm_all <- lm(y ~ x, data = dd_raw)
lm_lower <- lm(y ~ x, data = dd_lower)
lm_mid <- lm(y ~ x, data = dd_mid)
lm_upper <- lm(y ~ x, data = dd_upper)

summary(lm_all)
summary(lm_lower)
summary(lm_mid)
summary(lm_upper)
```

We observe that the standard error in the estimation of intercept increases. The standard error in the slope remains approximately equal for the three ranges (lower, mid and upper) of x values.

### 2021-11-15 inst/report/appendix.Rmd
All files
files

---
title: "appendix"
header-includes:
   - \usepackage{lineno}
   - \linenumbers
author: "Anubhav Gupta"
date: "11/30/2020"
output: pdf_document
---

## Uncertainty in gut content data
<!-- The text below is copied from Baker et al 2014 Fish gut content analysis: robust measures of diet composition -->

* The separation of prey items in fish guts can rarely be carried out unambiguously and attempts to do so introduces unquantifiable errors to any measure of prey bulk. Loose tissue amongst partially digested prey remains in the stomach cannot be visually allocated to any prey category with absolute confidence, regardless of how prey categories are defined [@schaferComparisonsInfluenceHabitat2002a]. This is because it may be the remains of separate prey items no longer represented by identifiable parts, or an inseparable mixture of digested tissues from multiple prey items. Consequently, loose tissue allocated to any category other than 'unidentified' potentially adds error to each volume or weight value obtained, meaning the summarized dietary composition unmeasurable and potentially substantial error.

* Even where it is possible to accurately separate prey items in a gut, the actual composition of a gut content in a single point in time is affected by a broad range of unquantifiable factors unrelated to the actual composition of the diet consumed. The sample size of consumers, mechanical prey handling, differential digestion and evacuation rates of different prey types and volumes, and the order of ingestion, combine to provide bulk data that are ambiguous, contain unquantifiable error and are difficult to interpret.

*

### Why use stable isotopes?

* Since different tissues integrate diet over different temporal scales, several distinct sources of information can be accesssed from a single sampling event. For example, carbon and nitrogen isotopes were measured in the blood and fur of the red fox Vulpes vulpes and coyote Canis latrans within an agriculture setting in Illinois (Lavin et al., 2003). Blood (the short-term indicator) was used to show a localized habitat effect showing the young fox pups foraging opportunistically around the den, whereas fur (the long-term indicator) provided the necessary temporal period to show that the adult foxes had adjusted their niche width, as a direct response to the additional competition for resources from the coyote. To achieve this insight conventionally would have been practically impos- sible and at the very least require a huge amount of time and sampling effort.

* If the phenology of growth is known, collection of keratinized tissues can provide dietary information from elusive stages of a mammal’s life history, which may otherwise remain unknown (i.e. during months when mammals are away from breeding areas or are difficult to capture). This feature has been used to great effect in understanding mammalian behaviour. For example, researchers have analysed the stable isotope ratios of fur to reveal hoary bat Lasiurus cinereus migration (Cryan et al., 2004); pinniped vibrissae to track temporal shifts in their diets (Hirons, Schell & Finney, 2001); and baleen to track the migrations of whales (Hobson & Schell, 1998).

* Stable isotopic characterization of diet generates a quantitative and continuously distributed variable, which makes for easier statistical analyses and construction of predictive models (Felicetti et al., 2003; Urton & Hobson, 2005; Inger et al., 2006). This becomes a particularly powerful tool when resolving issues of specialized diets (McIlwee & Johnson, 1998; Felicetti et al., 2003), especially useful in cases where the particular significance of scarce protein sources has a direct impact on species conservation. For example, it was known that the endangered Yellowstone grizzly bear Ursus arctos horribilis fed upon the nuts of whitebark pine Pinus albicaulis, itself an increasingly vulnerable species.

### Some caveats of stable isotope approaches

* The most common sources of error include variability in the isotopic fractionation values across different combinations of diets and tissues/species, unquantified temporal or spatial variation in prey isotopic values and variation caused by routing of particular dietary nutrients into particular tissues.

### Solution  to SIR problems

* Sensitivity of model outputs should be assessed by varying diet-tissue fractionation factors

### 2021-11-15 inst/report/ms_31_05_2021/report.Rmd
All files
files

---
title: 'Effects of data composition and diversity on precision and accuracy
  of network inference'
date: "`r format(Sys.time(), '%d %B %Y')`"
header-includes:
- \usepackage{lineno}
- \usepackage{xcolor}
- \linenumbers
- \usepackage{textcomp}
output:
  pdf_document:
    fig_caption: yes
    number_sections: yes
    toc: yes
  html_document:
    df_print: paged
    toc: yes
  word_document: null
indent: true
mainfont: Times New Roman
bibliography: ../../references.bib
---

# Abstract

# Introduction

## Why is knowing trophic interactions important?

Knowledge about the trophic interactions in a food web can be used to answer crucial ecological questions: Which species is a keystone species in a food web [@jordanKeystoneSpeciesFood2009]? How would a food web respond if the top predators are removed [@knightTrophicCascadesEcosystems2005]?  Which species should be given priority when conservation efforts are implemented [@mcdonald-maddenUsingFoodwebTheory2016]? How robust is a food web to extinctions [@dunneNetworkStructureBiodiversity2002]?

## What are the methods for knowing interactions?

Species interactions can be inferred from different types of methods (Table \ref{fig:tab_1}) such as gut content analysis [@peralta-maraverStructureDynamicsStability2017], stable isotope ratio analysis of tissues [@laymanCanStableIsotope2007], experimentation [@warrenSpatialTemporalVariation1989] and DNA metabarcoding [@roslinUseDNABarcodes2016]. The types of information extracted from these methods vary. E.g. Gut content analysis of a predator results in the identification of prey species fed upon by that predator, while the stable isotope ratio analysis of the organism's tissue can help us infer the approximate trophic position of that species in the food web.

## Gut content analysis

Gut content analysis is performed to know what an individual has consumed recently. The diet of that individual can be inferred from the items in the stomach. There is considerable uncertainty involved in this method [@bakerFishGutContent2014]. E.g. In fish, there is ambiguity while separating prey items in the gut. There are loose tissues that are not identifiable and cannot be assigned to a specific prey item with certainty. There are factors such as sample size of consumers, mechanical prey handling, differential digestion and evacuation rates of different types of different prey types and volumes, and the ingestion order that in combination result in an unquantifiable error which is difficult to interpret in the predator diet [@hyslopStomachContentsAnalysis1980; @rindorfBiasEstimatingFood2004; @bakerFishGutContent2014].

## Stable isotope analysis

Stable isotope composition of a specific element in a consumer's tissue is given by the ratio of a rarer, heavier isotope to a more common lighter isotope [@mccormackUsingStableIsotope2019]. Stable isotope analysis (SIA) of tissues from a single individual can be used to quantify its diet over varying temporal and spatial scales from one sample [@crawfordApplicationsStableIsotope2008]. Using SIA, several different sources of information can be extracted from a single sampling event as different tissues integrate diet over different temporal scales as well as spatial scales. However, there is uncertainty involved in this method which is due to variability in the isotopic fractionation values across multiple combinations of diets and tissues/species, unquantified temporal or spatial variation in prey isotopic values and variation caused by routing of particular dietary nutrients into particular tissues [@crawfordApplicationsStableIsotope2008].

Trophic level of a species $i (TL_i)$ is calculated as:

$TL_i = \frac{\delta^{15}N_i - \delta^{15}N_{base}}{\Delta^{15}N} + TL_{base}$

where $\delta^{15}N_i$ is the $\delta^{15}N$ value of species $i$, and $TL_{base}$ and $\delta^{15}N_{base}$ are known TL and $\delta^{15}N$ values corresponding to a reference baseline species from a given food web. $\Delta^{15}N$ is the trophic fractionation value (usually 3.4%)

<!-- * *Note:* update with a relevant symbol after 3.4  -->

## Why inferring interactions is not easy?

As a food web can be quite complex with many species and trophic interactions [@williamsSimpleRulesYield2000;@berlowSimplePredictionInteraction2009], inferring these trophic interactions with high accuracy and low uncertainty would require large amount of food web data (citreqd). E.g. One would need to sample many individuals for gut content data, and processing these guts require a large amount of effort and time as well. Hence, there needs to be prioritisation of sampling based on an individual trait which is easily identifiable in the field, which would lead to high accuracy in predicting food web with minimal effort.

Even though when one had finally made a decision to use a single type of food web data to infer the species interactions, it might not be practically feasible to infer the complete food web structure from only a single type of food web data. E.g. Stable isotope analysis from tissues can only provide the approximate trophic position of the species which might not be sufficient to predict the complete food web structure. Also, gut content data might only be used to infer partial diet of a predator individual because gut content data only provides the information of the prey individuals that have been foraged by the predator recently. There is also a possibility that some of the information provided by these types of food web data are redundant i.e. taking into account any further food web data does not necessarily increase the food web prediction significantly. E.g. This can happen if the guts of two predator individuals give same information about the prey the predator has consumed.

Gut content data and stable isotope data provide different types of information about a food web on different taxonomic, spatial and temporal scales which results in different amount of uncertainties in inferring the species interactions. E.g. Gut content data provides information about the diet of an individual on a local scale whereas stable isotope provides the information about the diet on a bigger spatial scale which is dependent upon the amount of space dispersed by that species. Therefore, it is crucial to integrate these diverse information simultaneously from these methods so that information from different taxonomic, spatial and temporal scale can be integrated, requiring less sampling effort and resulting in a high accuracy of the food webs.

<!-- * Note: Food web properties are highly sensitive to varying levels of sampling effort. -->

<!-- * *Note:* The amount of sampling effort affects how well the food web properties are predicted [@goldwasserSamplingEffectsEstimation1997]. -->

## What we do in our study and how?

These questions are addressed *in silico* by simulating food web networks whose true parameters are known. We used the allometric diet breadth model (ADBM) to simulate the food webs and approximate Bayesian computation (ABC) to parameterise the ADBM. We simulated the food web data which were used to parameterise the ADBM using ABC. We also used real gut content data from Broadstone Stream food web to address those questions.

<!-- * *Note:* Why did we choose gut content analysis and stable isotope analysis only? -->

<!-- * *Note:* Why ADBM and ABC? -->

<!-- * *Note:* Why body size trait? -->

```{r echo = FALSE, warning = FALSE}
options(knitr.kable.NA = '')
library(readxl)
library(knitr)
library(kableExtra)
fw_table <- read_excel("data_summary_fil.xlsx")

kable(fw_table, format = "latex",
      caption = "\\label{fig:tab_1}Studies showing the type of data used to infer trophic interactions in a food web",
      escape = FALSE) %>%
    kable_styling(latex_options="scale_down")

```

# Materials and Methods

Firstly, we present an *in silico* approach (Fig. \ref{fig:fig_m1}) to address the research questions where we simulated food web structure using the allometric diet breadth model (ADBM) whose true parameters were known. In the upcoming sections, we present methods to simulate gut content data and stable isotope ratio data with uncertainty. We vary the amount of simulated data and use partial data to predict food web using the ADBM parameterised via the rejection approximate Bayesian computation (ABC). Secondly, we used a gut content data from an observed Broadstone Stream food web to infer the trophic interactions.

<!-- * *Note:* A beautiful figure summarising the food web data types. -->

```{r fig_m1, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_m1} \\textit{In silico} approach for investigating the effect of quantity and composition of food web data in predicting food web structure using the ADBM."}
knitr::include_graphics("fig/flowchart.png")
```

<!-- * *Note:* 'in silico' to be in italics in the caption -->
<!-- * *Note:* Remove direct observation from the flowchart -->

## Gut content data simulation

We simulated a food web using the ADBM for a given set of parameters. For a given set of predators, we subset the diet from the simulated food web. Then using a probability mass function (distribution), we sampled the gut content data from predators' diet thereby incorporating the uncertainty in the gut content data. We repeated this process multiple number of times for every predator in the food web.

*Input:*

* Predators whose diet are to be simulated $P = \{p_1, \dots, p_n\}$

* A simulated food web $ADBM(\theta_i) = \{d_{p_1}, d_{p_1}, \dots, d_{p_k}\}$, where $d_{p_k}$ is a one-dimensional diet matrix of predator $k$ containing ones and zeros.

* A function which describes uncertainty in the diet $U(d)$

* Number of independent guts to be simulated for a predator $p_i: ngut$

*Sampling:*

* for $p_i \in P$

  - for $j = 1, \dots, ngut$, where $ngut$ is the number of guts to be simulated

    - Simulate a single gut of a predator $p_i: g(p_i) = d_{p_i} *  U(d_{p_i})$

  - Set of gut of a predator $p_i: G(p_i) = \{ g(p_i) : g(p_i) = d_{p_i}*U(d_{p_i}) \}$

*Output:*

* We simulated a pool of gut content data which contains simulated gut content data $G(p_i)$ for every predator $p_i$

## Inferring food web using gut content data

From a pool of gut content data, we draw a set of gut content data randomly. Then we used the rejection ABC to accept a parameter value which would have resulted in the minimum distance, where distance = 1 - True skill statistic and the true skill statistic was computed between the predators' diet predicted from the ADBM and the sampled gut content data. We repeated this process for $n~(= 100)$ number of times for every $i$ number of guts, where $i$ lies between 1 and total number of gut content data in the pool.

*Input:*

* Predators $P: P = \{p_1, p_2, \dots, p_k \}$

* A pool of gut content data $G: G = \{g_1, g_2, \dots, g_n\}$, where $g_{n}$ is a one-dimensional matrix containing ones and zeros.

* A model prediction $model(\theta): ADBM(\theta) = \{d_{p_1}, d_{p_1}, \dots, d_{p_k}\}$, where $d_{p_k}$ is a one-dimensional diet matrix of predator $k$ containing ones and zeros.

* A summary statistic $s(x): s(x) \subseteq model(\theta)$

* A distance function $d(x_i, y) : d(x_i,y) = 1 - TSS(x_i, y)$

* An observed food web $Y: Y = \{d_{p_1}', d_{p_1}', \dots, d_{p_k}'\}$

*Sampling:*

for $i = 1, \dots, tgut$ where $tgut$ is the total number of gut content data in the pool $G$

* for $j = 1, \dots, nsample$ where $nsample$ is the number of independent samples to be drawn

  - Draw a set of gut content data $y = \{g_1, g_2, \dots, g_i\}$ from the pool of gut content data $G$

  - for $k = 1, \dots, npar$ where $npar$ is the number of parameter values to be sampled

    - Draw a set of parameter values $\theta_k$ from the prior distribution $\pi(\theta)$

    - Compute the model result $x_i = model(\theta_k)$

    - Compute $s(x_i)$ and $d(s(x_i), y)$

  - Accept $\theta_j$, which results in the $min_i\{d(s(x_i), y)\}$

* Compute $TSS_{i}(x, y) = \{TSS(x_i,y): x_i = ADBM(\theta_j), \theta_j \text{ computed from previous step}\}$ using the accepted $\theta_1, \dots, \theta_{nsample}$

*Output:*

A prediction interval containing $TSS$ between observed and predicted food webs for every $i$ number of gut content data drawn from the pool of gut content data.

<!-- ## Stable isotope ratio data simulation -->

```{r fig_m2, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_m2} Distribution of proportion of prey in the gut of a predator belonging to a specific size class in the Broadstone Stream food web. The proportion of prey in a predator's gut is calculated as number of unique prey items observed in the predator gut divided by the total number of unique prey items in all the gut of that predator."}
knitr::include_graphics("../../results/misc/prey_propn_in_gut.png")
```

## Broadstone Stream food web

<!-- * *Note:* Which types of interactions are we interested in? -->

<!-- * *Note:* How was the gut content data collected? -->

<!-- * *Note:* Show the distribution of proportion of prey in the gut content data of Broadstone -->

Broadstone Stream (51$^\circ$ 05' N 0$^\circ$ 03' E; 120 m above sea-level) is a second-order tributary of the River Medway in south-east England. It is dominated by invertebrates as the acidity of the stream (pH 4.7-6.6) excludes fish. The stream consists of 25 common invertebrate species [@woodwardQuantificationResolutionComplex2005]. Among the predators, the three large species are *Cordulegaster boltonii* Donovan, *Sialis fuliginosa* Pict. and *Plectrocnemia conspersa* [Curtis] and the three small species are the larvae of the tanypod midges *Macropelopia nebulosa* [Meigen], *Trissopelopia longimana* [Staeger], and *Zavrelimyia barbatipes* [Kieffer]. Broadstone Stream food web is one of the most completely described food webs for any system [@schmid-arayaImportanceMeiofaunaFood2002; @hildrewChapterSustainedResearch2009; @layerFoodWebStructure2010; and @woodwardQuantificationResolutionComplex2005a].

The Broadstone Stream food web in our study was constructed by aggregating by size [@woodwardIndividualBasedFoodWebs2010] i.e a node is defined as collection of individuals within a specified size range. There were a total of 1008 gut content data. The number of prey items in predator's gut varied within a predator size class (Fig. \ref{fig:fig_m2}). A single gut cannot give information about the complete diet of a predator as can be observed from the right skewed distribution (Fig. \ref{fig:fig_m2}).

## Allometric Diet Breadth Model (ADBM)

The allometric diet breadth model (ADBM) is based on optimal foraging theory, specifically the contingency foraging model [@macarthurOptimalUsePatchy1966]. The ADBM predicts the set of prey species a consumer should feed upon to maximise its rate of energy intake [@petcheySizeForagingFood2008]. The foraging variables in the model: energy content of the resources, handling times of the prey, space clearance rate and prey densities are allometrically scaled to the body sizes of the species.

The model correctly predicted a greater proportion of links when the trophic interactions were more strongly dependent on size [@petcheySizeForagingFood2008]. Indeed, constructing a food web based only on body size (i.e. ignoring taxonomy) resulted in almost twice the number of correctly predicted links, i.e. 83%, in contrast to taxonomy [@woodwardChapterIndividualBasedFood2010]. The goodness of fit of the ADBM's predictions depends on the types of interactions in the food webs [@petcheySizeForagingFood2008], because some of the interactions are more size structured than other interactions. For instance, predacious and aquatic herbivore interations were predicted better than parasitoid and herbivory ones [@petcheySizeForagingFood2008].

<!-- ## The Rejection ABC method -->

## Assessment of prediction

The accuracy of the predicted diet of the predators was defined using true skill statistic (TSS) which takes into account the true and false predictions of both the presence and absence of links defined as:

$$ \text{TSS} = \frac{ad-bc}{(a+c)(b+d)} $$ where $a$ is the number of observed links that are predicted by the model (true positives), $d$ is the number of observed absences of links that are correctly predicted (true negatives), $b$ is the number of false positives, and $c$ is the number of false negatives.

The $TSS$ ranges from $-1$ to $1$, where +1 indicates a perfect prediction. A $TSS$ value of zero or less indicates a performance no better than random.

# Results

We first present the $\dots$

## Prediction using real gut content data from the Broadstone Stream food web

```{r fig_r1, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r1} True skill statistics between the predicted and observed Broadstone Stream food web computed for number of different predator guts sampled. There were a total of 1008 guts from 29 species. Line represents the mean and shaded region represents the range/uncertainty. Blue and red curve/region correspond to real and randomly generated gut content data respectively. "}
knitr::include_graphics("../../results/rejection/Broadstone Stream size_agg_v2/rule_ind/TSS_with_n_pred_prop_n_sel=1.png")
```

The value of true skill statistics between the predicted food web and observed food web saturated quickly with the increasing number of distinct real predator guts (Fig. \ref{fig:fig_r1}). With only 228 real predator guts, the ADBM parameterised with ABC predicted the food web with an accuracy of 90% of the maximum mean TSS (0.71). The uncertainty (red shaded region) in the TSS reduced with the increasing number of predators' guts. Although at a low number of predators' guts the maximum TSS was quite high the uncertainty was high as well. This was quite possibly just by chance which was suggested by the overlap of the TSS region with that of randomly generated gut content data.

<!-- We compared the TSS predicted from real gut content data with randomly generated gut content data. Unsurprisingly, the range/uncertainty of TSS was high and almost remained constant with increasing number of predator guts sampled. The mean TSS fluctuated for lower number of predator guts sampled but eventually became constant, and was close to 0 which suggests the prediction is no better than random. -->

True skill statistics between the predicted food web and the observed food web had a saturating curve with the increasing number of distinct predator guts (Fig. \ref{fig:fig_r3}) for both sets of gut predator guts: First set of gut data consisted of predator body sizes which were smaller than the mean body size and second set of gut data consisted of predator body sizes which were larger than the mean body size. However, the mean TSS corresponding to the guts of predators smaller than the mean body size was higher when compared to that from the guts of predators larger than the mean body size.

<!-- * *Note:* Compare the uncertainty (prediction intervals) between both set of gut data in Fig. \ref{fig:fig_r3}. -->

```{r fig_r3, echo=FALSE, fig.align='center', out.width="300px", fig.cap="\\label{fig:fig_r3} True skill statistics between predicted food web and observed food web estimated for different number of distinct predator guts. The estimation is done for three sets of gut data: gut content data of predators whose body sizes are smaller than the mean body size, larger than the mean body size, and all the gut content data."}
knitr::include_graphics("../../results/rejection/Broadstone Stream size_agg_v2/rule_lbs/TSS_with_n_pred_prop.png")
```

## Accuracy of model against accuracy of data

```{r fig_r31, echo=FALSE, fig.align='center', out.width="300px", fig.cap="\\label{fig:fig_r31} True skill statistic between predicted food web using ADBM, and observed food web plotted against the true skill statistic between food web constructed using incomplete gut content data, and observed food web."}
knitr::include_graphics("../../results/misc/TSS_model_vs_data.png")
```

## Mean standardised error in food web properties

```{r fig_r32, echo=FALSE, fig.align='center', out.width="300px", fig.cap="\\label{fig:fig_r32} Mean standardised error for structural food web properties plotted against the number of distinct predator gut content data "}
knitr::include_graphics("../../results/misc/plot_SE_vs_ngut.png")
```

## Prediction using simulated stable isotope ratio data from a simulated food web

<!-- ```{r fig_r4, echo=FALSE, fig.align='center', out.width="300px", fig.cap="\\label{fig:fig_r4} True skill statistics between predicted food web and observed food web for simulated small reef food web estimated for different number of predator species. For every value in the horizontal axis, there are 100 samples of randomly chosen species from a set of 50 species whose gut content data are simulated."} -->
<!-- knitr::include_graphics("../../results/rejection/sim_Small Reef/rule_s4/TSS_with_n_pred_prop_s3_s4.png") -->
<!-- ``` -->

## Prediction using both simulated stable isotope ratio and simulated gut content data from a simulated food web

<!-- ```{r, echo=FALSE, fig.align='center', out.width="300px", fig.cap="\\label{fig:fig_r5} True skill statistics between predicted food web and observed food web for simulated small reef food web estimated for different number of predator species. For every value in the horizontal axis, there are 100 samples of randomly chosen species from a set of 50 species whose gut content data are simulated."} -->
<!-- knitr::include_graphics("../../results/rejection/sim_Small Reef/rule_s_r_1/TSS_with_n_pred_prop.png") -->
<!-- ``` -->

<!-- ## Cost analysis: TSS vs the amount of money spent on the  -->

# Discussion

## Why did we achieve a higher TSS when we use gut content data for predators less than mean body size?

The predator diets in the observed food web is not nested i.e. the diet of smaller species is not subset of the diet of larger species. When diets of predators with body size lower than mean body size is used to infer the food web, the predicted food web contains the diets of bigger predators as well because the

<!-- ## Include digestion in the gut content simulation -->

<!-- ## On generalising ADBM's predictions over all food webs -->

<!-- ## Include other food web data type -->

<!-- * *Note:* experimentation (feeding trials) -->

<!-- * *Note:* DNA Metabarcoding -->

## Extension to other food web models

# Conclusion

# Supplementary Information

## Prediction using simulated gut content data from a simulated food web

```{r fig_r0, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r0} True skill statistics between predicted food web and observed food web for a simulated small reef food web estimated for distinct predator guts in a sample. The observed simulated food web consists of 50 species and \\dots links. The vertical bars correspond to the prediction intervals of the true skill statistics with filled circles representing the corresponding mean. A prediction interval of the TSS is formed using a set of 100 accepted TSS values using the ABC method."}
knitr::include_graphics("../../results/rejection/sim_Small Reef/rule_r8/TSS_with_n_pred_prop.png")
```

The true skill statistics (TSS) between the predicted food web and observed food web saturated with an increasing number of distinct predator guts in a sample (Fig. \ref{fig:fig_r0}). The TSS of the predicted food webs estimated using the complete individual gut data had shorter prediction intervals resulting in less uncertainty, and higher mean TSS than that using the partial individual gut data. The maximum limit of the prediction interval of TSS estimated using the complete gut data and the partial gut data were almost equal, with the minimum limit of the prediction interval of TSS using partial gut data being lower than that from the complete gut data. Eventually, the gap between the mean TSS using the partial gut data and the complete gut data reduced with an increasing number of distinct predator guts suggesting when we have enough predator species' gut data, the achieved TSS was almost constant and hence independent of the amount of gut data.

The maximum TSS estimated using the complete gut data was very close to one and almost remained constant with an increasing number of different predator species sampled. With the gut data sample of only five distinct predator species, 95% of the maximum mean TSS was achieved when complete individual gut data was used, while the same was achieved with 15 predator species for partial gut data. This shows that one does not need to know the gut data of all the species to predict the food web and the accuracy is dependent on the completeness of an individual gut data.

# References

<!-- # Notes: -->

<!-- ## Stable isotope ratios -->

<!-- * Isotope ratios are reported in parts per thousand  relative to standards, and atmospheric N for nitrogen, and defined in delta notation as -->

<!-- * $\delta^{15}N$ or $\delta^{13}C = (\frac{R_{sample}}{R_{standard}} - 1) * 10^3 $ -->

<!-- * Most commonly a fixed $\Delta^{15}N$ value of 3.4 ppt is used to estimate relative species TP -->

<!-- # Other notes: -->

<!-- * Audience: Researchers who are interested in food web data collection -->

### 2021-11-15 inst/report/ms_31_05_2021/test.Rmd
All files
files

---
title: "Untitled"
header-includes:
   - \usepackage{lineno}
   - \linenumbers
description: |
  A new article created using the Radix format.
author:
  - name: Nora Jones 
    url: https://example.com/norajones
    affiliation: Spacely Sprockets
    affiliation_url: https://example.com/spacelysprokets
date: "`r Sys.Date()`"
output: radix::radix_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Radix is a publication format for scientific and technical writing, native to the web.

Learn more about using Radix at <https://rstudio.github.io/radix>.

```{r fig_r0, echo=FALSE, fig.align='center', out.width="500px", results='asis', fig.cap="\\label{fig:fig_r0} True skill statistics between predicted food web and observed food web for simulated small reef food web estimated for different number of predator species' guts sampled. For every value in the horizontal axis, there are 100 samples of randomly chosen species from a set of 50 species whose gut content data are simulated."}
knitr::include_graphics("../report/fig/fig_1/fig_2/sim Small Reef/TSS_with_n_pred_prop.png")
```

### 2021-11-15 inst/report/report_C2.Rmd
All files
files

---
title: "report_C2"
author: "Anubhav Gupta"
date: "8/3/2021"
output: pdf_document
---

## Q1: Construct a graph with minimum number of gut content data with respect to the number of species.

## Q2: Plot number of false positives in ADBM's prediction with respect to the gut content data

## Q3: Make a list of journals for submission of ms

## Q4: Plot the graphs for a case when the ADBM’s best prediction is the true one

---

## Q1: Construct a graph with minimum number of gut content data wrt number of species.

```{r, echo=FALSE, fig.align='center', out.width="300px", fig.cap=" "}

knitr::include_graphics("fig_2021_10_15/plot_n_min_gut_vs_S.png")
knitr::include_graphics("fig_2021_10_15/plot_n_min_gut_vs_L.png")
knitr::include_graphics("fig_2021_10_15/plot_n_min_gut_vs_C.png")
knitr::include_graphics("fig_2021_10_15/plot_n_min_gut_vs_n_pred.png")
```

### Preliminary results:

-   There seems to be a positive relation between the number of minimum gut and the predictors (S, L, C and number of predator nodes) in Fig. 1-4 (Broadstone Stream is an outlier in Fig. 1,2 and 4).

## Q2: Plot number of false positives in ADBM's prediction with respect to the gut content data

```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap=" "}

knitr::include_graphics("fig_2021_10_15/plot_FPR.png")
```

### Preliminary results:

-   The food web with a high false positive rate in Fig. 5 has low true skill statistics.

## Q3: Make a list of journals for submission of ms

-   Methods in Ecology and Evolution (IF = 6.4)\
-   Journal of Animal Ecology (IF = 5)\
-   Food webs (IF = 2.3)

## Q4: Plot the graphs for a case when the ADBM’s best prediction is the true one

Here, we consider a case where the observed (true) food web is assumed to be the best food web simulated using the ADBM. The minimum number of gut content data to achieve 95% of the maximum TSS for the ADBM's best prediction case is higher than that for the empirical case (Fig. 6).

```{r, echo=FALSE, fig.align='center', out.width="500px", fig.cap=" "}

knitr::include_graphics("fig_2021_10_15/plot_TSS_vs_ngut_ADBM_obs.png")
```

### 2021-11-15 manuscript/ms_C2/ms_C1.tex
All files
files

\documentclass{article}

\usepackage{arxiv}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{lmodern}        % https://github.com/rstudio/rticles/issues/343
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}
\usepackage{graphicx}

\title{Simultaneously estimating food web complexity and structure with
uncertainty}

\author{
    Anubhav Gupta
    \thanks{Corresponding author}
   \\
    Department of Evolutionary Biology and Environmental Studies \\
    University of Zurich \\
  8057 Zurich, Switzerland \\
  \texttt{\href{mailto:anubhav.gupta@ieu.uzh.ch}{\nolinkurl{anubhav.gupta@ieu.uzh.ch}}} \\
   \And
    Owen L. Petchey
   \\
    Department of Evolutionary Biology and Environmental Studies \\
    University of Zurich \\
  8057 Zurich, Switzerland \\
  \texttt{\href{mailto:owen.petchey@ieu.uzh.ch}{\nolinkurl{owen.petchey@ieu.uzh.ch}}} \\
  }

% Pandoc citation processing

\usepackage{lineno}
\linenumbers
\usepackage {amsmath}
\setlength\parindent{24pt}
\usepackage{setspace}\doublespacing
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}

\begin{document}
\maketitle

\def\tightlist{}

\begin{abstract}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Food web models explain and predict the trophic interactions in a food
  web, and they can infer missing interactions among the organisms. The
  allometric diet breadth model (ADBM) is a food web model based on the
  foraging theory. In the ADBM the foraging parameters are
  allometrically scaled to body sizes of predators and prey. In Petchey
  et al. (2008), the parameterisation of the ADBM had two limitations:
  (a) the model parameters were point estimates, and (b) food web
  connectance was not estimated.
\item
  The novelty of our current approach is: (a) we consider multiple
  predictions from the ADBM by parameterising it with approximate
  Bayesian computation, to estimate parameter distributions and not
  point estimates. (b) Connectance emerges from the parameterisation, by
  measuring model fit using the true skill statistic, which takes into
  account prediction of both the presences and absences of links.
\item
  We fit the ADBM using approximate Bayesian computation to 16 observed
  food webs from a wide variety of ecosystems. Connectance was
  consistently overestimated in the new parameterisation method. In some
  of the food webs, considerable variation in estimated parameter
  distributions occurred, and resulted in considerable variation
  (i.e.~uncertainty) in predicted food web structure.
\item
  We conclude that the observed food web data is likely missing some
  trophic links that do actually occur, and that the ADBM likely
  predicts some links that do not exist. The latter could be addressed
  by accounting in the ADBM for additional traits other than body size.
  Further work could also address the significance of uncertainty in
  parameter estimates for predicted food web responses to environmental
  change.
\end{enumerate}
\end{abstract}

\keywords{
    connectance
   \and
    ABC
   \and
    ADBM
   \and
    food web
   \and
    true skill statistic
   \and
    uncertainty
  }

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Knowledge about the trophic interactions among the organisms in a
community is crucial for understanding the structure and dynamics of
ecological communities and for predicting their response to
environmental change (Dunne, Williams, and Martinez 2002; Tylianakis and
Binzer 2014; O'Connor et al. 2009; Bergamino, Lercari, and Defeo 2011;
Krause et al. 2003; Lurgi, L\a'opez, and Montoya 2012; Morris, Sinclair,
and Burwell 2015). The network of trophic interactions is often referred
to as a food web. The food web structure can provide answers to key
ecological questions: which species are more vulnerable to environmental
changes such as temperature (Petchey et al. 1999); how robust a food web
is to extinctions (Dunne, Williams, and Martinez 2002); and how a food
web reacts if the top predators are removed (Knight et al. 2005)?

Trophic interactions information from multiple sources can be used to
infer a food web, e.g.~gut contents (Peralta-Maraver,
L\a'opez-Rodríguez, and de Figueroa 2017), stable isotope composition of
tissues (Layman et al. 2007), and experimentation (Warren 1989).
Sometimes the methods used to infer the interactions may lead to
uncertainty in the constructed food web. E.g. In gut content analysis of
some fish predators, there can be tissues which are not identifiable and
cannot be assigned with certainty to a specific prey item (Baker,
Buckland, and Sheaves 2014). With stable isotope ratios of tissues,
uncertainty may be due to factors such as variability in the isotopic
fractionation values across multiple combinations of diets and
tissues/species, unquantified temporal or spatial variation in prey
isotopic values, and variation caused by routing of particular dietary
nutrients into particular tissues (Crawford, Mcdonald, and Bearhop
2008). Furthermore, complete recording of all interactions usually
requires a large sampling effort even at small spatial and temporal
scales (Hobson, Piatt, and Pitocchelli 1994). Food web structure is very
difficult to record at larger spatial and temporal scales without losing
resolution (spatial, temporal, and taxonomic) (Gravel et al. 2013;
Martinez 1991; Jord\a'an and Osv\a'ath 2009). Less than complete
sampling of interactions can result in no interaction being observed
between a pair of individuals that in fact do interact, which results in
missing links in a food web. Due to under-sampling, food webs can be
poorly understood, which may hinder further advances in the field
(Martinez et al. 1999).

When interactions are difficult to observe, and hence well-documented
food webs are not available, models which predict species interactions
may provide a solution (Tamaddoni-Nezhad et al. 2013; Gravel et al.
2013; Petchey et al. 2008; Allesina, Alonso, and Pascual 2008; Cohen,
Newman, and Steele 1985). A food web model can be used to predict
missing information about species interactions. For example, Petchey et
al. (2008) showed how a model of species interactions (and therefore
food web structure) could be parameterised from data on the known
presence and absence of trophic interactions. The model and its
parameter values encode the rules for occurrence or absence of species
interactions to predict food web structure. Observed data may be used to
select and parameterise the model. Tamaddoni-Nezhad et al. (2013) used
large agricultural datasets, logic-based machine learning and text
mining to assign interactions between nodes to automatically construct
food webs. Gravel et al. (2013), inspired by the niche model of food web
structure developed a method that used the statistical relationship
between predator and prey body size to infer the food web.

Food web models are also useful for ecological forecasting. Lindegren et
al. (2010) used a stochastic food web model driven by regional climate
scenarios to produce quantitative forecasts of cod dynamics in the
twenty-first century. Hattab et al. (2016) forecasted the potential
impacts of climate change on the local food web structure of the highly
threatened Gulf of Gabes ecosystem, located in the south of the
Mediterranean Sea. Hence, food web models have an important role in
filling gaps in knowledge about species interactions, including
predicting future changes in food web structure.

The allometric diet breadth model (ADBM) was the first model able to
predict food web complexity and structure (Beckerman, Petchey, and
Warren 2006; Petchey et al. 2008). The ADBM uses foraging theory,
specifically the contingency model (MacArthur and Pianka 1966), to
predict which set of the available prey species would be consumed by a
predator. This set is the prey species that maximises the energy intake
rate of the predator. The model requires the foraging related traits of
species, such as energy content of a potential prey item, the rate of
space clearance (also known as attack rate), the density of prey items,
and handling time (the amount of time required to handle food items).
The model is termed ``allometric'' because each of these quantities is
derived from the body size of the prey and predator using several
allometric relationships. The ADBM has also been used to investigate the
effect of temperature on an observed food web structure (O'Gorman et al.
2019).

The ADBM had variable success in explaining the structure of 15
different food webs, with the proportion of links correctly predicted
ranging from 5 \% to 65 \% (Table \ref{fig:tab_1}). The ADBM correctly
predicted 65\% of the presence of links in the Coachella valley food
web. The poorest prediction of presence of links was for the Grasslands
food web with only 7\% of the presence of links correctly predicted.
When trophic interactions were more strongly dependent on size, the
model correctly predicted a greater proportion of links. Indeed,
constructing a food web based only on body size (i.e.~ignoring taxonomy)
resulted in almost twice the number of correctly predicted links,
i.e.~83\%, in contrast to taxonomy (Woodward et al. 2010).

Although Petchey et al. (2008) demonstrated that foraging theory could
predict food web structure, their implementation of the ADBM included at
least two limitations. The parameterisation method provided estimates of
the parameters with no uncertainty: a single set of parameter values
that maximised the explanatory power was selected. In other words, the
parameterisation method led to point estimates of the parameters that
predicted a single food web structure (because the ADBM is purely
deterministic). Moreover, the best predicted food web was not exactly
the same as the observed one. In a sense then, the parameterisation
method used in Petchey et al. (2008) was akin to estimating the
intercept and slope of a regression line, but not any uncertainty in
those parameters. Given that uncertainty is an essential dimension in
ecological models, and in predictions about the future state of
ecological communities (Petchey et al. 2015; Carpenter 2016), this is an
important limitation.

The second limitation was in the estimation of the connectance of the
food web, which is the number of realised trophic links divided by the
total number of possible trophic links. Although the ADBM can in
principle predict connectance, Petchey et al. (2008) prevented the model
from doing so. They set the value of relevant parameters in the model to
instead ensure the predicted connectance was equal to the observed
connectance. The ADBM was not therefore used to simultaneously predict
complexity and structure of food webs. Moreover, fixing predicted
connectance to be equal to observed connectance does not account for the
possibility that the observed connectance was imperfectly measured.
Indeed, if low effort was used to observe the trophic links in a
community, the observed connectance are likely to be lower than if all
trophic links were observed. Connectance is an important driver for the
stability and dynamics of a food web (May 1972) and most of the
structural properties of food webs co-vary with connectance (Dunne,
Williams, and Martinez 2002; Poisot and Gravel 2014), thus this
limitation must be addressed.

In this article we report on how we address these limitations. We
removed the first limitation by applying approximate Bayesian
computation (ABC). The approach originated in population genetics and
has been used in a wide range of research fields: systems biology (Toni
et al. 2009), ecology (Jabot and Chave 2009), epidemiology (Shriner et
al. 2006) and ecological networks (Ibanez 2012; Poisot and Stouffer
2016). One of the advantages of ABC is that it does not require a
likelihood function. As ADBM is a complex deterministic model where the
likelihood can not be explicitly evaluated, ABC is a good choice of
parameterisation.

We addressed the second limitation by allowing estimation of number of
links as well as arrangement of links. To accomplish this, we measured
model fit by using the true skill statistic, which takes into account
both the number of presences and absences of links correctly predicted.
High values of the true skill statistic occurs when both the predicted
arrangement of links and the predicted number of links are close to the
observed arrangement and number of links, respectively.

\newgeometry{margin=1cm}
\begin{landscape}\begin{table}

\caption{\label{tab:unnamed-chunk-1}\label{fig:tab_1}Information about the food webs predicted using the ADBM.}
\centering
\resizebox{\linewidth}{!}{
\fontsize{7}{9}\selectfont
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}|>{\raggedright\arraybackslash}p{8em}|l|l|l|l|>{\raggedright\arraybackslash}p{8em}|>{\raggedright\arraybackslash}p{8em}|>{\raggedright\arraybackslash}p{8em}}
\hline
Common food web name & Predation matrix source & Body size source & General ecosystem & Number of species & Connectance & Body size range (approximate) & Proportion of presence of links correct & Type of interactions\\
\hline
Benguela Pelagic & (Yodzis 1998) & (Yodzis 1998) & Marine & 29 & 0.23 & $10^{-8}$ to $10^6$ & 0.57 & Predation\\
\hline
Broadstone Stream (taxonomic aggregation) & (Woodward and Hildrew 2001; Woodward
et al. 2005) & (Brose et al. 2005) & Freshwater & 29 & 0.19 & $10^{-6}$ to $10^{-2}$ & 0.62 & Predation\\
\hline
Broom & Memmott et al. 2000) & (Brose et al. 2005) & Terrestrial & 68 & 0.02 & $10^{-6}$ to $10^0$ & 0.08 & Herbivory, Parasitism, Predation, Pathogenic\\
\hline
Capinteria & (Lafferty et al. 2006) & (Reide, unpublished) & Marine (Salt Marsh) & 72 & 0.05 & $10^{-14}$ to $10^5$ & 0.16 & Predator-parasite, Parasite-parasite\\
\hline
Caricaie Lakes & (Cattin et al. 2004) & (Brose et al. 2005) & Freshwater & 158 & 0.05 & $10^{-5}$ to $10^5$ & 0.13 & Predation, Parasitism\\
\hline
Coachella Valley & (Polis 1991) & (Reide, unpublished) & Terrestrial (Desert) & 26 & 0.34 & $10^{-8}$ to $10^4$ & 0.65 & Herbivory, Predation\\
\hline
EcoWEB41 & (Cohen 1989) & (Jonsson 1998) & Marine & 19 & 0.14 & $10^{-11}$ to $10^6$ & 0.47 & Predation\\
\hline
EcoWEB60 & (Cohen 1989) & (Jonsson 1998) & Terrestrial & 33 & 0.06 & $10^{-5}$ to $10^6$ & 0.24 & Predation, Parasitism, Herbivory\\
\hline
Grasslands & (Dawah et al. 1995) & (Brose et al. 2005) & Terrestrial & 65 & 0.03 & $10^{-3}$ to $10^{-2}$ & 0.07 & Herbivory, Parasitism\\
\hline
Mill Stream & (Ledger, Edwards, Woodward unpublished) & (Brose et al. 2005) & Freshwater & 80 & 0.06 & $10^{-6}$ to $10^{-1}$ & 0.37 & Herbivory, Predation\\
\hline
Sierra Lakes & (Harper-Smith et al. 2005) & (Brose et al. 2005) & Freshwater & 33 & 0.16 & $10^{-4}$ to $10^0$ & 0.60 & Predation\\
\hline
Skipwith Pond & (Warren 1989) & (Brose et al. 2005) & Freshwater & 71 & 0.07 & $10^{-4}$ to $10^{-1}$ & 0.14 & Predation\\
\hline
Small Reef & (Opitz 1996) & (Reide unpublished) & Marine (Reef) & 50 & 0.22 & $10^{-11}$ to $10^5$ & 0.41 & Predation, Herbivory\\
\hline
Tuesday Lake & (Jonsson et al. 2005) & (Brose et al. 2005) & Freshwater & 73 & 0.08 & $10^{-11}$ to $10^3$ & 0.46 & Predation\\
\hline
Ythan & (Emmerson and Raffaelli 2004) & (Emmerson and Raffaelli 2004) & Marine (Estuarine) & 88 & 0.05 & $10^{-12}$ to $10^0$ & 0.22 & Predation\\
\hline
Broadstone Stream (size aggregation) & (Woodward
et al. 2010) & (Woodward
et al. 2010) & Freshwater & 29 & 0.24 & $10^{-7}$ to $10^2$ & 0.83 & Predation\\
\hline
\end{tabular}}
\end{table}
\end{landscape}
\restoregeometry

\hypertarget{materials-and-methods}{%
\section{Materials and Methods}\label{materials-and-methods}}

In the upcoming sections, we present a detailed account of the
application of ABC to parameterise the ADBM, the description of the ADBM
and of the food web data we used. We explain the rejection Monte Carlo
ABC method in the main text, and Markov chain Monte Carlo ABC and
sequential Monte Carlo ABC methods in the Supplementary information
(hereafter SI) Section S1 (hereafter SI-S1). We computed an accuracy
measure known as true skill statistic to assess the ADBM's predictions
and calculated different food web properties to compare these
predictions across food webs.

\hypertarget{allometric-diet-breadth-model-adbm}{%
\subsection{Allometric Diet Breadth Model
(ADBM)}\label{allometric-diet-breadth-model-adbm}}

The allometric diet breadth model (ADBM) is based on optimal foraging
theory, specifically the contingency foraging model (MacArthur and
Pianka 1966). The ADBM predicts the set of prey species a consumer
should feed upon to maximise its rate of energy intake (Petchey et al.
2008) (hereafter referred as PBRW study). The species in this set are
assumed to have the trophic link with the predator. To make these
predictions, the model assumes that a foraging predator is in one of two
exclusive states: searching for prey or handling a prey item. The model
requires four variables for each potential predator-prey interaction:

\begin{itemize}
\tightlist
\item
  The energy content of the resources \(E_i\) (only prey \(i\) specific)
  (energy).
\item
  The handling times \(H_{ij}\), which is the time not spent searching
  caused by consuming a prey item (prey \(i\) and predator \(j\)
  specific) (time).
\item
  The space clearance rates \(A_{ij}\) (also known as the attack rate;
  prey \(i\) and predator \(j\) specific) (area or volume per time).
\item
  The prey densities \(N_i\) (only prey \(i\) specific) (individuals per
  area or volume).
\end{itemize}

The term ``Allometric'' in the ADBM refers to the use of four allometric
relationships, one for each of these four variables, including the body
size of the predator \(M_j\) and prey \(M_i\) (Table \ref{fig:tab_2}).
With these four allometric relationships, and the body size of each of
the species in a community, we can predict the four variables (energy,
handling time, space clearance rate, and prey density), and then use the
contingency foraging model to predict diets.

Each of the four allometric equations has parameters: a constant and/or
at least one exponent (Table \ref{fig:tab_2}). It is the value of some
of these parameters that can be estimated to have the predicted food web
structure match (as closely as possible) the structure of an observed
food web. This is akin to choosing values of slope and intercept of a
linear regression that maximises the fit of the regression line to the
observed data.

Because some of the allometric constants and exponents are known, and
because others are redundant with respect to each other (see Table
\ref{fig:tab_2} for details), we estimate only the following parameters:
\(a\), \(a_i\), \(a_j\) and \(b\) in the model (Table \ref{fig:tab_2}).

\begin{table}

\caption{\label{tab:unnamed-chunk-2}\label{fig:tab_2}Traits with their allometric function and corresponding parameters in ADBM.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{l|l|l|l}
\hline
Traits (Unit) & Allometric function & Parameters & Comments\\
\hline
Energy $(Joules)$ & $E_i = eM_i$ & $e$ & Arbitrary. No effect on structure\\
\hline
Abundance $(\text{individual}/m^2 \text{ or } \text{individual}/m^3)$ & $N_i = nM_i^{n_i}$ & $n$ & Connectance affected by the product $nah^*$\\
\hline
 &  & $n_i$ & Assumed value of $\frac{-3}{4}$ based on empirical data\\
\hline
Space Clearance Rate $(m^2/s \text{ or }  m^3/s)$ & $A_{ij} = aM_i^{a_i}M_j^{a_j}$ & $a$ & Connectance affected by the product $nah^*$;\\
\hline
 &  &  & Estimated using ABC\\
\hline
 &  & $a_i$ & Estimated using ABC\\
\hline
 &  & $a_j$ & Estimated using ABC\\
\hline
Handling time $(s)$ & $H_{ij} = \frac{h}{b-\frac{M_i}{M_j}} \text{ if } \frac{M_i}{M_j} < b$ & $h$ & Connectance affected by the product $nah^*$\\
\hline
 & $H_{ij} = \infty \text{ if } \frac{M_i}{M_j} \geq b$ & $b$ & Estimated using ABC\\
\hline
\end{tabular}}
\end{table}

\hypertarget{observed-food-web-data}{%
\subsection{Observed food web data}\label{observed-food-web-data}}

The observed food webs that we fit the ADBM to belong to marine,
freshwater and terrestrial ecosystems (Table \ref{fig:tab_1}). The
observed connectance of these food webs is from 0.02 to 0.34 and there
are 19 to 158 species. The food webs contain primary producers,
herbivores, carnivores, parasites, and parasitoids. They also contain
various types of feeding interactions, including predation, herbivory,
bacterivory, parasitism, pathogenic, and parasitoid.

The goodness of fit of the ADBM's predictions depends on the types of
interactions in the food webs in the PBRW study. Because some of the
interactions are more size structured than other interactions.
Predacious and aquatic herbivore interactions were predicted better than
parasitoid and herbivory ones (PBRW study). Moreover, the ADBM's
predictions improve when the species (taxonomic) are replaced by size
classes (ignoring taxonomy) (Woodward et al. 2010).

All food webs with one exception (Broadstone Stream) was available only
at the species level, i.e.~with information about interactions between
species and the body size of species. We use the term ``species'' in
this study to indicate a ``node'' in a food web in which nodes are
connected by trophic interactions, and nodes are a collection of
individuals that share links. These species/nodes are not always
taxonomic species, but can be broader taxonomic ranks.

In contrast, the Broadstone Stream food web data contained interactions
between individuals and the individual body sizes. Thus, the Broadstone
Stream food web can be constructed by aggregating by either taxonomy or
size (Woodward et al. 2010). The ADBM can predict the food web
irrespective of the aggregation method, and aggregation by size,
ignoring taxonomy led to higher explanatory power i.e.~the match between
observed and predicted food web structure was higher. With aggregation
by size, 83\% of the links were correctly predicted than with taxonomic
aggregation where 40\% of links were correctly predicted (Woodward et
al. 2010).

\hypertarget{parameter-estimation-approximate-bayesian-computation}{%
\subsection{Parameter estimation: Approximate Bayesian
Computation}\label{parameter-estimation-approximate-bayesian-computation}}

We used approximate Bayesian computation (ABC) to identify sets of
parameter values that resulted in predicted food webs that were close in
structure to the observed food web. ABC is an approach that does not
require a likelihood function. Instead, there is a distance function
that measures the distance between a model's prediction and the observed
data. The approximation of the likelihood depends on the ABC method
used, which is further discussed below and SI. The model parameter
values are sampled from a prior distribution. The accepted parameter
values form an approximate posterior distribution for the model
parameter. We implemented three ABC methods to parameterise the ADBM:
namely rejection Monte Carlo (Fig. \ref{fig:fig_m1}), Markov chain Monte
Carlo, and sequential Monte Carlo. The three methods produced very
similar results (SI Figs S33-S34) and we therefore only include the
simplest (rejection) in this main text.

\begin{figure}

{\centering \includegraphics[width=400px]{../fig/schematic}

}

\caption{\label{fig:fig_m1} Flowchart of rejection approximate Bayesian computation method implemented to parameterise the ADBM.}\label{fig:unnamed-chunk-3}
\end{figure}

\hypertarget{prior-distribution}{%
\subsubsection{Prior distribution}\label{prior-distribution}}

The prior distributions for \(a_i\) and \(a_j\) were chosen to be
uniform distributions. The range of distribution was from -1.5 to 1.5
and 0 to 3 for \(a_i\) and \(a_j\) respectively, informed by the
estimates in Rall et al. (2012). However, we chose a prior range
specific to food webs for the parameter \(b\) because body size varies
greatly among the species in the observed food webs. For example: in the
Benguela Pelagic food web, the body sizes of species range from the
order of \(10^{-8}\) gm to \(10^5\) gm. Hence, the range of
prey-predator ratio was from the order of \(10^{-14}\) to \(10^{14}\).
To take this into account, we took the prior of \(log_{10}(b)\) from a
uniform distribution ranging from \(-15\) to \(15\). In the case of
parameter \(a\), we chose the prior of \(log_{10}(a)\) to be a uniform
distribution. However, the prior range varied between food webs. For
example, the prior range for Benguela Pelagic was chosen to be -12 to
10. The method for choosing the specific range of the prior distribution
of the \(a\) parameter is detailed in SI-S4.

\hypertarget{comparison-of-observed-and-predicted}{%
\subsubsection{Comparison of observed and
predicted}\label{comparison-of-observed-and-predicted}}

The difference between the model's prediction and the observed data
(e.g.~the sum of squared residuals is such a distance in linear
regression) is quantified by a distance measure. The distance is lower
when there is a closer match between the model's prediction and the
observation. A perfect match would result in zero distance.

The magnitude of the distance is used for the acceptance or rejection of
a set of parameter values. An accepted set of parameter values
contributes to the posterior distribution, rejected ones do not. This
makes the distance measure one of the important features of ABC. A
threshold distance is chosen, and if the distance for a particular set
of parameter values is less than the threshold, then that set of
parameter values contributes to the posterior distribution. When the
distance is greater than the threshold, the parameter values do not
contribute to the posterior. Hence, the magnitude of the distance
threshold determines the proportion of a model's parameters that are
accepted. A higher threshold causes a high proportion of acceptances but
less accuracy with the acceptance of some parameter sets that result in
predictions quite unlike the observed data. Below, we first describe and
justify our choice of distance measure, and then our choice of
threshold.

In the PBRW study the measure of distance was equivalent to
\(1 - a / (a + c)\), where \(a\) is the number of observed links that
were predicted (the number of true positives) and \(c\) is the number of
observed links that were not predicted (the number of false negatives).
A distance of 0 indicates that all observed links were correctly
predicted. One way for the ADBM to achieve this is to predict that every
species has a trophic link with every other species including itself --
a fully connected food web with connectance of 1. The PBRW study
prevented this by constraining the number of predicted links to be equal
to the number of observed links, i.e.~the model connectance was fixed to
be the same as the observed connectance. In this study, we relaxed this
constraint, with the number of links as well as the arrangement of links
being estimated. The first step was to choose an appropriate distance
measure.

The distance measure used in this study is 1 minus the true skill
statistic: \(\text{distance} = 1 - \text{TSS}\). This distance ranges
from 0 to 2.

TSS is defined as:

\[ \text{TSS} = \frac{ad-bc}{(a+c)(b+d)} \] where \(a\) is the number of
observed links that are predicted by the model (true positives), \(d\)
is the number of observed absences of links that are correctly predicted
(true negatives), \(b\) is the number of false positives, and \(c\) is
the number of false negatives.

The \(TSS\) ranges from \(-1\) to \(1\), where +1 indicates a perfect
prediction. A \(TSS\) value of zero or less indicates a performance no
better than random.

The inclusion of true and false negatives in the distance measure means
that the best theoretically possible prediction (smallest distance) is a
unique prediction, and specifically the one in which the predicted
presence and absence of links matches exactly with the observed presence
and absence of links.

Food web dynamics and stability are strongly dependent on connectance
(May 1972), we therefore set the distance threshold (for acceptance)
such that the model had a reasonable chance of predicting the observed
value of connectance.

To do this, we examined how the predicted connectance varied with the
distance threshold. An example of this relationship is given in Fig.
\ref{fig:fig_m2} for the Benguela Pelagic food web. We chose the minimum
threshold value that gave a range of predicted connectance containing
the observed connectance.

Furthermore, it is useful to note that in Fig. \ref{fig:fig_m2} there
are no connectance values below a distance threshold value of less than
0.5 because for this particular food web there were no sets of parameter
values that achieved a better model fit than is indicated by
\(1-TSS = 0.5\). I.e. it is impossible for the ADBM to make better
predictions than this. One reason for this is that the ADBM, when body
size is the only trait, can only predict contiguous diets in trait
space, whereas the observed data contains gaps in the diet.

\begin{figure}[h]

{\centering \includegraphics[width=200px]{../fig/Benguela_Pelagic_connectanceCI_vs_tol}

}

\caption{\label{fig:fig_m2}The prediction interval of the predicted connectance increases with increasing distance threshold for the Benguela Pelagic food web. The green line and black line represent the observed connectance and mean of predicted connectance respectively.}\label{fig:unnamed-chunk-4}
\end{figure}

\hypertarget{the-rejection-abc-method}{%
\subsubsection{The Rejection ABC
method}\label{the-rejection-abc-method}}

In the rejection ABC method, a set of parameter values are sampled from
the prior distributions. This set of parameter values is either
accepted, and thereby added to the posterior distribution of the
parameter values, or it is rejected (based on if the distance 1 -
\(TSS\) is less than or greater than the threshold distance, as
mentioned above). This process is repeated until there are enough
acceptances to give stable (approximate) posterior distributions. In
addition, we used a kernel function that assigns weight to each set of
parameter values, where the weight is inversely proportional to the
distance (1 - \(TSS\)).

In the upcoming section, we further detail the rejection ABC method.

\emph{Properties:}

\begin{itemize}
\item
  A prior distribution \(\pi(\theta)\): \(\pi\) is the uniform
  distribution for parameters \(\theta = (a, a_i, a_j, b)\)
\item
  A model prediction \(model(\theta)\): ADBM\((\theta)\). This is a
  predicted food web, \(x_i\), given by a particular set of parameter
  values \(\theta_i\). Hence, \(x_i = ADBM(\theta_i)\)
\item
  A summary statistic \(s(x)\): \(x\) is the predation matrix predicted
  by the ADBM.
\item
  \(\begin{aligned} \text{A kernel function } K(u): \text{ epanechnikov } K(u) &= \frac{3}{4}(1-\frac{u}{tol}) \text{ if } u \leq tol \\ &= 0 \text{ otherwise} \end{aligned}\)
\end{itemize}

where \(tol\) is the distance threshold

\begin{itemize}
\item
  A distance function \(d(x_i,y)\): \(d(x_i,y) = 1 - TSS(x_i,y)\)
\item
  An observed food web \(y\), in the form of a predation matrix
  containing zeros and ones.
\end{itemize}

\emph{Sampling:}

for \(i = 1 \dots n = 1000\)

\begin{itemize}
\item
  Draw a set of parameter values \(\theta_i\) from the prior
  distribution \(\pi(\theta)\).
\item
  Compute the model result \(x_i = model(\theta_i)\)
\item
  Compute \(s(x_i)\) and \(d(s(x_i), s(y))\)
\item
  Accept or reject the parameter set probabilistically:

  \begin{itemize}
  \item
    Assign a probability \(p_i\) to \(\theta_i\) as per the kernel
    \(K\); \(p = K(d)\), where \(d\) is the distance evaluated in the
    previous step.
  \item
    Compute \(\alpha \sim U(0,1)\)
  \item
    If \(p_i \leq \alpha\), then accept \(\theta_i\) and \(i = i + 1\)
  \end{itemize}
\end{itemize}

\emph{Output:}

An approximate joint posterior distribution using the accepted
\(\theta_1, \dots, \theta_n\).

\hypertarget{assessment-of-model-fit}{%
\subsection{Assessment of model fit}\label{assessment-of-model-fit}}

Accuracy is how close the model prediction is to the observation. The
ADBM's prediction is a predation matrix that consists of the presence
and absence of links thus comparing how close the prediction is to the
observation is not straightforward as comparing two numerical values. We
defined the accuracy of the ADBM using true skill statistics to take
into account the true and false predictions of both the presence and
absence of links, which is defined above.

We examined how closely structural properties of the predicted food web
matched those of the observed food webs. We evaluated properties such as
proportion of basal species, proportion of intermediate species,
proportion of top species, proportion of herbivores, mean omnivory,
clustering coefficient, standard deviation of generality, standard
deviation of vulnerability, diet similarity, mean path length and
nestedness. We did not compute mean trophic level and maximum trophic
level because their computation did not converge in the R \emph{cheddar}
package (Hudson et al. 2013) for all the food webs.

We investigated the performance of the ADBM parameterised with the ABC
by computing standardised error of the food web properties, where the
standardised error is the absolute raw error (the difference between
observed and predicted value) divided by the maximum absolute raw error
for that property. We did not calculate the standardised error for mean
omnivory and mean path length because it had some NA values and infinite
values for all the food webs respectively.

\hypertarget{results}{%
\section{Results}\label{results}}

As an example of the model outcomes, we first present the results for
the Benguela food web (e.g.~predicted food web structure, variation in
predicted food web structure, and posterior parameter distributions). We
chose this food web as it was well explained using the method of Petchey
et al (2008) (hereafter referred as PBRW study). The results of the
other food webs are included in the SI Figs S1-S32. We then compare
model outcomes across all empirical food webs between the PBRW study and
our current work. We compare the true skill statistic of the two
approaches and compare some food web properties, such as proportions of
basal, intermediate, and top species.

The true skill statistic (TSS) of the predicted Benguela Pelagic food
web varied between 0.4 and 0.52. This variation in the TSS is
represented in terms of predation matrices displayed in Fig.
\ref{fig:fig_r1}(a), which overlays 1000 independent predation matrices
created from the posterior parameter distributions. In all the 1000
independent predation matrices, the predicted links are mostly present
in the upper triangular portion of the matrix where most of the observed
links are also present. Links in the upper right triangle of the
predation matrix are for predators feeding on prey smaller than
themselves.

In the 1000 predicted predation matrices, there predators are sometimes
smaller than their predicted prey, the links in the lower left triangle
of the predation matrix. This is also portrayed in the marginal
distribution of \(log_{10}(b)\) in Fig. \ref{fig:fig_r3}(d), as it
includes values greater than \(b=2\) (\(log_{10}(b)=0.3\)). This is
relevant as values of \(b=2\) make the most profitable prey item equal
in size to the predator size. Lower values of \(b\) make the most
profitable prey item smaller than the size of the predator.

There were around 250 potential links in the lower left triangle of the
predation matrix that were never predicted in any of the 1000 predicted
predation matrix (Fig. \ref{fig:fig_r1}(b)). This strongly suggests that
the predator-prey size ratio of these links is so small (i.e.~very large
prey, very small predator) that the links cannot occur, given that the
preponderance of observed links are predators consuming prey smaller
than themselves.

\begin{figure}

{\centering \includegraphics[width=300px]{../fig/Benguela_Pelagic_pred_mat}

}

\caption{\label{fig:fig_r1} (a) Observed and predicted predation matrices for Benguela Pelagic food web. Body size increases from left to right and top to bottom along the predation matrix. Black circles show where there is an observed trophic link. The intensity of the pink circles shows the proportion of 1000 predicted food webs that had a trophic link between the corresponding species. This type of overlay is shown for two examples predicted in panel (c). (b) The histogram of the number of times a link was predicted across 1000 independently predicted food webs. There were 841 species pairs in this food web. About 150 of these were predicted to have a trophic link in all 1000 predicted predation matrices. The red bar shows the number of pairs of species for which a trophic link was never predicted. (c) Two predicted predation matrices for Benguela Pelagic food web corresponding to the minimum and the maximum value of estimated $b$, and their sum.}\label{fig:unnamed-chunk-5}
\end{figure}

The marginal posterior of parameter \(b\) in the Benguela Pelagic food
web was more constrained than the marginal posterior distribution of the
other three allometric parameters (Fig. \ref{fig:fig_r3}) as the
posterior range was the narrowest.

\begin{figure}

{\centering \includegraphics[width=300px]{../fig/Benguela_Pelagic_distribution}

}

\caption{\label{fig:fig_r3} Marginal prior and marginal posterior distribution of the ADBM parameters for the Benguela Pelagic food web estimated using rejection ABC.}\label{fig:unnamed-chunk-6}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=500px]{../fig/ABC_vs_point_estimates}

}

\caption{\label{fig:fig_r2} TSS (a), connectance (b) and ADBM parameters (c, d, e, f) computed using the ABC method compared with the corresponding point estimates from Petchey et al (2008). The red lines are the 95\% credible/prediction intervals and the black filled circles represent the corresponding means. The grey region represents the intervals of the prior distributions for $a_i$ and $a_j$. The grey lines represent the prior range of the parameters $a$ and $b$ in the $log_{10}$ scale. The prior range for the parameter $b$ extends above and below the y-axis limits for some food webs and so the values of the limits are shown on the plot. The dashed black lines are the 1:1 relationships for reference.}\label{fig:unnamed-chunk-7}
\end{figure}

The mean true skill statistic using the ABC approach was higher than the
point estimates from the PBRW study (Fig. \ref{fig:fig_r2}(a)) across
all food webs except one. Our present approach led to estimates of
connectance greater than the values of connectance of the PBRW study,
which were fixed to equal the observed values of connectance.

We did not find a consistent relationship between the parameters
estimated using the current approach and those estimated in the PBRW
study (Fig. \ref{fig:fig_r2}(c-f)), except for in the case of parameter
\(b\). The mean using the ABC approach was always higher than the
estimates from the PBRW study (Fig. \ref{fig:fig_r2}(f)) and the 95\%
credible interval of the posterior of \(b\) includes the estimate from
the PBRW study.

The marginal posterior of parameter \(b\) was more constrained than the
other three allometric parameters, i.e.~the posterior range was the
narrowest (SI Figs S17-S32). In most of the food webs, the parameter
\(b\) had a unimodal distribution (SI Figs S17-S32). EcoWEB60 and
Grasslands had a bimodal distribution and Sierra Lakes had three modes.

The structural food web properties proportion of intermediate species,
mean omnivory, clustering coefficient, sd of generality, sd of
vulnerability, diet similarity and nestedness estimated from the current
ABC approach were generally higher than the PBRW study (SI Fig. S36(b,
e-j)). The properties proportion of basal species, proportion of top
species, and proportion of herbivores were generally lower (SI Fig.
S36(a, c, d)).

The real values of the proportion of intermediate species, mean
omnivory, clustering coefficient, sd of generality, sd of vulnerability
and nestedness, were mostly within the lower range of the predicted 95\%
interval. The proportion of basal species, proportion of top species,
proportion of herbivores were underestimated in comparison to the real
values for most of the food webs.

The ADBM, when parameterised with the ABC, generally better predicted
the structural food web properties, such as proportion of basal species
when the true skill statistics was higher (Fig. \ref{fig:fig_r5}(a))
across the 16 food webs. However, the ABC parameterised ADBM less
accurately predicted food web properties on average than in the PBRW
study (Fig. \ref{fig:fig_r5}(b)).

\begin{figure}

{\centering \includegraphics[width=300px]{../../manuscript/fig/fig7}

}

\caption{\label{fig:fig_r5} (a) The mean standardised error of the food web properties predicted from the ADBM parameterised using rejection ABC plotted against the mean true skill statistic for each food webs. The vertical and horizontal bars correspond to 95\% prediction intervals of the standardised error and true skill statistic respectively. Solid blue line is linear regression through the means (t = -2.44, df = 14, P = 0.028). (b) The mean standardised error computed from the ABC method plotted against the mean standardised error from Petchey et al. (2008). The dashed line is the 1:1 relationship for reference.}\label{fig:unnamed-chunk-8}
\end{figure}

Within each food web, we found various relationships between the
standardised error and true skill statistic (SI Figs S37 and S38). E.g.
For Skipwith Pond food web (SI Fig. S37(l)), high values of TSS were
associated with high error, whereas the opposite was true for other food
webs, such as Broadstone Stream (SI Fig. S37(b, p)). The other food webs
showed more complex relationships.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

The ABC parameterisation method employed here improves on the basic
parameterisation methods applied in Petchey et al. (2008) (PBRW). The
ABC method provides uncertainty in parameter estimates, and thereby a
range of predicted food webs (Fig. \ref{fig:fig_r2}(c-f)). It also
allowed us to estimate parameters that were fixed by the PBRW study, and
thereby also predicts connectance (Fig. \ref{fig:fig_r2}(b)). Including
uncertainty and predicting connectance are significant advances in ADBM.
They allow predictions in changes of food web structure caused by
environmental changes that include uncertainty in the predicted food web
structure and including uncertainty in such predictions is critical
(Petchey et al. 2015; Cressie et al. 2009; Lindegren et al. 2010). A
future development will be to partition the contribution of different
sources of uncertainty such as incomplete sampling and model
deficiencies to make improvements in the model with the aim of reducing
uncertainty. Future research should investigate the functional and
dynamical significance of the uncertainty in the predicted food web
structure. Below we discuss some of the results of our study, and expand
on these opportunities and priorities for future research.

In all cases, the predicted connectance was greater than the observed
connectance (Fig. \ref{fig:fig_r2}(b)). Why did this occur? Firstly, it
is important to recognise that the ADBM (when using only body size as a
trait) can only predict diets that are contiguous with respect to the
size of prey. I.e. it cannot predict that a predator will consume prey
of size 1 and 3, and not prey of size 2. Such patterns can however be
predicted if a trait other than size and which is not perfectly
correlated with size, influences foraging parameters (Petchey et al.
2008). Secondly, it is important to note that the observed diets were
not contiguous when prey are ordered by their size. The estimation
process will result in a greater number of predicted links than observed
given these features, and the model attempts to maximise the coincidence
of predicted and observed link presence and absence (i.e.~the true skill
statistic).

These findings raise the question as to whether the model or the
observed data is incorrect. We expect that the observed data does not
contain some links that would occur in reality. This can be possible due
to low sampling effort causing some links that do occur to be not
observed. In this case, the model may correctly predict a link that was
not yet observed as the data was incorrect. More intensive and more
complete sampling of links in food webs has been recognised as
important, due to the potential that a low sampling effort will
influence the perceived food web structure (Martinez et al. 1999).

We expect there are cases where the model incorrectly predicts a feeding
link despite no possibility that such a link would occur in reality.
This may be the case when a trait other than, or in addition to, prey
size is influential. For example, a particular prey species may have a
defensive trait that means it takes longer to consume it than an
undefended prey of the same size. Incorporating traits other than body
size in the ADBM would allow for discontiguous diets along the size
axis. Furthermore, the ADBM's current form is a biology-only model; it
does not include an observation process, although this could be
included. The model would then be able to predict the absence of a link
due to incomplete observations.

It would be interesting to take a very well sampled food web, and test
if the ABC parameter estimation applied to a subset of the observed
links in a simulated poorly sampled food web predicts the connectance of
a well sampled food web. Such an outcome would indicate the potential to
compensate for under-sampling with an appropriate food web model and
estimation procedure.

The ABC parameterisation resulted in a lower prediction accuracy of
structural features of the food webs (Fig. \ref{fig:fig_r5} (b)) due to
the overestimation of connectance. This was confirmed by principal
component analysis of variation in the food web structural properties
which revealed a first PC axis representing on average 62\% of the
overall variance, and this first axis was highly correlated with
connectance, with an average Spearman correlation of 0.87.

Our parameterisation approach was to maximise the true skill statistic
(the coincidence of predicted and observed link presences, and the
coincidence of predicted and observed link absences). The TSS assigns
equal importance to the collection of presence and absence of observed
links with the weight of an observed single presence or absence link
being dependent on the connectance of the food web. If the connectance
is less than 0.5, the TSS assigns more weight to a presence of link than
to an absence of a link and vice versa.

Because the connectance of the observed food webs is less than 0.5
(Table \ref{fig:tab_1}), the TSS assigned more weight to a single
presence of link than to a single absence of link. This result is as
expected, as the chance that a recorded link is a correct is likely to
be greater than the chance that a recorded absence is correct. This is
because the observation of a single feeding interaction is sufficient to
record the presence of a link. However, this is not true for the absence
of links: one observation of a predator not consuming a prey does not
mean that it never do so. Nevertheless, if we observe no interaction
between two species during the sampling period, we conclude that there
is an absence of link.

To improve our estimation procedure we could quantify the uncertainty in
the recorded absence of links and include this uncertainty in the
parameterisation method. Weight/importance could be assigned to true
positives, true negatives, false positives and false negatives
calculated from empirical studies which may be specific to that food
web. Alternatively, an observation process could be added to the model,
such that the biological part of the model can predict that a feeding
link is possible, but then the observation process in the model leads to
that link not being predicted.

In the PBRW study, the parameter \(b\) played a major role in
maintaining the maximum predictive power of the ADBM. Indeed, they found
that estimating \(b\) only, and not estimating either \(a_i\) or \(a_j\)
slightly decreased model performance, and that estimating only \(b\) and
\(a_j\) did not decrease model performance relative to when all three
parameters were estimated.

We found that the posterior distribution of the parameter \(b\) was the
most constrained of all the parameters (Fig. \ref{fig:fig_r3}).
Parameter \(b\) defines the range of prey body size which has a finite
handling time, and the prey size with the highest energetic
profitability. As the parameter \(b\) relates to the prey-predator body
size ratio, the constrained posterior of \(b\) (Fig.
\ref{fig:fig_r3}(d)) indicates the importance of the ratio of body size
of prey and predator in determining the food web structure with the
ADBM.

The marginal posterior of parameter \(a\) was right-skewed (Fig.
\ref{fig:fig_r3}(c)). This may be because the ABC parameterisation
overestimates the connectance, which means that lower values of \(a\)
are preferred over higher values of \(a\) (a lower value of \(a\) leads
to a lower space clearance/attack rate, and a lower space clearance rate
results in a higher connectance).

Information about who eats who can be collected from multiple sources,
such as gut contents of organisms, stable isotope composition of
tissues, and experimentation (Peralta-Maraver, L\a'opez-Rodríguez, and
de Figueroa 2017; Layman et al. 2007; Warren 1989). Moreover,
experimentation provides independent estimates of allometric foraging
parameters, such as \(b\), \(a_i\), and \(a_j\) (Rall et al. 2012).
Diverse data could be used to parameterise the ADBM's predictions to
test how uncertainty in the different datasets influences the ADBM's
predictions using ABC. Appropriate summary statistics in the ABC method
could be used to address such challenges. We could use, as an example,
the approximate trophic position inferred from stable isotope ratio data
from an individual tissue and gut content data of a predator
simultaneously to parameterise the ADBM. The trophic position and the
gut content information would be the summary statistics in this example.
A further question that could be addressed in future studies is how the
quantity of data affects the ADBM's predictions. The outcome of such a
study could help food web researchers decide on how much data from a
specific source is needed to predict the food web structure, and help
further optimise the deployment of limited sampling resources.

When only partial food web data is available (Patonai and Jord\a'an
2017), the summary statistics in ABC can be used to infer these food web
structures from the ADBM. It would be possible to use gut content data
of only some of the species in a food web to parameterise the ADBM and
predict the food web structure. Summary statistics opens up a broad
spectrum of possibilities in parameterising food web models. There are
multiple empirical and theoretical studies on a range of different food
web properties of food webs across different ecosystems (Williams and
Martinez 2000; Goldwasser and Roughgarden 1993; Martinez 1991). These
can conceivably be used in parameterising food web models using ABC to
constrain the model predictions.

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

This work was supported by the University Research Priority Program
Global Change and Biodiversity (Grant number: U-704-04-11) of the
University of Zurich. We thank the Petchey group members for their
valuable suggestions in the manuscript. We thank Debra Zuppinger-Dingley
for proofreading the manuscript.

\hypertarget{author-contributions}{%
\section{Author contributions}\label{author-contributions}}

Anubhav Gupta: Conceptualization (equal), formal analysis (lead),
methodology (lead), software (lead), writing -- original draft
preparation (lead), writing - review and editing (equal). Owen L.
Petchey: Conceptualization (equal), funding acquisition (lead),
methodology (supporting), resources (lead), writing -- original draft
preparation (supporting), writing - review and editing (equal).

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-allesinaGeneralModelFood2008}{}%
Allesina, Stefano, David Alonso, and Mercedes Pascual. 2008. ``A General
Model for Food Web Structure.'' \emph{Science} 320 (5876). American
Association for the Advancement of Science: 658--61.
\url{https://doi.org/10.1126/science.1156269}.

\leavevmode\hypertarget{ref-bakerFishGutContent2014}{}%
Baker, Ronald, Amanda Buckland, and Marcus Sheaves. 2014. ``Fish Gut
Content Analysis: Robust Measures of Diet Composition.'' \emph{Fish and
Fisheries} 15 (1): 170--77. \url{https://doi.org/10.1111/faf.12026}.

\leavevmode\hypertarget{ref-beckermanForagingBiologyPredicts2006}{}%
Beckerman, A. P., O. L. Petchey, and P. H. Warren. 2006. ``Foraging
Biology Predicts Food Web Complexity.'' \emph{Proceedings of the
National Academy of Sciences of the United States of America} 103:
13745--9.

\leavevmode\hypertarget{ref-bergaminoFoodWebStructure2011}{}%
Bergamino, Leandro, Diego Lercari, and Omar Defeo. 2011. ``Food Web
Structure of Sandy Beaches: Temporal and Spatial Variation Using Stable
Isotope Analysis.'' \emph{Estuarine, Coastal and Shelf Science} 91 (4):
536--43. \url{https://doi.org/10.1016/j.ecss.2010.12.007}.

\leavevmode\hypertarget{ref-broseBodySizesConsumers2005}{}%
Brose, Ulrich, Lara Cushing, Eric L. Berlow, Tomas Jonsson, Carolin
Banasek-Richter, Louis-Felix Bersier, Julia L. Blanchard, et al. 2005.
``Body Sizes of Consumers and Their Resources.'' \emph{Ecology} 86 (9):
2545--5. \url{https://doi.org/10.1890/05-0379}.

\leavevmode\hypertarget{ref-carpenterEcologicalFuturesBuilding2016}{}%
Carpenter, Stephen R. 2016. ``Ecological Futures: Building an Ecology of
the Long Now.'' \emph{Ecology}, October, 2069--83.
\href{https://doi.org/10.1890/0012-9658(2002)083\%5B2069:EFBAEO\%5D2.0.CO;2@10.1002/(ISSN)1939-9170.MacArthurAward}{https://doi.org/10.1890/0012-9658(2002)083{[}2069:EFBAEO{]}2.0.CO;2@10.1002/(ISSN)1939-9170.MacArthurAward}.

\leavevmode\hypertarget{ref-cattinPhylogeneticConstraintsAdaptation2004}{}%
Cattin, Marie-France, Louis-F\a'elix Bersier, Carolin Banašek-Richter,
Richard Baltensperger, and Jean-Pierre Gabriel. 2004. ``Phylogenetic
Constraints and Adaptation Explain Food-Web Structure.'' \emph{Nature}
427 (6977, 6977). Nature Publishing Group: 835--39.
\url{https://doi.org/10.1038/nature02327}.

\leavevmode\hypertarget{ref-cohenJustProportionsFood1989}{}%
Cohen, Joel E. 1989. ``Just Proportions in Food Webs.'' \emph{Nature}
341 (6238, 6238). Nature Publishing Group: 104--5.
\url{https://doi.org/10.1038/341104b0}.

\leavevmode\hypertarget{ref-cohenStochasticTheoryCommunity1985}{}%
Cohen, Joel E., C. M. Newman, and John Hyslop Steele. 1985. ``A
Stochastic Theory of Community Food Webs I. Models and Aggregated
Data.'' \emph{Proceedings of the Royal Society of London. Series B.
Biological Sciences} 224 (1237). Royal Society: 421--48.
\url{https://doi.org/10.1098/rspb.1985.0042}.

\leavevmode\hypertarget{ref-crawfordApplicationsStableIsotope2008}{}%
Crawford, Kerry, Robbie A. Mcdonald, and Stuart Bearhop. 2008.
``Applications of Stable Isotope Techniques to the Ecology of Mammals.''
\emph{Mammal Review} 38 (1): 87--107.
\url{https://doi.org/10.1111/j.1365-2907.2008.00120.x}.

\leavevmode\hypertarget{ref-cressieAccountingUncertaintyEcological2009}{}%
Cressie, Noel, Catherine A. Calder, James S. Clark, Jay M. Ver Hoef, and
Christopher K. Wikle. 2009. ``Accounting for Uncertainty in Ecological
Analysis: The Strengths and Limitations of Hierarchical Statistical
Modeling.'' \emph{Ecological Applications} 19 (3): 553--70.
\url{https://doi.org/10.1890/07-0744.1}.

\leavevmode\hypertarget{ref-dawahStructureParasitoidCommunities1995}{}%
Dawah, Hassan Ali, Bradford A. Hawkins, and Michael F. Claridge. 1995.
``Structure of the Parasitoid Communities of Grass-Feeding Chalcid
Wasps.'' \emph{The Journal of Animal Ecology} 64 (6): 708.
\url{https://doi.org/10.2307/5850}.

\leavevmode\hypertarget{ref-dunneNetworkStructureBiodiversity}{}%
Dunne, Jennifer A., Richard J. Williams, and Neo D. Martinez. 2002.
``Network Structure and Biodiversity Loss in Food Webs: Robustness
Increases with Connectance.'' \emph{Ecology Letters} 5 (4): 558--67.

\leavevmode\hypertarget{ref-emmersonPredatorPreyBody2004}{}%
Emmerson, Mark C., and Dave Raffaelli. 2004. ``Predator--Prey Body Size,
Interaction Strength and the Stability of a Real Food Web.''
\emph{Journal of Animal Ecology} 73 (3): 399--409.
\url{https://doi.org/10.1111/j.0021-8790.2004.00818.x}.

\leavevmode\hypertarget{ref-goldwasserConstructionAnalysisLarge1993}{}%
Goldwasser, Lloyd, and Jonathan Roughgarden. 1993. ``Construction and
Analysis of a Large Caribbean Food Web: Ecological Archives E074-001.''
\emph{Ecology} 74 (4): 1216--33. \url{https://doi.org/10.2307/1940492}.

\leavevmode\hypertarget{ref-gravelInferringFoodWeb2013}{}%
Gravel, Dominique, Timoth\a'ee Poisot, Camille Albouy, Laure Velez, and
David Mouillot. 2013. ``Inferring Food Web Structure from Predator-Prey
Body Size Relationships.'' Edited by Robert Freckleton. \emph{Methods in
Ecology and Evolution} 4 (11): 1083--90.
\url{https://doi.org/10.1111/2041-210X.12103}.

\leavevmode\hypertarget{ref-harper-smithCOMMUNICATINGECOLOGYFOOD2005}{}%
Harper-Smith, Sarah, Eric L. Berlow, Roland A. Knapp, Richard J.
Williams, and Neo D. Martinez. 2005. ``COMMUNICATING ECOLOGY THROUGH
FOOD WEBS: VISUALIZING AND QUANTIFYING THE EFFECTS OF STOCKING ALPINE
LAKES WITH TROUT.'' In \emph{Dynamic Food Webs}, 407--23. Elsevier.
\url{https://doi.org/10.1016/B978-012088458-2/50038-2}.

\leavevmode\hypertarget{ref-hattabForecastingFinescaleChanges2016}{}%
Hattab, Tarek, Fabien Leprieur, Frida Ben Rais Lasram, Dominique Gravel,
François Le Loc'h, and Camille Albouy. 2016. ``Forecasting Fine-Scale
Changes in the Food-Web Structure of Coastal Marine Communities Under
Climate Change.'' \emph{Ecography} 39 (12): 1227--37.
\url{https://doi.org/10.1111/ecog.01937}.

\leavevmode\hypertarget{ref-hobsonUsingStableIsotopes1994}{}%
Hobson, Keith A., John F. Piatt, and Jay Pitocchelli. 1994. ``Using
Stable Isotopes to Determine Seabird Trophic Relationships.''
\emph{Journal of Animal Ecology} 63 (4). {[}Wiley, British Ecological
Society{]}: 786--98. \url{https://doi.org/10.2307/5256}.

\leavevmode\hypertarget{ref-hudsonCheddarAnalysisVisualisation2013}{}%
Hudson, Lawrence N., Rob Emerson, Gareth B. Jenkins, Katrin Layer, Mark
E. Ledger, Doris E. Pichler, Murray S. A. Thompson, Eoin J. O'Gorman,
Guy Woodward, and Daniel C. Reuman. 2013. ``Cheddar: Analysis and
Visualisation of Ecological Communities in R.'' \emph{Methods in Ecology
and Evolution} 4 (1): 99--104.
\url{https://doi.org/10.1111/2041-210X.12005}.

\leavevmode\hypertarget{ref-ibanezOptimizingSizeThresholds2012}{}%
Ibanez, S\a'ebastien. 2012. ``Optimizing Size Thresholds in a
Plant--Pollinator Interaction Web: Towards a Mechanistic Understanding
of Ecological Networks.'' \emph{Oecologia} 170 (1): 233--42.
\url{https://doi.org/10.1007/s00442-012-2290-3}.

\leavevmode\hypertarget{ref-jabotInferringParametersNeutral2009}{}%
Jabot, Franck, and J\a'erôme Chave. 2009. ``Inferring the Parameters of
the Neutral Theory of Biodiversity Using Phylogenetic Information and
Implications for Tropical Forests.'' \emph{Ecology Letters} 12 (3):
239--48. \url{https://doi.org/10.1111/j.1461-0248.2008.01280.x}.

\leavevmode\hypertarget{ref-JonssonPhD}{}%
Jonsson, Tomas. 1998. ``Food Webs and the Distribution of Body Sizes.''
PhD.

\leavevmode\hypertarget{ref-jonssonFoodWebsBody2005}{}%
Jonsson, Tomas, Joel E. Cohen, and Stephen R. Carpenter. 2005. ``Food
Webs, Body Size, and Species Abundance in Ecological Community
Description.'' In \emph{Advances in Ecological Research}, 36:1--84.
Elsevier. \url{https://doi.org/10.1016/S0065-2504(05)36001-6}.

\leavevmode\hypertarget{ref-jordanSensitivityFoodWeb2009}{}%
Jord\a'an, Ferenc, and Györgyi Osv\a'ath. 2009. ``The Sensitivity of
Food Web Topology to Temporal Data Aggregation.'' \emph{Ecological
Modelling} 220 (22): 3141--6.
\url{https://doi.org/10.1016/j.ecolmodel.2009.05.002}.

\leavevmode\hypertarget{ref-knightTrophicCascadesEcosystems2005}{}%
Knight, Tiffany M., Michael W. McCoy, Jonathan M. Chase, Krista A.
McCoy, and Robert D. Holt. 2005. ``Trophic Cascades Across Ecosystems.''
\emph{Nature} 437 (7060): 880--83.
\url{https://doi.org/10.1038/nature03962}.

\leavevmode\hypertarget{ref-krauseCompartmentsRevealedFoodweb2003}{}%
Krause, Ann E., Kenneth A. Frank, Doran M. Mason, Robert E. Ulanowicz,
and William W. Taylor. 2003. ``Compartments Revealed in Food-Web
Structure.'' \emph{Nature} 426 (6964): 282--85.
\url{https://doi.org/10.1038/nature02115}.

\leavevmode\hypertarget{ref-laffertyParasitesDominateFood2006}{}%
Lafferty, K. D., A. P. Dobson, and A. M. Kuris. 2006. ``Parasites
Dominate Food Web Links.'' \emph{Proceedings of the National Academy of
Sciences} 103 (30): 11211--6.
\url{https://doi.org/10.1073/pnas.0604755103}.

\leavevmode\hypertarget{ref-laymanCanStableIsotope2007}{}%
Layman, Craig A., D. Albrey Arrington, Carmen G. Montaña, and David M.
Post. 2007. ``Can Stable Isotope Ratios Provide for Community-Wide
Measures of Trophic Structure?'' \emph{Ecology} 88 (1): 42--48.
\href{https://doi.org/10.1890/0012-9658(2007)88\%5B42:CSIRPF\%5D2.0.CO;2}{https://doi.org/10.1890/0012-9658(2007)88{[}42:CSIRPF{]}2.0.CO;2}.

\leavevmode\hypertarget{ref-lindegrenEcologicalForecastingClimate2010}{}%
Lindegren, Martin, Christian Möllmann, Anders Nielsen, Keith Brander,
Brian R. MacKenzie, and Nils Chr. Stenseth. 2010. ``Ecological
Forecasting Under Climate Change: The Case of Baltic Cod.''
\emph{Proceedings of the Royal Society B: Biological Sciences} 277
(1691): 2121--30. \url{https://doi.org/10.1098/rspb.2010.0353}.

\leavevmode\hypertarget{ref-lurgiClimateChangeImpacts2012}{}%
Lurgi, Miguel, Bernat C. L\a'opez, and Jos\a'e M. Montoya. 2012.
``Climate Change Impacts on Body Size and Food Web Structure on Mountain
Ecosystems.'' \emph{Philosophical Transactions of the Royal Society B:
Biological Sciences} 367 (1605): 3050--7.
\url{https://doi.org/10.1098/rstb.2012.0239}.

\leavevmode\hypertarget{ref-macarthurOptimalUsePatchy1966}{}%
MacArthur, Robert H., and Eric R. Pianka. 1966. ``On Optimal Use of a
Patchy Environment.'' \emph{The American Naturalist} 100 (916): 603--9.

\leavevmode\hypertarget{ref-martinezArtifactsAttributesEffects1991}{}%
Martinez, Neo D. 1991. ``Artifacts or Attributes? Effects of Resolution
on the Little Rock Lake Food Web.'' \emph{Ecological Monographs} 61 (4):
367--92. \url{https://doi.org/10.2307/2937047}.

\leavevmode\hypertarget{ref-martinezEffectsSamplingEffort1999}{}%
Martinez, Neo D., Bradford A. Hawkins, Hassan Ali Dawah, and Brian P.
Feifarek. 1999. ``Effects of Sampling Effort on Characterization of
Food-Web Structure.'' \emph{Ecology} 80 (3): 1044--55.
\href{https://doi.org/10.1890/0012-9658(1999)080\%5B1044:EOSEOC\%5D2.0.CO;2}{https://doi.org/10.1890/0012-9658(1999)080{[}1044:EOSEOC{]}2.0.CO;2}.

\leavevmode\hypertarget{ref-mayWillLargeComplex1972}{}%
May, Robert M. 1972. ``Will a Large Complex System Be Stable?''
\emph{Nature} 238 (5364): 413. \url{https://doi.org/10.1038/238413a0}.

\leavevmode\hypertarget{ref-memmottPredatorsParasitoidsPathogens2000}{}%
Memmott, J., N.D. Martinez, and J.E. Cohen. 2000. ``Predators,
Parasitoids and Pathogens: Species Richness, Trophic Generality and Body
Sizes in a Natural Food Web.'' \emph{Journal of Animal Ecology} 69 (1):
1--15. \url{https://doi.org/10.1046/j.1365-2656.2000.00367.x}.

\leavevmode\hypertarget{ref-morrisFoodWebStructure2015}{}%
Morris, Rebecca J., Frazer H. Sinclair, and Chris J. Burwell. 2015.
``Food Web Structure Changes with Elevation but Not Rainforest
Stratum.'' \emph{Ecography} 38 (8): 792--802.
\url{https://doi.org/10.1111/ecog.01078}.

\leavevmode\hypertarget{ref-oconnorWarmingResourceAvailability2009}{}%
O'Connor, Mary I., Michael F. Piehler, Dina M. Leech, Andrea Anton, and
John F. Bruno. 2009. ``Warming and Resource Availability Shift Food Web
Structure and Metabolism.'' Edited by Michel Loreau. \emph{PLoS Biology}
7 (8): e1000178. \url{https://doi.org/10.1371/journal.pbio.1000178}.

\leavevmode\hypertarget{ref-ogormanSimpleModelPredicts2019}{}%
O'Gorman, Eoin J., Owen L. Petchey, Katy J. Faulkner, Bruno Gallo,
Timothy A. C. Gordon, Joana Neto-Cerejeira, J\a'on S. \a'Olafsson, Doris
E. Pichler, Murray S. A. Thompson, and Guy Woodward. 2019. ``A Simple
Model Predicts How Warming Simplifies Wild Food Webs.'' \emph{Nature
Climate Change} 9 (8): 611--16.
\url{https://doi.org/10.1038/s41558-019-0513-x}.

\leavevmode\hypertarget{ref-opitz1996}{}%
Opitz, Silvia. 1996. ``Quantitative Models of Trophic Interactions in
Caribbean Coral Reefs.'' Iclarm.

\leavevmode\hypertarget{ref-patonaiAggregationIncompleteFood2017}{}%
Patonai, Katalin, and Ferenc Jord\a'an. 2017. ``Aggregation of
Incomplete Food Web Data May Help to Suggest Sampling Strategies.''
\emph{Ecological Modelling} 352 (May): 77--89.
\url{https://doi.org/10.1016/j.ecolmodel.2017.02.024}.

\leavevmode\hypertarget{ref-peralta-maraverStructureDynamicsStability2017}{}%
Peralta-Maraver, I., M. J. L\a'opez-Rodríguez, and J. M. Tierno de
Figueroa. 2017. ``Structure, Dynamics and Stability of a Mediterranean
River Food Web.'' \emph{Marine and Freshwater Research} 68 (3). CSIRO
PUBLISHING: 484--95. \url{https://doi.org/10.1071/MF15154}.

\leavevmode\hypertarget{ref-petchey2008size}{}%
Petchey, Owen L, Andrew P Beckerman, Jens O Riede, and Philip H Warren.
2008. ``Size, Foraging, and Food Web Structure.'' \emph{Proceedings of
the National Academy of Sciences} 105 (11). National Acad Sciences:
4191--6.

\leavevmode\hypertarget{ref-petcheyEnvironmentalWarmingAlters1999}{}%
Petchey, Owen L., P. Timon McPhearson, Timothy M. Casey, and Peter J.
Morin. 1999. ``Environmental Warming Alters Food-Web Structure and
Ecosystem Function.'' \emph{Nature} 402 (6757): 69--72.
\url{https://doi.org/10.1038/47023}.

\leavevmode\hypertarget{ref-petcheyEcologicalForecastHorizon2015}{}%
Petchey, Owen L., Mikael Pontarp, Thomas M. Massie, Sonia K\a'efi, Arpat
Ozgul, Maja Weilenmann, Gian Marco Palamara, et al. 2015. ``The
Ecological Forecast Horizon, and Examples of Its Uses and
Determinants.'' \emph{Ecology Letters} 18 (7): 597--611.
\url{https://doi.org/10.1111/ele.12443}.

\leavevmode\hypertarget{ref-poisotWhenEcologicalNetwork2014}{}%
Poisot, Timoth\a'ee, and Dominique Gravel. 2014. ``When Is an Ecological
Network Complex? Connectance Drives Degree Distribution and Emerging
Network Properties.'' \emph{PeerJ} 2 (February). PeerJ Inc.: e251.
\url{https://doi.org/10.7717/peerj.251}.

\leavevmode\hypertarget{ref-poisotHowEcologicalNetworks2016}{}%
Poisot, Timoth\a'ee, and Daniel B. Stouffer. 2016. ``How Ecological
Networks Evolve.'' Preprint. Ecology.
\url{https://doi.org/10.1101/071993}.

\leavevmode\hypertarget{ref-polisComplexTrophicInteractions1991}{}%
Polis, Gary A. 1991. ``Complex Trophic Interactions in Deserts: An
Empirical Critique of Food-Web Theory.'' \emph{The American Naturalist}
138 (1): 123--55.

\leavevmode\hypertarget{ref-rallUniversalTemperatureBodymass2012}{}%
Rall, B. C., U. Brose, M. Hartvig, G. Kalinkat, F. Schwarzmuller, O.
Vucic-Pestic, and O. L. Petchey. 2012. ``Universal Temperature and
Body-Mass Scaling of Feeding Rates.'' \emph{Philosophical Transactions
of the Royal Society B: Biological Sciences} 367 (1605): 2923--34.
\url{https://doi.org/10.1098/rstb.2012.0242}.

\leavevmode\hypertarget{ref-shrinerEvolutionIntrahostHiv2006}{}%
Shriner, Daniel, Yi Liu, David C. Nickle, and James I. Mullins. 2006.
``Evolution of Intrahost Hiv - 1 Genetic Diversity During Chronic
Infection.'' \emph{Evolution} 60 (6): 1165--76.
\url{https://doi.org/10.1111/j.0014-3820.2006.tb01195.x}.

\leavevmode\hypertarget{ref-tamaddoni-nezhadConstructionValidationFood2013}{}%
Tamaddoni-Nezhad, Alireza, Ghazal Afroozi Milani, Alan Raybould, Stephen
Muggleton, and David A. Bohan. 2013. ``Construction and Validation of
Food Webs Using Logic-Based Machine Learning and Text Mining.'' In
\emph{Advances in Ecological Research}, 49:225--89. Elsevier.
\url{https://doi.org/10.1016/B978-0-12-420002-9.00004-4}.

\leavevmode\hypertarget{ref-toniApproximateBayesianComputation2009}{}%
Toni, Tina, David Welch, Natalja Strelkowa, Andreas Ipsen, and Michael
P.H. Stumpf. 2009. ``Approximate Bayesian Computation Scheme for
Parameter Inference and Model Selection in Dynamical Systems.''
\emph{Journal of the Royal Society Interface} 6 (31): 187--202.
\url{https://doi.org/10.1098/rsif.2008.0172}.

\leavevmode\hypertarget{ref-tylianakisEffectsGlobalEnvironmental2014}{}%
Tylianakis, Jason M., and Amrei Binzer. 2014. ``Effects of Global
Environmental Changes on ParasitoidHost Food Webs and Biological
Control.'' \emph{Biological Control} 75 (August): 77--86.
\url{https://doi.org/10.1016/j.biocontrol.2013.10.003}.

\leavevmode\hypertarget{ref-warrenSpatialTemporalVariation1989}{}%
Warren, Philip H. 1989. ``Spatial and Temporal Variation in the
Structure of a Freshwater Food Web.'' \emph{Oikos} 55 (3): 299.
\url{https://doi.org/10.2307/3565588}.

\leavevmode\hypertarget{ref-williamsSimpleRulesYield2000}{}%
Williams, Richard J., and Neo D. Martinez. 2000. ``Simple Rules Yield
Complex Food Webs.'' \emph{Nature} 404 (6774, 6774). Nature Publishing
Group: 180--83. \url{https://doi.org/10.1038/35004572}.

\leavevmode\hypertarget{ref-woodwardChapterIndividualBasedFood2010}{}%
Woodward, Guy, Julia Blanchard, Rasmus B. Lauridsen, Francois K.
Edwards, J. Iwan Jones, David Figueroa, Philip H. Warren, and Owen L.
Petchey. 2010. ``Chapter 6 - Individual-Based Food Webs: Species
Identity, Body Size and Sampling Effects.'' In \emph{Advances in
Ecological Research}, edited by Guy Woodward, 43:211--66. Integrative
Ecology: From Molecules to Ecosystems. Academic Press.
\url{https://doi.org/10.1016/B978-0-12-385005-8.00006-X}.

\leavevmode\hypertarget{ref-woodwardInvasionStreamFood2001}{}%
Woodward, Guy, and Alan G. Hildrew. 2001. ``Invasion of a Stream Food
Web by a New Top Predator.'' \emph{Journal of Animal Ecology} 70 (2):
273--88. \url{https://doi.org/10.1111/j.1365-2656.2001.00497.x}.

\leavevmode\hypertarget{ref-woodwardQuantificationResolutionComplex2005}{}%
Woodward, Guy, Dougie C. Speirs, and Alan G. Hildrew. 2005.
``Quantification and Resolution of a Complex, Size-Structured Food
Web.'' In \emph{Advances in Ecological Research}, 36:85--135. Elsevier.
\url{https://doi.org/10.1016/S0065-2504(05)36002-8}.

\leavevmode\hypertarget{ref-yodzisLocalTrophodynamicsInteraction1998}{}%
Yodzis, Peter. 1998. ``Local Trophodynamics and the Interaction of
Marine Mammals and Fisheries in the Benguela Ecosystem.'' \emph{Journal
of Animal Ecology} 67 (4): 635--58.
\url{https://doi.org/10.1046/j.1365-2656.1998.00224.x}.

\bibliographystyle{unsrt}
\bibliography{bibliography.bib}

\end{document}

### 2021-11-15 manuscript/ms_C2/ms_C2.Rmd
All files
files

---
title: "Optimal amount of gut content data required to predict trophic interactions using a food web model"
authors:
- affiliation: University of Zurich
  department: Department of Evolutionary Biology and Environmental Studies
  email: anubhav.gupta@ieu.uzh.ch
  location: 8057 Zurich, Switzerland
  name: Anubhav Gupta
  thanks: Corresponding author
- affiliation: University of Essex
  department: School of Life Sciences
  email: e.ogorman@essex.ac.uk
  location: CO4 3SQ Colchester, UK
  name: Eoin O' Gorman
- affiliation: University of Zurich
  department: Department of Evolutionary Biology and Environmental Studies
  email: owen.petchey@ieu.uzh.ch
  location: 8057 Zurich, Switzerland
  name: Owen L. Petchey
bibliography: bibliography.bib
output:
  rticles::arxiv_article:
    keep_tex: yes
  pdf_document: default
header-includes:
  - \usepackage{lineno}
  - \linenumbers
  - \usepackage {amsmath}
  - \setlength\parindent{24pt}
  - \usepackage{setspace}\doublespacing
# - \usepackage{setspace}\doublespacing
keywords:
- gut content data
- ADBM
- food web accuracy
- food web prediction
mainfont: Times New Roman
geometry: margin=1in
abstract: "1) \n2)  \n3)  \n4)  \n"
---

# Alternate titles

-   Predicting trophic interactions using incomplete gut content data

-   Effect of the amount of gut content data on the accuracy and precision of food web prediction

# Introduction

Knowledge about the trophic interactions in a food web is crucial in ecology from identifying keystone species [@jordanKeystoneSpeciesFood2009] to quantifying robustness of a food web to species extinctions [@dunneNetworkStructureBiodiversity2002]. This has led to the development of numerous food web models [@allesinaGeneralModelFood2008; @cohenStochasticTheoryCommunity1985; @gravelInferringFoodWeb2013; @petcheySizeForagingFood2008; @tamaddoni-nezhadConstructionValidationFood2013]. Along with inferring missing links in an observed food web, the food web models are also used for ecological forecasting [@hattabForecastingFinescaleChanges2016; @lindegrenEcologicalForecastingClimate2010] and understanding the underlying mechanism governing the interactions in a food web [@ogormanSimpleModelPredicts2019].

Although food web models are constructed using prior theory governing the food webs, interaction data is required to parameterise a model. For example, @petcheySizeForagingFood2008 used presence-absence information about trophic interactions to parameterise the allometric diet breadth model and thereby predict species interactions. These information can be inferred from diverse set of methods such as gut content analysis [@peralta-maraverStructureDynamicsStability2017], stable isotope ratio analysis of tissues [@laymanCanStableIsotope2007], experimentation [@warrenSpatialTemporalVariation1989], DNA metabarcoding [@roslinUseDNABarcodes2016] and literature research [@grayJoiningDotsAutomated2015; @cohenSoilInvertebratesChemistry2014; @goldwasserConstructionAnalysisLarge1993a]. All of these methods can infer the diet of a consumer, however different methods measure different consumed components, thereby resulting in different levels of uncertainty in the inferred diet (citreqd). A single gut content of a predator describes what that individual has consumed recently which can be used to infer the diet of the predator [@eitzingerTestingValidityFunctional2018; @omalleyEffectsFoodWeb2017; @dixonAssessingDietNorth2017; @mcclain-countsTrophicStructureMesopelagic2017b; @peralta-maraverStructureDynamicsStability2017]. Stable isotope data when combined with mixing models can be used to determine which prey items are most likely fed upon by a predator [@kadoyaIsoWebBayesianIsotope2012; @crawfordApplicationsStableIsotope2008].

Acquiring food web data from these methods is time consuming and expensive (reference). For example, many gut content data needs to be collected to infer the complete presence-absence information of a food web structure with high accuracy and precision. Also further time and resource investment is required to process the collected samples. Hence, there is an utmost demand to know the minimum number of presence-absence information of a food web to parameterise a food web model with high accuracy and high precision, so that one knows when to stop collecting any further data on the food web.

The key question we are interested in answering is how much presence-absence information is required to infer food web structure from a food web model with high accuracy and high precision. In other words, in case of gut content data how many samples of gut content should one collect from the field to parameterise a food web model? To answer this question, we use the presence-absence information from gut content data, and allometric diet breadth model (ADBM) to predict trophic interactions. We parameterise the model using approximate Bayesian computation/rejection Monte Carlo sampling.

```{r echo = FALSE, warning = FALSE}
# options(knitr.kable.NA = '')
# library(readxl)
# library(knitr)
# library(kableExtra)
# fw_table <- read_excel("../table/data_summary_fil.xlsx")
# 
# kable(fw_table, format = "latex",
#       caption = "\\label{fig:tab_1}Studies showing the type of data used to infer trophic interactions in a food web",
#       escape = FALSE) %>%
#     kable_styling(latex_options="scale_down")

```

# Materials and Methods

In the upcoming sections, we present the allometric diet breadth model (ADBM) and the gut content data used to infer trophic interactions. We also give a detailed account of using partial gut content data to parameterise the ADBM using approximate Bayesian computation (ABC). We assessed model predictions using true skill statistic and various structural food web properties for comparison across food webs.

## Allometric Diet Breadth Model (ADBM)

The allometric diet breadth model (ADBM) is based on optimal foraging theory, specifically the contingency foraging model [@macarthurOptimalUsePatchy1966]. The ADBM predicts the set of prey species a consumer should feed upon to maximise its rate of energy intake [@petcheySizeForagingFood2008]. The foraging variables in the model: energy content of the resources, handling times of the prey, space clearance rate and prey densities are allometrically scaled to the body sizes of the species.

## Broadstone Stream

Broadstone Stream (51$^\circ$ 05' N 0$^\circ$ 03' E; 120 m above sea-level) is a second-order tributary of the River Medway in south-east England. It is dominated by invertebrates as the acidity of the stream (pH 4.7-6.6) excludes fish. The stream consists of 25 common invertebrate species [@woodwardQuantificationResolutionComplex2005]. Among the predators, the three large species are *Cordulegaster boltonii* Donovan, *Sialis fuliginosa* Pict. and *Plectrocnemia conspersa* [Curtis] and the three small species are the larvae of the tanypod midges *Macropelopia nebulosa* [Meigen], *Trissopelopia longimana* [Staeger], and *Zavrelimyia barbatipes* [Kieffer]. Broadstone Stream food web is one of the most completely described food webs available for any system [@schmid-arayaImportanceMeiofaunaFood2002; @hildrewChapterSustainedResearch2009; @layerFoodWebStructure2010; and @woodwardQuantificationResolutionComplex2005a].

## Celtic Sea

The Celtic Sea is an area of continental shelf bordered by Ireland, the UK and the Bay of Biscay. Precise sampling locations and dates were not given in the Barnes et al. (2008) dataset, from where the data used in this chapter were extracted, so we pooled data over the whole time period and locations to capture general patterns. Only locations consistently sampled through the 1987--2001 time series were used (Blanchard et al., 2005).

The feeding links of fishes in the Celtic Sea have been described in a published global dataset of individual predator and prey body sizes and taxonomy (Barnes et al., 2008): in total, 1988 feeding events from 29 predator species were included in the food web presented here. The original stomach contents data were collected from dissections carried out on board research vessels during the annual surveys carried out by the Centre for Environment, Fisheries and Aquaculture Science (Cefas) (Pinnegar et al., 2003). Predator and prey length were recorded and converted to body mass by Barnes et al. (2008) using published regression equations. Only vertebrate prey were identified and measured, with the vast majority being identified to species.

## Afon Hirnant

The Afon Hirnant is a tributary of the Welsh Dee in North Wales, U.K. (52$^\circ$ 52'N 03$^\circ$ 34) with the study being conducted at three sites. The pH within each site ranged from about 5.5 to 7 over the course of the year.

A total of 180 invertebrate samples were collected for the whole sampling periods. All individuals within the benthic samples were counted and identified to the lowest possible taxonomic level (usually species). Prey items were identified using a combination of taxonomic keys and reference slides of previously identified species, after @schmid-arayaConnectanceStreamFood2002; @schmid-arayaImportanceMeiofaunaFood2002.

## Tadnoll Brook

Description of Tadnoll Brook here

## Coilaco

Description of Coilaco here

## Guampoe

Description of Guampoe here

## Trancura

Description of Trancura here

## Food web construction

Presence and absence interactions of food web data can be aggregated in different ways [@gilljamSeeingDouble2011]. A common way of aggregating food web data is the taxonomic approach, where a species is defined as predating on another if at least one prey species individual was found in the gut of a predator species individual. Whereas in size-class food web, a feeding link was assigned if at least one prey item within a size class was found in the gut of a predator of another size class, irrespective of their taxonomy. In our study, we aggregate the food web on the basis of size class.

## Assessment of prediction

The accuracy of the predicted diet of the predators was defined using true skill statistic (TSS) which takes into account the true and false predictions of both the presence and absence of links defined as:

$$ \text{TSS} = \frac{ad-bc}{(a+c)(b+d)} $$ where $a$ is the number of observed links that are predicted by the model (true positives), $d$ is the number of observed absences of links that are correctly predicted (true negatives), $b$ is the number of false positives, and $c$ is the number of false negatives.

The $TSS$ ranges from $-1$ to $1$, where +1 indicates a perfect prediction. A $TSS$ value of zero or less indicates a performance no better than random [@alloucheAssessingAccuracySpecies2006].

## Inferring food web using partial gut content data

From a pool of gut content data, we draw a set of gut content data randomly. Then we used the rejection ABC to accept a parameter value from a prior distribution which would have resulted in the minimum distance, where distance = 1 - True skill statistic. The true skill statistic was computed between the predators' diet predicted from the ADBM, and that from the sampled gut content data. We repeated this process for $n~(= 100)$ number of times for every $i$ number of guts, where $i$ lies between 1 and total number of gut content data in the pool.

*Input:*

-   Predators $P: P = \{p_1, p_2, \dots, p_k \}$

-   A pool of gut content data $G: G = \{g_1, g_2, \dots, g_n\}$, where $g_{n}$ is a one-dimensional matrix containing ones and zeros.

-   A model prediction $model(\theta): ADBM(\theta) = \{d_{p_1}, d_{p_1}, \dots, d_{p_k}\}$, where $d_{p_k}$ is a one-dimensional diet matrix of predator $k$ containing ones and zeros.

-   A summary statistic $s(x): s(x) \subseteq model(\theta)$

-   A distance function $d(x_i, y) : d(x_i,y) = 1 - TSS(x_i, y)$

-   An observed food web $Y: Y = \{d_{p_1}', d_{p_1}', \dots, d_{p_k}'\}$

*Sampling:*

for $i = 1, \dots, tgut$ where $tgut$ is the total number of gut content data in the pool $G$

-   for $j = 1, \dots, nsample$ where $nsample$ is the number of independent samples to be drawn

    -   Draw a set of gut content data $y = \{g_1, g_2, \dots, g_i\}$ from the pool of gut content data $G$

    -   for $k = 1, \dots, npar$ where $npar$ is the number of parameter values to be sampled

        -   Draw a set of parameter values $\theta_k$ from the prior distribution $\pi(\theta)$

        -   Compute the model result $x_i = model(\theta_k)$

        -   Compute $s(x_i)$ and $d(s(x_i), y)$

    -   Accept $\theta_j$, which results in the $min_i\{d(s(x_i), y)\}$

-   Compute $TSS_{i}(x, y) = \{TSS(x_i,y): x_i = ADBM(\theta_j), \theta_j \text{ computed from previous step}\}$ using the accepted $\theta_1, \dots, \theta_{nsample}$

*Output:*

A prediction interval containing $TSS$ between observed and predicted food webs for every $i$ number of gut content data drawn from the pool of gut content data.

# Results

We first present how the accuracy of the food web model vary in predicting trophic interactions when we increase the amount the gut content data provided to the food web model. Then, we calculate the number of gut content data for each food webs corresponding to which the accuracy results in 90% of the maximum true skill statistics predicted by the food web model. We also compute the goodness of the food web model in predicting structural properties from incomplete gut content data. We did that by computing mean standardised error in food web properties.

## Inferring trophic interactions using ADBM and incomplete gut content data

```{r, echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_ra} (a, c, e, g, i, k, m) Accuracy of the predicted food web measured using the true skill statistics, predicted by the ADBM parameterised using gut content data. Line and shaded grey region represents the mean and the prediction interval of 100 independent samples respectively. Red line represents the number of predator guts required to achieve a TSS of 95\\% of the maximum TSS. (b, d, f, h, j, l, n) Ratio of the true skill statistic of the predicted food web by the ADBM parameterised using gut content data to that of the predicted food web constructed using gut content data only. The dashed line shows where the ratio is one for reference."}
knitr::include_graphics("../../results/misc/plot_TSS_ratio.png")
```

The true skill statistics of the food webs predicted by the ADBM using subsets of gut content data improved quickly for lower number of predator guts (Fig. \ref{fig:fig_ra}) (a, c, e, g, i, k, m). The prediction interval of the true skill statistics reduced with the increasing number of predator guts with the mean TSS asymptoting to the maximum mean TSS achieved by the ADBM when all the gut content data was used. Although the maximum TSS varied among the food webs, the qualitative increase in the TSS was the same.

For a low number of predator guts, the TSS of the model predicted food web was higher compared to the TSS of the food web constructed from gut content data (Fig. \ref{fig:fig_ra} (b, d, f, h, j, l, n)), recommending when a model can be used to compensate for undersampled links. After a certain increase in the number of predator guts, the ratio TSS(Model)/TSS(data) reduced to less than one, and reduced further gradually.

With only 381 number of gut content data which is 38% of the total gut content data, the ADBM predicted the food web with TSS of 0.74 which was 95% of the mean TSS (0.78) achieved using complete gut content data by the ADBM for Broadstone Stream food web (Fig. \ref{fig:fig_ra}(a)). In the case of the Celtic Sea food web, only 171 gut content data was required by the ADBM to predict food web with TSS equal to 95% of the mean TSS (0.68) achieved using complete gut content data by the ADBM (Fig. \ref{fig:fig_ra}(c)).

## Dependence of minimum gut content data on number of species, links and connectance

There seems to be a positive relationship between number of minimum gut content data and number of species (S) (Fig. \ref{fig:fig_rb} (a)), links (L) (Fig. \ref{fig:fig_rb} (c)), connectance (C) (Fig. \ref{fig:fig_rb} (d)) and number of predator nodes (Fig. \ref{fig:fig_rb} (e)), with Broadstone Stream being an outlier in Fig. \ref{fig:fig_rb} (a, c, e). The number of minimum gut content data increases with number of maximum gut content data sampled (Fig. \ref{fig:fig_rb} (b)). There seems to be a negative relationship between proportion of minimum gut (= Number of minimum gut / Number of maximum guts sampled) and number of species (S) (Fig. \ref{fig:fig_rb} (f)), links (L) (Fig. \ref{fig:fig_rb} (g)), connectance (C) (Fig. \ref{fig:fig_rb} (h)).

```{r echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_rb} (a, b, c, d, e) Number of minimum gut content data plotted against number of species (S), number of maximum guts sampled, number of links (L), connectance (C) and number of predator nodes respectively. (f, g, h) Proportion of minimum gut content data plotted against number of species (S), number of links (L) and connectance (C) respectively."}
knitr::include_graphics("../../results/misc/plot_min_gut_vs_X.png")
```

```{r echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_rc} True skill statistics of the food web constructed using gut content data plotted against number of gut content data."}
knitr::include_graphics("../../results/misc/plot_empTSS_ngut.png")
```

# Discussion

<!-- We have demonstrated how a food web model can be used to predict food web in the availability of incomplete data. At lower amount of gut content data, ADBM is quite better at predicting trophic interactions. We also compute the upper limit of amount of gut content data till when it is advantageous to use the ADBM. This can help us decide how much gut content data to actually collect when we are using a food web model to infer trophic interactions. -->

## Why Broadstone Stream is an outlier?

Broadstone Stream is the most sampled food web compared to all the other food webs (Fig. \ref{fig:fig_rc}), which means the observed Broadstone Stream food web might be more accurate compared to others.

## Why incomplete gut content data can be used to infer trophic interactions?

-   Model fills up the missing interactions

-   Partial data helps to constrain the parameter space

<!-- Food web model is set of rules based on ecological theory which defines trophic interactions in a food web. A food web model does better in predicting trophic interactions provided the trophic interactions in an ecosystem is governed by these rules.  -->

## There is uncertainty in gut content data and needs to be propagated into model's predictions

There is considerable uncertainty involved in gut content analysis [@bakerFishGutContent2014] such as in fish's guts, there are sometimes loose tissues that are not identifiable and cannot be assigned to a specific prey item with certainty. There are factors such as sample size of consumers, mechanical prey handling, differential digestion and evacuation rates of different prey types and volumes, and the ingestion order that in combination result in an unquantifiable error which is difficult to interpret in the predator diet [@hyslopStomachContentsAnalysis1980; @rindorfBiasEstimatingFood2004; @bakerFishGutContent2014]. Therefore, a future development would be to consider how this uncertainty is propagated into food web prediction.

## Comparing our study with other studies of predicting food webs using incomplete data

Some studies have presented how the accuracy of food web prediction change when we vary the amount of food web data [@grayJoiningDotsAutomated2015].

## What is the generalisability of our results?

-   Dependent on how size structured a food web is, how the food web is aggregated, the type of interactions

<!-- The model correctly predicted a greater proportion of links when the trophic interactions were more strongly dependent on size [@petcheySizeForagingFood2008]. Indeed, constructing a food web based only on body size (i.e. ignoring taxonomy) resulted in almost twice the number of correctly predicted links, i.e. 83%, in contrast to taxonomy [@woodwardChapterIndividualBasedFood2010]. The goodness of fit of the ADBM's predictions depends on the types of interactions in the food webs [@petcheySizeForagingFood2008], because some of the interactions are more size structured than other interactions. For instance, predacious and aquatic herbivore interations were predicted better than parasitoid and herbivory ones [@petcheySizeForagingFood2008]. -->

## Assumption that the food web constructed with the total gut content data is the true food web and how can this be improved

Our study is based on the assumption that the food web constructed using the complete gut content data is the true food web. However, it might not be the case as the links are still under-sampled for many nodes [@woodwardIndividualBasedFoodWebs2010]. This could result in a lower TSS of the predicted food web from the model which can lead to a higher upper limit on the amount of gut content data.

## Limitation of the model

The maximum predictive power of a model is constrained by the rules it is based on.

## How can we include other food web data type?

A future prospect would be to include other types of food web data

-   experimentation (feeding trials)

-   DNA Metabarcoding

## Extending the approach to other food web models

-   Current approach could be implemented with other food web models

<!-- We have used rejection ABC to make use of incomplete gut content data to parameterise the ADBM. In theory, the ADBM could be replaced with any other food web models that predicts presence and absence interactions. -->

# Conclusion

# Supplementary Information

<!-- ```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_s1} \\textit{In silico} approach for investigating the effect of quantity and composition of food web data in predicting food web structure using the ADBM."} -->

<!-- knitr::include_graphics("../fig/flowchart.png") -->

<!-- ``` -->

## Gut content data simulation

We simulated a food web using the ADBM for a given set of parameters. For a given set of predators, we subset the diet from the simulated food web. Then using a probability mass function (distribution), we sampled the gut content data from predators' diet thereby incorporating the uncertainty in the gut content data. We repeated this process multiple number of times for every predator in the food web.

*Input:*

-   Predators whose diet are to be simulated $P = \{p_1, \dots, p_n\}$

-   A simulated food web $ADBM(\theta_i) = \{d_{p_1}, d_{p_1}, \dots, d_{p_k}\}$, where $d_{p_k}$ is a one-dimensional diet matrix of predator $k$ containing ones and zeros.

-   A function which describes uncertainty in the diet $U(d)$

-   Number of independent guts to be simulated for a predator $p_i: ngut$

*Sampling:*

-   for $p_i \in P$

    -   for $j = 1, \dots, ngut$, where $ngut$ is the number of guts to be simulated

        -   Simulate a single gut of a predator $p_i: g(p_i) = d_{p_i} * U(d_{p_i})$

    -   Set of gut of a predator $p_i: G(p_i) = \{ g(p_i) : g(p_i) = d_{p_i}*U(d_{p_i}) \}$

*Output:*

-   We simulated a pool of gut content data which contains simulated gut content data $G(p_i)$ for every predator $p_i$

## Prediction using simulated gut content data from a simulated food web

```{r fig_r0, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r0} True skill statistics between predicted food web and observed food web for a simulated small reef food web estimated for distinct predator guts in a sample. The observed simulated food web consists of 50 species and \\dots links. The vertical bars correspond to the prediction intervals of the true skill statistics with filled circles representing the corresponding mean. A prediction interval of the TSS is formed using a set of 100 accepted TSS values using the ABC method."}
knitr::include_graphics("../fig/TSS_with_n_pred_prop_simulated.png")
```

The true skill statistics (TSS) between the predicted food web and observed food web saturated with an increasing number of distinct predator guts in a sample (Fig. \ref{fig:fig_r0}). The TSS of the predicted food webs estimated using the complete individual gut data had shorter prediction intervals resulting in less uncertainty, and higher mean TSS than that using the partial individual gut data. The maximum limit of the prediction interval of TSS estimated using the complete gut data and the partial gut data were almost equal, with the minimum limit of the prediction interval of TSS using partial gut data being lower than that from the complete gut data. Eventually, the gap between the mean TSS using the partial gut data and the complete gut data reduced with an increasing number of distinct predator guts suggesting when we have enough predator species' gut data, the achieved TSS was almost constant and hence independent of the amount of gut data.

The maximum TSS estimated using the complete gut data was very close to one and almost remained constant with an increasing number of different predator species sampled. With the gut data sample of only five distinct predator species, 95% of the maximum mean TSS was achieved when complete individual gut data was used, while the same was achieved with 15 predator species for partial gut data. This shows that one does not need to know the gut data of all the species to predict the food web and the accuracy is dependent on the completeness of an individual gut data.

```{r fig_r3, echo=FALSE, fig.align='center', out.width="300px", fig.cap="\\label{fig:fig_r3} True skill statistics between predicted food web and observed food web estimated for different number of distinct predator guts. The estimation is done for three sets of gut data: gut content data of predators whose body sizes are smaller than the mean body size, larger than the mean body size, and all the gut content data."}
knitr::include_graphics("../fig/TSS_with_n_pred_prop.png")
```

```{r fig_r31, echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_r31} True skill statistic between predicted food web using ADBM and incomplete gut content data, and observed food web against the true skill statistic between food web constructed using incomplete gut content data, and observed food web. Error bars represent prediction intervals of 100 independent samples. Dashed line is 1:1 line for reference."}
knitr::include_graphics("../../results/misc/TSS_model_vs_data.png")
```

```{r fig_r32, echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_r32} Mean standardised error in structural properties in the food web predicted using ADBM and incomplete gut content data against structural properties in the predicted food web constructed using incomplete gut content data. Error bars represent prediction intervals of 100 independent samples. Dashed line is 1:1 line for reference."}
knitr::include_graphics("../../results/misc/mse_model_vs_data.png")
```

<!-- # Notes: -->

<!-- ## Stable isotope ratios -->

<!-- * Isotope ratios are reported in parts per thousand  relative to standards, and atmospheric N for nitrogen, and defined in delta notation as -->

<!-- * $\delta^{15}N$ or $\delta^{13}C = (\frac{R_{sample}}{R_{standard}} - 1) * 10^3 $ -->

<!-- * Most commonly a fixed $\Delta^{15}N$ value of 3.4 ppt is used to estimate relative species TP -->

<!-- # Other notes: -->

<!-- * Audience: Researchers who are interested in food web data collection -->

# Acknowledgements

# Author contributions

# References

<!-- ## Why knowing trophic interactions is important? -->

<!-- Knowledge about the trophic interactions in a food web can be used to answer crucial ecological questions: Which species is a keystone species in a food web [@jordanKeystoneSpeciesFood2009]? How would a food web respond if the top predators are removed [@knightTrophicCascadesEcosystems2005]?  Which species should be given priority when conservation efforts are implemented [@mcdonald-maddenUsingFoodwebTheory2016]? How robust is a food web to extinctions [@dunneNetworkStructureBiodiversity2002]? -->

<!-- ## What are the methods for knowing interactions? -->

<!-- Species interactions can be directly or indirectly inferred from different types of methods such as gut content analysis [@peralta-maraverStructureDynamicsStability2017], stable isotope ratio analysis of tissues [@laymanCanStableIsotope2007], experimentation [@warrenSpatialTemporalVariation1989], DNA metabarcoding [@roslinUseDNABarcodes2016], food web model [@gravelInferringFoodWeb2013; @petcheySizeForagingFood2008; @williamsSimpleRulesYield2000] and literature research [@grayJoiningDotsAutomated2015; @cohenSoilInvertebratesChemistry2014; @goldwasserConstructionAnalysisLarge1993a]. -->

<!-- ## What are the shortcomings of the methods mentioned above? -->

<!-- These food web methods mentioned above have multiple shortcomings. Stable isotope ratio analysis of the organism's tissue does not give a direct information of the diet of that organism but rather approximate trophic position of that species in the food web. Although mixing models can be used to determine what prey items are most likely fed upon by a predator but this results in uncertainty in the estimates [@kadoyaIsoWebBayesianIsotope2012; @crawfordApplicationsStableIsotope2008]. Experimentation (e.g. feeding trials) may create unrealistic conditions where a predator is confined in a small space with a potential "prey" and is effectively "forced" into eating it (citreqd). DNA metabarcoding could have many issues such as failure to relate OTUs to species, or inability to distinguish secondary predation, i.e. the DNA signature of the prey consumed by the prey consumed by the primary item found in the predator's gut. Another approach to infer missing links is literature research which involves assuming that a link will occur because another author described it in some other system, or for related predator/prey species, e.g. from the same genus or family  [@grayJoiningDotsAutomated2015; @cohenSoilInvertebratesChemistry2014; @goldwasserConstructionAnalysisLarge1993a] (citreqd). This typically results in a food web that will be very oversampled with false positives in the presence of links (citreqd). -->

<!-- ## Food web model -->

<!-- Food web models are set of rules governed by ecological theory which defines trophic interactions in a food web. Along with inferring missing links in a food web, they can be used for understanding the mechanistic of the food web and ecological forecasting. Observed food web data can be used to parameterise the food web model. -->

<!-- ## Parameterising a food web model using food web data -->

<!-- One of the common method of knowing presence-absence information of trophic links in food web is by gut content analysis of predator guts, which can be used to parameterise a food web model. Gut content data have been used to predict the diet of a predator in a food web [@eitzingerTestingValidityFunctional2018; @omalleyEffectsFoodWeb2017; @dixonAssessingDietNorth2017; @mcclain-countsTrophicStructureMesopelagic2017b; @peralta-maraverStructureDynamicsStability2017]. A single gut content data of a predator gives the information what the predator has consumed recently. The diet of that individual can be inferred from the items in the stomach. -->

<!-- ## Why inferring interactions is not easy? -->

<!-- As a food web can be quite complex with many species and trophic interactions [@williamsSimpleRulesYield2000;@berlowSimplePredictionInteraction2009], inferring these trophic interactions with high accuracy and low uncertainty would require a large amount of food web data (citreqd). E.g. One would need to sample many individuals for gut content data, and processing these guts require a large amount of effort and time as well. -->

<!-- A single gut content of a predator provides information of the prey individuals that have been consumed by the predator in a small temporal and spatial scale (citreqd). Therfore, given a spatial and temporal scale of a food web, the sampling of the gut content data needs to be carried out. This means that for a food web constructed on a large spatial and temporal scale large number of gut content data needs to be collected. There is also a possibility that some of the information provided by these types of food web data are redundant i.e. taking into account any further food web data does not necessarily increase the food web prediction significantly. E.g. This can happen if the guts of two predator individuals give the same information about the prey the predator has consumed. This issue can be resolved by using a yield-effort curve which suggests when sampling of new predator guts can be stopped [@hernandezParasitesAlterTopology2008]. -->

<!-- ## Undersampled food web -->

<!-- When it is difficult to obtain food web data, this can result in missing links in the food web thereby resulting in an undersampled food web. Limitations of resources and time can also lead to an undersampled food web because collecting and analysing gut content data is tedious and expensive task (citreqd). It is crucial to have well sampled food web because food web properties are highly sensitive to varying levels of sampling effort [@goldwasserSamplingEffectsEstimation1997]. So, it is important to predict food web properties with high accuracy and high precision. -->

<!-- ## What is a food web model and how can it be used to compensate for undersampling? -->

<!-- When we have an undersampled food web, food web models can be used to predict which trophic interactions are feasible and which are not [@allesinaGeneralModelFood2008; @cohenStochasticTheoryCommunity1985; @gravelInferringFoodWeb2013; @petcheySizeForagingFood2008; @tamaddoni-nezhadConstructionValidationFood2013]. Food web model are set of rules governed by ecological theory which defines trophic interactions in a food web. For example, @petcheySizeForagingFood2008 based on foraging traits allometrically scaled using body size data of species predicted trophic interactions where the model was parameterised using known presence and absence of trophic interactions. -->

<!-- ## Research question -->

<!-- How much gut content data is required when a food web model is used to predict trophic interactions? We are interested in maximizing the accuracy and precision of the predicted food web and simultaneously minimizing the amount of gut content data used, because we do not want to spend a lot of resources in sampling gut content data. -->

### 2021-11-15 manuscript/ms_C2/ms_C2.tex
All files
files

\documentclass{article}

\usepackage{arxiv}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{lmodern}        % https://github.com/rstudio/rticles/issues/343
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}
\usepackage{graphicx}

\title{Optimal amount of gut content data required to predict trophic
interactions using a food web model}

\author{
    Anubhav Gupta
    \thanks{Corresponding author}
   \\
    Department of Evolutionary Biology and Environmental Studies \\
    University of Zurich \\
  8057 Zurich, Switzerland \\
  \texttt{\href{mailto:anubhav.gupta@ieu.uzh.ch}{\nolinkurl{anubhav.gupta@ieu.uzh.ch}}} \\
   \And
    Eoin O' Gorman
   \\
    School of Life Sciences \\
    University of Essex \\
  CO4 3SQ Colchester, UK \\
  \texttt{\href{mailto:e.ogorman@essex.ac.uk}{\nolinkurl{e.ogorman@essex.ac.uk}}} \\
   \And
    Owen L. Petchey
   \\
    Department of Evolutionary Biology and Environmental Studies \\
    University of Zurich \\
  8057 Zurich, Switzerland \\
  \texttt{\href{mailto:owen.petchey@ieu.uzh.ch}{\nolinkurl{owen.petchey@ieu.uzh.ch}}} \\
  }

% Pandoc citation processing
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
% for Pandoc 2.8 to 2.10.1
\newenvironment{cslreferences}%
  {}%
  {\par}
% For Pandoc 2.11+
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for calculating minipage widths
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{lineno}
\linenumbers
\usepackage {amsmath}
\setlength\parindent{24pt}
\usepackage{setspace}\doublespacing

\begin{document}
\maketitle

\def\tightlist{}

\begin{abstract}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
\item
\item
\item
\end{enumerate}
\end{abstract}

\keywords{
    gut content data
   \and
    ADBM
   \and
    food web accuracy
   \and
    food web prediction
  }

\hypertarget{alternate-titles}{%
\section{Alternate titles}\label{alternate-titles}}

\begin{itemize}
\item
  Predicting trophic interactions using incomplete gut content data
\item
  Effect of the amount of gut content data on the accuracy and precision
  of food web prediction
\end{itemize}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Knowledge about the trophic interactions in a food web is crucial in
ecology from identifying keystone species (Jord'an 2009) to quantifying
robustness of a food web to species extinctions (Dunne, Williams, and
Martinez 2002). This has led to the development of numerous food web
models (Allesina, Alonso, and Pascual 2008; Cohen, Newman, and Steele
1985; Gravel et al. 2013; Petchey et al. 2008; Tamaddoni-Nezhad et al.
2013). Along with inferring missing links in an observed food web, the
food web models are also used for ecological forecasting (Hattab et al.
2016; Lindegren et al. 2010) and understanding the underlying mechanism
governing the interactions in a food web (O'NAGorman et al. 2019).

Although food web models are constructed using prior theory governing
the food webs, interaction data is required to parameterise a model. For
example, Petchey et al. (2008) used presence-absence information about
trophic interactions to parameterise the allometric diet breadth model
and thereby predict species interactions. These information can be
inferred from diverse set of methods such as gut content analysis
(Peralta-Maraver, Lopez-Rodriguez, and de Figueroa 2017), stable isotope
ratio analysis of tissues (Layman et al. 2007), experimentation (Warren
1989), DNA metabarcoding (Roslin and Majaneva 2016) and literature
research (Gray et al. 2015; Cohen and Mulder 2014; Goldwasser and
Roughgarden 1993). All of these methods can infer the diet of a
consumer, however different methods measure different consumed
components, thereby resulting in different levels of uncertainty in the
inferred diet (citreqd). A single gut content of a predator describes
what that individual has consumed recently which can be used to infer
the diet of the predator (Eitzinger et al. 2018; O'NAMalley et al. 2017;
Dixon et al. 2017; McClain-Counts, Demopoulos, and Ross 2017;
Peralta-Maraver, Lopez-Rodriguez, and de Figueroa 2017). Stable isotope
data when combined with mixing models can be used to determine which
prey items are most likely fed upon by a predator (Kadoya, Osada, and
Takimoto 2012; Crawford, Mcdonald, and Bearhop 2008).

Acquiring food web data from these methods is time consuming and
expensive (reference). For example, many gut content data needs to be
collected to infer the complete presence-absence information of a food
web structure with high accuracy and precision. Also further time and
resource investment is required to process the collected samples. Hence,
there is an utmost demand to know the minimum number of presence-absence
information of a food web to parameterise a food web model with high
accuracy and high precision, so that one knows when to stop collecting
any further data on the food web.

The key question we are interested in answering is how much
presence-absence information is required to infer food web structure
from a food web model with high accuracy and high precision. In other
words, in case of gut content data how many samples of gut content
should one collect from the field to parameterise a food web model? To
answer this question, we use the presence-absence information from gut
content data, and allometric diet breadth model (ADBM) to predict
trophic interactions. We parameterise the model using approximate
Bayesian computation/rejection Monte Carlo sampling.

\hypertarget{materials-and-methods}{%
\section{Materials and Methods}\label{materials-and-methods}}

In the upcoming sections, we present the allometric diet breadth model
(ADBM) and the gut content data used to infer trophic interactions. We
also give a detailed account of using partial gut content data to
parameterise the ADBM using approximate Bayesian computation (ABC). We
assessed model predictions using true skill statistic and various
structural food web properties for comparison across food webs.

\hypertarget{allometric-diet-breadth-model-adbm}{%
\subsection{Allometric Diet Breadth Model
(ADBM)}\label{allometric-diet-breadth-model-adbm}}

The allometric diet breadth model (ADBM) is based on optimal foraging
theory, specifically the contingency foraging model (MacArthur and
Pianka 1966). The ADBM predicts the set of prey species a consumer
should feed upon to maximise its rate of energy intake (Petchey et al.
2008). The foraging variables in the model: energy content of the
resources, handling times of the prey, space clearance rate and prey
densities are allometrically scaled to the body sizes of the species.

\hypertarget{broadstone-stream}{%
\subsection{Broadstone Stream}\label{broadstone-stream}}

Broadstone Stream (51\(^\circ\) 05' N 0\(^\circ\) 03' E; 120 m above
sea-level) is a second-order tributary of the River Medway in south-east
England. It is dominated by invertebrates as the acidity of the stream
(pH 4.7-6.6) excludes fish. The stream consists of 25 common
invertebrate species (Woodward, Speirs, and Hildrew 2005a). Among the
predators, the three large species are \emph{Cordulegaster boltonii}
Donovan, \emph{Sialis fuliginosa} Pict. and \emph{Plectrocnemia
conspersa} {[}Curtis{]} and the three small species are the larvae of
the tanypod midges \emph{Macropelopia nebulosa} {[}Meigen{]},
\emph{Trissopelopia longimana} {[}Staeger{]}, and \emph{Zavrelimyia
barbatipes} {[}Kieffer{]}. Broadstone Stream food web is one of the most
completely described food webs available for any system (J. M.
Schmid-Araya et al. 2002; Hildrew 2009; Layer et al. 2010; and Woodward,
Speirs, and Hildrew 2005b).

\hypertarget{celtic-sea}{%
\subsection{Celtic Sea}\label{celtic-sea}}

The Celtic Sea is an area of continental shelf bordered by Ireland, the
UK and the Bay of Biscay. Precise sampling locations and dates were not
given in the Barnes et al.~(2008) dataset, from where the data used in
this chapter were extracted, so we pooled data over the whole time
period and locations to capture general patterns. Only locations
consistently sampled through the 1987--2001 time series were used
(Blanchard et al., 2005).

The feeding links of fishes in the Celtic Sea have been described in a
published global dataset of individual predator and prey body sizes and
taxonomy (Barnes et al., 2008): in total, 1988 feeding events from 29
predator species were included in the food web presented here. The
original stomach contents data were collected from dissections carried
out on board research vessels during the annual surveys carried out by
the Centre for Environment, Fisheries and Aquaculture Science (Cefas)
(Pinnegar et al., 2003). Predator and prey length were recorded and
converted to body mass by Barnes et al.~(2008) using published
regression equations. Only vertebrate prey were identified and measured,
with the vast majority being identified to species.

\hypertarget{afon-hirnant}{%
\subsection{Afon Hirnant}\label{afon-hirnant}}

The Afon Hirnant is a tributary of the Welsh Dee in North Wales, U.K.
(52\(^\circ\) 52'N 03\(^\circ\) 34) with the study being conducted at
three sites. The pH within each site ranged from about 5.5 to 7 over the
course of the year.

A total of 180 invertebrate samples were collected for the whole
sampling periods. All individuals within the benthic samples were
counted and identified to the lowest possible taxonomic level (usually
species). Prey items were identified using a combination of taxonomic
keys and reference slides of previously identified species, after Jenny
M. Schmid-Araya et al. (2002); J. M. Schmid-Araya et al. (2002).

\hypertarget{tadnoll-brook}{%
\subsection{Tadnoll Brook}\label{tadnoll-brook}}

Description of Tadnoll Brook here

\hypertarget{coilaco}{%
\subsection{Coilaco}\label{coilaco}}

Description of Coilaco here

\hypertarget{guampoe}{%
\subsection{Guampoe}\label{guampoe}}

Description of Guampoe here

\hypertarget{trancura}{%
\subsection{Trancura}\label{trancura}}

Description of Trancura here

\hypertarget{food-web-construction}{%
\subsection{Food web construction}\label{food-web-construction}}

Presence and absence interactions of food web data can be aggregated in
different ways (Gilljam et al. 2011). A common way of aggregating food
web data is the taxonomic approach, where a species is defined as
predating on another if at least one prey species individual was found
in the gut of a predator species individual. Whereas in size-class food
web, a feeding link was assigned if at least one prey item within a size
class was found in the gut of a predator of another size class,
irrespective of their taxonomy. In our study, we aggregate the food web
on the basis of size class.

\hypertarget{assessment-of-prediction}{%
\subsection{Assessment of prediction}\label{assessment-of-prediction}}

The accuracy of the predicted diet of the predators was defined using
true skill statistic (TSS) which takes into account the true and false
predictions of both the presence and absence of links defined as:

\[ \text{TSS} = \frac{ad-bc}{(a+c)(b+d)} \] where \(a\) is the number of
observed links that are predicted by the model (true positives), \(d\)
is the number of observed absences of links that are correctly predicted
(true negatives), \(b\) is the number of false positives, and \(c\) is
the number of false negatives.

The \(TSS\) ranges from \(-1\) to \(1\), where +1 indicates a perfect
prediction. A \(TSS\) value of zero or less indicates a performance no
better than random (Allouche, Tsoar, and Kadmon 2006).

\hypertarget{inferring-food-web-using-partial-gut-content-data}{%
\subsection{Inferring food web using partial gut content
data}\label{inferring-food-web-using-partial-gut-content-data}}

From a pool of gut content data, we draw a set of gut content data
randomly. Then we used the rejection ABC to accept a parameter value
from a prior distribution which would have resulted in the minimum
distance, where distance = 1 - True skill statistic. The true skill
statistic was computed between the predators' diet predicted from the
ADBM, and that from the sampled gut content data. We repeated this
process for \(n~(= 100)\) number of times for every \(i\) number of
guts, where \(i\) lies between 1 and total number of gut content data in
the pool.

\emph{Input:}

\begin{itemize}
\item
  Predators \(P: P = \{p_1, p_2, \dots, p_k \}\)
\item
  A pool of gut content data \(G: G = \{g_1, g_2, \dots, g_n\}\), where
  \(g_{n}\) is a one-dimensional matrix containing ones and zeros.
\item
  A model prediction
  \(model(\theta): ADBM(\theta) = \{d_{p_1}, d_{p_1}, \dots, d_{p_k}\}\),
  where \(d_{p_k}\) is a one-dimensional diet matrix of predator \(k\)
  containing ones and zeros.
\item
  A summary statistic \(s(x): s(x) \subseteq model(\theta)\)
\item
  A distance function \(d(x_i, y) : d(x_i,y) = 1 - TSS(x_i, y)\)
\item
  An observed food web
  \(Y: Y = \{d_{p_1}', d_{p_1}', \dots, d_{p_k}'\}\)
\end{itemize}

\emph{Sampling:}

for \(i = 1, \dots, tgut\) where \(tgut\) is the total number of gut
content data in the pool \(G\)

\begin{itemize}
\item
  for \(j = 1, \dots, nsample\) where \(nsample\) is the number of
  independent samples to be drawn

  \begin{itemize}
  \item
    Draw a set of gut content data \(y = \{g_1, g_2, \dots, g_i\}\) from
    the pool of gut content data \(G\)
  \item
    for \(k = 1, \dots, npar\) where \(npar\) is the number of parameter
    values to be sampled

    \begin{itemize}
    \item
      Draw a set of parameter values \(\theta_k\) from the prior
      distribution \(\pi(\theta)\)
    \item
      Compute the model result \(x_i = model(\theta_k)\)
    \item
      Compute \(s(x_i)\) and \(d(s(x_i), y)\)
    \end{itemize}
  \item
    Accept \(\theta_j\), which results in the \(min_i\{d(s(x_i), y)\}\)
  \end{itemize}
\item
  Compute
  \(TSS_{i}(x, y) = \{TSS(x_i,y): x_i = ADBM(\theta_j), \theta_j \text{ computed from previous step}\}\)
  using the accepted \(\theta_1, \dots, \theta_{nsample}\)
\end{itemize}

\emph{Output:}

A prediction interval containing \(TSS\) between observed and predicted
food webs for every \(i\) number of gut content data drawn from the pool
of gut content data.

\hypertarget{results}{%
\section{Results}\label{results}}

We first present how the accuracy of the food web model vary in
predicting trophic interactions when we increase the amount the gut
content data provided to the food web model. Then, we calculate the
number of gut content data for each food webs corresponding to which the
accuracy results in 90\% of the maximum true skill statistics predicted
by the food web model. We also compute the goodness of the food web
model in predicting structural properties from incomplete gut content
data. We did that by computing mean standardised error in food web
properties.

\hypertarget{inferring-trophic-interactions-using-adbm-and-incomplete-gut-content-data}{%
\subsection{Inferring trophic interactions using ADBM and incomplete gut
content
data}\label{inferring-trophic-interactions-using-adbm-and-incomplete-gut-content-data}}

\begin{figure}

{\centering \includegraphics[width=500px]{../../results/misc/plot_TSS_ratio}

}

\caption{\label{fig:fig_ra} (a, c, e, g, i, k, m) Accuracy of the predicted food web measured using the true skill statistics, predicted by the ADBM parameterised using gut content data. Line and shaded grey region represents the mean and the prediction interval of 100 independent samples respectively. Red line represents the number of predator guts required to achieve a TSS of 95\% of the maximum TSS. (b, d, f, h, j, l, n) Ratio of the true skill statistic of the predicted food web by the ADBM parameterised using gut content data to that of the predicted food web constructed using gut content data only. The dashed line shows where the ratio is one for reference.}\label{fig:unnamed-chunk-2}
\end{figure}

The true skill statistics of the food webs predicted by the ADBM using
subsets of gut content data improved quickly for lower number of
predator guts (Fig. \ref{fig:fig_ra}) (a, c, e, g, i, k, m). The
prediction interval of the true skill statistics reduced with the
increasing number of predator guts with the mean TSS asymptoting to the
maximum mean TSS achieved by the ADBM when all the gut content data was
used. Although the maximum TSS varied among the food webs, the
qualitative increase in the TSS was the same.

For a low number of predator guts, the TSS of the model predicted food
web was higher compared to the TSS of the food web constructed from gut
content data (Fig. \ref{fig:fig_ra} (b, d, f, h, j, l, n)), recommending
when a model can be used to compensate for undersampled links. After a
certain increase in the number of predator guts, the ratio
TSS(Model)/TSS(data) reduced to less than one, and reduced further
gradually.

With only 381 number of gut content data which is 38\% of the total gut
content data, the ADBM predicted the food web with TSS of 0.74 which was
95\% of the mean TSS (0.78) achieved using complete gut content data by
the ADBM for Broadstone Stream food web (Fig. \ref{fig:fig_ra}(a)). In
the case of the Celtic Sea food web, only 171 gut content data was
required by the ADBM to predict food web with TSS equal to 95\% of the
mean TSS (0.68) achieved using complete gut content data by the ADBM
(Fig. \ref{fig:fig_ra}(c)).

\hypertarget{dependence-of-minimum-gut-content-data-on-number-of-species-links-and-connectance}{%
\subsection{Dependence of minimum gut content data on number of species,
links and
connectance}\label{dependence-of-minimum-gut-content-data-on-number-of-species-links-and-connectance}}

There seems to be a positive relationship between number of minimum gut
content data and number of species (S) (Fig. \ref{fig:fig_rb} (a)),
links (L) (Fig. \ref{fig:fig_rb} (c)), connectance (C) (Fig.
\ref{fig:fig_rb} (d)) and number of predator nodes (Fig.
\ref{fig:fig_rb} (e)), with Broadstone Stream being an outlier in Fig.
\ref{fig:fig_rb} (a, c, e). The number of minimum gut content data
increases with number of maximum gut content data sampled (Fig.
\ref{fig:fig_rb} (b)). There seems to be a negative relationship between
proportion of minimum gut (= Number of minimum gut / Number of maximum
guts sampled) and number of species (S) (Fig. \ref{fig:fig_rb} (f)),
links (L) (Fig. \ref{fig:fig_rb} (g)), connectance (C) (Fig.
\ref{fig:fig_rb} (h)).

\begin{figure}

{\centering \includegraphics[width=500px]{../../results/misc/plot_min_gut_vs_X}

}

\caption{\label{fig:fig_rb} (a, b, c, d, e) Number of minimum gut content data plotted against number of species (S), number of maximum guts sampled, number of links (L), connectance (C) and number of predator nodes respectively. (f, g, h) Proportion of minimum gut content data plotted against number of species (S), number of links (L) and connectance (C) respectively.}\label{fig:unnamed-chunk-3}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=500px]{../../results/misc/plot_empTSS_ngut}

}

\caption{\label{fig:fig_rc} True skill statistics of the food web constructed using gut content data plotted against number of gut content data.}\label{fig:unnamed-chunk-4}
\end{figure}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{why-broadstone-stream-is-an-outlier}{%
\subsection{Why Broadstone Stream is an
outlier?}\label{why-broadstone-stream-is-an-outlier}}

Broadstone Stream is the most sampled food web compared to all the other
food webs (Fig. \ref{fig:fig_rc}), which means the observed Broadstone
Stream food web might be more accurate compared to others.

\hypertarget{why-incomplete-gut-content-data-can-be-used-to-infer-trophic-interactions}{%
\subsection{Why incomplete gut content data can be used to infer trophic
interactions?}\label{why-incomplete-gut-content-data-can-be-used-to-infer-trophic-interactions}}

\begin{itemize}
\item
  Model fills up the missing interactions
\item
  Partial data helps to constrain the parameter space
\end{itemize}

\hypertarget{there-is-uncertainty-in-gut-content-data-and-needs-to-be-propagated-into-models-predictions}{%
\subsection{There is uncertainty in gut content data and needs to be
propagated into model's
predictions}\label{there-is-uncertainty-in-gut-content-data-and-needs-to-be-propagated-into-models-predictions}}

There is considerable uncertainty involved in gut content analysis
(Baker, Buckland, and Sheaves 2014) such as in fish's guts, there are
sometimes loose tissues that are not identifiable and cannot be assigned
to a specific prey item with certainty. There are factors such as sample
size of consumers, mechanical prey handling, differential digestion and
evacuation rates of different prey types and volumes, and the ingestion
order that in combination result in an unquantifiable error which is
difficult to interpret in the predator diet (Hyslop 1980; Rindorf and
Lewy 2004; Baker, Buckland, and Sheaves 2014). Therefore, a future
development would be to consider how this uncertainty is propagated into
food web prediction.

\hypertarget{comparing-our-study-with-other-studies-of-predicting-food-webs-using-incomplete-data}{%
\subsection{Comparing our study with other studies of predicting food
webs using incomplete
data}\label{comparing-our-study-with-other-studies-of-predicting-food-webs-using-incomplete-data}}

Some studies have presented how the accuracy of food web prediction
change when we vary the amount of food web data (Gray et al. 2015).

\hypertarget{what-is-the-generalisability-of-our-results}{%
\subsection{What is the generalisability of our
results?}\label{what-is-the-generalisability-of-our-results}}

\begin{itemize}
\tightlist
\item
  Dependent on how size structured a food web is, how the food web is
  aggregated, the type of interactions
\end{itemize}

\hypertarget{assumption-that-the-food-web-constructed-with-the-total-gut-content-data-is-the-true-food-web-and-how-can-this-be-improved}{%
\subsection{Assumption that the food web constructed with the total gut
content data is the true food web and how can this be
improved}\label{assumption-that-the-food-web-constructed-with-the-total-gut-content-data-is-the-true-food-web-and-how-can-this-be-improved}}

Our study is based on the assumption that the food web constructed using
the complete gut content data is the true food web. However, it might
not be the case as the links are still under-sampled for many nodes
(Woodward et al. 2010). This could result in a lower TSS of the
predicted food web from the model which can lead to a higher upper limit
on the amount of gut content data.

\hypertarget{limitation-of-the-model}{%
\subsection{Limitation of the model}\label{limitation-of-the-model}}

The maximum predictive power of a model is constrained by the rules it
is based on.

\hypertarget{how-can-we-include-other-food-web-data-type}{%
\subsection{How can we include other food web data
type?}\label{how-can-we-include-other-food-web-data-type}}

A future prospect would be to include other types of food web data

\begin{itemize}
\item
  experimentation (feeding trials)
\item
  DNA Metabarcoding
\end{itemize}

\hypertarget{extending-the-approach-to-other-food-web-models}{%
\subsection{Extending the approach to other food web
models}\label{extending-the-approach-to-other-food-web-models}}

\begin{itemize}
\tightlist
\item
  Current approach could be implemented with other food web models
\end{itemize}

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

\hypertarget{supplementary-information}{%
\section{Supplementary Information}\label{supplementary-information}}

\hypertarget{gut-content-data-simulation}{%
\subsection{Gut content data
simulation}\label{gut-content-data-simulation}}

We simulated a food web using the ADBM for a given set of parameters.
For a given set of predators, we subset the diet from the simulated food
web. Then using a probability mass function (distribution), we sampled
the gut content data from predators' diet thereby incorporating the
uncertainty in the gut content data. We repeated this process multiple
number of times for every predator in the food web.

\emph{Input:}

\begin{itemize}
\item
  Predators whose diet are to be simulated \(P = \{p_1, \dots, p_n\}\)
\item
  A simulated food web
  \(ADBM(\theta_i) = \{d_{p_1}, d_{p_1}, \dots, d_{p_k}\}\), where
  \(d_{p_k}\) is a one-dimensional diet matrix of predator \(k\)
  containing ones and zeros.
\item
  A function which describes uncertainty in the diet \(U(d)\)
\item
  Number of independent guts to be simulated for a predator
  \(p_i: ngut\)
\end{itemize}

\emph{Sampling:}

\begin{itemize}
\item
  for \(p_i \in P\)

  \begin{itemize}
  \item
    for \(j = 1, \dots, ngut\), where \(ngut\) is the number of guts to
    be simulated

    \begin{itemize}
    \tightlist
    \item
      Simulate a single gut of a predator
      \(p_i: g(p_i) = d_{p_i} * U(d_{p_i})\)
    \end{itemize}
  \item
    Set of gut of a predator
    \(p_i: G(p_i) = \{ g(p_i) : g(p_i) = d_{p_i}*U(d_{p_i}) \}\)
  \end{itemize}
\end{itemize}

\emph{Output:}

\begin{itemize}
\tightlist
\item
  We simulated a pool of gut content data which contains simulated gut
  content data \(G(p_i)\) for every predator \(p_i\)
\end{itemize}

\hypertarget{prediction-using-simulated-gut-content-data-from-a-simulated-food-web}{%
\subsection{Prediction using simulated gut content data from a simulated
food
web}\label{prediction-using-simulated-gut-content-data-from-a-simulated-food-web}}

\begin{figure}

{\centering \includegraphics[width=400px]{../fig/TSS_with_n_pred_prop_simulated}

}

\caption{\label{fig:fig_r0} True skill statistics between predicted food web and observed food web for a simulated small reef food web estimated for distinct predator guts in a sample. The observed simulated food web consists of 50 species and \dots links. The vertical bars correspond to the prediction intervals of the true skill statistics with filled circles representing the corresponding mean. A prediction interval of the TSS is formed using a set of 100 accepted TSS values using the ABC method.}\label{fig:fig_r0}
\end{figure}

The true skill statistics (TSS) between the predicted food web and
observed food web saturated with an increasing number of distinct
predator guts in a sample (Fig. \ref{fig:fig_r0}). The TSS of the
predicted food webs estimated using the complete individual gut data had
shorter prediction intervals resulting in less uncertainty, and higher
mean TSS than that using the partial individual gut data. The maximum
limit of the prediction interval of TSS estimated using the complete gut
data and the partial gut data were almost equal, with the minimum limit
of the prediction interval of TSS using partial gut data being lower
than that from the complete gut data. Eventually, the gap between the
mean TSS using the partial gut data and the complete gut data reduced
with an increasing number of distinct predator guts suggesting when we
have enough predator species' gut data, the achieved TSS was almost
constant and hence independent of the amount of gut data.

The maximum TSS estimated using the complete gut data was very close to
one and almost remained constant with an increasing number of different
predator species sampled. With the gut data sample of only five distinct
predator species, 95\% of the maximum mean TSS was achieved when
complete individual gut data was used, while the same was achieved with
15 predator species for partial gut data. This shows that one does not
need to know the gut data of all the species to predict the food web and
the accuracy is dependent on the completeness of an individual gut data.

\begin{figure}

{\centering \includegraphics[width=300px]{../fig/TSS_with_n_pred_prop}

}

\caption{\label{fig:fig_r3} True skill statistics between predicted food web and observed food web estimated for different number of distinct predator guts. The estimation is done for three sets of gut data: gut content data of predators whose body sizes are smaller than the mean body size, larger than the mean body size, and all the gut content data.}\label{fig:fig_r3}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=500px]{../../results/misc/TSS_model_vs_data}

}

\caption{\label{fig:fig_r31} True skill statistic between predicted food web using ADBM and incomplete gut content data, and observed food web against the true skill statistic between food web constructed using incomplete gut content data, and observed food web. Error bars represent prediction intervals of 100 independent samples. Dashed line is 1:1 line for reference.}\label{fig:fig_r31}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=500px]{../../results/misc/mse_model_vs_data}

}

\caption{\label{fig:fig_r32} Mean standardised error in structural properties in the food web predicted using ADBM and incomplete gut content data against structural properties in the predicted food web constructed using incomplete gut content data. Error bars represent prediction intervals of 100 independent samples. Dashed line is 1:1 line for reference.}\label{fig:fig_r32}
\end{figure}

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

\hypertarget{author-contributions}{%
\section{Author contributions}\label{author-contributions}}

\hypertarget{references}{%
\section{References}\label{references}}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-allesinaGeneralModelFood2008}{}%
Allesina, Stefano, David Alonso, and Mercedes Pascual. 2008. {``A
{General Model} for {Food Web Structure}.''} \emph{Science} 320 (5876):
658--61. \url{https://doi.org/10.1126/science.1156269}.

\leavevmode\hypertarget{ref-alloucheAssessingAccuracySpecies2006}{}%
Allouche, Omri, Asaf Tsoar, and Ronen Kadmon. 2006. {``Assessing the
Accuracy of Species Distribution Models: Prevalence, Kappa and the True
Skill Statistic ({TSS}).''} \emph{Journal of Applied Ecology} 43 (6):
1223--32. \url{https://doi.org/10.1111/j.1365-2664.2006.01214.x}.

\leavevmode\hypertarget{ref-bakerFishGutContent2014}{}%
Baker, Ronald, Amanda Buckland, and Marcus Sheaves. 2014. {``Fish Gut
Content Analysis: Robust Measures of Diet Composition.''} \emph{Fish and
Fisheries} 15 (1): 170--77. \url{https://doi.org/10.1111/faf.12026}.

\leavevmode\hypertarget{ref-cohenSoilInvertebratesChemistry2014}{}%
Cohen, Joel E., and Christian Mulder. 2014. {``Soil Invertebrates,
Chemistry, Weather, Human Management, and Edaphic Food Webs at 135 Sites
in {The Netherlands}: {SIZEWEB}.''} \emph{Ecology} 95 (2): 578--78.
\url{https://doi.org/10.1890/13-1337.1}.

\leavevmode\hypertarget{ref-cohenStochasticTheoryCommunity1985}{}%
Cohen, Joel E., C. M. Newman, and John Hyslop Steele. 1985. {``A
Stochastic Theory of Community Food Webs {I}. {Models} and Aggregated
Data.''} \emph{Proceedings of the Royal Society of London. Series B.
Biological Sciences} 224 (1237): 421--48.
\url{https://doi.org/10.1098/rspb.1985.0042}.

\leavevmode\hypertarget{ref-crawfordApplicationsStableIsotope2008}{}%
Crawford, Kerry, Robbie A. Mcdonald, and Stuart Bearhop. 2008.
{``Applications of Stable Isotope Techniques to the Ecology of
Mammals.''} \emph{Mammal Review} 38 (1): 87--107.
\url{https://doi.org/10.1111/j.1365-2907.2008.00120.x}.

\leavevmode\hypertarget{ref-dixonAssessingDietNorth2017}{}%
Dixon, Heather J., J. Brian Dempson, Timothy F. Sheehan, Mark D.
Renkawitz, and Michael Power. 2017. {``Assessing the Diet of {North
American Atlantic} Salmon ({Salmo} Salar {L}.) Off the {West Greenland}
Coast Using Gut Content and Stable Isotope Analyses.''} \emph{Fisheries
Oceanography} 26 (5): 555--68. \url{https://doi.org/10.1111/fog.12216}.

\leavevmode\hypertarget{ref-dunneNetworkStructureBiodiversity2002}{}%
Dunne, Jennifer A., Richard J. Williams, and Neo D. Martinez. 2002.
{``Network Structure and Biodiversity Loss in Food Webs: Robustness
Increases with Connectance.''} \emph{Ecology Letters} 5 (4): 558--67.
\url{https://doi.org/10.1046/j.1461-0248.2002.00354.x}.

\leavevmode\hypertarget{ref-eitzingerTestingValidityFunctional2018}{}%
Eitzinger, Bernhard, Björn C. Rall, Michael Traugott, and Stefan Scheu.
2018. {``Testing the Validity of Functional Response Models Using
Molecular Gut Content Analysis for Prey Choice in Soil Predators.''}
\emph{Oikos} 127 (7): 915--26. \url{https://doi.org/10.1111/oik.04885}.

\leavevmode\hypertarget{ref-gilljamSeeingDouble2011}{}%
Gilljam, David, Aaron Thierry, Francois K. Edwards, David Figueroa,
Anton T. Ibbotson, J. Iwan Jones, Rasmus B. Lauridsen, Owen L. Petchey,
Guy Woodward, and Bo Ebenman. 2011. {``Seeing {Double}:''} In
\emph{Advances in {Ecological Research}}, 45:67--133. {Elsevier}.
\url{https://doi.org/10.1016/B978-0-12-386475-8.00003-4}.

\leavevmode\hypertarget{ref-goldwasserConstructionAnalysisLarge1993a}{}%
Goldwasser, Lloyd, and Jonathan Roughgarden. 1993. {``Construction and
{Analysis} of a {Large Caribbean Food Web}.''} \emph{Ecology} 74 (4):
1216--33. \url{https://doi.org/10.2307/1940492}.

\leavevmode\hypertarget{ref-gravelInferringFoodWeb2013}{}%
Gravel, Dominique, Timoth'ee Poisot, Camille Albouy, Laure Velez, and
David Mouillot. 2013. {``Inferring Food Web Structure from Predator-Prey
Body Size Relationships.''} Edited by Robert Freckleton. \emph{Methods
in Ecology and Evolution} 4 (11): 1083--90.
\url{https://doi.org/10.1111/2041-210X.12103}.

\leavevmode\hypertarget{ref-grayJoiningDotsAutomated2015}{}%
Gray, Clare, David H. Figueroa, Lawrence N. Hudson, Athen Ma, Dan
Perkins, and Guy Woodward. 2015. {``Joining the Dots: {An} Automated
Method for Constructing Food Webs from Compendia of Published
Interactions.''} \emph{Food Webs} 5 (December): 11--20.
\url{https://doi.org/10.1016/j.fooweb.2015.09.001}.

\leavevmode\hypertarget{ref-hattabForecastingFinescaleChanges2016}{}%
Hattab, Tarek, Fabien Leprieur, Frida Ben Rais Lasram, Dominique Gravel,
François Le Loc'h, and Camille Albouy. 2016. {``Forecasting Fine-Scale
Changes in the Food-Web Structure of Coastal Marine Communities Under
Climate Change.''} \emph{Ecography} 39 (12): 1227--37.
\url{https://doi.org/10.1111/ecog.01937}.

\leavevmode\hypertarget{ref-hildrewChapterSustainedResearch2009}{}%
Hildrew, Alan G. 2009. {``Chapter 4 {Sustained Research} on {Stream
Communities}.''} In \emph{Advances in {Ecological Research}},
41:175--312. {Elsevier}.
\url{https://doi.org/10.1016/S0065-2504(09)00404-8}.

\leavevmode\hypertarget{ref-hyslopStomachContentsAnalysis1980}{}%
Hyslop, E. J. 1980. {``Stomach Contents Analysis---a Review of Methods
and Their Application.''} \emph{Journal of Fish Biology} 17 (4):
411--29. \url{https://doi.org/10.1111/j.1095-8649.1980.tb02775.x}.

\leavevmode\hypertarget{ref-jordanKeystoneSpeciesFood2009}{}%
Jord'an, Ferenc. 2009. {``Keystone Species and Food Webs.''}
\emph{Philosophical Transactions of the Royal Society B: Biological
Sciences} 364 (1524): 1733--41.
\url{https://doi.org/10.1098/rstb.2008.0335}.

\leavevmode\hypertarget{ref-kadoyaIsoWebBayesianIsotope2012}{}%
Kadoya, Taku, Yutaka Osada, and Gaku Takimoto. 2012. {``{IsoWeb}: {A
Bayesian Isotope Mixing Model} for {Diet Analysis} of the {Whole Food
Web}.''} Edited by Simon Thrush. \emph{PLoS ONE} 7 (7): e41057.
\url{https://doi.org/10.1371/journal.pone.0041057}.

\leavevmode\hypertarget{ref-layerFoodWebStructure2010}{}%
Layer, Katrin, Jens O. Riede, Alan G. Hildrew, and Guy Woodward. 2010.
{``Food {Web Structure} and {Stability} in 20 {Streams Across} a {Wide
pH Gradient}.''} In \emph{Advances in {Ecological Research}},
42:265--99. {Elsevier}.
\url{https://doi.org/10.1016/B978-0-12-381363-3.00005-8}.

\leavevmode\hypertarget{ref-laymanCanStableIsotope2007}{}%
Layman, Craig A., D. Albrey Arrington, Carmen G. Montaña, and David M.
Post. 2007. {``Can {Stable Isotope Ratios Provide} for {Community}-{Wide
Measures} of {Trophic Structure}?''} \emph{Ecology} 88 (1): 42--48.
\url{https://doi.org/10.1890/0012-9658(2007)88\%5B42:CSIRPF\%5D2.0.CO;2}.

\leavevmode\hypertarget{ref-lindegrenEcologicalForecastingClimate2010}{}%
Lindegren, Martin, Christian Möllmann, Anders Nielsen, Keith Brander,
Brian R. MacKenzie, and Nils Chr. Stenseth. 2010. {``Ecological
Forecasting Under Climate Change: The Case of {Baltic} Cod.''}
\emph{Proceedings of the Royal Society B: Biological Sciences} 277
(1691): 2121--30. \url{https://doi.org/10.1098/rspb.2010.0353}.

\leavevmode\hypertarget{ref-macarthurOptimalUsePatchy1966}{}%
MacArthur, Robert H., and Eric R. Pianka. 1966. {``On {Optimal Use} of a
{Patchy Environment}.''} \emph{The American Naturalist} 100 (916):
603--9. \url{http://www.jstor.org/stable/2459298}.

\leavevmode\hypertarget{ref-mcclain-countsTrophicStructureMesopelagic2017b}{}%
McClain-Counts, Jennifer P., Amanda W. J. Demopoulos, and Steve W. Ross.
2017. {``Trophic Structure of Mesopelagic Fishes in the {Gulf} of
{Mexico} Revealed by Gut Content and Stable Isotope Analyses.''} Journal
Article. \emph{Marine Ecology} 38 (4).
\url{https://doi.org/10.1111/maec.12449}.

\leavevmode\hypertarget{ref-ogormanSimpleModelPredicts2019}{}%
O'NAGorman, Eoin J., Owen L. Petchey, Katy J. Faulkner, Bruno Gallo,
Timothy A. C. Gordon, Joana Neto-Cerejeira, J'on S. 'Olafsson, Doris E.
Pichler, Murray S. A. Thompson, and Guy Woodwar. 2019. {``A Simple Model
Predicts How Warming Simplifies Wild Food Webs.''} \emph{Nature Climate
Change} 9 (8, 8): 611--16.
\url{https://doi.org/10.1038/s41558-019-0513-x}.

\leavevmode\hypertarget{ref-omalleyEffectsFoodWeb2017}{}%
O'NAMalley, Brian P., Lars G. Rudstam, James M. Watkins, Toby J. Holda,
and Brian C. Weide. 2017. {``Effects of Food Web Changes on {Mysis}
Diluviana Diet in {Lake Ontario}.''} \emph{Journal of Great Lakes
Research}, Special {section} on {Lake Ontario CSMI} 2013, 43 (5):
813--22. \url{https://doi.org/10.1016/j.jglr.2017.02.003}.

\leavevmode\hypertarget{ref-peralta-maraverStructureDynamicsStability2017}{}%
Peralta-Maraver, I., M. J. Lopez-Rodriguez, and J. M. Tierno de
Figueroa. 2017. {``Structure, Dynamics and Stability of a
{Mediterranean} River Food Web.''} \emph{Marine and Freshwater Research}
68 (3): 484--95. \url{https://doi.org/10.1071/MF15154}.

\leavevmode\hypertarget{ref-petcheySizeForagingFood2008}{}%
Petchey, Owen L., Andrew P. Beckerman, Jens O. Riede, and Philip H.
Warren. 2008. {``Size, Foraging, and Food Web Structure.''}
\emph{Proceedings of the National Academy of Sciences} 105: 4191--96.
\url{https://doi.org/10.1073/pnas.0710672105}.

\leavevmode\hypertarget{ref-rindorfBiasEstimatingFood2004}{}%
Rindorf, A, and P Lewy. 2004. {``Bias in Estimating Food Consumption of
Fish by Stomach-Content Analysis''} 61: 12.

\leavevmode\hypertarget{ref-roslinUseDNABarcodes2016}{}%
Roslin, Tomas, and Sanna Majaneva. 2016. {``The Use of {DNA} Barcodes in
Food Web Construction---Terrestrial and Aquatic Ecologists Unite!''}
Edited by Elizabeth Clare. \emph{Genome} 59 (9): 603--28.
\url{https://doi.org/10.1139/gen-2015-0229}.

\leavevmode\hypertarget{ref-schmid-arayaImportanceMeiofaunaFood2002}{}%
Schmid-Araya, J. M., A. G. Hildrew, A. Robertson, P. E. Schmid, and J.
Winterbottom. 2002. {``The {Importance} of {Meiofauna} in {Food Webs}:
{Evidence} from an {Acid Stream}.''} \emph{Ecology} 83 (5): 1271--85.
\url{https://doi.org/10.1890/0012-9658(2002)083\%5B1271:TIOMIF\%5D2.0.CO;2}.

\leavevmode\hypertarget{ref-schmid-arayaConnectanceStreamFood2002}{}%
Schmid-Araya, Jenny M., Peter E. Schmid, Anne Robertson, Julie
Winterbottom, Charlotte Gjerløv, and Alan G. Hildrew. 2002.
{``Connectance in {Stream Food Webs}.''} \emph{Journal of Animal
Ecology} 71 (6): 1056--62. \url{http://www.jstor.org/stable/1555780}.

\leavevmode\hypertarget{ref-tamaddoni-nezhadConstructionValidationFood2013}{}%
Tamaddoni-Nezhad, Alireza, Ghazal Afroozi Milani, Alan Raybould, Stephen
Muggleton, and David A. Bohan. 2013. {``Construction and {Validation} of
{Food Webs Using Logic}-{Based Machine Learning} and {Text Mining}.''}
In \emph{Advances in {Ecological Research}}, 49:225--89. {Elsevier}.
\url{https://doi.org/10.1016/B978-0-12-420002-9.00004-4}.

\leavevmode\hypertarget{ref-warrenSpatialTemporalVariation1989}{}%
Warren, Philip H. 1989. {``Spatial and {Temporal Variation} in the
{Structure} of a {Freshwater Food Web}.''} \emph{Oikos} 55 (3): 299.
\url{https://doi.org/10.2307/3565588}.

\leavevmode\hypertarget{ref-woodwardIndividualBasedFoodWebs2010}{}%
Woodward, Guy, Julia Blanchard, Rasmus B. Lauridsen, Francois K.
Edwards, J. Iwan Jones, David Figueroa, Philip H. Warren, and Owen L.
Petchey. 2010. {``Individual-{Based Food Webs}.''} In \emph{Advances in
{Ecological Research}}, 43:211--66. {Elsevier}.
\url{https://doi.org/10.1016/B978-0-12-385005-8.00006-X}.

\leavevmode\hypertarget{ref-woodwardQuantificationResolutionComplex2005}{}%
Woodward, Guy, Dougie C. Speirs, and Alan G. Hildrew. 2005a.
{``Quantification and {Resolution} of a {Complex}, {Size}-{Structured
Food Web}.''} In \emph{Advances in {Ecological Research}}, 36:85--135.
{Elsevier}. \url{https://doi.org/10.1016/S0065-2504(05)36002-8}.

\leavevmode\hypertarget{ref-woodwardQuantificationResolutionComplex2005a}{}%
---------. 2005b. {``Quantification and {Resolution} of a {Complex},
{Size}-{Structured Food Web}.''} In \emph{Advances in {Ecological
Research}}, 36:85--135. {Elsevier}.
\url{https://doi.org/10.1016/S0065-2504(05)36002-8}.

\end{CSLReferences}

\bibliographystyle{unsrt}
\bibliography{bibliography.bib}

\end{document}

### 2021-11-15 R/ADBM_Get.web.R

@@ -1,0 +1,88 @@
+Get.web <- function(EHL, energy.intake=F){
+
+  S <- length(EHL[[1]])
+  
+  web <- matrix(0, S, S)
+  overall.energy <- numeric(S)
+  per.species.energy <- matrix(0, S, S)
+  
+  ## in matrix P, columns are cosumers and contain profit of that consumer
+  ## feeding on each prey (row)
+  P <- EHL[[1]]/EHL[[2]]
+  
+  ## split code depending on whether encounter rates are predator specific or not
+  if(is.matrix(EHL[[3]])){
+    for(j in 1:S){
+      
+      p <- P[,j]
+      
+      if(sum(p>0)==1)
+        web[which(p>0),j] <- 1
+      
+      if(sum(p>0)>1){
+        
+        ## ordering of p required
+        
+        order.by.p <- order(p, decreasing=T)
+        p <- p[order.by.p]
+        Lj <- EHL[[3]][,j][order.by.p]
+        hj <- EHL[[2]][,j][order.by.p]
+        Ej <- EHL[[1]][order.by.p]
+        
+        cumulative.profit <- cumsum(Ej * Lj) / (1 + cumsum( Lj * hj))
+        
+        dj <- max(which(cumulative.profit==max(cumulative.profit)))
+        
+        web[,j] <- c(rep(1, dj), rep(0, S-dj))[order(order.by.p)]
+        
+        overall.energy[j] <- cumulative.profit[dj]
+        
+        energies <- c(Ej * Lj)[1:sum(web[,j])] / (1 + cumsum( Lj * hj)[sum(web[,j])]) 
+        all.energies <- c(energies, rep(0, S-length(energies)))
+        
+        per.species.energy[,j] <- all.energies[order(order.by.p)]
+        
+      }
+    }
+  }
+  
+  ## This if encounter rates are not predator specific
+  if(is.vector(EHL[[3]])){
+    for(j in 1:S){
+      
+      if(sum(p>0)==1)
+        web[which(p>0),j] <- 1
+      
+      if(sum(p>0)>1){
+        
+        ## ordering of p required
+        p <- P[,j]
+        order.by.p <- order(p, decreasing=T)
+        p <- p[order.by.p]
+        Lj <- EHL[[3]][order.by.p]
+        hj <- EHL[[2]][,j][order.by.p]
+        Ej <- EHL[[1]][order.by.p]
+        
[…]

### 2021-11-15 R/ADBM_Ratio.allometric.EHL.R

@@ -1,0 +1,44 @@
+## This function takes the model parameters and 
+## body masses, and returns the
+## vector of energies E
+## matrix of handling times H
+## and matrix of encounter rates L
+Ratio.allometric.EHL <- function(M,
+                                 e,
+                                 r.a, r.b,
+                                 a, ai, aj,
+                                 n, ni=-3/4){
+  
+  ## The handling time function
+  get.h <- function(Mi, Mj, r.a, r.b)
+    ifelse((r.b-Mi/Mj)>0,
+           r.a/(r.b-Mi/Mj),
+           Inf)
+  
+  
+  ## in matrix H resources are rows and consumers are columns
+  if(!r.b==0)
+    H <- outer(M, M, get.h, r.a, r.b)
+  if(r.b==0)
+    H = matrix(r.a, length(M),length(M))
+  
+  
+  ## ENCOUNTER RATES: consumer - resource mass specific encounter rates
+  get.a <- function(Mi, Mj,
+                    a, ai, aj)
+    a * Mi^ai * Mj^aj
+  A <- outer(M, M, get.a,
+             a=a, ai=ai, aj=aj)
+  L <- A* n*M^ni
+  
+  ## Check if body sizes are sorted, as they need to be
+  if(sum(order(M)==1:length(M))!=length(M))
+    stop("Body sizes not sorted")
+  
+  ## energy values
+  E <- e*M
+  
+  ## object to return
+  list(E=E, H=H, L=L)
+  
+}

### 2021-11-15 R/ADBM_ratio.power.R

@@ -1,0 +1,51 @@
+## the function that takes the parameters to optimise in opt and
+## returns the web
+ratio.power <- function(opt, x){
+
+  a = as.numeric(opt["a"])
+  ai = as.numeric(opt["ai"])
+  aj = as.numeric(opt["aj"])
+  r.b = as.numeric(opt["r.b"])
+  
+  e=x[["e"]]
+  n=x[["n"]]
+  ni=x[["ni"]]
+  r.a=x[["r.a"]]
+  M=x[["M"]]
+  S=x[["S"]]
+  real.web <- x[["real.web"]]
+  
+  EHL <- Ratio.allometric.EHL(M=M,
+                              e=e,
+                              a=a, ai=ai, aj=aj,
+                              n=n, ni=ni,
+                              r.a=r.a, r.b=r.b)
+  
+  web <- Get.web(EHL)
+  return(web)
+}
+
+ratio.power_exp <- function(opt, x){
+  
+  a = 10^as.numeric(opt["a"])
+  ai = as.numeric(opt["ai"])
+  aj = as.numeric(opt["aj"])
+  r.b = 10^as.numeric(opt["r.b"])
+  
+  e=x[["e"]]
+  n=x[["n"]]
+  ni=x[["ni"]]
+  r.a=x[["r.a"]]
+  M=x[["M"]]
+  S=x[["S"]]
+  real.web <- x[["real.web"]]
+  
+  EHL <- Ratio.allometric.EHL(M=M,
+                              e=e,
+                              a=a, ai=ai, aj=aj,
+                              n=n, ni=ni,
+                              r.a=r.a, r.b=r.b)
+  
+  web <- Get.web(EHL)
+  return(web)
+}

### 2021-11-15 R/Plot.matrix_uncertainty.r

@@ -1,0 +1,316 @@
+# #plots the predation matrix 
+# 
+# Plot.matrix_uncertainty <- function(web, title=" ", point.cex=0.5, trait.cex=1,
+#                         diag.line=T, traits=F, by.consumer=T, axes.labels=T, sp.pt.ch=NA,
+#                         nsim){
+#   colfunc <- colorRampPalette(c("red", "white", "blue"))
+#   user_pal <- c("#a6611a", "#dfc27d", "#f5f5f5", "#80cdc1", "#018571")
+#   palette <- "Green-Brown"
+#   n_col <- nsim
+#   h_col <- diverge_hcl(n = n_col, palette = palette)
+#   
+#   S <- length(web[,1])
+# 
+#   ##point.cex <- 30/30
+#   ##trait.cex <- 30/30
+#   
+#   dimnames(web) <- list(1:S, 1:S)
+#   consumer <- rep(1:S, each=S)
+#   resource <- rep(1:S, S)
+#   web.list <- Matrix.to.list_uncertainty(web)
+#   par(xpd=T)
+#   par(mar = c(8, 8, 10, 8))
+#   par(fig=c(0,3,0,4)/4)
+#   plot(consumer, resource, pch=19, type="n", cex=0.1,
+#        ann=F, axes=F,
+#        xlim=c(1, S), ylim=c(1, S))
+#   if(diag.line==T)
+#     lines(1:S, S:1, lty="dashed", col = "black", lwd = 4)
+#   
+#   if(length(traits)==1)
+#   index <- as.numeric(web.list[,3])
+#   # index <- ceiling(index/(nsim/n_col))
+#   points(web.list[,2], (S+1-as.numeric(web.list[,1])),
+#          type="p", pch=19, cex=4,
+#          col = h_col[index], lwd = 4)
+#   
+#   par(xpd=F)
+#   mtext(side=3, text=title, line=6.2, cex=4.0, family="Comic Sans MS")
+#   if(axes.labels){
+#     mtext(side=2, "Resource", line=3.0, cex=3, family="Comic Sans MS")
+#     mtext(side=2, "<--- Increasing bodysize ---<", line=1.0, cex=1.5, family="Comic Sans MS")
+#     mtext(side=3, "Consumer", line=3.0, cex=3, family="Comic Sans MS")
+#     mtext(side=3, ">--- Increasing bodysize --->", line=1.0, cex=1.5, family="Comic Sans MS")
+#   }
+# 
+#   
+#   # ## Plots the legend for the matrix
[…]

### 2021-11-15 R/abundance.R

@@ -1,0 +1,4 @@
+abundance <- function(n, M, ni){
+  abund <- n*M^ni
+  return(abund)
+}

### 2021-11-15 R/after_burn.R

@@ -1,0 +1,4 @@
+after_burn <- function(posterior){
+  lt <- dim(posterior)[1]
+  return(posterior[(lt/2):lt,])
+}

### 2021-11-15 R/display_info.R

@@ -1,0 +1,60 @@
+#prints info about no. of simulations and acceptance in an output file
+ 
+display_info_rej <- function(prop_acc_sim, time, dirnam, ncores){
+  
+  time_elapsed = round((as.numeric(time$toc)-as.numeric(time$tic))/60,3)
+    
+  pdf(paste(c(dirnam,'/',"display_info_rejection.pdf"), collapse = ''),width=5,height=5)
+  a1 <- paste(c("Proportion of accepted simulations = ", prop_acc_sim), collapse = '')
+  a2 <- paste(c("Time elapsed = ", time_elapsed, " min"), collapse = '')
+  a3 <- paste(c("No. of cores = ", ncores), collapse = '')
+  
+  plot(NA, xlim=c(0,20), ylim=c(0,5), bty='n',xaxt='n', yaxt='n', xlab='', ylab='')
+  text(1,3,a1, pos=4)
+  text(1,2,a2, pos=4)
+  text(1,1,a3, pos=4)
+  points(rep(1,3),1:3, pch=15)
+  dev.off()
+}
+
+
+display_info_mcmc <- function(prop_acc_sim = prop_acc_sim, time = time, dirnam = dirnam){
+  
+  time_elapsed = round((as.numeric(time$toc)-as.numeric(time$tic))/60,3)
+  
+  pdf(paste(c(dirnam,'/',"display_info.pdf"), collapse = ''),width=5,height=5)
+  a1 <- paste(c("Number of jumps = ", prop_acc_sim), collapse = '')
+  a2 <- paste(c("Time elapsed = ", time_elapsed, " min"), collapse = '')
+  
+  plot(NA, xlim=c(0,20), ylim=c(0,5), bty='n',xaxt='n', yaxt='n', xlab='', ylab='')
+  text(1,2,a1, pos=4)
+  text(1,1,a2, pos=4)
+  points(rep(1,2),1:2, pch=15)
+  dev.off()
+}
+
+
+display_info_smc <- function(time = time, dirnam = dirnam){
+  
+  time_elapsed = round((as.numeric(time$toc)-as.numeric(time$tic))/60,3)
+  
+  pdf(paste(c(dirnam,'/',"display_info.pdf"), collapse = ''),width=5,height=5)
+  a1 <- paste(c("Time elapsed = ", time_elapsed, " min"), collapse = '')
+  
[…]

### 2021-11-15 R/dist_ACC.R

@@ -1,0 +1,146 @@
+dist_ACC <- function(ss_sim, ss_real){
+  TP <- sum(ss_sim==ss_real & ss_real==1)
+  TN <- sum(ss_sim==ss_real & ss_real==0)
+  P <- sum(ss_real==1)
+  N <- sum(ss_real==0)
+  
+  acc <- (TP+TN)/(P+N)
+  dist_ACC_r <- 1-acc
+  
+  return(dist_ACC_r)
+  
+}
+
+dist_alphaACC <- function(ss_sim, ss_real){
+  TP <- sum(ss_sim==ss_real & ss_real==1)
+  TN <- sum(ss_sim==ss_real & ss_real==0)
+  P <- sum(ss_real==1)
+  N <- sum(ss_real==0)
+  alpha <- 1
+  acc <- alpha*(TP/P) + (1-alpha)*(TN/N)
+  dist_alphaACC_r <- 1-acc
+  
+  return(dist_alphaACC_r)
+}
+
+
+dist_connectance_ACC <- function(ss_sim, ss_real){
+  if(dist_connectance(ss_sim, ss_real) <= 0.01){
+    dist_connectance_ACC_r <- dist_ACC(ss_sim, ss_real)
+  }
+  else dist_connectance_ACC_r <- 100
+  
+  return(dist_connectance_ACC_r)
+}
+
+dist_TSS_old <- function(ss_sim, ss_real){
+  a <- sum(ss_sim==ss_real & ss_real==1)
+  c <- sum(ss_real==1)-a
+  d <- sum(ss_sim==ss_real & ss_real==0)
+  b <- sum(ss_real==0)-d
+  TSS_func <- (a*d-b*c)/((a+c)*(b+d))
+  dist_TSS_r <- 1-TSS_func
+  if(is.nan(dist_TSS_r)==TRUE){dist_TSS_r <- 1000}
+  
+  return(dist_TSS_r)
+}
+
+dist_TSS <- function(ss_sim, ss_real){
+  a <- sum(ss_sim==1 & ss_real==1)
+  b <- sum(ss_sim==1 & ss_real==0)
+  c <- sum(ss_sim==0 & ss_real==1)
+  d <- sum(ss_sim==0 & ss_real==0)
+  
+  TSS_func <- (a*d-b*c)/((a+c)*(b+d))
+  dist_TSS_r <- 1-TSS_func
+  if(is.nan(dist_TSS_r)==TRUE){dist_TSS_r <- 1000}
+  
+  return(dist_TSS_r)
+}
[…]

### 2021-11-15 R/encounter_rate.R

@@ -1,0 +1,3 @@
+encounter_rate <- function(abundance, space_clearance_rate){
+  ecr <- abundance*space_clearance_rate
+}

### 2021-11-15 R/foodweb_mat.R

@@ -1,0 +1,35 @@
+foodweb_mat <- function(parameters, foodweb){
+  
+  n_length <- length(parameters$a)
+  n_species <- length(M)
+  avg_att_rate_list<- numeric(n_length)
+  other <- ADBM_core_par(foodweb = foodweb)
+  M <- other$M
+  for(i in 1:n_length){
+    a=parameters$a[i]
+    ai=parameters$ai[i]
+    aj=parameters$aj[i]
+    r.b=parameters$r.b[i]
+    
+    best.EHL <- Ratio.allometric.EHL(M=M,
+                                     e=other$e,
+                                     a=a, ai = ai, aj=aj,
+                                     n=other$n, ni=other$ni,
+                                     r.a=other$r.a, r.b=r.b)
+    best.web <- Get.web(best.EHL, energy.intake = F)
+    
+    att_rate_mat <- matrix(nrow = n_species, ncol = n_species)
+    
+    for(j in 1:n_species){
+      for(k in 1:n_species){
+        att_rate_mat[j,k] <- a*M[j]^(ai)*M[k]^(aj)
+      }
+    }
+    feas_att_rate <- att_rate_mat
+    avg_att_rate <- mean(feas_att_rate)
+    avg_att_rate_list[i] <- avg_att_rate
+  }
+  
+  return(avg_att_rate_list)
+}
+

### 2021-11-15 R/foodweb_prop_v2.R

@@ -1,0 +1,181 @@
+#21.10.2020
+#The proportion of basal, intermediate and top species have been computed using a different function
+
+fw_prop_v2 <- function(foodweb, other, all.web.info){
+  parameters <- foodweb$post_dists
+  M <- all.web.info$species.sizes
+  title <- all.web.info$web.name
+  # fw_prop <- data.frame(prop_basal = double(), prop_inter = double(), prop_top = double(),
+  #                       prop_herb = double(), mean_trop_lvl = double(), max_trop_lvl = double(),
+  #                       mean_omn = double(), clus_coeff = double(), sd_gen = double(),
+  #                       sd_vulner = double(), diet_sim = double(), mean_path_lt = double(),
+  #                       prop.1.corr = double(), prop.0.corr = double(), nest_prop = double())
+  
+  best.EHL1 <- Ratio.allometric.EHL(M=M,
+                                    e=other$e,
+                                    a=10^parameters$a[1], ai=parameters$ai[1], aj=parameters$aj[1],
+                                    n=other$n, ni=other$ni,
+                                    r.a=other$r.a, r.b=10^parameters$r.b[1])
+  best.web1 <- Get.web(best.EHL1)
+  community <- mat.to.comm(best.web1, title)
+  
+  prop.1.corr <- round(sum(best.web1==1 & all.web.info$predation.matrix==1)/sum(all.web.info$predation.matrix), 2)
+  prop.0.corr <- round(sum(best.web1==0 & all.web.info$predation.matrix==0)/
+                         (dim(all.web.info$predation.matrix)[1]^2-sum(all.web.info$predation.matrix)), 2)
+  
+  connectance <- sum(best.web1)/(dim(best.web1)[1]^2)
+  prop_species <- prop_basal_inter_top_herb(pred_mat = best.web1)
+  prop_basal <- prop_species$prop_basal
+  prop_inter <- prop_species$prop_inter
+  prop_top <- prop_species$prop_top
+  n_singleton <- prop_species$n_singleton
+  # without_basal <- RemoveNodes(community, BasalNodes(community))
+  prop_herb <- prop_species$prop_herb
+  
+  # mtl <- try(mean(ShortWeightedTrophicLevel(community)))
+  # mean_trop_lvl <- if(is.numeric(mtl)==TRUE) mtl else -999
[…]

### 2021-11-15 R/give_web.R

@@ -1,0 +1,12 @@
+give_web <- function(par, other_par){
+  
+  best.EHL <- Ratio.allometric.EHL(M=other_par$M,
+                                    e=other_par$e,
+                                    a=10^par$a, ai=par$ai, aj=par$aj,
+                                    n=other_par$n, ni=other_par$ni,
+                                    r.a=other_par$r.a, r.b=10^par$r.b)
+  best.web <- Get.web(best.EHL)
+  
+  return(best.web)
+}
+

### 2021-11-15 R/gut_contents.R

@@ -1,0 +1,139 @@
+## Returns diet of a species as per a rule.
+## Rule: probability of a presence of a prey in the gut of a predator is directly proportional to the body size of the prey
+
+set.seed(1)
+
+pbly_r1 <- function(diet_breadth, M){
+  pbly_temp <- (M*diet_breadth)/sum(M*diet_breadth)
+  return(pbly_temp)
+}
+
+pbly_r2 <- function(diet_breadth, M){
+  pbly_temp <- diet_breadth/sum(diet_breadth)
+  return(pbly_temp)
+}
+
+
+diet <- function(diet_breadth, M, pbly_f){
+  pbly <- pbly_f(diet_breadth, M)
+  nspecies <- length(diet_breadth)
+  species_index <- 1:nspecies
+  diet_temp <- numeric(nspecies)
+  n_diet <- sum(diet_breadth)
+  if(sum(diet_breadth)!=0){
+    diet_index <- sample(species_index, size = n_diet, replace = TRUE, prob = pbly)
+    diet_temp[diet_index] <- rep(1, length(diet_index))
+  }
+  
+  return(diet_temp)
+}
+
+
+
+gut_matrix <- function(pred_mat, M, pbly_f){
+  nspecies <- length(M)
+  diet_mat <- matrix(data = rep(0, nspecies^2), nrow = nspecies, ncol = nspecies)
+  for(i in 1:nspecies){
+    diet_mat[,i] <- diet(pred_mat[,i], M, pbly_f)
+  }
+  
+  return(diet_mat)
+}
+
+diet_r3 <- function(diet_breadth){
+  if(sum(diet_breadth) !=0 ){
+    smallest_prey_index <- min(which(diet_breadth == 1))
+    largest_prey_index <- max(which(diet_breadth == 1))
+    diet_temp <- numeric(length(diet_breadth))
+    diet_temp[c(smallest_prey_index, largest_prey_index)] =  c(1,1)
+  }
+  else{
+    diet_temp <- diet_breadth
+  }
+  return(diet_temp)
+}
+
+gut_matrix_r3 <- function(pred_mat){
+  nspecies <- dim(pred_mat)[1]
+  diet_mat <- matrix(data = rep(0, nspecies^2), nrow = nspecies, ncol = nspecies)
[…]

### 2021-11-15 R/gut_data_partial.R

@@ -1,0 +1,46 @@
+#this samples 'propn' amount of links from the predation matrix 'gut_mat'
+gut_data_partial <- function(gut_mat, propn){
+  
+  L <- sum(gut_mat)
+  S <- dim(gut_mat)[1]
+  C <- L/S^2
+  
+  n <- as.integer(propn*L)
+  ind <- which(gut_mat == 1)
+  sel_ind <- sample(ind, n)
+  
+  gut_mat_partial <- matrix(0, nrow = S, ncol = S)
+  gut_mat_partial[sel_ind] <- 1
+  
+  return(gut_mat_partial)
+}
+
+
+#this returns the diet breadth of n number of predators through sampling
+gut_data_pred_index <- function(pred_index, n){
+  samp_ind <- sample(pred_index, n)
+  
+  return(samp_ind)
+}
+
+
+#this samples 'propn_diet' amount of diets from the predation matrix 'gut mat' and 'propn_links' number of links
+#from the diet breadth
+
+gut_data_partial_1 <- function(gut_mat, propn_diet, propn_links){
+  
+  L <- sum(gut_mat)
+  S <- dim(gut_mat)[1]
+  C <- L/S^2
+  
+  n <- as.integer(propn_diet*L)
+  ind <- which(gut_mat == 1)
+  sel_ind <- sample(ind, n)
+  
+  gut_mat_partial <- matrix(0, nrow = S, ncol = S)
+  gut_mat_partial[sel_ind] <- 1
+  
+  
+  
+  return(gut_mat_partial)
+}

### 2021-11-15 R/input_parameters.R

@@ -1,0 +1,14 @@
+## Other parameters
+input_parameters <- function(){
+  return(data.frame(tol = 2,
+                    N = 1e5,
+                    n_cores = 5))
+}
+
+
+
+epsilon_t <- function(){
+  final_tol <- input_parameters()$tol
+  return(seq(0.9, final_tol, length = 5))
+}
+

### 2021-11-15 R/lag_mcmc.R

@@ -1,0 +1,29 @@
+lag_mcmc <- function(par){
+  
+  flag = 0
+  lag_ind <- 500
+  while(flag != 1){
+    cor_res_acf <- acf(par, lag.max = lag_ind)$acf
+    mat <- cor_res_acf <= 0.05
+    cor_a <- mat[,1,1]
+    cor_ai <- mat[,2,2]
+    cor_aj <- mat[,3,3]
+    cor_r.b <- mat[,4,4]
+    
+    if(min(sum(cor_a), sum(cor_ai), sum(cor_aj), sum(cor_r.b)) > 0){
+      flag = 1
+      ind_cor_a <- which.max(cor_a)
+      ind_cor_ai <- which.max(cor_ai)
+      ind_cor_aj <- which.max(cor_aj)
+      ind_cor_r.b <- which.max(cor_r.b)
+      
+      lagg <- max(ind_cor_a, ind_cor_ai, ind_cor_aj, ind_cor_r.b)
+    }
+    else{
+      lag_ind <- lag_ind + 100
+    }
+  }
+  
+  return(lagg)
+  
+}

### 2021-11-15 R/mcmc.R

@@ -1,0 +1,95 @@
+mcmc <- function(all.web.info, model = ratio.power, model_core_par = ADBM_core_par,
+                 model_prior_par= ADBM_prior_par, input_parameters,dist_ss,
+                 prior_dist_x, prior_dist_pbly, proposal_dist_pbly,
+                 proposal_dist_x, ADBM_par_sd)
+{
+  M <- all.web.info$species.sizes    #body size
+  tol <- input_parameters$tol
+  N <- input_parameters$N
+  n_cores <- input_parameters$n_cores
+
+  
+  registerDoParallel(cores=n_cores)
+  
+  ss_real <- model_core_par$real.web
+  
+  post_dists <- data.frame(a=double(), ai=double(), aj=double(), r.b=double())
+  
+  acc_ss <- numeric(N)
+  dist <- numeric(N)
+  qnty <- numeric(N)
+  
+  final_list <- list()
+  res_pcores <- foreach(i = 1:n_cores) %dopar%{
+    ## Initialise:
+    set.seed(i*9)
+    Kh <- 0
+    K <- weights(0, tol, "epanechnikov")
+    while(Kh<=0){
+      local_par <- prior_dist_x(par=model_prior_par, no=1)
+      ss_sim <- model(opt=local_par, x=model_core_par)
+      dist_temp <- dist_ss(ss_sim = ss_sim, ss_real = ss_real)
+      Kh <- weights(dist_temp, tol, "epanechnikov")/K
+    }
+    
+    dist[1] <- dist_temp
+    
+    ## Sampling:
+    par_i <- local_par
+    Kh_i <- Kh
+    post_dists <- local_par
+    i <- 1
+    n_jump <- 1
+    n_count <- numeric()
+    n_count[n_jump] <- 1
+    
+    t_prior_frac <- as.numeric()
+    t_prop_frac <- as.numeric()
+    t_Kh_frac <- as.numeric()
+    
+    while(i <= N-1){
+      par_temp <- proposal_dist_x(par_i, ADBM_par_sd)
+      ss_sim_temp <- model(opt=par_temp, x=model_core_par)
+      
+      distt <- dist_ss(ss_sim = ss_sim_temp, ss_real = ss_real)
+      dist[i] <- distt
+      
+      Kh_temp <- weights(distt, tol = tol, kernel = "epanechnikov" )/K
[…]

### 2021-11-15 R/mcmc_burn_thin.R

@@ -1,0 +1,13 @@
+mcmc_burn_thin <- function(raw_result){
+  
+  t_length <- dim(raw_result$post_dists)[1]
+  nlag <- lag_mcmc(raw_result$post_dists[(t_length/2+1):t_length,])
+  
+  n_take <- as.integer((t_length/2)/nlag)
+  ind <- t_length/2 + nlag*(0:n_take)
+  
+  result <- list(acc_ss = raw_result$acc_ss[ind], dist = raw_result$dist[ind],
+                 post_dists = raw_result$post_dists[ind,], total_sim = raw_result$total_sim)
+  
+  return(result)
+}

### 2021-11-15 R/mcmc_contd.R

@@ -1,0 +1,95 @@
+mcmc_contd <- function(all.web.info, model = ratio.power, model_core_par = ADBM_core_par,
+                 model_prior_par= ADBM_prior_par, input_parameters,dist_ss,
+                 prior_dist_x, prior_dist_pbly, proposal_dist_pbly,
+                 proposal_dist_x, ADBM_par_sd)
+{
+  M <- all.web.info$species.sizes    #body size
+  tol <- input_parameters$tol
+  N <- input_parameters$N
+  n_cores <- input_parameters$n_cores
+
+  
+  registerDoParallel(cores=n_cores)
+  
+  ss_real <- model_core_par$real.web
+  
+  post_dists <- data.frame(a=double(), ai=double(), aj=double(), r.b=double())
+  
+  acc_ss <- numeric(N)
+  dist <- numeric(N)
+  qnty <- numeric(N)
+  
+  final_list <- list()
+  res_pcores <- foreach(i = 1:n_cores) %dopar%{
+    ## Initialise:
+    set.seed(i*9)
+    Kh <- 0
+    K <- weights(0, tol, "epanechnikov")
+    
+    local_par <- prior_dist_x[i,]
+    ss_sim <- model(opt=local_par, x=model_core_par)
+    dist_temp <- dist_ss(ss_sim = ss_sim, ss_real = ss_real)
+    Kh <- weights(dist_temp, tol, "epanechnikov")/K
+
+    
+    dist[1] <- dist_temp
+    
+    ## Sampling:
+    par_i <- local_par
+    Kh_i <- Kh
+    post_dists <- local_par
+    i <- 1
+    n_jump <- 1
+    n_count <- numeric()
+    n_count[n_jump] <- 1
+    
+    t_prior_frac <- as.numeric()
+    t_prop_frac <- as.numeric()
+    t_Kh_frac <- as.numeric()
+    
+    while(i <= N-1){
+      par_temp <- proposal_dist_x(par_i, ADBM_par_sd)
+      ss_sim_temp <- model(opt=par_temp, x=model_core_par)
+      
+      distt <- dist_ss(ss_sim = ss_sim_temp, ss_real = ss_real)
+      dist[i] <- distt
+      
+      Kh_temp <- weights(distt, tol = tol, kernel = "epanechnikov" )/K
[…]

### 2021-11-15 R/plot_dist_prop.R

@@ -1,0 +1,15 @@
+plot_dist_prop <- function(connectance, prop.1.corr, prop.0.corr,
+                           dist, ACC, TSS, dirnam, real_connectance){
+  
+  p0 <- plot_prop(connectance, "Connectance", real_connectance, x_min = 0, x_max = 1)
+  p1 <- plot_prop(prop.1.corr, "proportion of 1s correct", real = 1, x_min = 0, x_max = 1)
+  p2 <- plot_prop(prop.0.corr, "proportion of 0s correct", real = 1, x_min = 0, x_max = 1)
+  p3 <- plot_prop(dist, "distance", real = 0, x_min = 0, x_max = 1)
+  p4 <- plot_prop(ACC, "accuracy ACC",real = 1, x_min = 0, x_max = 1)
+  p5 <- plot_prop(TSS, "true skill statistic TSS",real = 1, x_min = -1, x_max = 1)
+  figure1 <- ggarrange(p0,p1,p2,p3,p4,p5, nrow = 6, ncol=1)
+  name <-  paste(c(dirnam,"/",'distribution of connectance 1 0.png'), collapse = '')
+  annotate_figure(figure1, top = paste("distribution of connectance 1 0 with ss = ", desc))
+  ggsave(filename = name, width=6, height=11)
+  
+}

### 2021-11-15 R/plot_foodweb.R

@@ -1,0 +1,179 @@
+plot_prop <- function(dd, property, real, x_min, x_max){
+  dd = data.frame(data = dd)
+  inter <- hdi(dd$data)
+  mean_data <- mean(dd$data)
+  ggplot(dd, aes(x = dd$data, y = ..density..)) +
+    geom_histogram(bins = 50) +
+    geom_vline(xintercept = real, color = "green", size = 1.5) +
+    geom_vline(xintercept = inter[1], color = "red")+
+    geom_vline(xintercept = inter[2], color = "red")+
+    geom_vline(xintercept = mean_data, color = "blue",size = 1.5)+
+    theme_classic()+
+    xlab(property) +
+    # ylab("Distribution")+
+    theme(axis.title=element_text(family="Times New Roman", size = 20), axis.title.y = element_blank()) +
+    xlim(c(x_min, x_max))
+}
+
+plot_foodweb <- function(real_foodweb = real_foodweb, predicted_foodweb = predicted_foodweb,
+                         dirnam = dirnam, model_core_par = model_core_par, 
+                         model_prior_par = model_prior_par,
+                         model = model, desc, prior_dist_x, 
+                         web.to.analyse = web.to.analyse){
+  nsim <- dim(predicted_foodweb$post_dists)[1]
+  prop_web <- fw_prop(predicted_foodweb, model_core_par, real_foodweb)
+  
+  saveRDS(prop_web, file = paste(c(dirnam,"/",web.to.analyse,"_prop",".Rdata"), collapse = ''))
+  real <- real_prop(real_foodweb)
+  prop <- prop_web$prop
+  best.web <- prop_web$web
+  prop.0.corr <- prop$prop.0.corr
+  prop.1.corr <- prop$prop.1.corr
+  
+  # Plotting predation matrices
+  fname <- paste(dirnam, "/", web.to.analyse, ".Rdata", sep = "")
+  par_full <- readRDS(fname)
+  par_full <- par_full$post_dists
+  parA <- par_full[which.min(par_full$r.b),]
+  parB <- par_full[which.max(par_full$r.b),]
+
+  webA = give_web(par = parA, other_par = model_core_par)
+  webB = give_web(par = parB, other_par = model_core_par)
+  plot_pred_mat(real_pred_mat = real_foodweb$predation.matrix, pred_pred_mat = best.web,
+                dirnam = dirnam, nsim = nsim, webA = webA, webB = webB)
+  
+
[…]

### 2021-11-15 R/plot_marg_dist.R

@@ -1,0 +1,167 @@
+plot_distribution <- function(xval, labell, prior_dist, n_bins, true_val_plot, real_par, parA, parB){
+  if(true_val_plot == F){
+    if(labell == "a") {
+      xpr <- prior_dist$a; xi <- min(xpr); xf <- max(xpr); labell = "a"
+      df <- data.frame(xval = xpr, Distribution = "prior")
+      df <- rbind(df, 
+                  data.frame(xval = xval, Distribution = "posterior"))
+      plot_distribution <- ggplot(df) +
+        # geom_histogram(bins = n_bins) +
+        geom_density(mapping = aes(x = xval, y = ..density.. , color = Distribution, fill = Distribution), alpha = 0.5) +
+        # geom_density(color="red", fill = "red", alpha = 0.5) +
+        xlab(TeX("log(a)")) +
+        xlim(c(xi,xf))+
+        # scale_x_log10() +
+        theme(axis.title=element_text(size=18, face = "bold"))+
+        theme_classic()
+      # geom_vline(xintercept = parA, color = "brown") +
+      # geom_vline(xintercept = parB, color = "purple")
+    }
+    else if (labell == "a_i") {
+      xpr <- prior_dist$ai; xval = xval; xi <- min(xpr); xf <- max(xpr); labell = "a_i"
+      df <- data.frame(xval = xpr, Distribution = "prior")       
+      df <- rbind(df,                    
+                  data.frame(xval = xval, Distribution = "posterior"))
+      plot_distribution <- ggplot(df) +
+        # geom_histogram(bins = n_bins) +
+        geom_density(mapping = aes(x = xval, y = ..density.. , color = Distribution, fill = Distribution), alpha = 0.5) +
+        # geom_density(color="red", fill = "red", alpha = 0.5) +
+        xlab(TeX(labell)) +
+        xlim(c(xi,xf))+
+        theme(axis.title=element_text(size=18, face = "bold"))+
+        theme_classic()
+      # geom_vline(xintercept = parA, color = "brown") +
+      # geom_vline(xintercept = parB, color = "purple")
+    }
+    else if (labell == "a_j") {
+      xpr <- prior_dist$aj; xval = xval; xi <- min(xpr); xf <- max(xpr); labell = "a_j"
+      df <- data.frame(xval = xpr, Distribution = "prior")       
+      df <- rbind(df,                    
[…]

### 2021-11-15 R/plot_pred_mat.R

@@ -1,0 +1,83 @@
+
+# par_full <- readRDS("results/rejection/Benguela Pelagic/rN=1000_tol=0.6_TSS_unif_rall_WBF_3/Benguela Pelagic.Rdata")
+# par_full <- par_full$post_dists
+# parA <- par_full[which.min(par_full$r.b),]
+# parB <- par_full[which.max(par_full$r.b),]
+# 
+# webA = give_web(par = parA, other_par = model_core_par) 
+# webB = give_web(par = parB, other_par = model_core_par)
+
+plot_pred_mat <- function(real_pred_mat, pred_pred_mat, gut_data, dirnam, nsim, webA, webB){
+  
+  # conn.real.web = format(round(sum(real_pred_mat)/dim(real_pred_mat)[1]^2, 2), nsmall = 2)
+  # png(paste(c(dirnam,"/",'observed_matrix.png'),collapse = ''), width=1000,height=1000)
+
+  ## Plot the real predation matrix
+  # Plot.matrix(web = real_pred_mat, title = paste("Observed predation matrix"), axes.labels = T)
+  # dev.off()
+  
+  
+  ## Plot the predicted predation matrix
+  # png(paste(c(dirnam,"/",'predicted_matrix.png'),collapse = ''),width=1333,height=1000)
+  # Plot.matrix_uncertainty(web = pred_pred_mat, title = paste(c("Predicted predation matrix"), collapse = ''), nsim = nsim)
+  # dev.off()
+  
+  ## Plot the predicted predation matrix with real foodweb imposed
+  # nsim <- 1000
+  # png(paste(c(dirnam,"/",'predicted_matrix_real.png'),collapse = ''),width=1333,height=1000)
+  # Plot.matrix_uncertainty_real(web = pred_pred_mat, real_pred_mat, title = paste(c("Predicted predation matrix for Benguela Pelagic  "), collapse = ''), nsim = nsim)
+  # dev.off()
+  
+  ## Plot predation matrix (A+B)
+  # png(paste(c(dirnam,"/",'predicted_matrix_AplusB.png'),collapse = ''),width=1100,height=300)
+  # Plot.matrix_AplusB(webA = webA, webB = webB)
+  # dev.off()
+  
+  
[…]

### 2021-11-15 R/plot_smc.R

@@ -1,0 +1,76 @@
+# plots the posterior distribution of parameters in SMC method
+
+plot_smc <- function(pred_data, dirnam){
+  
+  par_dict <- c("a", "ai", "aj", "r.b")
+  par_index <- 1
+  for(par in par_dict){
+    print(par)
+    if(par == "a"){
+      xlow <- model_prior_par$l_log_a
+      xhigh <- model_prior_par$r_log_a
+    }
+    else if(par == "ai"){
+      xlow <- model_prior_par$l_ai
+      xhigh <- model_prior_par$r_ai
+    }
+    else if(par == "aj"){
+      xlow <- model_prior_par$l_aj
+      xhigh <- model_prior_par$r_aj
+    }
+    else if(par == "r.b"){
+      xlow <- model_prior_par$l_log_r.b
+      xhigh <- model_prior_par$r_log_r.b
+    }
+    pbly <- 1/(xhigh-xlow)
+    n_run <- dim(pred_data$w)[2]
+    
+    tidy_posts <- tibble(par_val = pred_data$post_dists[,par_index,1],
+                         weight = pred_data$w[,1]/sum(pred_data$w[,1]),
+                         run = 1,
+                         par_name = par)
+    for(i in 2:n_run){
+      tidy_posts <- bind_rows(tidy_posts,
+                              tibble(par_val = pred_data$post_dists[,par_index,i],
+                                     weight = pred_data$w[,i]/sum(pred_data$w[,i]),
+                                     run = i,
+                                     par_name = par))
+    }
+    
+    fname <- paste(c(dirnam, "/", par, ".png"), collapse = "")
+    col_pal <- c("#d7191c", "#fdae61", "#ffffbf", "#abd9e9", "#2c7bb6")
+    plt <- ggplot(tidy_posts) +
+      geom_density(aes(x = par_val, y = ..density.., weight = weight,
+                         fill = factor(run)),
+                   alpha = 0.25) +
+      # geom_histogram(aes(x = par_val, y = ..density.., weight = weight,
+      #                  fill = factor(run)), bins = 50, position = "identity",
+      #              alpha = 0.25) +
+      # facet_wrap(~run, ncol = 1) +
+      theme_bw()+
+      theme(axis.title = element_text(size=18, face = "bold"),
+            axis.text = element_text(size=18, face = "bold"),
+            legend.title = element_text(size=18, face = "bold"),
[…]

### 2021-11-15 R/plot_str_prop.R

@@ -1,0 +1,23 @@
+plot_str_prop <- function(prop, real, dirnam){
+  
+  s0 <- plot_prop(prop$connectance, "Connectance", real$connectance, x_min = 0, x_max = 1)
+  s1 <- plot_prop(prop$prop_basal, "Proportion basal", real$prop_basal, x_min = 0, x_max = 1)
+  s2 <- plot_prop(prop$prop_inter, "Proportion intermediate", real$prop_inter, x_min = 0, x_max = 1)
+  s3 <- plot_prop(prop$prop_top, "Proportion top", real$prop_top, x_min = 0, x_max = 1)
+  s4 <- plot_prop(prop$prop_herb, "Proportion herbivores", real$prop_herb, x_min = 0, x_max = 1)
+  # s5 <- plot_prop(prop$mean_trop_lvl, "Mean trophic level", real$mean_trop_lvl)
+  # s6 <- plot_prop(prop$max_trop_lvl, "Max trophic level", real$max_trop_lvl)
+  s7 <- plot_prop(prop$mean_omn, "Mean omnivory", real$mean_omn, x_min = 0, x_max = max(prop$mean_omn))
+  s8 <- plot_prop(prop$sd_gen, "Standard deviation of generalism", real$sd_gen, x_min = 0, x_max = max(prop$sd_gen))
+  s9 <- plot_prop(prop$sd_vulner, "Standard deviation of vulnerability", real$sd_vulner, x_min = 0, x_max = max(prop$sd_vulner))
+  s10 <- plot_prop(prop$diet_sim, "Diet similarity", real$diet_sim, x_min = 0, x_max = 1)
+  mpl <- prop$mean_path_lt[is.finite(prop$mean_path_lt)]
+  s11 <- plot_prop(mpl, "Mean path length", real$mean_path_lt, x_min = 0, x_max = max(mpl))
+
+  figure <- ggarrange(s0,s1,s2,s3,s4,s7,s8,s9,s10,s11, nrow = 5, ncol=2)
+  name <-  paste(c(dirnam,"/",'properties.png'), collapse = '')
+  # annotate_figure(figure, top = paste("foodweb properties with ss = ", desc))
+  annotate_figure(figure, left = text_grob("density", size = 20, family = "Times New Roman", rot = 90))
+  ggsave(filename = name, width=9, height=12)
+  
+}

### 2021-11-15 R/prior.R

@@ -1,0 +1,159 @@
+## Here, we define the prior distributions for the parameter
+# Last updated: 09.03.2021
+
+prior_weibull_x <- function(par = par, no = no){
+  local_a <- rweibull(no, shape = par$a.shape, scale = par$a.scale)
+  local_ai <- runif(no, par$l_ai, par$r_ai)
+  local_aj <- runif(no, par$l_aj, par$r_aj)
+  local_r.b <- rweibull(no, shape = par$r.b.shape, scale = par$r.b.scale)
+  
+  return(data.frame(a=local_a, ai=local_ai, aj=local_aj, r.b=local_r.b))
+}
+
+prior_weibull_pbly <- function(par = par, model_par ){
+  pbly_a <- dweibull(par$a, shape = model_par$a.shape, scale = model_par$a.scale)
+  pbly_ai <- dunif(par$ai, model_par$l_ai, model_par$r_ai)
+  pbly_aj <- dunif(par$aj, model_par$l_aj, model_par$r_aj)
+  pbly_r.b <- dweibull(par$r.b, shape = model_par$r.b.shape, scale = model_par$r.b.scale)
+  
+  return(pbly_a*pbly_ai*pbly_aj*pbly_r.b)
+}
+
+prior_unif_x <- function(par, no){
+  local_a <- runif(no, par$l_log_a, par$r_log_a)
+  local_ai <- runif(no, par$l_ai, par$r_ai)
+  local_aj <- runif(no, par$l_aj, par$r_aj)
+  local_r.b <- runif(no, par$l_log_r.b, par$r_log_r.b)
+  
+  return(data.frame(a=local_a, ai=local_ai, aj=local_aj, r.b=local_r.b))
+}
+
+prior_only_ai <- function(par = par, no = no){
+  local_a <- 5
+  local_ai <- runif(no, par$l_ai, par$r_ai)
+  local_aj <- -0.2
+  local_r.b <- 0.02
+  
+  return(data.frame(a=local_a, ai=local_ai, aj=local_aj, r.b=local_r.b))
+}
+
+prior_only_r.b <- function(par_ = par, no = no){
+  local_a <- log10(8.56e-6)
+  local_ai <- -5.39e-1
+  local_aj <- 5.80e-1
+  local_r.b <- runif(no, par_$l_log_r.b, par_$r_log_r.b)
+  
+  return(data.frame(a=local_a, ai=local_ai, aj=local_aj, r.b=local_r.b))
+}
[…]

### 2021-11-15 R/prop_basal.R

@@ -1,0 +1,26 @@
+#Computes proportion of basal species in a food web with using the predation matrix (where, column represents consumer and row represents resources)
+
+prop_basal_inter_top <- function(pred_mat){
+  nspecies <- dim(pred_mat)[1]
+  var_colsum <- colSums(pred_mat)
+  var_rowsum <- rowSums(pred_mat)
+  
+  zero_colsum <- which(var_colsum == 0)
+  zero_rowsum <- which(var_rowsum == 0)
+  
+  singleton_species <- intersect(zero_colsum, zero_rowsum) #one which has no links at all including itself
+  basal_species <- setdiff(zero_colsum, zero_rowsum)
+  top_species <- setdiff(zero_rowsum, zero_colsum)
+  
+  n_basal <- length(basal_species)
+  n_top <- length(top_species)
+  n_inter <- nspecies - n_basal - n_top
+  n_singleton <- length(singleton_species)
+    
+  prop_basal <- n_basal/nspecies
+  prop_top <- n_top/nspecies
+  prop_inter <- n_inter/nspecies
+  
+  return(list(prop_basal = prop_basal, prop_inter = prop_inter, 
+              prop_top = prop_top, n_singleton = n_singleton))
+}

### 2021-11-15 R/prop_basal_inter_top_herb.R

@@ -1,0 +1,38 @@
+#Computes proportion of basal species in a food web with using the predation matrix (where, column represents consumer and row represents resources)
+
+prop_basal_inter_top_herb <- function(pred_mat){
+  nspecies <- dim(pred_mat)[1]
+  var_colsum <- colSums(pred_mat)
+  var_rowsum <- rowSums(pred_mat)
+  
+  zero_colsum <- which(var_colsum == 0)
+  zero_rowsum <- which(var_rowsum == 0)
+  
+  singleton_species <- intersect(zero_colsum, zero_rowsum) #node which has no links including itself
+  basal_species <- setdiff(zero_colsum, zero_rowsum)
+  top_species <- setdiff(zero_rowsum, zero_colsum)
+  
+  without_basal_species <- pred_mat[-zero_colsum, -zero_colsum]
+  nspecies_2 <- dim(without_basal_species)[1]
+  
+  var_colsum_2 <- colSums(without_basal_species)
+  var_rowsum_2 <- rowSums(without_basal_species)
+  zero_colsum_2 <- which(var_colsum_2 == 0)
+  zero_rowsum_2 <- which(var_rowsum_2 == 0)
+  herb_species <- setdiff(zero_colsum_2, zero_rowsum_2)
+  
+  n_basal <- length(basal_species)
+  n_top <- length(top_species)
+  n_inter <- nspecies - n_basal - n_top
+  n_singleton <- length(singleton_species)
+  n_herbivores <- length(herb_species)
+  
+  prop_basal <- n_basal/nspecies
+  prop_top <- n_top/nspecies
+  prop_inter <- n_inter/nspecies
+  prop_herbivores <- n_herbivores/nspecies
+  
+  return(list(prop_basal = prop_basal, prop_inter = prop_inter, 
+              prop_top = prop_top, n_singleton = n_singleton,
+              prop_herb = prop_herbivores))
+}

### 2021-11-15 R/proposal_dist.R

@@ -1,0 +1,88 @@
+# proposal distributions for different methods
+
+proposal_dist_pbly <- function(par, par_prime, ADBM_par_sd){
+  pbly.a <- dlnorm(par_prime$a, meanlog = par$a, sdlog = ADBM_par_sd$a)
+  pbly.ai <- dnorm(par_prime$ai, mean = par$ai, sd = ADBM_par_sd$ai)
+  pbly.aj <- dnorm(par_prime$aj, mean = par$aj, sd = ADBM_par_sd$aj)
+  pbly.r.b <- dlnorm(par_prime$r.b, meanlog = par$r.b, sdlog = ADBM_par_sd$r.b)
+  
+  return(pbly.a*pbly.ai*pbly.aj*pbly.r.b)
+}
+
+proposal_dist_x <- function(par, ADBM_par_sd){
+  a <- rlnorm(1, meanlog = par$a, sdlog = ADBM_par_sd$a)
+  ai <- rnorm(1, mean = par$ai, sd = ADBM_par_sd$ai)
+  aj <- rnorm(1, mean = par$aj, sd = ADBM_par_sd$aj)
+  r.b <- rlnorm(1, meanlog = par$r.b, sdlog = ADBM_par_sd$r.b)
+  
+  return(data.frame(a=a, ai=ai, aj=aj, r.b=r.b))
+}
+
+proposal_dist_pbly_mcmc <- function(par, par_prime, ADBM_par_sd){
+  pbly.a <- dnorm(par_prime$a, mean = par$a, sd = ADBM_par_sd$a)
+  pbly.ai <- dnorm(par_prime$ai, mean = par$ai, sd = ADBM_par_sd$ai)
+  pbly.aj <- dnorm(par_prime$aj, mean = par$aj, sd = ADBM_par_sd$aj)
+  pbly.r.b <- dnorm(par_prime$r.b, mean = par$r.b, sd = ADBM_par_sd$r.b)
+  
+  return(pbly.a*pbly.ai*pbly.aj*pbly.r.b)
+}
+
+proposal_dist_x_mcmc <- function(par, ADBM_par_sd){
+  a <- rnorm(1, mean = par$a, sd = ADBM_par_sd$a)
+  ai <- rnorm(1, mean = par$ai, sd = ADBM_par_sd$ai)
+  aj <- rnorm(1, mean = par$aj, sd = ADBM_par_sd$aj)
+  r.b <- rnorm(1, mean = par$r.b, sd = ADBM_par_sd$r.b)
+  
[…]

### 2021-11-15 R/real_prop_predator.R

@@ -1,0 +1,43 @@
+# 04.05.2021
+# Computes food web properties for a real food web
+
+real_prop_predator <- function(all.web.info){
+  
+  title <- all.web.info$web.name
+  community <- mat.to.comm(all.web.info$predation.matrix, title)
+  connectance <- sum(all.web.info$predation.matrix)/(dim(all.web.info$predation.matrix)[1]^2)
+  prop_species <- prop_basal_inter_top_herb(pred_mat = all.web.info$predation.matrix)
+  prop_basal <- prop_species$prop_basal
+  prop_inter <- prop_species$prop_inter
+  prop_top <- prop_species$prop_top
+  n_singleton <- prop_species$n_singleton
+  prop_herb <- prop_species$prop_herb
+  
+  mtl <- try(mean(ShortWeightedTrophicLevel(community)))
+  mean_trop_lvl <- if(is.numeric(mtl)==TRUE) mtl else NA
+
+  maxtl <- try(max(LongestTrophicLevel(community)))
+  max_trop_lvl <- if(is.numeric(maxtl)==TRUE) maxtl else NA
+
+  mean_omn <- FractionOmnivorous(community)
+  clus_coeff <- ClustF(all.web.info$predation.matrix, type = "directed")$GlobaltotalCC
+  
+  sd_gen <- sd(InDegree(community))
+  sd_vulner <- sd(OutDegree(community))
+  
+  mean_max_trophic_sim <- MeanMaximumTrophicSimilarity(community)
+  
+  shortest_paths <- ShortestPaths(community)
+  finite_paths <- is.finite(shortest_paths)
+  mean_path_lt <- mean(shortest_paths[finite_paths])
+  
+  nest_prop <- as.numeric(nested(all.web.info$predation.matrix))
+  
+  real_prop_f <- data.frame(connectance = connectance, prop_basal = prop_basal, prop_inter = prop_inter, prop_top = prop_top,
+                            prop_herb = prop_herb, mean_trop_lvl = mean_trop_lvl, max_trop_lvl = max_trop_lvl,
+                            mean_omn = mean_omn, clus_coeff = clus_coeff, sd_gen = sd_gen,
+                            sd_vulner = sd_vulner, mean_max_trophic_sim = mean_max_trophic_sim, mean_path_lt = mean_path_lt,
+                            n_singleton = n_singleton, nest_prop = nest_prop)
+  
+  return(real_prop_f)
+}

### 2021-11-15 R/rejection_SIR.R

@@ -1,0 +1,73 @@
+# implements rejection algorithm from Handbook of Approximate Bayesian Computation
+
+rejection_SIR <- function(all.web.info, model, model_core_par,
+                      model_prior_par, input_parameters, dist_ss,
+                      prior_dist, SIR_data, sp_ind)
+{
+  M <- all.web.info$species.sizes    #body size
+  tol <- input_parameters$tol
+  N <- input_parameters$N
+  n_cores <- input_parameters$n_cores
+  e <- model_core_par$e
+  n <- model_core_par$n
+  ni <- model_core_par$ni
+  r.a = model_core_par$r.a
+  
+  registerDoParallel(cores=n_cores)
+  
+  ss_real <- SIR_data
+  
+  count <- 1
+  post_dists <- data.frame(a=double(), ai=double(), aj=double(), r.b=double())
+  n <- N/n_cores
+  
+  res_pcores <- foreach(i = 1:n_cores, .combine = rbind) %dopar% 
+    {
+      set.seed(i)
+      acc_ss <- numeric(n)
+      dist <- numeric(n)
+      total_sim <- 0
+      while(count <= n)
+      {
+        ## Generating parameters from sampling
+        local_par <- prior_dist(par=model_prior_par, no=1)
+        
+        ## Generating summary stat from likelihood
+        ss_sim <- model(opt=local_par, x=model_core_par)
+        num_gen <- runif(1, 0, 1)
+        K <- weights(0, tol, "epanechnikov")
+        
+        dist_temp <- dist_ss(ss_sim = ss_sim, ss_real = ss_real, sp_ind = sp_ind)
+        
+        pbly <- weights(dist_temp, tol, "epanechnikov")/K
+        if (num_gen<pbly)
+        {
+          acc_ss[count] <- connectance_f(ss_sim = ss_sim)
+          dist[count] <- dist_temp
+          post_dists <- rbind(post_dists, local_par)
+          count <- count + 1
+        }
+        total_sim <- total_sim+1
+      }
+      list(post_dists_pcore = post_dists, acc_ss_pcore = acc_ss, dist_pcore = dist, total_sim_pcore = total_sim)
+    }
+  
+  post_dists <- res_pcores[[1]]
+  acc_ss <- res_pcores[[n_cores+1]]
+  dist <- res_pcores[[2*n_cores+1]]
[…]

### 2021-11-15 R/rejection_e1.R

@@ -1,0 +1,103 @@
+# implements rejection algorithm from Handbook of Approximate Bayesian Computation
+# Rule e1
+
+rejection_e1 <- function(fw_data, model, model_core_par,
+                         model_prior_par, input_parameters, dist_main,
+                         prior_dist, gut_data_main, n_dietbreadth, main_propn,
+                         weight_type)
+{
+  M <- fw_data$species.sizes    #body size
+  tol <- input_par$tol
+  N <- input_par$N
+  n_cores <- input_par$n_cores
+  e <- model_core_par$e
+  n_abund <- model_core_par$n
+  ni <- model_core_par$ni
+  r.a <- model_core_par$r.a
+  
+  registerDoParallel(cores=n_cores)
+  
+  # ss_real <- gut_data
+  
+  count <- 1
+  post_dists <- data.frame(a=double(), ai=double(), aj=double(), r.b=double())
+  n <- N/n_cores
+  
+  res_pcores <- foreach(i = 1:n_cores, .combine = rbind) %dopar% 
+    {
+      set.seed(i)
+      acc_ss <- numeric(n)
+      dist <- numeric(n)
+      total_sim <- 0
+      
+      
+      while(count <= n)
+      {
+        local_par <- prior_dist(par=model_prior_par, no=1)
+        
+        #Extracting partial gut data here
+        nspecies <- dim(gut_data_main)[1]
+        indexes <- gut_data_pred_index(pred_index = c(1:nspecies), n = n_dietbreadth)
+        dist_ss <- dist_main
+        gut_data <- matrix(0, nrow = nspecies, ncol = nspecies)
+        
+        for(k in indexes){
+          
+          diet_breadth <- gut_data_main[,k]
+          pred_diet <- diet_e1(diet_breadth = diet_breadth, M = M, Mj = M[k], n = n_abund, ni = ni, 
+                                a = local_par$a, ai = local_par$ai, aj = local_par$aj)
+          gut_data[,k] <- pred_diet
+        }
+        
+        ss_real <- gut_data
+        #print(ss_real)
+        
+        # local_count <- 0
+        # if(local_count == 0){
+          ## Generating parameters from sampling
+          # local_par <- prior_dist(par=model_prior_par, no=1)
+          
+          ## Generating summary stat from likelihood
[…]

### 2021-11-15 R/rejection_g1.R

@@ -1,0 +1,107 @@
+# implements rejection algorithm from Handbook of Approximate Bayesian Computation
+
+rejection_g1 <- function(fw_data, model, model_core_par,
+                         model_prior_par, input_parameters, dist_main,
+                         prior_dist, gut_data_main, n_dietbreadth, main_propn,
+                         weight_type, species_ind)
+{
+  M <- fw_data$species.sizes    #body size
+  tol <- input_parameters$tol
+  N <- input_parameters$N
+  n_cores <- input_parameters$n_cores
+  e <- model_core_par$e
+  n_par <- model_core_par$n
+  ni <- model_core_par$ni
+  r.a <- model_core_par$r.a
+  
+  registerDoParallel(cores=n_cores)
+  
+  # ss_real <- gut_data
+  
+  
+  post_dists <- data.frame(a=double(), ai=double(), aj=double(), r.b=double())
+  n <- N/n_cores
+  
+  res_pcores <- foreach(i = 1:n_cores, .combine = rbind) %dopar% 
+    {
+      set.seed(i*200+n_gut)
+      
+      acc_ss <- numeric(n)
+      dist <- numeric(n)
+      total_sim <- 0
+      
+      #Extracting partial gut data here
+      nspecies <- dim(gut_data_main)[1]
+      indexes <- species_ind
+      dist_ss <- dist_main
+      gut_data <- matrix(0, nrow = nspecies, ncol = nspecies)
+      
+      for(k in indexes){
+        link_ind <- which(as.numeric(gut_data_main[,k]) == 1)
+        n_link_ind <- length(link_ind)
+        nsubsamples <- as.integer(main_propn*n_link_ind)
+        sub_link_ind <- sample(link_ind, nsubsamples, replace = FALSE)
+        if(n_link_ind == 1 && main_propn == 1){
+          sub_link_ind <- link_ind
+        }
+        gut_data[,k][c(sub_link_ind)] <- gut_data_main[,k][c(sub_link_ind)]
+      }
+      
+      ss_real <- gut_data
+      
+      count <- 1
+      while(count <= n)
+      {
+        
+        #print(ss_real)
+        
+        local_count <- 0
+        if(local_count == 0){
+          ## Generating parameters from sampling
+          local_par <- prior_dist(par=model_prior_par, no=1)
+          
+          ## Generating summary stat from likelihood
[…]

### 2021-11-15 R/rejection_r5.R

@@ -1,0 +1,84 @@
+# implements rejection algorithm from Handbook of Approximate Bayesian Computation
+
+rejection_r5 <- function(all.web.info, model, model_core_par,
+                          model_prior_par, input_parameters, dist_ss,
+                          prior_dist, gut_data, n_dietbreadth)
+{
+  M <- all.web.info$species.sizes    #body size
+  tol <- input_parameters$tol
+  N <- input_parameters$N
+  n_cores <- input_parameters$n_cores
+  e <- model_core_par$e
+  n <- model_core_par$n
+  ni <- model_core_par$ni
+  r.a = model_core_par$r.a
+  
+  registerDoParallel(cores=n_cores)
+  
+  # ss_real <- gut_data
+  
+  count <- 1
+  post_dists <- data.frame(a=double(), ai=double(), aj=double(), r.b=double())
+  n <- N/n_cores
+  
+  res_pcores <- foreach(i = 1:n_cores, .combine = rbind) %dopar% 
+    {
+      set.seed(i)
+      acc_ss <- numeric(n)
+      dist <- numeric(n)
+      total_sim <- 0
+      
+      #Extracting partial gut data here
+      gut_data_main <- gut_data
+      nspecies <- dim(gut_data_main)[1]
+      indexes <- gut_data_pred_index(pred_index = c(1:nspecies), n = n_dietbreadth)
+      dist_ss <- dist_exact_index(index = indexes)
+      gut_data <- matrix(0, nrow = nspecies, ncol = nspecies)
+      
+      gut_data[,indexes] <- gut_data_main[,indexes]
+      ss_real <- gut_data
+      
+      while(count <= n)
+      {
+        ## Generating parameters from sampling
+        local_par <- prior_dist(par=model_prior_par, no=1)
+        
+        ## Generating summary stat from likelihood
+        ss_sim <- model(opt=local_par, x=model_core_par)
+        num_gen <- runif(1, 0, 1)
+        K <- weights(0, tol, "epanechnikov")
+        
+        dist_temp <- dist_ss(ss_sim = ss_sim, ss_real = ss_real)
+        
+        pbly <- weights(dist_temp, tol, "epanechnikov")/K
+        if (num_gen<pbly)
+        {
+          acc_ss[count] <- connectance_f(ss_sim = ss_sim)
[…]

### 2021-11-15 R/rejection_r8.R

@@ -1,0 +1,107 @@
+# implements rejection algorithm from Handbook of Approximate Bayesian Computation
+
+rejection_r8 <- function(fw_data, model, model_core_par,
+                         model_prior_par, input_parameters, dist_main,
+                         prior_dist, gut_data_main, n_dietbreadth, main_propn,
+                         weight_type, species_ind)
+{
+  M <- fw_data$species.sizes    #body size
+  tol <- input_parameters$tol
+  N <- input_parameters$N
+  n_cores <- input_parameters$n_cores
+  e <- model_core_par$e
+  n_par <- model_core_par$n
+  ni <- model_core_par$ni
+  r.a <- model_core_par$r.a
+  
+  registerDoParallel(cores=n_cores)
+  
+  # ss_real <- gut_data
+  
+  
+  post_dists <- data.frame(a=double(), ai=double(), aj=double(), r.b=double())
+  n <- N/n_cores
+  
+  res_pcores <- foreach(i = 1:n_cores, .combine = rbind) %dopar% 
+    {
+      set.seed(i)
+
+      acc_ss <- numeric(n)
+      dist <- numeric(n)
+      total_sim <- 0
+      
+      #Extracting partial gut data here
+      nspecies <- dim(gut_data_main)[1]
+      indexes <- species_ind
+      dist_ss <- dist_main
+      gut_data <- matrix(0, nrow = nspecies, ncol = nspecies)
+      
+      for(k in indexes){
+        link_ind <- which(as.numeric(gut_data_main[,k]) == 1)
+        n_link_ind <- length(link_ind)
+        nsubsamples <- as.integer(main_propn*n_link_ind)
+        sub_link_ind <- sample(link_ind, nsubsamples, replace = FALSE)
+        if(n_link_ind == 1 && main_propn == 1){
+          sub_link_ind <- link_ind
+        }
+        gut_data[,k][c(sub_link_ind)] <- gut_data_main[,k][c(sub_link_ind)]
+      }
+      
+      ss_real <- gut_data
+      
+      count <- 1
+      while(count <= n)
+      {
+        
+        #print(ss_real)
+        
+        local_count <- 0
+        if(local_count == 0){
+          ## Generating parameters from sampling
+          local_par <- prior_dist(par=model_prior_par, no=1)
+          
+          ## Generating summary stat from likelihood
[…]

### 2021-11-15 R/rejection_s2.R

@@ -1,0 +1,87 @@
+# implements rejection algorithm from Handbook of Approximate Bayesian Computation
+
+rejection_s2 <- function(fw_data, model, model_core_par,
+                         model_prior_par, input_parameters, dist_ss,
+                         prior_dist, sir_data_main,
+                         weight_type, species_ind, real_pred_mat,
+                         dist_TSS, n_sir = n_sir)
+{
+  M <- fw_data$species.sizes    #body size
+  tol <- input_parameters$tol
+  N <- input_parameters$N
+  n_cores <- input_parameters$n_cores
+  
+  registerDoParallel(cores=n_cores)
+  
+  ss_real <- sir_data_main
+  
+  post_dists <- data.frame(a=double(), ai=double(), aj=double(), r.b=double())
+  n <- N/n_cores
+  
+  res_pcores <- foreach(i = 1:n_cores, .combine = rbind) %dopar% 
+    {
+      set.seed(n_sir + i*200)
+      
+      acc_ss <- numeric(n)
+      dist <- numeric(n)
+      total_sim <- 0
+      
+      count <- 1
+      while(count <= n)
+      {
+        
+        local_count <- 0
+        while(local_count == 0){
+          ## Generating parameters from sampling
+          local_par <- prior_dist(par=model_prior_par, no=1)
+          
+          ## Generating summary stat from likelihood
+          ss_sim <- model(opt=local_par, x=model_core_par)
+          # num_gen <- runif(1, 0, 1)
+          # K <- weights(0, tol, weight_type)
+          ss_sim_tl <- trophic_position(web = ss_sim, title = "sim_foodweb")
+          
+          if(sum(is.na(ss_sim_tl)) == 0){
+            dist_temp <- dist_ss(ss_sim = ss_sim_tl, ss_real = ss_real, sp_ind = species_ind)
+            #print(paste("dist = ", dist_temp))
+            # pbly <- weights(dist_temp, tol, weight_type)/K
+            #print(paste("pbly = ", pbly))
+            #print(paste("count = ", count))
+            # if (num_gen<pbly)
+            # {
+            acc_ss[count] <- dist_TSS(ss_sim = ss_sim, ss_real = real_pred_mat)
+            dist[count] <- dist_temp
+            post_dists <- rbind(post_dists, local_par)
+            count <- count + 1
[…]

### 2021-11-15 R/rejection_s5.R

@@ -1,0 +1,78 @@
+# 08.04.2021
+# implements rejection algorithm from Handbook of Approximate Bayesian Computation
+
+rejection_s5 <- function(fw_data, model, model_core_par,
+                         model_prior_par, input_parameters, dist_ss,
+                         prior_dist, sir_data_main,
+                         weight_type, species_ind, real_pred_mat,
+                         dist_TSS, n_sir = n_sir)
+{
+  M <- fw_data$species.sizes    #body size
+  tol <- input_parameters$tol
+  N <- input_parameters$N
+  n_cores <- input_parameters$n_cores
+  
+  registerDoParallel(cores=n_cores)
+  
+  ss_real <- sir_data_main
+  
+  post_dists <- data.frame(a=double(), ai=double(), aj=double(), r.b=double())
+  n <- N/n_cores
+  
+  res_pcores <- foreach(i = 1:n_cores, .combine = rbind) %dopar% 
+    {
+      set.seed(n_sir*200 + i + 1)
+      
+      dist_tl <- numeric(n)
+      dist_fw <- numeric(n)
+      total_sim <- 0
+      
+      count <- 1
+      while(count <= n)
+      {
+        
+        local_count <- 0
+        while(local_count == 0){
+          ## Generating parameters from sampling
+          local_par <- prior_dist(par=model_prior_par, no=1)
+          
+          ## Generating summary stat from likelihood
+          ss_sim <- model(opt=local_par, x=model_core_par)
+          ss_sim_tl <- trophic_position(web = ss_sim, title = "sim_foodweb")
+          
+          if(sum(is.na(ss_sim_tl)) == 0){
+            dist_temp <- dist_ss(ss_sim = ss_sim_tl, ss_real = ss_real, sp_ind = species_ind)
+            dist_fw[count] <- dist_TSS(ss_sim = ss_sim, ss_real = real_pred_mat)
+            dist_tl[count] <- dist_temp
+            post_dists <- rbind(post_dists, local_par)
+            count <- count + 1
+            local_count <- local_count + 1
+          }
+          else(print(3))
+        }
+        total_sim <- total_sim + 1
+        
+      }
+      
[…]

### 2021-11-15 R/rejection_s_r_1.R

@@ -1,0 +1,104 @@
+# implements rejection algorithm from Handbook of Approximate Bayesian Computation
+# 09.03.2021
+rejection_s_r_1 <- function(fw_data, model, model_core_par, model_prior_par, 
+                            input_parameters, dist_main, prior_dist, 
+                            gut_data_main, main_propn, species_ind,
+                            n_gut)
+{
+  M <- fw_data$species.sizes
+  tol <- input_parameters$tol
+  N <- input_parameters$N
+  n_cores <- input_parameters$n_cores
+  e <- model_core_par$e
+  n_par <- model_core_par$n
+  ni <- model_core_par$ni
+  r.a <- model_core_par$r.a
+  
+  registerDoParallel(cores=n_cores)
+  
+  # ss_real <- gut_data
+  
+  
+  post_dists <- data.frame(a=double(), ai=double(), aj=double(), r.b=double())
+  n <- N/n_cores
+  
+  res_pcores <- foreach(i = 1:n_cores, .combine = rbind) %dopar% 
+    {
+      set.seed(n_gut * 200 + i + 1)
+      
+      TSS <- numeric(n)
+      dist <- numeric(n)
+      total_sim <- 0
+      
+      #Extracting partial gut data here
+      nspecies <- dim(gut_data_main)[1]
+      indexes <- species_ind
+      dist_ss <- dist_main
+      gut_data <- matrix(0, nrow = nspecies, ncol = nspecies)
+      
+      for(k in indexes){
+        link_ind <- which(as.numeric(gut_data_main[,k]) == 1)
+        n_link_ind <- length(link_ind)
+        nsubsamples <- as.integer(main_propn*n_link_ind)
+        sub_link_ind <- sample(link_ind, nsubsamples, replace = FALSE)
+        if(n_link_ind == 1 && main_propn == 1){
+          sub_link_ind <- link_ind
+        }
+        gut_data[,k][c(sub_link_ind)] <- gut_data_main[,k][c(sub_link_ind)]
+      }
+      
+      ss_real <- gut_data
+      
+      count <- 1
+      while(count <= n)
+      {
+        
+        #print(ss_real)
+        
+        local_count <- 0
+        if(local_count == 0){
+          ## Generating parameters from sampling
+          local_par <- prior_dist(par=model_prior_par, no=1)
+          
+          ## Generating summary stat from likelihood
[…]

### 2021-11-15 R/rejection_s_r_2.R

@@ -1,0 +1,92 @@
+# 05.05.2021
+rejection_s_r_2 <- function(fw_data, model, model_core_par, model_prior_par, 
+                            input_parameters, dist_main, prior_dist, 
+                            gut_data_main, main_propn, species_ind,
+                            n_gut, pred_nodes, sir_data_main)
+{
+  M <- fw_data$species.sizes
+  tol <- input_parameters$tol
+  N <- input_parameters$N
+  n_cores <- input_parameters$n_cores
+  e <- model_core_par$e
+  n_par <- model_core_par$n
+  ni <- model_core_par$ni
+  r.a <- model_core_par$r.a
+  
+  registerDoParallel(cores=n_cores)
+  
+  # ss_real <- gut_data
+  
+  
+  post_dists <- data.frame(a=double(), ai=double(), aj=double(), r.b=double())
+  n <- N/n_cores
+  
+  res_pcores <- foreach(i = 1:n_cores, .combine = rbind) %dopar% 
+    {
+      set.seed(n_gut * 200 + i + 1)
+      
+      TSS <- numeric(n)
+      dist_tl <- numeric(n)
+      dist_diet <- numeric(n)
+      TSS_fw <- numeric(n)
+      total_sim <- 0
+
+      
+      count <- 1
+      while(count <= n)
+      {
+        
+        #print(ss_real)
+        
+        local_count <- 0
+        if(local_count == 0){
+          ## Generating parameters from sampling
+          local_par <- prior_dist(par = model_prior_par, no = 1)
+          
+
+          ss_sim <- model(opt = local_par, x = model_core_par)
+          ss_sim[, -pred_nodes] <- 0
+          
+          ss_sim_tl <- trophic_position(web = ss_sim, title = "sim_foodweb")
+          
+          if(sum(is.na(ss_sim_tl)) == 0){
+            dist_diet[count] <- dist_TSS(ss_sim = ss_sim[, species_ind], ss_real = gut_data_main[, species_ind])
+            dist_tl[count] <- dist_SIR(ss_sim = ss_sim_tl[species_ind], ss_real = sir_data_main[species_ind])
+            TSS_fw[count] <- 1 - dist_TSS(ss_sim = ss_sim[, pred_nodes], ss_real = gut_data_main[, pred_nodes])
+            
[…]

### 2021-11-15 R/sim_foodweb.R

@@ -1,0 +1,81 @@
+# Simulates a user defined food web
+
+# Remember a and r.b are not in log scale here
+sim_foodweb_par <- function(){
+  return(data.frame(a = 10^-7.379692,
+                    ai = -1.472906,
+                    aj = 1.271297,
+                    r.b = 10^0.4634886))
+}
+
+
+sim_foodweb <- function(sim_par, fw_name){
+  
+  
+  fname <- paste("data/", fw_name, ".web.Rdata", sep = "")
+  fw_data <- readRDS(file = fname)
+  
+  n_species <- length(fw_data$species.sizes)
+  
+  # set.seed(1)
+  M <- fw_data$species.sizes
+  M <- sort(M)
+  
+  sim_a <- sim_par$a
+  sim_ai <- sim_par$ai
+  sim_aj <- sim_par$aj
+  sim_r.b <- sim_par$r.b
+  
+  local_par <- data.frame(a = sim_a, ai = sim_ai, aj = sim_aj, r.b = sim_r.b)
+  sim_model_core_par <- list(e = 1, n = 1, ni = -3/4, r.a = 1, M  = M)
+  pred_mat <- ratio.power(opt=local_par, x = sim_model_core_par)
+  rownames(pred_mat) <- as.character(seq(1, n_species))
+  colnames(pred_mat) <- as.character(seq(1, n_species))
+  
+  
+  all.web.info <- list(web.name = fw_name, species.sizes = M, 
+                       species.names = as.character(seq(1, n_species)),
+                       predation.matrix = pred_mat, a = sim_a, ai = sim_ai, 
+                       aj = sim_aj, r.b = sim_r.b)
+
+  # saveRDS(all.web.info, file = paste(c("data/sim_", fw_name, ".web.Rdata"), collapse = ""))
+  # saveRDS(all.web.info, file = paste(c("data/sim_best_", fw_name, ".web.Rdata"), collapse = ""))
+  return(all.web.info)
+}
+
+
+
+sim_foodweb_predator <- function(sim_par, fw_name){
+  
+  fname <- paste("data/", fw_name, ".web.Rdata", sep = "")
+  fw_data <- readRDS(file = fname)
+  pred_nodes <- which(colSums(fw_data$predation.matrix)>0)
+  
+  n_species <- length(fw_data$species.sizes)
+  
+  set.seed(1)
+  M <- fw_data$species.sizes
+  M <- sort(M)
+  
[…]

### 2021-11-15 R/tolerance_seln.R

@@ -1,0 +1,15 @@
+# used to calculate the tolerance for a given foodweb 
+
+tolerance_seln <- function(dirnam, fw_name){
+  
+  file <- paste(c(dirnam,"/",fw_name,".Rdata"), collapse = "")
+  fw_data <- readRDS(file)
+  distance <- fw_data$dist
+  
+  sort_dist <- sort(unique(distance))  
+  nsim <- length(unique(distance))
+  index <- as.integer(nsim*0.001)
+  tol <- sort_dist[index]
+  
+  return(tol)
+}

### 2021-11-15 inst/main/ADBM_best_pred.R

@@ -1,0 +1,17 @@
+## 11.08.2021
+
+## Plot the graphs for a case when the ADBM’s best prediction is the true one 
+
+
+## Broadstone Stream size_agg
+# 36 sample correspond to the best prediction
+
+
+bs_1008_36 <- readRDS("../../../../../../Volumes/SSD1/Secondary_storage/PhD_local/C2_files/Broadstone Stream size_agg_v2/rule_ind_predator/N=1e+05_tol=2_n_diet = 1008/rn_sample=36_N=1e+05_tol=2_TSS_gut_ind_l1008/Broadstone Stream size_agg_v2.Rdata")
+
+ind_max_TSS <- which.max(bs_1008_36$TSS_fw)
+
+par_max_TSS <- bs_1008_36$post_dists[ind_max_TSS,]
+
+
+

### 2021-11-15 inst/main/Mi_by_Mj.R

@@ -1,0 +1,97 @@
+# 22.07.2021
+# We look at the Mi/Mj ratio of body size 
+
+library(readr)
+library(dplyr)
+library(R.utils)
+library(cheddar)
+
+sourceDirectory("../C1_method/C1_method/R", modifiedOnly = FALSE)
+
+bs_data <- read.csv("~/Google Drive/PhD (UZH)/tadnoll/AfonHirnantData_Gilljam_etal_AER_v45ch3.csv", comment.char="#")
+
+bs_data <- bs_data %>%
+  filter(!is.na(preyID) & !is.na(predID))
+
+prey_range <- range(log10(bs_data$preyMass))
+pred_range <- range(log10(bs_data$predMass))
+l_limit <- min(prey_range, pred_range)
+u_limit <- max(prey_range, pred_range)
+
+n_species <- 33
+nbin <- n_species
+minimum <- l_limit
+h <- (u_limit-l_limit)/nbin
+M <- 10^(l_limit + ((0:(nbin-1)+0.5))*h)
+
+
+mass_to_ind <- function(mass){
+  index <- ceiling((mass-minimum)/h)
+  if(index == 0) { index = 1}
+  
+  return(as.integer(index))
+}
+
+
+species_name <- as.character(1:nbin)
+ndim <- length(species_name)
+pred_mat <- matrix(rep(0,ndim*ndim), nrow = ndim, ncol = ndim,
+                   dimnames = list(as.character(1:nbin), as.character(1:nbin)))
+count <- 0
+
+dd <- data.frame(Mi_by_Mj_ratio = double(), row_no = integer())
+
+for(row_no in 1:nrow(bs_data)){
+  
+  count <- count + 1
+  
+  mt <- bs_data[row_no,]
+  prey_mass <- log10(bs_data$preyMass[row_no])
+  pred_mass <- log10(bs_data$predMass[row_no])
+  
+  predator_node <- mass_to_ind(pred_mass)
+  prey_node <- mass_to_ind(prey_mass)
+  
+  Mi_by_Mj_ratio <- (bs_data$preyMass[row_no])/(bs_data$predMass[row_no])
+  
+  dd <- rbind(dd,
+              data.frame(Mi_by_Mj_ratio = Mi_by_Mj_ratio, row_no = row_no))
+  
+  pred_mat[prey_node, predator_node] <- 1
+  
+  
+}
+
+
[…]

### 2021-11-15 inst/main/SIR_from_foodweb.R

@@ -1,0 +1,53 @@
+# 26.03.2021
+# We simulate SIR data from a simulated food web for rule s5
+
+
+fw_name <- "sim_Benguela Pelagic"
+fw <- readRDS("data/sim_Benguela Pelagic.web.Rdata")
+
+pred_mat <- fw$predation.matrix
+
+# Removing isolated nodes
+fw_community <- mat.to.comm(pred.mat = pred_mat, fw_title = fw_name)
+
+# Check if there are any isolated nodes, if yes remove those
+isolated_nodes <- IsolatedNodes(community = fw_community)
+
+
+tp <- trophic_position(web = pred_mat, title = fw_name)
+
+
+
+set.seed(1)
+sir <- sir_from_Tl(TL = tp, trophic_frac = 3.4, sir_base_mean = 8, sir_base_error = 1)
+TL_pred <- TL_from_sir(sir = sir, trophic_frac = 3.4, sir_base = 8)
+for(i in 2:1000){
+  sir <- sir_from_Tl(TL = tp, trophic_frac = 3.4, sir_base_mean = 8, sir_base_error = 1)
+  Trophic_levels <- TL_from_sir(sir = sir, trophic_frac = 3.4, sir_base = 8)
+  TL_pred <- rbind(TL_pred, Trophic_levels)
+  rownames(TL_pred)[1] <- "Trophic_levels"
+}
+
+rule <- "s5"
+fname <- paste0("data/sir_data/", fw_name, "_", rule, ".sir.Rdata")
+# saveRDS(object = TL_pred, file = fname)
+
+
+
+
+
+
+fw_name <- "sim_Broadstone Stream size_agg_v2"
+fw <- readRDS("data/sim_Broadstone Stream size_agg_v2.web.Rdata")
+
+pred_mat <- fw$predation.matrix
+
+# Removing isolated nodes
+fw_community <- mat.to.comm(pred.mat = pred_mat, fw_title = fw_name)
+
+# Check if there are any isolated nodes, if yes remove those
+isolated_nodes <- IsolatedNodes(community = fw_community)
+
+
+tp <- trophic_position(web = pred_mat, title = fw_name)
+# saveRDS(object = tp, file = "data/sir_data/sim_Broadstone Stream size_agg_v2_s_r_2_predator.sir.Rdata")

### 2021-11-15 inst/main/TSS_diet_tl.R

@@ -1,0 +1,59 @@
+
+
+library(ggplot2)
+library(dplyr)
+dd <- readRDS("results/rejection/sim_Broadstone Stream size_agg_v2/rule_s_r_2_predator/N=1e+05_tol=Inf_n_pred = 29/rn_gut=1_N=1e+05_tol=Inf_TSS_sir_gut_s_r_2_l29_prop_1/sim_Broadstone Stream size_agg_v2.Rdata")
+
+
+df <- data.frame(dist_diet = dd$dist_diet, dist_tl = dd$dist_tl, TSS = dd$TSS_fw)
+
+df <- mutate(df, TSS_round = round(TSS, digits = 1), dist_diet_round = round(dist_diet, digits = 1))
+
+# df <- df[sample(x = 1:100000, size = 10000, replace = FALSE ),]
+
+df %>%
+  filter(dist_tl < 1 & TSS_round > 0) %>%
+  # filter(dist_diet == 0) %>%
+ggplot() +
+  geom_point(aes(x = dist_diet, y = dist_tl, color = as.factor(TSS_round)), position = "jitter", size = 4, alpha = 0.5) +
+  theme_classic() +
+  scale_color_brewer(name = "TSS", palette = "Paired")
+
+
+df %>%
+  filter(dist_tl < 3 & TSS_round > 0) %>%
+  ggplot(aes(x = dist_diet, y = dist_tl, fill = TSS)) +
+  geom_raster()
+
+df %>%
+filter(dist_tl < 3 & TSS_round > 0) %>%
+  ggplot() +
+    geom_point(aes(x = dist_tl, y = TSS, color = as.factor(dist_diet_round))) +
+  theme_bw()
+
+
+df %>%
+  filter(dist_tl < 3 & TSS_round > 0) %>%
+  ggplot() +
+  geom_point(aes(x = dist_diet, y = TSS)) +
+  theme_bw()
+
+
+hist(log10(dd$dist_tl))
+
+which(dd$dist_tl >= 6.06042e+13)
+
+df_fil <- df %>%
+  filter(dist_tl <= 10)
+
+TSS_lm <- lm(TSS ~ dist_tl*dist_diet , data = df_fil)
+summary(TSS_lm)
+anova(TSS_lm)
+
+
+
+df %>%
+  filter(dist_tl < 5) %>%
+  ggplot() +
+  geom_point(aes(x = dist_tl, y = TSS), alpha = 0.2) +
+  theme_bw()

### 2021-11-15 inst/main/acc_plot_all_one.R

@@ -1,0 +1,83 @@
+#Use to plot distribution of statistical properties
+
+library(R.utils)
+library(tictoc)
+
+## Loading required libraries
+library(ggpubr); library(plotrix); library(ggplot2)
+library(cowplot); library(latex2exp); library(HDInterval)
+library(doParallel); library(foreach); library(raster)
+library(cheddar); library(dplyr); library(reshape2)
+library(psych); library(DirectedClustering)
+library(readxl)
+
+## Relative path from the project directory
+sourceDirectory("R", modifiedOnly=FALSE)
+
+library(ggjoy)
+
+## Just looking at TSS, ACC, prop.0.corr, prop.1.corr
+
+dist_par_data <- read_excel("data/dist_TSS_conn.xlsx")
+dist_par_data <- dist_par_data[c(1:4,6:15),]
+foodweb_all <- dist_par_data$foodweb
+
+plot_par <- list()
+tot_prop <- 4
+tot_fw <- length(foodweb_all)
+prop_name <-  c("proportion of links correct", "proportion of no links correct",
+                "accuracy", "true skill statistics")
+desc <- "conn_TSS_1"
+for(ind in 1:tot_prop){
+  real_array <- rep(1, tot_fw)
+  pred_prop <- data.frame(prop = double(), foodweb = character())
+  fw_ind <- 1
+  for(foodweb in foodweb_all){
+    
+    dist <- dist_par_data$dist[fw_ind]
+    dirnam <- paste("results/rejection/",foodweb,"/rN=1000_tol=", dist, "_", desc, sep = "")
+    
+    prop_val <- readRDS(paste(c(dirnam,"/properties.Rdata"),collapse = ''))$prop[,ind+13]
+    
+    pred_prop <- rbind(pred_prop, data.frame(prop = prop_val, foodweb = foodweb))
+    
+    fw_ind <- fw_ind + 1
+  }
+  
+  pred_ci<- pred_prop %>%
+    group_by(foodweb) %>%
+    summarise(ci_lower = as.numeric(hdi(prop)[1]), ci_higher = as.numeric(hdi(prop)[2]))
+  
+  red_prop_lines <- data.frame(x0 = as.numeric(real_array))
+  green_prop_lines <- data.frame(x0 = c(as.numeric(pred_ci$ci_lower)),
+                                 x1 = c(as.numeric(pred_ci$ci_higher)))
+  
+  
+  
[…]

### 2021-11-15 inst/main/comp_acc.R

@@ -1,0 +1,48 @@
+
+fw_prop_1 <- readRDS("results/rejection/Benguela Pelagic/rN=1000_tol=0.7_TSS_unif_rall/Benguela Pelagic_prop.Rdata")$prop
+fw_prop_2 <- readRDS("results/rejection/Grasslands/rN=1000_tol=1_TSS_unif_rall/Grasslands_prop.Rdata")$prop
+fw_dist_1 <- 1-fw_prop_1$TSS
+fw_dist_2 <- 1-fw_prop_2$TSS
+fw_name_1 <- "Benguela Pelagic"
+fw_name_2 <- "Grasslands"
+tidy_post <- tibble(prop.1.corr = fw_prop_1$prop.1.corr, prop.0.corr = fw_prop_1$prop.0.corr,
+                    ACC = fw_prop_1$ACC, TSS = fw_prop_1$TSS, dist = fw_dist_1, foodweb = fw_name_1)
+
+tidy_post <- bind_rows(tidy_post,
+                       tibble(prop.1.corr = fw_prop_2$prop.1.corr, prop.0.corr = fw_prop_2$prop.0.corr,
+                              ACC = fw_prop_2$ACC, TSS = fw_prop_2$TSS, dist = fw_dist_2, foodweb = fw_name_2)
+                       )
+alpha_f <- 0.5
+
+
+dd <- data.frame(prop = tidy_post$prop.1.corr, foodweb = tidy_post$foodweb)
+cols <- c("Benguela Pelagic" = "red", "Grasslands" = "blue")
+plot_density <- function(dd, prop_name, cols){
+  
+  plot_dd<- ggplot(dd) +
+      geom_density(aes(x = prop, fill = foodweb), alpha = alpha_f, position = 'identity') +
+      theme_classic() +
+    theme(legend.position = "none", text = element_text(family = "Times New Roman", size = 20), axis.title.y = element_blank(),
+          plot.margin = margin(0,0.5,0.5,1, "cm")) +
+    xlab(prop_name) +
+    scale_fill_manual(values = cols) +
+    xlim(c(0,1))
+  
+  return(plot_dd)
+}
+dd1 <- data.frame(prop = tidy_post$prop.1.corr, foodweb = tidy_post$foodweb)
+p1 <- plot_density(dd = dd1, prop_name = "proportion of presence of links correct", cols = cols)
+dd2 <- data.frame(prop = tidy_post$prop.0.corr, foodweb = tidy_post$foodweb)
[…]

### 2021-11-15 inst/main/data_chilean.R

@@ -1,0 +1,282 @@
+# 07.10.2021
+# Extract the dataset from food webs Coilaco, Guampoe and Trancura
+
+library(dplyr)
+library(ggplot2)
+
+org_data <- read.csv("~/Google Drive/GitHub/C2_comp_qnty/data/raw_data/ChileanRiverData_Gilljam_etal_AER_v45ch3.csv", comment.char="#")
+
+
+###################### Coilaco food web ###########################
+
+bs_data <- org_data %>%
+  filter(locality == "Coilaco")
+
+# We first construct the predation matrix
+
+n_node <- length(unique(c(bs_data$predID, bs_data$preyID)))
+
+pred_ind <- c()
+max_size <- numeric(1)
+min_size <- numeric(1)
+
+min_size <- log10(min(bs_data$preyMass, bs_data$preyMass))
+max_size <- log10(max(bs_data$predMass, bs_data$predMass))
+
+h <- (max_size-min_size)/n_node
+nbin <- n_node
+M <- 10^(min_size + ((0:(nbin-1)+0.5))*h)
+
+mass_to_ind <- function(mass){
+  index <- ceiling((mass-min_size)/h)
+  if(index == 0) {index = 1}
+  return(index)
+}
+
+species_name <- as.character(1:nbin)
+ndim <- length(species_name)
+pred_mat <- matrix(rep(0,ndim*ndim), nrow = ndim, ncol = ndim,
+                   dimnames = list(as.character(1:nbin), as.character(1:nbin)))
+
+
+for(row_no in 1:nrow(bs_data)){
+  
+  mt <- bs_data[row_no,]
+  prey_mass <- log10(bs_data$preyMass[row_no])
+  pred_mass <- log10(bs_data$predMass[row_no])
+  
+  predator_node <- mass_to_ind(pred_mass)
+  prey_node <- mass_to_ind(prey_mass)
+  
+  pred_mat[prey_node, predator_node] <- 1
+  
+}
+
+all.web.info <- list(predation.matrix = pred_mat,
+                     species.sizes = M,
+                     web.name = "Coilaco size_agg")
+
+
+# saveRDS(object = all.web.info, file = "../C2_comp_qnty/data/Coilaco size_agg.web.Rdata")
+
+
+# Now, we construct the diet matrix of predators
+
+uniq_ind <- unique(bs_data$predUniqueID)
+
+n_pred_ind <- length(uniq_ind)
+
[…]

### 2021-11-15 inst/main/dist_plot_WBF.R

@@ -1,0 +1,167 @@
+#Use to plot distribution of food web properties and statistical properties
+
+library(R.utils)
+library(tictoc)
+
+## Loading required libraries
+library(ggpubr); library(plotrix); library(ggplot2)
+library(cowplot); library(latex2exp); library(HDInterval)
+library(doParallel); library(foreach); library(raster)
+library(cheddar); library(dplyr); library(reshape2)
+library(psych); library(DirectedClustering)
+
+## Relative path from the project directory
+sourceDirectory("R", modifiedOnly=FALSE)
+
+library(ggjoy)
+
+web.to.analyse <- "Benguela Pelagic"
+dirnam <- "results/rejection/Benguela Pelagic/rN=1000_tol=0.6_TSS_unif_rall_WBF_3"
+
+prop_val <- readRDS(paste(c(dirnam,"/properties.Rdata"),collapse = ''))$prop
+
+foodweb_data <- load(paste("data/", web.to.analyse, ".web.Rdata", sep=""))
+all.web.info <- get(foodweb_data)
+real_val <- real_prop(all.web.info)
+
+# dd <- subset(prop_val, select = -c(mean_trop_lvl, sd_vulner, sd_gen, mean_path_lt))
+# 
+# dd <- cbind(dd, id = 1:length(dd$connectance))
+# dd <- melt(data = dd, id.vars = "id" )
+# 
+# ggplot(dd, aes(x = variable, y = value, fill = variable)) +
+#   geom_violin(stat = "ydensity", adjust = 16, draw_quantiles = TRUE, trim = FALSE) +
+#   theme_classic() +
+#   coord_flip() +
+#   geom_vline(data = real_val, xintercept = real_val$connectance) + 
+#   scale_color_brewer(palette="Dark2")
+# 
+# real_val <- subset(real_val, select = -c(mean_trop_lvl))
+# 
+# real_val1 <- c(real_val$connectance, real_val$prop_basal, real_val$prop_inter, real_val$prop_top,
+#                real_val$prop_herb, real_val$max_trop_lvl, real_val$mean_omn, real_val$clus_coeff,
+#                real_val$diet_sim, 1, 1, 1, 1)
+# 
+# iris_lines <- data.frame(Species = 1:13, x0 = as.numeric(real_val1))
+# 
+# ggplot(dd, aes(x = value, y = variable)) +
+#   geom_joy() +
+#   theme_joy() +
+#   geom_segment(data = iris_lines, aes(x = x0, xend = x0, y = 1:13,
[…]

### 2021-11-15 inst/main/dist_plot_all_one.R

@@ -1,0 +1,113 @@
+#Use to plot distribution of food web properties
+
+library(R.utils)
+library(tictoc)
+
+## Loading required libraries
+library(ggpubr); library(plotrix); library(ggplot2)
+library(cowplot); library(latex2exp); library(HDInterval)
+library(doParallel); library(foreach); library(raster)
+library(cheddar); library(dplyr); library(reshape2)
+library(psych); library(DirectedClustering)
+library(readxl)
+
+## Relative path from the project directory
+sourceDirectory("R", modifiedOnly=FALSE)
+
+library(ggjoy)
+
+dist_par_data <- read_excel("results/check/check_TSS.xlsx")
+dist_par_data <- dist_par_data[c(1:15),]
+tot_fw <- length(dist_par_data$foodweb)
+foodweb_all <- dist_par_data$foodweb[1:tot_fw]
+
+## Just looking at structural properties of a food web
+
+plot_par <- list()
+tot_prop <- 13
+real_list <- readRDS(file = paste(c("data/","real_prop.Rdata"), collapse = ''))
+#
+for(foodweb in dist_par_data$foodweb){
+  foodweb_data <- load(paste("data/", foodweb, ".web.Rdata", sep=""))
+  all.web.info <- get(foodweb_data)
+  real_list[[foodweb]] <- real_prop(all.web.info)
+}
+# saveRDS(real_list, file = paste(c("data/","real_prop.Rdata"), collapse = ''))
+
+prop_name <-  c("connectance", "proportion basal", "proportion intermediate", "proportion top", 
+                "proportion herbivores", "mean trophic level", "maximum trophic level", "mean omnivory",
+                "clustering coefficient", "SD of generality", "SD of vulnerability", "diet similarity",
+                "mean path length")
+desc <- "TSS_unif_rall"
+for(ind in 1:tot_prop){
+  real_array <- as.numeric(tot_fw)
+  mean_array <- as.numeric(tot_fw)
+  pred_prop <- data.frame(prop = double(), foodweb = character())
+  fw_ind <- 1
+  for(foodweb in foodweb_all){
+    
+    dist <- dist_par_data$dist_r[fw_ind]
+    dirnam <- paste("results/rejection/",foodweb,"/rN=1000_tol=", dist, "_", desc, sep = "")
+    real_array[fw_ind] <- real_list[[foodweb]][ind]
+    
[…]

### 2021-11-15 inst/main/e1_TSS_vs_pred.R

@@ -1,0 +1,122 @@
+##Rule e1
+fw_name <- "sim_Small Reef"
+n <- 50
+dir_org <- paste("results/rejection/", fw_name, "/rule_e1/rN=1e+05_tol=2_TSS_gut_e1_l", sep = "")
+l_acc <- numeric(n)
+r_acc <- numeric(n)
+mean_acc <- numeric(n)
+propn <- 1:n
+long_acc <- data.frame(acc = double(), n = integer())
+for(i in 1:n){
+  dirnam <- paste(dir_org, i, sep = "")
+  fname <- paste(dirnam, "/", fw_name, ".Rdata", sep = "")
+  prop_acc <- readRDS(fname)
+  gut_TSS <- 1 - prop_acc$dist
+  gut_TSS_indexes <- order(gut_TSS, decreasing = TRUE)[1:1e3]
+  sim_TSS <- 1 - prop_acc$acc_ss[gut_TSS_indexes]
+  hdi_acc <- hdi(sim_TSS, credMass = 0.9999999)
+  l_acc[i] <- hdi_acc[1]
+  r_acc[i] <- hdi_acc[2]
+  mean_acc[i] <- mean(sim_TSS)
+  long_acc <- rbind(long_acc,
+                    data.frame(acc = sim_TSS, n = i))
+}
+
+dd <- data.frame(l_acc = l_acc, r_acc = r_acc, mean_acc = mean_acc, propn = propn, main_prop = as.factor(main_prop))
+dd <- rbind(dd_1, dd_2, dd_3)
+ggplot(dd) +
+  # geom_line(aes(x = propn, y = mean_acc)) +
+  geom_point(aes(x = as.factor(propn), y = mean_acc, color = as.factor(main_prop)), 
+             position=position_dodge(width=0.5)) +
+  geom_errorbar(aes(x = propn, ymin = l_acc, ymax = r_acc, color = as.factor(main_prop)), 
+                position=position_dodge(width=0.5)) +
+  xlab("Number of different predator individuals sampled") +
+  ylab("True Skill Statistics") +
+  theme_classic()
+
+ggplot(long_acc) +
+  geom_violin(aes(x = as.factor(n), y = acc), color = "blue", scale = 3, fill = "red", alpha = 0.7) +
+  theme_classic() +
+  ylim(c(-1,1)) +
+  xlab("Number of predator individuals sampled") +
[…]

### 2021-11-15 inst/main/fig1_ms.R

@@ -1,0 +1,363 @@
+# 14.10.2021
+# We construct the Fig. 1 of the ms
+library(latex2exp)
+
+df_min_gut_vs_S <- readRDS("../../../../../Volumes/SSD1/Secondary_storage/PhD_local/C2_files/Misc/df_min_gut_vs_S.RDS")
+
+
+####################################################################################################
+fw_name <- "Broadstone Stream size_agg_v2"
+
+dd_bs <- readRDS(paste0("../../../../../Volumes/SSD1/Secondary_storage/PhD_local/C2_files/", fw_name, "/rule_ind_predator/dd_bs.Rdata"))
+
+min_gut_bs <- df_min_gut_vs_S$n_min_gut[which(df_min_gut_vs_S$foodweb == "Broadstone Stream")]
+
+tsize <- 30
+dd_plot_broadstone_stream <- ggplot(dd_bs) +
+  geom_vline(xintercept = min_gut_bs, color = "red") +
+  geom_line(aes(x = propn, y = mean_acc), 
+            position=position_dodge(width = 3)) +
+  geom_ribbon(aes(x = propn, ymin = l_acc, ymax = r_acc), alpha = 0.5, show.legend = FALSE,
+              position=position_dodge(width = 3)) +
+  xlab("Number of predator guts") +
+  ylab("True skill statistic") +
+  theme_classic() +
+  scale_color_manual(name = "Gut content data", values = c("red", "blue")) +
+
+  labs(tag = "(a)") +
+  theme(plot.tag = element_text(face = "bold")) 
+
+model_TSS <- readRDS(paste0("../../../../../Volumes/SSD1/Secondary_storage/PhD_local/C2_files/", fw_name, "/rule_ind_predator/dd_bs.Rdata"))
+data_TSS <- readRDS(paste0("../../../../../Volumes/SSD1/Secondary_storage/PhD_local/C2_files/", fw_name, "/rule_ind_predator/empirical_TSS_ngut.Rdata"))
+
+
+model_data_TSS_bs <- data.frame(l_model_TSS = model_TSS$l_acc, u_model_TSS = model_TSS$r_acc, mean_model_TSS = model_TSS$mean_acc,
+                                l_data_TSS = data_TSS$l_TSS, u_data_TSS = data_TSS$u_TSS, mean_data_TSS = data_TSS$mean_TSS,
+                                ngut = model_TSS$propn)
[…]

### 2021-11-15 inst/main/fig2_ms.R

@@ -1,0 +1,83 @@
+# 09.11.2021
+
+library(ggplot2)
+library(ggpubr)
+library(dplyr)
+
+df_min_gut_vs_S <- readRDS("results/misc/df_min_gut_vs_S.RDS")
+
+plot_n_min_gut_vs_S <- ggplot(df_min_gut_vs_S) +
+  geom_point(aes(x = S, y = n_min_gut, color = foodweb), size = 5) +
+  theme_classic() +
+  scale_color_discrete(name = "Food web") +
+  xlab("Number of species (S)") +
+  labs(tag = "(a)") +
+  ylab("Number of minimum gut")
+
+plot_n_min_gut_vs_n_max_gut <- ggplot(df_min_gut_vs_S) +
+  geom_point(aes(x = max_ngut, y = n_min_gut, color = foodweb), size = 5) +
+  theme_classic() +
+  scale_color_discrete(name = "Food web") +
+  xlab("Number of maximum guts sampled") +
+  labs(tag = "(b)") +
+  ylab("Number of minimum gut")
+
+plot_n_min_gut_vs_L <- 
+  df_min_gut_vs_S %>%
+  ggplot() +
+  geom_point(aes(x = L, y = n_min_gut, color = foodweb), size = 5) +
+  theme_classic() +
+  scale_color_discrete(name = "Food web") +
+  xlab("Number of links (L)") +
+  labs(tag = "(c)") +
+  ylab("Number of minimum gut")
+
+plot_n_min_gut_vs_C <- ggplot(df_min_gut_vs_S) +
+  geom_point(aes(x = C, y = n_min_gut, color = foodweb), size = 5) +
+  theme_classic() +
+  scale_color_discrete(name = "Food web") +
+  xlab("Connectance (C)") +
+  labs(tag = "(d)") +
+  ylab("Number of minimum gut") 
+
+plot_n_min_gut_vs_n_pred <- 
+  df_min_gut_vs_S %>%
+  ggplot() +
+  geom_point(aes(x = n_pred, y = n_min_gut, color = foodweb), size = 5) +
+  theme_classic() +
+  scale_color_discrete(name = "Food web") +
+  xlab("Number of predator nodes") +
+  labs(tag = "(e)") +
+  ylab("Number of minimum gut")
+
+plot_prop_min_gut_vs_S <- ggplot(df_min_gut_vs_S) +
+  geom_point(aes(x = S, y = prop_min_gut, color = foodweb), size = 5) +
+  theme_classic() +
[…]

### 2021-11-15 inst/main/g1_TSS_vs_pred.R

@@ -1,0 +1,77 @@
+#Rule g1
+#We plot TSS with number of predator diets sampled
+
+
+fw_name <- "Broadstone Stream size_agg"
+n <- 29
+l_acc <- numeric(n)
+r_acc <- numeric(n)
+mean_acc <- numeric(n)
+dir_N <- 1000
+dir_tol <- 2
+n_gut_sample <- 100
+propn <- 1:n
+n_sel <- dir_N*0.1
+main_prop <- 1
+long_acc <- data.frame(acc = double(), n = integer())
+
+desc_main <- "TSS_gut_g1"
+for(i in 1:n){
+  
+  desc <- paste(desc_main, '_l', i, "_prop_",main_prop, sep = '')
+  dir_main <- paste("results/rejection/",fw_name,"/", "rule_", rule,'/N=', dir_N, '_tol=', dir_tol, '_n_pred = ', i,
+                    sep = "")
+  sim_TSS <- c()
+  for(n_sample  in 1:n_gut_sample){
+    dirnam <- paste(c(dir_main, '/rn_gut=', n_sample,'_N=', dir_N, '_tol=', dir_tol,"_", desc), collapse = '')
+    fname <- paste(dirnam, "/", fw_name, ".Rdata", sep = "")
+    prop_acc <- readRDS(fname)
+    gut_TSS <- 1 - prop_acc$dist
+    gut_TSS_indexes <- order(gut_TSS, decreasing = TRUE)[1:n_sel]
+    sim_TSS_temp <- 1 - prop_acc$acc_ss[gut_TSS_indexes]
+    sim_TSS <- c(sim_TSS, sim_TSS_temp)
+  }
+  
+  hdi_acc <- hdi(sim_TSS, credMass = 0.9999)
+  l_acc[i] <- hdi_acc[1]
+  r_acc[i] <- hdi_acc[2]
+  mean_acc[i] <- mean(sim_TSS)
+  dd <- data.frame(l_acc = l_acc, r_acc = r_acc, mean_acc = mean_acc, propn = propn, main_prop = as.factor(main_prop))
+  
+}
+
+
+dd <- rbind(dd_1, dd_2)
+
+dd_plot <- ggplot(dd) +
+  # geom_line(aes(x = propn, y = mean_acc)) +
+  geom_point(aes(x = propn, y = mean_acc, color = as.factor(main_prop)), 
+             position=position_dodge(width=0.5)) +
[…]

### 2021-11-15 inst/main/generate_diet.R

@@ -1,0 +1,117 @@
+#We sample k number of distinct predator individuals from n number of species
+
+
+fw_name <- "Broadstone Stream size_agg"
+rule <- "g1"
+fname <- paste("data/gut_data/",fw_name,"_",rule,".gut.Rdata", sep = "")
+pred_mat <- readRDS(fname)
+
+n_species <- dim(pred_mat)[1]
+n_sample <- 1000
+
+for(i in 1:n_species){
+  species_ind_mat <- matrix(data = 0, nrow = n_sample, ncol = i)
+  for(k in 1:n_sample){
+    species_ind_mat[k,] <- sample(x = 1:n_species, size = i)
+  }
+  f_name <- paste("results/rejection/",fw_name,"/rule_",rule,"/diet/",fw_name,"_", i, ".gut_index.Rdata", sep = "")
+  # saveRDS(object = species_ind_mat, file = f_name)
+}
+
+
+
+#We sample k number of distinct predator guts from n number of predators gut
+
+fw_name <- "Trancura size_agg"
+rule <- "ind_predator"
+fname <- paste("data/gut_data/",fw_name,"_",rule,".gut.Rdata", sep = "")
+gut_mat <- readRDS(fname)
+
+n_ind_gut <- dim(gut_mat)[2]
+n_sample <- 1000
+
+set.seed(1)
+for(i in 1:n_ind_gut){
+  species_ind_mat <- matrix(data = 0, nrow = n_sample, ncol = i)
+  for(k in 1:n_sample){
+    species_ind_mat[k,] <- sample(x = 1:n_ind_gut, size = i)
+  }
+  f_name <- paste("../../../../../Volumes/SSD1/Secondary_storage/PhD_local/C2_files/", fw_name,"/rule_",rule,"/diet/",fw_name,"_", i, ".gut_index.Rdata", sep = "")
+  saveRDS(object = species_ind_mat, file = f_name)
+}
+
+
+
+#We sample k number of distinct predator guts from n number of predators gut
+#the predator guts fall in two sets: first set where body size is less than average and other set where the body size greater
+#than average
+
+fw_name <- "Celtic Sea size_agg"
+rule <- "ind_predator"
+fname <- paste("data/gut_data/",fw_name,"_",rule,".gut.Rdata", sep = "")
+gut_mat <- readRDS(fname)
+
+avg_M <- mean(gut_mat[1,])
[…]

### 2021-11-15 inst/main/ind_TSS_vs_pred_prop.R

@@ -1,0 +1,84 @@
+#Rule ind
+#We plot TSS with number of predator diets sampled for different values of n_sel
+
+fw_name <- "Broadstone Stream size_agg_v2"
+dir_N <- 1e5
+dir_tol <- 2 #different for ind and rand
+n_gut_sample <- 100 
+propn <- seq(8, 1008, by = 20)
+n_sel <- 1 #number of diets of predator selected with maximum TSS
+n <- length(propn)
+l_acc <- numeric(n)
+r_acc <- numeric(n)
+mean_acc <- numeric(n)
+
+desc_main <- "TSS_gut_ind"
+rule <- "ind"
+l_ind <- 1
+for(i in propn){
+  
+  desc <- paste(desc_main, '_l', i, sep = '')
+  # dir_main <- paste("results/rejection/",fw_name,"/", "rule_", rule,'/N=', dir_N, '_tol=', dir_tol, '_n_diet = ', i,
+  #                   sep = "")
+  dir_main <- paste("../../../PhD_local/C2_files/", fw_name, "/rule_", rule ,'/N=', dir_N, '_tol=', dir_tol, '_n_diet = ', i,
+                    sep = "")
+  sim_TSS <- c()
+  for(n_sample  in 1:n_gut_sample){
+    dirnam <- paste(c(dir_main, '/rn_sample=', n_sample,'_N=', dir_N, '_tol=', dir_tol,"_", desc), collapse = '')
+    fname <- paste(dirnam, "/", fw_name, ".Rdata", sep = "")
+    prop_acc <- readRDS(fname)
+    gut_TSS <- 1 - prop_acc$dist
+    gut_TSS_indexes <- order(gut_TSS, decreasing = TRUE)[1:n_sel]
+    sim_TSS_temp <- 1 - prop_acc$acc_ss[gut_TSS_indexes]
+    sim_TSS <- c(sim_TSS, sim_TSS_temp)
+  }
+  
+  range_acc <- range(sim_TSS)
+  l_acc[l_ind] <- range_acc[1]
+  r_acc[l_ind] <- range_acc[2]
+  mean_acc[l_ind] <- mean(sim_TSS)
+  l_ind <- l_ind+1
+}
+
+# dd_real <- data.frame(l_acc = l_acc, r_acc = r_acc, mean_acc = mean_acc, propn = propn, type = "real")
+# dd_rand <- data.frame(l_acc = l_acc, r_acc = r_acc, mean_acc = mean_acc, propn = propn, type = "random")
+
[…]

### 2021-11-15 inst/main/ind_gut_data.R

@@ -1,0 +1,70 @@
+# 07.10.2021
+# We compile individual gut data 
+
+# 14.05.2021
+# We compile individual gut data of predator individuals from the Celtic Sea
+
+
+library(dplyr)
+library(ggplot2)
+
+
+n_node <- 48
+
+pred_ind <- c()
+max_size <- numeric(1)
+min_size <- numeric(1)
+
+bs_data <- read_delim("data/Predator_and_prey_body_sizes_in_marine_food_webs_vsn4.txt", 
+                      "\t", escape_double = FALSE, trim_ws = TRUE)
+bs_data <- bs_data %>%
+  filter(!Prey %in% c("fish larvae", "fish unidentified", "flatfish") ) %>%
+  filter(!is.na(Prey) & !is.na(Predator)) %>%
+  filter(`Geographic location` == "Europe, Celtic Sea ecosystem")
+
+min_size <- log10(min(bs_data$`SI prey mass`, bs_data$`SI predator mass`))
+max_size <- log10(max(bs_data$`SI prey mass`, bs_data$`SI predator mass`))
+
+h <- (max_size-min_size)/n_node
+
+mass_to_ind <- function(mass){
+  index <- ceiling((mass-min_size)/h)
+  if(index == 0) {index = 1}
+  return(index)
+}
+
+uniq_ind <- unique(bs_data$`Individual ID`)
+
+n_pred_ind <- length(uniq_ind)
+
+#The first row of the diet_mat corresponds to the predator identity denoted by a unique number and second row consists of bin number
+diet_mat <- matrix(data = 0, nrow = n_node+2, ncol = n_pred_ind,)
+diet_mat[1,] <- c(1:n_pred_ind)
+i <- 1 
+
+
+for(row_no in 1:nrow(bs_data)){
+  
+  mt <- bs_data[row_no,]
+  
+  pseudo_pred_ind <- which(uniq_ind == bs_data$`Individual ID`[row_no])
+  
+  prey_mass <- log10(mt$`SI prey mass`)
+  prey_name <- mass_to_ind(prey_mass)
+  
+  pred_mass <- log10(mt$`SI predator mass`)
+  pred_name <- mass_to_ind(pred_mass)
+  
+  pred_ind <- mt$`Individual ID`
+  pseudo_pred_ind <- which(uniq_ind == pred_ind) 
+  
+  
+  
[…]

### 2021-11-15 inst/main/linear_test.R

@@ -1,0 +1,23 @@
+#13.12.2020
+library(dplyr)
+library(tidyverse)
+
+m <- 4
+c <- 5
+npoints <- 1001
+x <- seq(0, 100, length.out = npoints)
+epsilon <- rnorm(npoints, mean = 0, sd = 30)
+y <- m * x + c + epsilon
+
+dd_raw <- data.frame(x = x, y = y)
+ggplot(dd_raw) +
+  geom_point(aes(x = x, y = y))
+
+dd_l <- dd_raw %>%
+  filter(x <= 50)
+
+dd_u <- dd_raw %>%
+  filter(x >= 50)
+
+lm_l <- lm(y ~ x, data = dd_l)
+lm_u <- lm(y ~ x, data = dd_u)

### 2021-11-15 inst/main/main.R

@@ -1,0 +1,55 @@
+#Date: 10 June 2020
+
+library(R.utils)
+
+## Relative path from the project directory
+sourceDirectory("R", modifiedOnly=FALSE)
+
+
+sim_fw <- readRDS("data/sim_Small Reef.web.Rdata")
+
+pred_mat <- sim_fw$predation.matrix
+M <- sim_fw$species.sizes
+
+
+# gut_data <- gut_matrix(pred_mat = pred_mat, M = M, pbly_f = pbly_r2)
+gut_data_e1r1 <- gut_matrix_e1r1(pred_mat = pred_mat, M = M, n = model_core_par$n, ni = model_core_par$ni, a = sim_fw$a, ai = sim_fw$ai, aj = sim_fw$aj)
+gut_data_e1 <- gut_matrix_e1(pred_mat = pred_mat, M = M, n = model_core_par$n, ni = model_core_par$ni, a = sim_fw$a, ai = sim_fw$ai, aj = sim_fw$aj)
+gut_data_r1 <- gut_matrix(pred_mat = pred_mat, M = M, pbly_f = pbly_r1)
+fname_gut <- "data/gut_data/sim_Small Reef_e1.gut.Rdata"
+saveRDS(gut_data, file = fname_gut)
+
+
+
+
+sr <- readRDS("results/rejection/sim_Small Reef/rN=1000_tol=0.2_TSS_gut/sim_Small Reef_prop.Rdata")
+sr_web <- sr$web
+sr_gut <- readRDS("data/gut_data/sim_Small Reef.gut.Rdata")
+sr_real_web <- readRDS("data/sim_Small Reef.web.Rdata")$predation.matrix
+
+Plot.matrix_uncertainty_real_gut(web = sr_web, real_web = sr_real_web, gut_data = sr_gut, nsim = 1000)
+
+
+
+sr_all <- readRDS("results/rejection/sim_Small Reef/rN=1e+05_tol=2_TSS_gut/sim_Small Reef.Rdata")
+range(sr_all$dist)
+hist(sr_all$acc_ss[sr_all$dist>1.2 & sr_all$dist<1.3])
+
+
+###################################################################
+##
+
+
+
+
+# Calculating trophic levels from the predation matrix and saving in a file
+
+trop_levels <- trophic_position(web = sim_fw$predation.matrix, title = sim_fw$web.name)
+d_TEF <- 1
+d_ref <- 1
[…]

### 2021-11-15 inst/main/main_mcmc.R

@@ -1,0 +1,89 @@
+library(R.utils); library(tictoc); library(stringr)
+library(ggpubr); library(plotrix); library(ggplot2)
+library(cowplot); library(latex2exp); library(HDInterval)
+library(doParallel); library(foreach); library(raster)
+library(cheddar); library(dplyr); library(reshape2)
+library(psych); library(DirectedClustering); library(colorspace)
+library(coda)
+
+## Start of computation time
+tic("Time elapsed:")
+
+## Relative path from the project directory
+sourceDirectory("R", modifiedOnly=FALSE)
+
+#Remember to check these:
+fw_name <- "Sierra Lakes" 
+prior_dist_pbly <- prior_pbly_unif
+prior_dist_x <- prior_unif_x
+proposal_dist_pbly <- proposal_dist_pbly_unif_mcmc
+proposal_dist_x <- proposal_dist_x_unif_mcmc
+ADBM_par_sd_f <- ADBM_par_sd()
+dist_ss <- dist_TSS
+desc <- "TSS_unif_rall_contd"
+##########################
+
+fname_data <- paste("data_new/", fw_name, ".web.Rdata", sep="")
+fw_data <- readRDS(fname_data)
+
+model <- ratio.power_exp
+model_core_par <- ADBM_core_par(fw_data)
+model_prior_par <- ADBM_prior_par(fw_data)
+input_par <- input_parameters()
+
+## Creating a directory where all the results will be stored
+dir_N <- input_par$N 
+dir_tol <- input_par$tol
+dirnam <- paste(c("results/mcmc/",fw_name,"/",'mN=', dir_N, '_tol=', dir_tol,"_", desc), collapse = '')
+dir.create(dirnam)
+
+output <- mcmc(all.web.info = fw_data, model = model, model_core_par = model_core_par,
+               model_prior_par = model_prior_par, input_parameters = input_par, 
+               dist_ss = dist_ss, prior_dist_pbly= prior_dist_pbly, 
+               prior_dist_x= prior_dist_x, proposal_dist_pbly = proposal_dist_pbly, 
+               proposal_dist_x =  proposal_dist_x, ADBM_par_sd = ADBM_par_sd_f)
+
+saveRDS(output, file = paste(c(dirnam,"/",fw_name,".Rdata"), collapse = ''))
+
+time_elap <- toc()
+print(paste("No.of jumps =", output[[1]]$n_jump))
+
+## Displaying some important information in a pdf file
[…]

### 2021-11-15 inst/main/main_rejection.R

@@ -1,0 +1,74 @@
+library(R.utils); library(tictoc); library(stringr)
+library(ggpubr); library(plotrix); library(ggplot2)
+library(cowplot); library(latex2exp); library(HDInterval)
+library(doParallel); library(foreach); library(raster)
+library(cheddar); library(dplyr); library(reshape2)
+library(psych); library(DirectedClustering); library(colorspace)
+library(ggimage); library(nos); library(bipartite)
+
+## Start of computation time
+tic("Time elapsed:")
+
+## Relative path from the project directory
+sourceDirectory("R", modifiedOnly=FALSE)
+
+#Remember to check these:
+fw_name <- "Tadnoll Brook size_agg" 
+prior_dist_x <- prior_unif_x
+dist_ss <- dist_TSS
+desc <- "TSS_min_a"
+##########################
+
+fname_data <- paste("data/", fw_name, ".web.Rdata", sep = "")
+fw_data <- readRDS(fname_data)
+
+model <- ratio.power_exp
+model_core_par <- ADBM_core_par(fw_data)
+model_prior_par <- ADBM_prior_par(fw_data)
+input_par <- input_parameters()
+
+## Creating a directory where all the results will be stored
+dir_N <- input_par$N 
+dir_tol <- input_par$tol
+dirnam <- paste(c("results/rejection/",fw_name,"/",'rN=', dir_N, '_tol=', dir_tol,"_", desc), collapse = '')
+dir.create(dirnam)
+
+## Running the rejection algorithm
+output <- rejection(all.web.info = fw_data, model = model, model_core_par = model_core_par,
+                    model_prior_par=model_prior_par, input_parameters=input_par, dist_ss = dist_ss,
+                    prior_dist=prior_dist_x, weight_type = "uniform")
+saveRDS(output, file = paste(c(dirnam,"/",fw_name,".Rdata"), collapse = ''))
+
+time_elap <- toc()
+print(paste("Proportion of accepted simulations =", round(dir_N/output$total_sim,3)))
+
+## Displaying some important information in a pdf file
+display_info_rej(prop_acc_sim = round(dir_N/output$total_sim,6), time = time_elap, dirnam = dirnam, ncores = input_par$n_cores)
+
+tic()
+
+## Computing food web properties
+fname_output <- paste(dirnam, "/", fw_name, ".Rdata", sep = "")
+output <- readRDS(file = fname_output)
[…]

### 2021-11-15 inst/main/main_rejection_e1.R

@@ -1,0 +1,86 @@
+library(R.utils); library(tictoc); library(stringr)
+library(ggpubr); library(plotrix); library(ggplot2)
+library(cowplot); library(latex2exp); library(HDInterval)
+library(doParallel); library(foreach); library(raster)
+library(cheddar); library(dplyr); library(reshape2)
+library(psych); library(DirectedClustering); library(colorspace)
+
+
+## Relative path from the project directory
+sourceDirectory("R", modifiedOnly=FALSE)
+
+#Remember to check these:
+fw_name <- "sim_Small Reef" 
+prior_dist_x <- prior_unif_x
+dist_ss <- dist_TSS
+desc_main <- "TSS_gut_e1"
+##########################
+
+fname_data <- paste("data/", fw_name, ".web.Rdata", sep="")
+fw_data <- readRDS(fname_data)
+nspecies <- dim(fw_data$predation.matrix)[1]
+rule <- "e1"
+fname_gut <- paste("data/gut_data/", fw_name, "_", rule, ".gut.Rdata", sep="")
+gut_data_main <- readRDS(fname_gut)
+
+model <- ratio.power_exp
+model_core_par <- ADBM_core_par(fw_data)
+model_prior_par <- ADBM_prior_par(fw_data)
+input_par <- input_parameters()
+
+for(i in 6:nspecies){
+  
+  desc <- paste(desc_main, '_l', i, sep = '')
+  ## Start of computation time
+  tic("Time elapsed:")
+  
+  ## Creating a directory where all the results will be stored
+  dir_N <- input_par$N 
+  dir_tol <- input_par$tol
+  dirnam <- paste(c("results/rejection/",fw_name,"/", "rule_", rule,'/rN=', dir_N, '_tol=', dir_tol,"_", desc), collapse = '')
+  dir.create(dirnam)
+  
+  print(i)
+  ## Running the rejection algorithm
+  output <- rejection_e1(fw_data = fw_data, model = model, model_core_par = model_core_par,
+                         model_prior_par = model_prior_par, input_parameters = input_par, dist_main = dist_ss,
+                         prior_dist = prior_dist_x, gut_data_main = gut_data_main, n_dietbreadth = i,
+                         main_propn = main_propn, weight_type = "epanechnikov")
+  print(i)
+  saveRDS(output, file = paste(c(dirnam,"/",fw_name,".Rdata"), collapse = ''))
+  
+  time_elap <- toc()
[…]

### 2021-11-15 inst/main/main_rejection_e1r1.R

@@ -1,0 +1,71 @@
+library(R.utils); library(tictoc); library(stringr)
+library(ggpubr); library(plotrix); library(ggplot2)
+library(cowplot); library(latex2exp); library(HDInterval)
+library(doParallel); library(foreach); library(raster)
+library(cheddar); library(dplyr); library(reshape2)
+library(psych); library(DirectedClustering); library(colorspace)
+
+## Relative path from the project directory
+sourceDirectory("R", modifiedOnly=FALSE)
+
+#Remember to check these:
+fw_name <- "sim_Small Reef" 
+prior_dist_x <- prior_unif_x
+dist_ss <- dist_TSS
+desc_main <- "TSS_gut_e1r1"
+##########################
+
+fname_data <- paste("data/", fw_name, ".web.Rdata", sep="")
+fw_data <- readRDS(fname_data)
+nspecies <- dim(fw_data$predation.matrix)[1]
+rule <- "e1r1"
+fname_gut <- paste("data/gut_data/", fw_name, "_", rule, ".gut.Rdata", sep="")
+gut_data_main <- readRDS(file = fname_gut)
+main_propn <- 1
+n_gut_sample <- 100
+
+model <- ratio.power_exp
+model_core_par <- ADBM_core_par(fw_data)
+model_prior_par <- ADBM_prior_par(fw_data)
+input_par <- input_parameters()
+
+for(i in 1:nspecies){
+  dir_N <- input_par$N
+  dir_tol <- input_par$tol
+  
+  desc <- paste(desc_main, '_l', i, "_prop_", main_propn, sep = '')
+  
+  fname_sp_ind <- paste("results/rejection/",fw_name,"/rule_r8/diet/", fw_name ,"_",i,".gut_index.Rdata", sep = "")
+  species_ind <- readRDS(fname_sp_ind)
+  
+  dir_main <- paste("results/rejection/",fw_name,"/", "rule_", rule,'/N=', dir_N, '_tol=', dir_tol, '_n_pred = ', i,
+                    sep = "")
+  dir.create(dir_main)
+  for(n_gut in 1:n_gut_sample){
+    ## Start of computation time
+    tic("Time elapsed:")
+    
+    ## Creating a directory where all the results will be stored
+    dirnam <- paste(c(dir_main, '/rn_gut=', n_gut,'_N=', dir_N, '_tol=', dir_tol,"_", desc), collapse = '')
+    dir.create(dirnam)
+    
+    print(i)
+    ## Running the rejection algorithm
[…]

### 2021-11-15 inst/main/main_rejection_gut.R

@@ -1,0 +1,90 @@
+library(R.utils); library(tictoc); library(stringr)
+library(ggpubr); library(plotrix); library(ggplot2)
+library(cowplot); library(latex2exp); library(HDInterval)
+library(doParallel); library(foreach); library(raster)
+library(cheddar); library(dplyr); library(reshape2)
+library(psych); library(DirectedClustering); library(colorspace)
+
+## Start of computation time
+tic("Time elapsed:")
+
+## Relative path from the project directory
+sourceDirectory("R", modifiedOnly=FALSE)
+
+#Remember to check these:
+fw_name <- "sim_Small Reef" 
+prior_dist_x <- prior_unif_x
+dist_ss <- dist_gut
+desc <- "TSS_gut_r5_100"
+##########################
+
+fname_data <- paste("data/", fw_name, ".web.Rdata", sep="")
+fw_data <- readRDS(fname_data)
+rule <- "r5"
+fname_gut <- paste("data/gut_data/", fw_name, "_", rule, ".gut.Rdata", sep="")
+gut_data_org <- readRDS(file = fname_gut)
+gut_data <- gut_data_partial(gut_mat = gut_data_org, propn = 1)
+
+
+model <- ratio.power_exp
+model_core_par <- ADBM_core_par(fw_data)
+model_prior_par <- ADBM_prior_par(fw_data)
+input_par <- input_parameters()
+
+## Creating a directory where all the results will be stored
+dir_N <- input_par$N 
+dir_tol <- input_par$tol
+dirnam <- paste(c("results/rejection/",fw_name,"/",'rN=', dir_N, '_tol=', dir_tol,"_", desc), collapse = '')
+dir.create(dirnam)
+
+## Running the rejection algorithm
+# output <- rejection(all.web.info = fw_data, model = model, model_core_par = model_core_par,
+#                     model_prior_par=model_prior_par, input_parameters=input_par, dist_ss = dist_ss,
+#                     prior_dist=prior_dist_x, gut_data = gut_data)
+
+output <- rejection(all.web.info = fw_data, model = model, model_core_par = model_core_par,
+                        model_prior_par = model_prior_par, input_parameters = input_par, dist_ss = dist_ss,
+                        prior_dist = prior_dist_x, gut_data = gut_data)
+
+saveRDS(output, file = paste(c(dirnam,"/",fw_name,".Rdata"), collapse = ''))
+
+time_elap <- toc()
[…]

### 2021-11-15 inst/main/main_rejection_lbs.R

@@ -1,0 +1,80 @@
+# We look at how food web prediction measured by TSS varies with number of predator gut data and variation in the body size of the predators sampled.
+# The predator guts chosen have body size lower than the average
+# We only fit the diet of predators
+
+library(R.utils); library(tictoc); library(stringr)
+library(bipartite); library(ggpubr)
+library(plotrix); library(ggplot2)
+library(cowplot); library(latex2exp); library(HDInterval)
+library(doParallel); library(foreach); library(raster)
+library(cheddar); library(dplyr); library(reshape2)
+library(psych); library(DirectedClustering); library(colorspace)
+
+
+## Relative path from the project directory
+sourceDirectory("R", modifiedOnly=FALSE)
+
+#Remember to check these:
+fw_name <- "Celtic Sea size_agg" 
+prior_dist_x <- prior_unif_x
+dist_ss <- dist_TSS
+desc_main <- "TSS_gut_ind"
+##########################
+
+fname_data <- paste("data/", fw_name, ".web.Rdata", sep="")
+fw_data <- readRDS(fname_data)
+nspecies <- dim(fw_data$predation.matrix)[1]
+rule <- "lbs_predator"
+fname_gut <- paste("data/gut_data/", fw_name, "_", rule, ".gut.Rdata", sep="")
+gut_data_main <- readRDS(file = fname_gut)
+
+model <- ratio.power_exp
+model_core_par <- ADBM_core_par(fw_data)
+model_prior_par <- ADBM_prior_par(fw_data)
+input_par <- input_parameters()
+n_ind_gut <- 237
+n_gut_sample <- 10
+seq_ind_gut <- seq(237, n_ind_gut, by = 20)
+
+for(i in seq_ind_gut){
+  dir_N <- input_par$N
+  dir_tol <- input_par$tol
+  
+  desc <- paste(desc_main, '_l', i, sep = '')
+  
+  fname_sp_ind <- paste("results/rejection/",fw_name,"/rule_", rule, "/diet/", fw_name ,"_",i,".gut_index.Rdata", sep = "")
+  species_ind <- readRDS(fname_sp_ind)
+  
+  dir_main <- paste("results/rejection/",fw_name,"/", "rule_", rule,'/N=', dir_N, '_tol=', dir_tol, '_n_diet = ', i,
+                    sep = "")
+  dir.create(dir_main)
+  for(n_sample in 1:n_gut_sample){
+    ## Start of computation time
+    tic("Time elapsed:")
+    
+    
+    ## Creating a directory where all the results will be stored
[…]

### 2021-11-15 inst/main/main_rejection_r4.R

@@ -1,0 +1,73 @@
+library(R.utils); library(tictoc); library(stringr)
+library(plotrix); library(ggplot2)
+library(cowplot); library(latex2exp); library(HDInterval)
+library(doParallel); library(foreach); library(raster)
+library(cheddar); library(dplyr); library(reshape2)
+library(psych); library(DirectedClustering); library(colorspace)
+
+## Relative path from the project directory
+sourceDirectory("R", modifiedOnly=FALSE)
+
+#Remember to check these:
+fw_name <- "sim_Small Reef" 
+prior_dist_x <- prior_unif_x
+dist_ss <- dist_SIR
+dist_TSS <- dist_TSS
+desc_main <- "TSS_sir_s4"
+##########################
+
+fname_data <- paste("data/", fw_name, ".web.Rdata", sep="")
+fw_data <- readRDS(fname_data)
+real_pred_mat <- fw_data$predation.matrix
+nspecies <- dim(fw_data$predation.matrix)[1]
+rule <- "s4"
+fname_sir <- paste("data/sir_data/", fw_name, "_", rule, ".sir.Rdata", sep="")
+sir_data_main <- readRDS(file = fname_sir)
+n_sir_sample <- 1
+
+model <- ratio.power_exp
+model_core_par <- ADBM_core_par(fw_data)
+model_prior_par <- ADBM_prior_par(fw_data)
+input_par <- input_parameters()
+
+for(i in 1:nspecies){
+  dir_N <- input_par$N
+  dir_tol <- input_par$tol
+  
+  desc <- paste(desc_main, '_l', i, sep = '')
+  
+  fname_sp_ind <- paste("results/rejection/",fw_name,"/rule_s4/SIR/", fw_name ,"_",i,".SIR_index.Rdata", sep = "")
+  species_ind <- readRDS(fname_sp_ind)
+  
+  dir_main <- paste("results/rejection/",fw_name,"/", "rule_", rule,'/N=', dir_N, '_tol=', dir_tol, '_n_pred = ', i,
+                    sep = "")
+  dir.create(dir_main)
+  for(n_sir in 1:n_sir_sample){
+    ## Start of computation time
+    tic("Time elapsed:")
+    
+    ## Creating a directory where all the results will be stored
+    dirnam <- paste(c(dir_main, '/rn_sir=', n_sir,'_N=', dir_N, '_tol=', dir_tol,"_", desc), collapse = '')
+    dir.create(dirnam)
+    
+    print(i)
+    ## Running the rejection algorithm
[…]

### 2021-11-15 inst/main/main_rejection_r5.R

@@ -1,0 +1,91 @@
+library(R.utils); library(tictoc); library(stringr)
+library(ggpubr); library(plotrix); library(ggplot2)
+library(cowplot); library(latex2exp); library(HDInterval)
+library(doParallel); library(foreach); library(raster)
+library(cheddar); library(dplyr); library(reshape2)
+library(psych); library(DirectedClustering); library(colorspace)
+
+
+## Relative path from the project directory
+sourceDirectory("R", modifiedOnly=FALSE)
+
+#Remember to check these:
+fw_name <- "sim_Small Reef" 
+prior_dist_x <- prior_unif_x
+#dist_ss <- dist_exact_main
+desc_main <- "TSS_gut_r5"
+##########################
+
+fname_data <- paste("data/", fw_name, ".web.Rdata", sep="")
+fw_data <- readRDS(fname_data)
+nspecies <- dim(fw_data$predation.matrix)[1]
+rule <- "r5"
+fname_gut <- paste("data/gut_data/", fw_name, "_", rule, ".gut.Rdata", sep="")
+gut_data_main <- readRDS(file = fname_gut)
+
+model <- ratio.power_exp
+model_core_par <- ADBM_core_par(fw_data)
+model_prior_par <- ADBM_prior_par(fw_data)
+input_par <- input_parameters()
+
+for(i in 1:nspecies){
+  
+  # indexes <- gut_data_pred_index(pred_index = c(1:nspecies), n = i)
+  # dist_ss <- dist_exact_index(index = indexes)
+  # gut_data <- matrix(0, nrow = nspecies, ncol = nspecies)
+  # 
+  # gut_data[,indexes] = gut_data_main[,indexes]
+  
+  desc <- paste(desc_main, '_la', i, sep = '')
+  ## Start of computation time
+  tic("Time elapsed:")
+  
+  ## Creating a directory where all the results will be stored
+  dir_N <- input_par$N 
+  dir_tol <- input_par$tol
+  dirnam <- paste(c("results/rejection/",fw_name,"/",'rN=', dir_N, '_tol=', dir_tol,"_", desc), collapse = '')
+  dir.create(dirnam)
+  
+  print(i)
+  ## Running the rejection algorithm
+  output <- rejection(all.web.info = fw_data, model = model, model_core_par = model_core_par,
+                      model_prior_par=model_prior_par, input_parameters=input_par, dist_ss = dist_ss,
+                      prior_dist=prior_dist_x, gut_data = gut_data)
+  print(i)
[…]

### 2021-11-15 inst/main/main_rejection_r6.R

@@ -1,0 +1,100 @@
+library(R.utils); library(tictoc); library(stringr)
+library(ggpubr); library(plotrix); library(ggplot2)
+library(cowplot); library(latex2exp); library(HDInterval)
+library(doParallel); library(foreach); library(raster)
+library(cheddar); library(dplyr); library(reshape2)
+library(psych); library(DirectedClustering); library(colorspace)
+
+
+## Relative path from the project directory
+sourceDirectory("R", modifiedOnly=FALSE)
+
+#Remember to check these:
+fw_name <- "sim_Small Reef" 
+prior_dist_x <- prior_unif_x
+dist_ss <- dist_gut
+desc_main <- "TSS_gut_r6"
+##########################
+
+fname_data <- paste("data/", fw_name, ".web.Rdata", sep="")
+fw_data <- readRDS(fname_data)
+nspecies <- dim(fw_data$predation.matrix)[1]
+rule <- "r6"
+fname_gut <- paste("data/gut_data/", fw_name, "_", rule, ".gut.Rdata", sep="")
+gut_data_main <- readRDS(file = fname_gut)
+main_propn <- 0.7
+
+model <- ratio.power_exp
+model_core_par <- ADBM_core_par(fw_data)
+model_prior_par <- ADBM_prior_par(fw_data)
+input_par <- input_parameters()
+
+for(i in 1:nspecies){
+  
+  # indexes <- gut_data_pred_index(pred_index = c(1:nspecies), n = i)
+  # dist_ss <- dist_exact_index(index = indexes)
+  # gut_data <- matrix(0, nrow = nspecies, ncol = nspecies)
+  # 
+  # for(k in indexes){
+  #   link_ind <- which(as.numeric(gut_data_main[,k]) == 1)
+  #   n_link_ind <- length(link_ind)
+  #   nsubsamples <- as.integer(main_propn*n_link_ind)
+  #   sub_link_ind <- sample(link_ind, nsubsamples)
+  #   gut_data[,k][c(sub_link_ind)] <- gut_data_main[,k][c(sub_link_ind)]
+  # }
+  # 
+  
+  desc <- paste(desc_main, '_l', i, "_prop_", main_propn, sep = '')
+  ## Start of computation time
+  tic("Time elapsed:")
+  
+  ## Creating a directory where all the results will be stored
+  dir_N <- input_par$N 
+  dir_tol <- input_par$tol
[…]

### 2021-11-15 inst/main/main_rejection_s3.R

@@ -1,0 +1,73 @@
+library(R.utils); library(tictoc); library(stringr)
+library(plotrix); library(ggplot2)
+library(cowplot); library(latex2exp); library(HDInterval)
+library(doParallel); library(foreach); library(raster)
+library(cheddar); library(dplyr); library(reshape2)
+library(psych); library(DirectedClustering); library(colorspace)
+
+## Relative path from the project directory
+sourceDirectory("R", modifiedOnly=FALSE)
+
+#Remember to check these:
+fw_name <- "sim_Small Reef" 
+prior_dist_x <- prior_unif_x
+dist_ss <- dist_SIR
+dist_TSS <- dist_TSS
+desc_main <- "TSS_sir_s3"
+##########################
+
+fname_data <- paste("data/", fw_name, ".web.Rdata", sep="")
+fw_data <- readRDS(fname_data)
+real_pred_mat <- fw_data$predation.matrix
+nspecies <- dim(fw_data$predation.matrix)[1]
+rule <- "s3"
+fname_sir <- paste("data/sir_data/", fw_name, "_", rule, ".sir.Rdata", sep="")
+sir_data_main <- readRDS(file = fname_sir)
+n_sir_sample <- 1
+
+model <- ratio.power_exp
+model_core_par <- ADBM_core_par(fw_data)
+model_prior_par <- ADBM_prior_par(fw_data)
+input_par <- input_parameters()
+
+for(i in 1:nspecies){
+  dir_N <- input_par$N
+  dir_tol <- input_par$tol
+  
+  desc <- paste(desc_main, '_l', i, sep = '')
+  
+  fname_sp_ind <- paste("results/rejection/",fw_name,"/rule_s3/SIR/", fw_name ,"_",i,".SIR_index.Rdata", sep = "")
+  species_ind <- readRDS(fname_sp_ind)
+  
+  dir_main <- paste("results/rejection/",fw_name,"/", "rule_", rule,'/N=', dir_N, '_tol=', dir_tol, '_n_pred = ', i,
+                    sep = "")
+  dir.create(dir_main)
+  for(n_sir in 1:n_sir_sample){
+    ## Start of computation time
+    tic("Time elapsed:")
+    
+    ## Creating a directory where all the results will be stored
+    dirnam <- paste(c(dir_main, '/rn_sir=', n_sir,'_N=', dir_N, '_tol=', dir_tol,"_", desc), collapse = '')
+    dir.create(dirnam)
+    
+    print(i)
+    ## Running the rejection algorithm
[…]

### 2021-11-15 inst/main/main_rejection_s5.R

@@ -1,0 +1,74 @@
+# 08.04.2021
+library(R.utils); library(tictoc); library(stringr)
+library(plotrix); library(ggplot2)
+library(cowplot); library(latex2exp); library(HDInterval)
+library(doParallel); library(foreach); library(raster)
+library(cheddar); library(dplyr); library(reshape2)
+library(psych); library(DirectedClustering); library(colorspace)
+
+## Relative path from the project directory
+sourceDirectory("R", modifiedOnly=FALSE)
+
+#Remember to check these:
+fw_name <- "sim_Benguela Pelagic" 
+prior_dist_x <- prior_unif_x
+dist_ss <- dist_SIR
+dist_TSS <- dist_TSS
+desc_main <- "TSS_sir_s5"
+##########################
+
+fname_data <- paste("data/", fw_name, ".web.Rdata", sep="")
+fw_data <- readRDS(fname_data)
+real_pred_mat <- fw_data$predation.matrix
+nspecies <- dim(fw_data$predation.matrix)[1]
+rule <- "s5"
+fname_sir <- paste("data/sir_data/", fw_name, "_", rule, ".sir.Rdata", sep="")
+sir_data_main <- readRDS(file = fname_sir)
+n_sir_sample <- 10
+
+model <- ratio.power_exp
+model_core_par <- ADBM_core_par(fw_data)
+model_prior_par <- ADBM_prior_par(fw_data)
+input_par <- input_parameters()
+
+for(i in 1:nspecies){
+  dir_N <- input_par$N
+  dir_tol <- input_par$tol
+  
+  desc <- paste(desc_main, '_l', i, sep = '')
+  
+  fname_sp_ind <- paste("results/rejection/",fw_name,"/rule_", rule, "/sir/", fw_name ,"_",i,".sir_index.Rdata", sep = "")
+  species_ind <- readRDS(fname_sp_ind)
+  
+  dir_main <- paste("results/rejection/",fw_name,"/", "rule_", rule,'/N=', dir_N, '_tol=', dir_tol, '_n_pred = ', i,
+                    sep = "")
+  dir.create(dir_main)
+  for(n_sir in 1:n_sir_sample){
+    ## Start of computation time
+    tic("Time elapsed:")
+    
+    ## Creating a directory where all the results will be stored
+    dirnam <- paste(c(dir_main, '/rn_sir=', n_sir,'_N=', dir_N, '_tol=', dir_tol,"_", desc), collapse = '')
[…]

### 2021-11-15 inst/main/main_rejection_s_r_1.R

@@ -1,0 +1,82 @@
+# 09.03.2021
+library(R.utils); library(tictoc); library(stringr)
+library(plotrix); library(ggplot2)
+library(cowplot); library(latex2exp); library(HDInterval)
+library(doParallel); library(foreach); library(raster)
+library(cheddar); library(dplyr); library(reshape2)
+library(psych); library(DirectedClustering); library(colorspace)
+
+
+## Relative path from the project directory
+sourceDirectory("R", modifiedOnly=FALSE)
+
+#Remember to check these:
+fw_name <- "sim_Small Reef" 
+
+prior_dist_x <- prior_s_r_1
+dist_ss <- dist_TSS
+desc_main <- "TSS_sir_gut_s_r_1"
+##########################
+
+fname_data <- paste("data/", fw_name, ".web.Rdata", sep="")
+fw_data <- readRDS(fname_data)
+nspecies <- dim(fw_data$predation.matrix)[1]
+rule <- "s_r_1"
+fname_gut <- paste("data/gut_data/", fw_name, "_", rule, ".gut.Rdata", sep="")
+gut_data_main <- readRDS(file = fname_gut)
+
+main_propn <- 1
+
+# Number of gut samples for a single set of predators
+n_gut_sample <- 100 
+
+model <- ratio.power_exp
+model_core_par <- ADBM_core_par(fw_data)
+# model_prior_par <- ADBM_prior_par(fw_data)
+# The prior is chosen from a posterior distribution from rule_s3
+fname_prior <- paste("data/prior_par/", fw_name, "_", rule, ".prior.Rdata", sep="")
+model_prior_par <- readRDS(file = fname_prior)
+
+input_par <- input_parameters()
+
+for(i in 1:nspecies){
+  dir_N <- input_par$N
+  dir_tol <- input_par$tol
+  
+  desc <- paste(desc_main, '_l', i, "_prop_", main_propn, sep = '')
+  
+  fname_sp_ind <- paste("results/rejection/",fw_name,"/rule_", rule, "/diet/", fw_name ,"_",i,".gut_index.Rdata", sep = "")
+  species_ind <- readRDS(fname_sp_ind)
+  
+  dir_main <- paste("results/rejection/",fw_name,"/", "rule_", rule,'/N=', dir_N, '_tol=', dir_tol, '_n_pred = ', i,
+                    sep = "")
+  dir.create(dir_main)
+  for(n_gut in 1:n_gut_sample){
+    ## Start of computation time
+    tic("Time elapsed:")
+    
[…]

### 2021-11-15 inst/main/main_rejection_s_r_2.R

@@ -1,0 +1,82 @@
+# 05.05.2021
+library(R.utils); library(tictoc); library(stringr)
+library(plotrix); library(ggplot2)
+library(cowplot); library(latex2exp); library(HDInterval)
+library(doParallel); library(foreach); library(raster)
+library(cheddar); library(dplyr); library(reshape2)
+library(psych); library(DirectedClustering); library(colorspace)
+library(bipartite)
+
+## Relative path from the project directory
+sourceDirectory("R", modifiedOnly=FALSE)
+
+#Remember to check these:
+fw_name <- "sim_Broadstone Stream size_agg_v2" 
+
+prior_dist_x <- prior_unif_x
+desc_main <- "TSS_sir_gut_s_r_2"
+##########################
+
+fname_data <- paste("data/", fw_name, ".web.Rdata", sep="")
+fw_data <- readRDS(fname_data)
+nspecies <- dim(fw_data$predation.matrix)[1]
+pred_nodes <- which(colSums(fw_data$predation.matrix)>0)
+rule <- "s_r_2_predator"
+# fname_gut <- paste("data/gut_data/", fw_name, "_", rule, ".gut.Rdata", sep="")
+# gut_data_main <- readRDS(file = fname_gut)
+gut_data_main <- fw_data$predation.matrix
+fname_sir <- paste("data/sir_data/", fw_name, "_", rule, ".sir.Rdata", sep="")
+sir_data_main <- readRDS(file = fname_sir)
+
+main_propn <- 1
+
+# Number of gut samples for a single set of predators
+n_gut_sample <- 1 
+
+model <- ratio.power_exp
+model_core_par <- ADBM_core_par(fw_data)
+model_prior_par <- ADBM_prior_par(fw_data)
+
+input_par <- input_parameters()
+
+for(i in nspecies:nspecies){
+  dir_N <- input_par$N
+  dir_tol <- input_par$tol
+  
+  desc <- paste(desc_main, '_l', i, "_prop_", main_propn, sep = '')
+  
+  species_ind <- i
+  
+  dir_main <- paste("results/rejection/",fw_name,"/", "rule_", rule,'/N=', dir_N, '_tol=', dir_tol, '_n_pred = ', i,
+                    sep = "")
+  dir.create(dir_main)
+  
+  for(n_gut in 1:n_gut_sample){
+    ## Start of computation time
+    tic("Time elapsed:")
+    
+    ## Creating a directory where all the results will be stored
[…]

### 2021-11-15 inst/main/main_smc.R

@@ -1,0 +1,94 @@
+library(R.utils); library(tictoc); library(stringr)
+library(ggpubr); library(plotrix); library(ggplot2)
+library(cowplot); library(latex2exp); library(HDInterval)
+library(doParallel); library(foreach); library(raster)
+library(cheddar); library(dplyr); library(reshape2)
+library(psych); library(DirectedClustering); library(colorspace)
+
+## Start of computation time
+tic("Time elapsed:")
+
+## Relative path from the project directory
+sourceDirectory("R", modifiedOnly=FALSE)
+
+#Remember to check these:
+fw_name <- "Benguela Pelagic" 
+prior_dist_pbly <- prior_prob_joint_smc
+prior_dist_x <- prior_unif_x
+proposal_dist_pbly <- proposal_prob_joint_smc
+proposal_dist_x <- proposal_dist_joint_x_smc
+dist_ss <- dist_TSS
+desc <- "TSS_unif_rall"
+##########################
+
+fname_data <- paste("data_new/", fw_name, ".web.Rdata", sep="")
+fw_data <- readRDS(fname_data)
+
+npar <- 4
+model <- ratio.power_exp
+model_core_par <- ADBM_core_par(fw_data)
+model_prior_par <- ADBM_prior_par(fw_data)
+epsilon <- epsilon_t()
+input_par <- input_parameters()
+
+## Creating a directory where all the results will be stored
+dir_N <- input_par$N 
+dir_tol <- input_par$tol
+dirnam <- paste(c("results/smc/",fw_name,"/",'sN=', dir_N, '_tol=', dir_tol,"_", desc), collapse = '')
+dir.create(dirnam)
+
+output <- smc(all.web.info = fw_data, model = model, model_core_par,
+                      model_prior_par, input_par, dist_ss,
+                      prior_dist_x, prior_dist_pbly, proposal_dist_x,
+                      proposal_dist_pbly, epsilon, npar)
+
+saveRDS(output, file = paste(c(dirnam,"/",fw_name,".Rdata"), collapse = ''))
+
+time_elap <- toc()
+
+## Displaying some important information in a pdf file
+display_info_smc(time = time_elap, dirnam = dirnam)
+
+fname_output <- paste(dirnam, "/", fw_name, ".Rdata", sep = "")
+output <- readRDS(file = fname_output)
+
+## Creating parameters'distribution graph
+plot_smc(output, dirnam)
+
+for(n_th in 1:5){
[…]

### 2021-11-15 inst/main/main_subset.R

@@ -1,0 +1,49 @@
+library(R.utils)
+library(tictoc)
+
+## Loading required libraries
+library(ggpubr); library(plotrix); library(ggplot2)
+library(cowplot); library(latex2exp); library(HDInterval)
+library(doParallel); library(foreach); library(raster)
+library(cheddar); library(dplyr); library(reshape2)
+
+library(psych); library(DirectedClustering); library(colorspace)
+library(stringr)
+
+sourceDirectory("R", modifiedOnly=FALSE)
+
+foodweb <- "Benguela Pelagic"
+dirnam <- "rN=10000_tol=1_connectance_prop"
+
+fw_data <- readRDS(paste("results/rejection/", foodweb, "/", dirnam, "/", foodweb, ".Rdata", sep = ""))
+
+order_index_dist <- order(fw_data$dist)
+sort_fw_dist <- sort(fw_data$dist)
+till <- 5000
+tol <- sort_fw_dist[till]
+
+sub_index <- which(fw_data$dist <= tol)
+sub_index <- sub_index[1:till]
+  
+sub_fw_data <- list(acc_ss = fw_data$acc_ss[sub_index], dist = fw_data$dist[sub_index], 
+                       post_dists = fw_data$post_dists[sub_index,], total_sim = till)
+
+dirnam_sub <- "rN=5000_tol=1_connectance_prop"
+dirnam_sub <- paste("results/rejection/", foodweb, "/", dirnam_sub, sep = "")
+dir.create(dirnam_sub)
+fname <- paste(dirnam_sub, "/", foodweb, ".Rdata", sep = "")
+saveRDS(sub_fw_data, file = fname)
+
+foodweb_data <- load(paste("data/", foodweb, ".web.Rdata", sep=""))
+all.web.info <- get(foodweb_data)
+model_core_par <- ADBM_core_par(all.web.info)
+model_prior_par <- ADBM_prior_par(all.web.info)
+model <- ratio.power_exp
+desc <- "conn_prop_rall"
+prior_dist = prior_unif_x
+
+## Plotting the real and predicted food web matrix alongwith some food web properties
+plot_foodweb(real_foodweb = all.web.info, predicted_foodweb = sub_fw_data,
+             dirnam = dirnam_sub, model_core_par = model_core_par, 
+             model_prior_par = model_prior_par,
+             model = model, desc=desc, prior_dist_x = prior_dist, web.to.analyse = foodweb)

### 2021-11-15 inst/main/mcmc_thin.R

@@ -1,0 +1,17 @@
+foodweb <- "sim_Small Reef"
+dirnam <- paste("results/mcmc/",foodweb,"/mN=8e+05_tol=0.3_TSS_unif_rall", sep = "")
+fname <- paste(dirnam, "/", foodweb, ".Rdata", sep = "")
+raw_result <- readRDS(fname)[[1]]
+
+nlag <- lag_mcmc(raw_result$post_dists)
+
+t_length <- dim(raw_result$post_dists)[1]
+n_take <- as.integer(t_length/nlag)
+ind <- nlag*(2:n_take)
+
+
+result <- list(acc_ss = raw_result$acc_ss[ind], dist = raw_result$dist[ind],
+               post_dists = raw_result$post_dists[ind,], total_sim = raw_result$total_sim)
+
+fname_new <- paste(dirnam, "/", foodweb, "_thin.Rdata", sep = "")
+saveRDS(result, file = fname_new)

### 2021-11-15 inst/main/model_mse_vs_empirical_mse.R

@@ -1,0 +1,435 @@
+# 31.05.2021
+# Plot model mse vs empirical mse
+
+
+########### Broadstone Stream size_agg_v2
+
+propn <- c(8, 28, 48, 68, 88, 108, 208, 308, 408, 508, 808, 1008)
+desc_main <- "TSS_gut_ind"
+rule <- "ind_predator"
+n_gut_sample <- 100
+dir_N <- 1e5
+dir_tol <- Inf
+
+prop_name <- c("connectance", "prop_basal", "prop_inter", "prop_top", "prop_herb",
+               "mean_omn", "clus_coeff", "sd_gen", "sd_vulner", "mean_max_trophic_sim", "mean_path_lt",
+               "nest_prop")
+
+n_prop <- length(prop_name)
+plot_list <- list()
+
+# Computing the max SE for a property (ADBM)
+max_error <- numeric(n_prop)
+min_error <- numeric(n_prop)
+
+fw_name <- "Broadstone Stream size_agg_v2"
+
+foodweb_data <- readRDS(paste("data/", fw_name, ".web.Rdata", sep=""))
+real_prop_org <- real_prop_predator(foodweb_data)
+
+SE_vs_ngut <- data.frame(l_SE = double(), u_SE = double(), mean_SE = double(),
+                         ngut = integer(),
+                         foodweb = character())
+
+for(ngut in propn){
+  
+  desc <- paste(desc_main, '_l', ngut, sep = '')
+  dir_main <- paste("../../../PhD_local/C2_files/", fw_name, "/rule_", rule ,'/N=', dir_N, '_tol=', dir_tol, '_n_diet = ', ngut,
+                    sep = "")
+  fname <- paste(dir_main, "/", fw_name, "_prop.Rdata", sep = "")
+  
+  prop_data_org <- readRDS(fname)
+  prop_all <- prop_data_org$prop
+  real_prop <- real_prop_org[prop_name]
+  
+  err_mat <- prop_all[prop_name]
+  
+  for(i in 1:n_gut_sample){
+    err_mat[i,] <- abs(err_mat[i,] - real_prop)
+  }
+  
+  for(i in 1:n_prop){
+    max_error_temp <- max(as.numeric(na.omit(err_mat[,i])))
+    print(max_error_temp)
+    max_error[i] <- max(max_error_temp, max_error[i])
+    
+    min_error_temp <- min(as.numeric(na.omit(err_mat[,i])))
+    min_error[i] <- min(min_error_temp, min_error[i])
+  }
+  
[…]

### 2021-11-15 inst/main/par_dist_comp.R

@@ -1,0 +1,84 @@
+# Used to compare predicted parameter values of posterior distribution from different ABC methods
+
+library(HDInterval)
+library(ggplot2)
+
+foodweb <- "Broadstone Stream"
+foodweb_data <- load(paste("data/", web.to.analyse, ".web.Rdata", sep=""))
+all.web.info <- get(foodweb_data)
+
+dir_rej <- "rN=1000_tol=0.7_TSS_unif_rall"
+dir_mcmc <- "mN=1e+05_tol=0.7_TSS_unif_rall"
+rej_data <- readRDS(paste("results/rejection/", foodweb, "/", dir_rej, "/", foodweb, ".Rdata", sep = ""))
+mcmc_data <- readRDS(paste("results/mcmc/", foodweb, "/", dir_mcmc, "/", foodweb, ".Rdata", sep = ""))
+# smc_data <- readRDS("results/smc/Benguela Pelagic/sN=1000_tol=0.6_TSS_unif_rall_WBF/Benguela Pelagic.Rdata")
+pnas_data <- data.frame(a = log10(1.08e-22), ai = -2, aj = -1.85, r.b = log10(8.43e-2))
+
+rej_post <- rej_data$post_dists
+mcmc_post <- mcmc_data[[1]]$post_dists
+after_burn_mcmc_post <- after_burn(mcmc_post)
+after_thin <- thinning(after_burn_mcmc_post, 140)
+# smc_post <- smc_data$post_dists[,,5] * smc_data$w[,5]
+
+rej_par <- hdi(rej_post)
+mcmc_par <- hdi(after_thin)
+# smc_par <- hdi(smc_post)
+pp <- ADBM_prior_par(all.web.info)
+prior_par <- array(dim = c(2,4))
+prior_par[1,1] <- pp$l_log_a
+prior_par[2,1] <- pp$r_log_a
+prior_par[1,2] <- pp$l_ai
+prior_par[2,2] <- pp$r_ai
+prior_par[1,3] <- pp$l_aj
+prior_par[2,3] <- pp$r_aj
+prior_par[1,4] <- pp$l_log_r.b
+prior_par[2,4] <- pp$r_log_r.b
+
+
+i <- 2
+j <- 5
+
+#Prior parameters
[…]

### 2021-11-15 inst/main/par_dist_comp_all.R

@@ -1,0 +1,91 @@
+# Used to compare predicted parameter values of posterior distribution from different ABC methods
+
+library(HDInterval)
+library(ggplot2)
+library(readxl)
+
+dist_par_data <- read_excel("data/dist_par_data.xlsx")
+ind <- 1
+for(foodweb in dist_par_data$foodweb){
+  
+  foodweb_data <- load(paste("data/", web.to.analyse, ".web.Rdata", sep=""))
+  all.web.info <- get(foodweb_data)
+  
+  dir_rej <- paste("rN=1000_tol=", dist_par_data$dist[ind] ,"_TSS_unif_rall", sep = "")
+  dir_mcmc <- paste("mN=1e+05_tol=", dist_par_data$dist[ind] ,"_TSS_unif_rall", sep = "")
+  rej_data <- readRDS(paste("results/rejection/", foodweb, "/", dir_rej, "/", foodweb, ".Rdata", sep = ""))
+  mcmc_data <- readRDS(paste("results/mcmc/", foodweb, "/", dir_mcmc, "/", foodweb, ".Rdata", sep = ""))
+  # smc_data <- readRDS("results/smc/Benguela Pelagic/sN=1000_tol=0.6_TSS_unif_rall_WBF/Benguela Pelagic.Rdata")
+  pnas_data <- data.frame(a = log10(dist_par_data$a[ind]), ai = dist_par_data$ai[ind], 
+                          aj = dist_par_data$aj[ind], r.b = dist_par_data$r.b[ind])
+  
+  rej_post <- rej_data$post_dists
+  mcmc_post <- mcmc_data[[1]]$post_dists
+  after_burn_mcmc_post <- after_burn(mcmc_post)
+  after_thin <- thinning(after_burn_mcmc_post, 140)
+  # smc_post <- smc_data$post_dists[,,5] * smc_data$w[,5]
+  
+  rej_par <- hdi(rej_post)
+  mcmc_par <- hdi(after_thin)
+  # smc_par <- hdi(smc_post)
+  pp <- ADBM_prior_par(all.web.info)
+  prior_par <- array(dim = c(2,4))
+  prior_par[1,1] <- pp$l_log_a
+  prior_par[2,1] <- pp$r_log_a
+  prior_par[1,2] <- pp$l_ai
+  prior_par[2,2] <- pp$r_ai
+  prior_par[1,3] <- pp$l_aj
+  prior_par[2,3] <- pp$r_aj
[…]

### 2021-11-15 inst/main/r7_TSS_vs_pred.R

@@ -1,0 +1,134 @@
+##Rule r7
+
+TSS_vs_pred_TSS <- function(main_prop){
+  fw_name <- "sim_Small Reef"
+  n <- 50
+  dir_org <- paste("results/rejection/", fw_name, "/rN=1e+05_tol=2_TSS_gut_r7_l", sep = "")
+  l_acc <- numeric(n)
+  r_acc <- numeric(n)
+  mean_acc <- numeric(n)
+  propn <- 1:n
+  long_acc <- data.frame(acc = double(), n = integer())
+  for(i in 1:n){
+    dirnam <- paste(dir_org, i,"_prop_", main_prop, sep = "")
+    fname <- paste(dirnam, "/", fw_name, ".Rdata", sep = "")
+    prop_acc <- readRDS(fname)
+    gut_TSS <- 1 - prop_acc$dist
+    gut_TSS_indexes <- which(gut_TSS > 0.8)
+    sim_TSS <- 1 - prop_acc$acc_ss[gut_TSS_indexes]
+    hdi_acc <- hdi(sim_TSS, credMass = 0.9999999)
+    l_acc[i] <- hdi_acc[1]
+    r_acc[i] <- hdi_acc[2]
+    mean_acc[i] <- mean(sim_TSS)
+    long_acc <- rbind(long_acc,
+                      data.frame(acc = sim_TSS, n = i))
+  }
+  
+  
+  dd <- data.frame(l_acc = l_acc, r_acc = r_acc, mean_acc = mean_acc, propn = propn, main_prop = as.factor(main_prop))
+  return(dd)
+}
+
+
+
+dd_1 <- TSS_vs_pred_TSS(main_prop = 0.2)
+dd_2 <- TSS_vs_pred_TSS(main_prop = 0.5)
+dd_3 <- TSS_vs_pred_TSS(main_prop = 1)
+
+dd <- rbind(dd_1, dd_2, dd_3)
+ggplot(dd) +
+  # geom_line(aes(x = propn, y = mean_acc)) +
+  geom_point(aes(x = propn, y = mean_acc, color = as.factor(main_prop)), 
+             position=position_dodge(width=0.5)) +
+  geom_errorbar(aes(x = propn, ymin = l_acc, ymax = r_acc, color = as.factor(main_prop)), 
+                position=position_dodge(width=0.5)) +
+  xlab("Number of different predator individuals sampled") +
+  ylab("True Skill Statistics") +
+  theme_classic()
+
[…]

### 2021-11-15 inst/main/r8_TSS_vs_pred.R

@@ -1,0 +1,86 @@
+#Rule r8
+#We plot TSS with number of predator diets sampled
+
+
+fw_name <- "sim_Small Reef"
+nspecies <- 50
+propn <- 1:nspecies
+l_acc <- numeric(nspecies)
+r_acc <- numeric(nspecies)
+mean_acc <- numeric(nspecies)
+dir_N <- 10000
+dir_tol <- 1000
+n_gut_sample <- 100
+n_sel <- 1
+main_prop <- 1
+long_acc <- data.frame(acc = double(), n = integer())
+rule <- "r8"
+
+
+# dir_org <- paste("results/rejection/", fw_name, "/rN=1e+05_tol=2_TSS_gut_r7_l", sep = "")
+desc_main <- "TSS_gut_r8"
+for(i in 1:50){
+  
+  desc <- paste(desc_main, '_l', i, "_prop_",main_prop, sep = '')
+  dir_main <- paste("../../../PhD_local/C2_files/",fw_name,"/", "rule_", rule,'/N=', dir_N, '_tol=', dir_tol, '_n_pred = ', i,
+                    sep = "")
+  sim_TSS <- c()
+  for(n_sample  in 1:n_gut_sample){
+    dirnam <- paste(c(dir_main, '/rn_gut=', n_sample,'_N=', dir_N, '_tol=', dir_tol,"_", desc), collapse = '')
+    fname <- paste(dirnam, "/", fw_name, ".Rdata", sep = "")
+    prop_acc <- readRDS(fname)
+    gut_TSS <- 1 - prop_acc$dist
+    gut_TSS_indexes <- order(gut_TSS, decreasing = TRUE)[1:n_sel]
+    sim_TSS_temp <- 1 - prop_acc$acc_ss[gut_TSS_indexes]
+    sim_TSS <- c(sim_TSS, sim_TSS_temp)
+  }
+  
+  range_acc <- range(sim_TSS)
+  l_acc[i] <- range_acc[1]
+  r_acc[i] <- range_acc[2]
+  mean_acc[i] <- mean(sim_TSS)
+  
+}
+
+
+# dd_1 <- data.frame(l_acc = l_acc, r_acc = r_acc, mean_acc = mean_acc, propn = propn, main_prop = as.factor(main_prop))
+
[…]

### 2021-11-15 inst/main/s2_TSS_vs_pred.R

@@ -1,0 +1,75 @@
+#Rule s2
+#We plot TSS with number of SIR data sampled
+
+
+fw_name <- "sim_Small Reef"
+n <- 11
+l_acc <- numeric(n)
+r_acc <- numeric(n)
+mean_acc <- numeric(n)
+dir_N <- 1000
+dir_tol <- 1000
+n_sir_sample <- 100
+propn <- 1:n
+n_sel <- dir_N*0.01
+long_acc <- data.frame(acc = double(), n = integer())
+rule <- "s2"
+desc_main <- "TSS_sir_s2"
+for(i in 1:n){
+  
+  desc <- paste(desc_main, '_l', i, sep = '')
+  dir_main <- paste("results/rejection/",fw_name,"/", "rule_", rule,'/N=', dir_N, '_tol=', dir_tol, '_n_pred = ', i,
+                    sep = "")
+  sim_TSS <- c()
+  for(n_sample  in 1:n_sir_sample){
+    dirnam <- paste(c(dir_main, '/rn_sir=', n_sample,'_N=', dir_N, '_tol=', dir_tol,"_", desc), collapse = '')
+    fname <- paste(dirnam, "/", fw_name, ".Rdata", sep = "")
+    prop_acc <- readRDS(fname)
+    sir_TSS <- 1 - prop_acc$dist
+    sir_TSS_indexes <- order(sir_TSS, decreasing = TRUE)[1:n_sel]
+    sim_TSS_temp <- 1 - prop_acc$acc_ss[sir_TSS_indexes]
+    sim_TSS <- c(sim_TSS, sim_TSS_temp)
+  }
+  
+  hdi_acc <- hdi(sim_TSS, credMass = 0.9999)
+  l_acc[i] <- hdi_acc[1]
+  r_acc[i] <- hdi_acc[2]
+  mean_acc[i] <- mean(sim_TSS)
+  dd <- data.frame(l_acc = l_acc, r_acc = r_acc, mean_acc = mean_acc, propn = propn)
+  
+}
+
+
+dd <- rbind(dd_1, dd_2)
+
+dd_plot <- ggplot(dd) +
+  # geom_line(aes(x = propn, y = mean_acc)) +
+  geom_point(aes(x = propn, y = mean_acc), 
+             position=position_dodge(width=0.5)) +
+  geom_errorbar(aes(x = propn, ymin = l_acc, ymax = r_acc), 
+                position=position_dodge(width=0.5)) +
+  xlab("Number of different predator species sampled") +
[…]

### 2021-11-15 inst/main/s3_TSS_vs_pred.R

@@ -1,0 +1,80 @@
+#Rule s3
+#We plot TSS with number of SIR data sampled
+#s3: varying the number of SIR data from 1 to many (species based sampling) with decreasing body size
+
+
+fw_name <- "sim_Small Reef"
+n <- 50
+nspecies <- n
+l_acc <- numeric(n)
+r_acc <- numeric(n)
+mean_acc <- numeric(n)
+dir_N <- 1e5
+dir_tol <- Inf
+n_sir_sample <- 1
+propn <- 1:n
+n_sel <- 1
+long_acc <- data.frame(acc = double(), n = integer())
+rule <- "s3"
+desc_main <- "TSS_sir_s3"
+for(i in 1:n){
+  
+  desc <- paste(desc_main, '_l', i, sep = '')
+  dir_main <- paste("../../../PhD_local/C2_files/",fw_name,"/", "rule_", rule,'/N=', dir_N, '_tol=', dir_tol, '_n_pred = ', i,
+                    sep = "")
+  sim_TSS <- c()
+  for(n_sample  in 1:n_sir_sample){
+    dirnam <- paste(c(dir_main, '/rn_sir=', n_sample,'_N=', dir_N, '_tol=', dir_tol,"_", desc), collapse = '')
+    fname <- paste(dirnam, "/", fw_name, ".Rdata", sep = "")
+    prop_acc <- readRDS(fname)
+    sir_TSS <- 1 - prop_acc$dist[1:100000]
+    sir_TSS_indexes <- order(sir_TSS, decreasing = TRUE)[1:n_sel]
+    sim_TSS_temp <- 1 - prop_acc$acc_ss[sir_TSS_indexes]
+    sim_TSS <- c(sim_TSS, sim_TSS_temp)
+  }
+  
+  range_acc <- range(sim_TSS)
+  l_acc[i] <- range_acc[1]
+  r_acc[i] <- range_acc[2]
+  mean_acc[i] <- mean(sim_TSS)
+  dd <- data.frame(l_acc = l_acc, r_acc = r_acc, mean_acc = mean_acc, propn = propn)
+  
+}
+
+
+# dd <- rbind(dd_1, dd_2)
+
+dd_plot <- ggplot(dd) +
+  # geom_line(aes(x = propn, y = mean_acc)) +
+  geom_point(aes(x = propn, y = mean_acc), 
+             position=position_dodge(width=0.5)) +
[…]

### 2021-11-15 inst/main/s_r_1_TSS_vs_pred.R

@@ -1,0 +1,88 @@
+# 10.03.2021
+# Rule s_r_1
+# We plot TSS with number of predator diets sampled where the SIR data for the largest k species have already beeen used
+
+
+fw_name <- "sim_Small Reef"
+nspecies <- 50
+propn <- 1:nspecies
+l_acc <- numeric(nspecies)
+r_acc <- numeric(nspecies)
+mean_acc <- numeric(nspecies)
+dir_N <- 10000
+dir_tol <- Inf
+n_gut_sample <- 100
+n_sel <- 1
+main_prop <- 1
+long_acc <- data.frame(acc = double(), n = integer())
+rule <- "s_r_1"
+
+
+# dir_org <- paste("results/rejection/", fw_name, "/rN=1e+05_tol=2_TSS_gut_r7_l", sep = "")
+desc_main <- "TSS_sir_gut_s_r_1"
+for(i in 1:50){
+  
+  desc <- paste(desc_main, '_l', i, "_prop_",main_prop, sep = '')
+  dir_main <- paste("../../../PhD_local/C2_files/",fw_name,"/", "rule_", rule,'/N=', dir_N, '_tol=', dir_tol, '_n_pred = ', i,
+                    sep = "")
+  sim_TSS <- c()
+  for(n_sample  in 1:n_gut_sample){
+    dirnam <- paste(c(dir_main, '/rn_gut=', n_sample,'_N=', dir_N, '_tol=', dir_tol,"_", desc), collapse = '')
+    fname <- paste(dirnam, "/", fw_name, ".Rdata", sep = "")
+    prop_acc <- readRDS(fname)
+    gut_TSS <- 1 - prop_acc$dist
+    gut_TSS_indexes <- order(gut_TSS, decreasing = TRUE)[1:n_sel]
+    sim_TSS_temp <- prop_acc$TSS[gut_TSS_indexes]
+    sim_TSS <- c(sim_TSS, sim_TSS_temp)
+  }
+  
+  range_acc <- range(sim_TSS)
+  l_acc[i] <- range_acc[1]
+  r_acc[i] <- range_acc[2]
+  mean_acc[i] <- mean(sim_TSS)
+  
+}
+
+
+# dd_with_SIR <- data.frame(l_acc = l_acc, r_acc = r_acc, mean_acc = mean_acc, propn = propn, data_type = "With SIR")
+
[…]

### 2021-11-15 inst/main/save_foodweb_prop.R

@@ -1,0 +1,15 @@
+foodweb <- "sim_Small Reef"
+dirnam <- paste("results/mcmc/",foodweb,"/mN=8e+05_tol=0.3_TSS_unif_rall", sep = "")
+fname <- paste(dirnam, "/", foodweb, "_thin.Rdata", sep = "")
+
+foodweb_data <- load(paste("data/", foodweb, ".web.Rdata", sep=""))
+all.web.info <- get(foodweb_data)
+
+
+predicted_foodweb <- readRDS(fname)
+model_core_par = ADBM_core_par(all.web.info)
+properties <- fw_prop(predicted_foodweb, model_core_par, all.web.info = all.web.info)
+
+
+fname_new <- paste(dirnam, "/", foodweb, "_prop.Rdata", sep = "")
+saveRDS(properties, file = fname_new)

### 2021-11-15 inst/main/save_plot.R

@@ -1,0 +1,29 @@
+foodweb <- "Benguela Pelagic"
+dirnam <- paste("results/rejection/",foodweb,"/rN=1000_tol=0.7_TSS_unif_rall", sep = "")
+
+
+# foodweb <- "Grasslands"
+# dirnam <- paste("results/rejection/",foodweb,"/rN=1000_tol=1_TSS_unif_rall", sep = "")
+fname <- paste(dirnam, "/", foodweb, "_prop.Rdata", sep = "")
+
+
+foodweb_data <- readRDS(paste("data_new/", foodweb, ".web.Rdata", sep=""))
+
+
+fname_pred_fw <- paste(dirnam, "/", foodweb, ".Rdata", sep = "")
+predicted_foodweb <- readRDS(file = fname_pred_fw)
+
+fname_prop <- paste(dirnam, "/", foodweb, "_prop.Rdata", sep = "")
+prop_web <- readRDS(file = fname_prop)
+
+model_core_par = ADBM_core_par(foodweb_data)
+model_prior_par = ADBM_prior_par(foodweb_data)
+model = ratio.power_exp
+prior_dist_x = prior_unif_x
+desc = "TSS_unif_rall"
+
+plot_foodweb_prop(real_foodweb = foodweb_data, predicted_foodweb = predicted_foodweb,
+                  dirnam = dirnam, model_core_par = model_core_par, 
+                  model_prior_par = model_prior_par,
+                  model = model, desc = desc, prior_dist_x = prior_dist_x, web.to.analyse = foodweb, prop_web = prop_web,
+                  true_val_plot = F)

### 2021-11-15 inst/main/str_prop_wrt_ngut.R

@@ -1,0 +1,130 @@
+# 20.09.2021
+# We plot the predicted structural properties wrt ngut
+
+library(R.utils); library(tictoc); library(stringr)
+library(ggpubr); library(plotrix); library(ggplot2)
+library(cowplot); library(latex2exp); library(HDInterval)
+library(doParallel); library(foreach); library(raster)
+library(cheddar); library(dplyr); library(reshape2)
+library(psych); library(DirectedClustering); library(colorspace)
+library(bipartite)
+
+## Relative path from the project directory
+sourceDirectory("R", modifiedOnly=FALSE)
+
+fw_name <- "Tadnoll Brook size_agg"
+propn <- c(seq(1, 688, 14), 688)
+
+dir_N <- 1e5
+dir_tol <- 2 #different for ind and lbs and ubs
+n_gut_sample <- 100 
+
+rule <- "ind_predator"
+
+fname_data <- paste("data/", fw_name, ".web.Rdata", sep="")
+fw_data <- readRDS(fname_data)
+model_core_par <- ADBM_core_par(fw_data)
+
+real_prop_calc <- real_prop_predator(fw_data)
+prop_name_list <- c("connectance" = "Connectance")
+
+prop_all <- c("connectance", "prop_basal", "prop_inter", "prop_top", "prop_herb",
+              "mean_trop_lvl", "max_trop_lvl", "mean_omn", "clus_coeff", "sd_gen",
+              "sd_vulner", "mean_max_trophic_sim", "mean_path_lt", "nest_prop")
+
+prop_labeller <- c(connectance = "Connectance", prop_basal = "Proportion of Basal Species",
+                   prop_inter = "Proportion of Intermediate Species", prop_top = "Proportion of Top Predators",
+                   prop_herb = "Proportion of Herbivores", mean_trop_lvl = "Mean Trophic Level",
+                   max_trop_lvl = "Maximum Trophic Level", mean_omn = "Mean Omnivory",
+                   clus_coeff = "Clustering Coefficient", sd_gen = "SD of Generality",
+                   sd_vulner = "SD of Vulnerability", mean_max_trophic_sim = "Mean Maximum Trophic Similarity",
+                   mean_path_lt = "Mean Path Length", nest_prop  = "Nestedness")
+
[…]

### 2021-11-15 inst/main/threshold.R

@@ -1,0 +1,396 @@
+# 23.07.2021
+# We compute the minimum number of gut content data for food webs
+
+library(dplyr)
+library(ggplot2)
+
+df_min_gut_vs_S <- data.frame(n_min_gut = integer(), S = integer(), C = double(), L = integer(), 
+                              foodweb = character(), prop_min_gut = double(), max_ngut = integer(),
+                              max_TSS = double(), n_pred = integer(), mean_prey = double(),
+                              sd_prey = double())
+threshold_per <- 0.95
+  
+## Broadstone Stream
+
+fw_name <- "Broadstone Stream size_agg_v2"
+pred_mat <- readRDS(paste0("data/", fw_name, ".web.Rdata"))$predation.matrix
+n_pred <- sum(colSums(pred_mat)!=0)
+
+gut_data <- readRDS(paste0("data/gut_data/", fw_name, "_ind_predator.gut.Rdata"))
+gut_data <- gut_data[-c(1,2),]
+mean_prey <- mean(colSums(gut_data))
+sd_prey <- sd(colSums(gut_data))
+
+dd <- readRDS(paste0("../../../../../Volumes/SSD1/Secondary_storage/PhD_local/C2_files/", fw_name, "/rule_ind_predator/dd_bs.Rdata"))
+max_ngut <- max(dd$propn)
+
+max_TSS <- dd$mean_acc[length(dd$mean_acc)]
+threshold_TSS <- threshold_per*max_TSS
+
+k <- 1
+repeat{
+  if(dd$mean_acc[k] > threshold_TSS){
+    N <- k - 1
+    break
+  }
+  k <- k + 1
+}
+
+n_min_gut <- dd$propn[k]
+
+df_min_gut_vs_S <- rbind(df_min_gut_vs_S, 
+                         data.frame(n_min_gut = n_min_gut, S = 28, C = 0.24, L = 185, foodweb = "Broadstone Stream",
+                                    prop_min_gut = n_min_gut/max_ngut, max_ngut = max_ngut, max_TSS = max_TSS,
+                                    n_pred = n_pred, mean_prey = mean_prey, sd_prey = sd_prey))
+
+
+
+
+## Celtic Sea
+
+fw_name <- "Celtic Sea size_agg"
[…]

### 2021-11-15 inst/main/tophic_level_wrt_M.R

@@ -1,0 +1,21 @@
+#Plot trophic level of species with their body sizes
+
+pred_output <- readRDS("../C1_method/results/rejection/Benguela Pelagic/rN=1e+05_tol=2_TSS_only_a/Benguela Pelagic.Rdata")
+
+
+tl_plot <-  trop_levels %>%
+  na.omit() %>%
+  # filter(sp_names == c("n20")) %>%
+  ggplot() +
+  geom_point(aes(x = sp_names, y = tl, color = conn)) +
+  xlab("Connectance of food web") +
+  ylab("Trophic levels") +
+  # scale_color_discrete(name = "Species identity") +
+  theme_classic() +
+  theme(axis.text = element_text(family = "Times New Roman", size = 20),
+        axis.title = element_text(family = "Times New Roman", size = 20),
+        legend.title = element_text(family = "Times New Roman", size = 20),
+        legend.text = element_text(family = "Times New Roman", size = 20))+
+  scale_x_discrete(limits = c("n1", "n2", "n3", "n4", "n5", "n6", "n7", "n8", "n9", "n10",
+                              "n11", "n12", "n13", "n14", "n15", "n16", "n17", "n18", "n19", "n20",
+                              "n21", "n22", "n23", "n24", "n25", "n26", "n27", "n28", "n29"))

### 2021-12-08 manuscript/ms_C2/ms_C2.Rmd
owen comments and edits

@@
 
+**OP: For my comments, please search for "**OP:"
+
 # Alternate titles
@@
 
-Knowledge about the trophic interactions in a food web is crucial in ecology from identifying keystone species [@jordanKeystoneSpeciesFood2009] to quantifying robustness of a food web to species extinctions [@dunneNetworkStructureBiodiversity2002].
+Knowledge about the trophic interactions in a food web is crucial in ecology for purposes ranging from identifying keystone species [@jordanKeystoneSpeciesFood2009] to quantifying robustness of a food web to species extinctions [@dunneNetworkStructureBiodiversity2002].
 This has led to the development of numerous food web models [@allesinaGeneralModelFood2008; @cohenStochasticTheoryCommunity1985; @gravelInferringFoodWeb2013; @petcheySizeForagingFood2008; @tamaddoni-nezhadConstructionValidationFood2013].
-Along with inferring missing links in an observed food web, the food web models are also used for ecological forecasting [@hattabForecastingFinescaleChanges2016; @lindegrenEcologicalForecastingClimate2010] and understanding the underlying mechanism governing the interactions in a food web [@ogormanSimpleModelPredicts2019].
+Along with inferring missing links in an observed food web, the food web models are also used for ecological forecasting [@hattabForecastingFinescaleChanges2016; @lindegrenEcologicalForecastingClimate2010] and for understanding the underlying mechanism governing the interactions in a food web [@ogormanSimpleModelPredicts2019].
 
-Although food web models are constructed using prior theory governing the food webs, interaction data is required to parameterise a model.
+Although food web models are constructed using prior theory about the factors that determine trophic interactions, empirical data about interactions is required to parameterise a model.
 For example, @petcheySizeForagingFood2008 used presence-absence information about trophic interactions to parameterise the allometric diet breadth model and thereby predict species interactions.
-These information can be inferred from diverse set of methods such as gut content analysis [@peralta-maraverStructureDynamicsStability2017], stable isotope ratio analysis of tissues [@laymanCanStableIsotope2007], experimentation [@warrenSpatialTemporalVariation1989], DNA metabarcoding [@roslinUseDNABarcodes2016] and literature research [@grayJoiningDotsAutomated2015; @cohenSoilInvertebratesChemistry2014; @goldwasserConstructionAnalysisLarge1993a].
-All of these methods can infer the diet of a consumer, however different methods measure different consumed components, thereby resulting in different levels of uncertainty in the inferred diet (citreqd).
+Empirical information about interactions can be inferred from diverse set of methods such as gut content analysis [@peralta-maraverStructureDynamicsStability2017], stable isotope ratio analysis of tissues [@laymanCanStableIsotope2007], experimentation [@warrenSpatialTemporalVariation1989], DNA metabarcoding [@roslinUseDNABarcodes2016] and literature research [@grayJoiningDotsAutomated2015; @cohenSoilInvertebratesChemistry2014; @goldwasserConstructionAnalysisLarge1993a].
+
+**OP: The following three sentences may not be necessary here, or could perhaps go elsewhere.** All of these methods can provide information useful to infer the diet of a consumer, however different methods can result in different levels of uncertainty in the inferred diet (citreqd).
 A single gut content of a predator describes what that individual has consumed recently which can be used to infer the diet of the predator [@eitzingerTestingValidityFunctional2018; @omalleyEffectsFoodWeb2017; @dixonAssessingDietNorth2017; @mcclain-countsTrophicStructureMesopelagic2017b; @peralta-maraverStructureDynamicsStability2017].
@@
 
-Acquiring food web data from these methods is time consuming and expensive (reference).
-For example, many gut content data needs to be collected to infer the complete presence-absence information of a food web structure with high accuracy and precision.
-Also further time and resource investment is required to process the collected samples.
-Hence, there is an utmost demand to know the minimum number of presence-absence information of a food web to parameterise a food web model with high accuracy and high precision, so that one knows when to stop collecting any further data on the food web.
+**There should be I think, a paragraph that transition from the many methods mentioned just above, to the focus on the gut content method, which should mention, for example, some of the advantages (and possibly disadvantages) of the gut content method.
 
-The key question we are interested in answering is how much presence-absence information is required to infer food web structure from a food web model with high accuracy and high precision.
+Acquiring food web data from gut content analysis is time consuming and expensive (reference).
+In part this is due to the need for many gut contents to be collected and analysed in order to be confident that the majority of possible trophic links have been observed.
+Furthermore, considerable time, resource investment, and expertise is required to process the collected samples.
+Hence, there is of considerable importance to know the minimum number of gut contents and of which consumer species that are required to parameterise a food web model with high accuracy and high precision, so that one knows when is a good time to stop collecting any further empirical data on the food web.
+
+Therefore, the key question we are interested in answering is how much presence-absence information, in the form of gut content data, is required to infer food web structure from a food web model with high accuracy and high precision.
 In other words, in case of gut content data how many samples of gut content should one collect from the field to parameterise a food web model?
@@
 We parameterise the model using approximate Bayesian computation/rejection Monte Carlo sampling.
+**OP: A more complete, though still very brief description of what we do, is important to add here.**
 
@@
 We also give a detailed account of using partial gut content data to parameterise the ADBM using approximate Bayesian computation (ABC).
-We assessed model predictions using true skill statistic and various structural food web properties for comparison across food webs.
+We assessed model predictions using the true skill statistic and various structural food web properties for comparison across food webs.
 
-## Allometric Diet Breadth Model (ADBM)
+## The Empirical Food Webs
 
-The allometric diet breadth model (ADBM) is based on optimal foraging theory, specifically the contingency foraging model [@macarthurOptimalUsePatchy1966].
-The ADBM predicts the set of prey species a consumer should feed upon to maximise its rate of energy intake [@petcheySizeForagingFood2008].
-The foraging variables in the model: energy content of the resources, handling times of the prey, space clearance rate and prey densities are allometrically scaled to the body sizes of the species.
+*OP: Here state what criteria were used to select the empirical food webs that are used in this study.
 
-## Broadstone Stream
+Presence and absence interactions of food web data can be aggregated in different ways [@gilljamSeeingDouble2011].
+A common way of aggregating food web data is the taxonomic approach, in which nodes in the food web are taxa (e.g.
+species) and one species is said to feed on another species if at least one individual of the latter is found in at least one gut of the former.
+Another approach is based on size, rather than taxonomy, and in this the nodes in the food web are size classes.
+Here, a feeding link occurs between two size classes if at least one prey item within a size class was found in the gut of another size class, irrespective of their taxonomy.
+In our study, we aggregate the food web on the basis of size class **OP: state why!
+In general here and in any methods section, when we state what we did, we must state why...
+i.e.
+we must justify our choices.**
+
+### Broadstone Stream
 
@@
 
-## Celtic Sea
+### Celtic Sea
 
@@
 Only locations consistently sampled through the 1987--2001 time series were used (Blanchard et al., 2005).
-
 The feeding links of fishes in the Celtic Sea have been described in a published global dataset of individual predator and prey body sizes and taxonomy (Barnes et al., 2008): in total, 1988 feeding events from 29 predator species were included in the food web presented here.
@@
 
-## Afon Hirnant
+### Afon Hirnant
 
@@
 The pH within each site ranged from about 5.5 to 7 over the course of the year.
-
 A total of 180 invertebrate samples were collected for the whole sampling periods.
@@
 
-## Tadnoll Brook
+### Tadnoll Brook
 
@@
 
-## Coilaco
+### Coilaco
 
@@
 
-## Guampoe
+### Guampoe
 
@@
 
-## Trancura
+### Trancura
 
@@
 
-Presence and absence interactions of food web data can be aggregated in different ways [@gilljamSeeingDouble2011].
-A common way of aggregating food web data is the taxonomic approach, where a species is defined as predating on another if at least one prey species individual was found in the gut of a predator species individual.
-Whereas in size-class food web, a feeding link was assigned if at least one prey item within a size class was found in the gut of a predator of another size class, irrespective of their taxonomy.
-In our study, we aggregate the food web on the basis of size class.
+## Allometric Diet Breadth Model (ADBM)
+
+**OP: In this section there must be justification of why this food web model in particular was used, and why not others.**
+
+The allometric diet breadth model (ADBM) is based on optimal foraging theory, specifically the contingency foraging model [@macarthurOptimalUsePatchy1966].
+The ADBM predicts the set of prey species a consumer should feed upon to maximise its rate of energy intake [@petcheySizeForagingFood2008].
+The foraging variables in the model are: energy content of the resources, handling times of the prey, space clearance rate and prey densities are allometrically scaled to the body sizes of the species.
+**OP: please complete -> Further details can be found...
 
@@
 
-From a pool of gut content data, we draw a set of gut content data randomly.
-Then we used the rejection ABC to accept a parameter value from a prior distribution which would have resulted in the minimum distance, where distance = 1 - True skill statistic.
+From an empirical dataset of gut content data, we draw a set of gut contents data randomly to create a partial gut content dataset. We then fit the ADBM to this partial dataset.
+
+To fit the ADBM to a gut content dataset (be it complete or partial), we used the method we previously developed (**OP: citation).
+rejection ABC to accept a parameter value from a prior distribution which would have resulted in the minimum distance, where distance = 1 - True skill statistic.
 The true skill statistic was computed between the predators' diet predicted from the ADBM, and that from the sampled gut content data.
@@
 
-A prediction interval containing $TSS$ between observed and predicted food webs for every $i$ number of gut content data drawn from the pool of gut content data.
+The $TSS$ between observed and predicted food webs for every $i$ number of gut content data drawn from the pool of gut content data.
 
@@
 For a low number of predator guts, the TSS of the model predicted food web was higher compared to the TSS of the food web constructed from gut content data (Fig.
-\ref{fig:fig_ra} (b, d, f, h, j, l, n)), recommending when a model can be used to compensate for undersampled links.
+\ref{fig:fig_ra} (b, d, f, h, j, l, n)) **OP: leave the following type of content for the Discussion section: recommending when a model can be used to compensate for undersampled links.
 After a certain increase in the number of predator guts, the ratio TSS(Model)/TSS(data) reduced to less than one, and reduced further gradually.
 
-With only 381 number of gut content data which is 38% of the total gut content data, the ADBM predicted the food web with TSS of 0.74 which was 95% of the mean TSS (0.78) achieved using complete gut content data by the ADBM for Broadstone Stream food web (Fig.
+For Broadstone Stream food web, with only 381 number of gut content data which is 38% of the total gut content data, the ADBM predicted the food web with TSS of 0.74 which was 95% of the mean TSS (0.78) achieved using complete gut content data by the ADBM  (Fig.
 \ref{fig:fig_ra}(a)).
-In the case of the Celtic Sea food web, only 171 gut content data was required by the ADBM to predict food web with TSS equal to 95% of the mean TSS (0.68) achieved using complete gut content data by the ADBM (Fig.
+In the case of the Celtic Sea food web, only 171 gut content data (**OP: state what percentage this is) was required by the ADBM to predict food web with TSS equal to 95% of the mean TSS (0.68) achieved using complete gut content data by the ADBM (Fig.
 \ref{fig:fig_ra}(c)).
@@
 
-There seems to be a positive relationship between number of minimum gut content data and number of species (S) (Fig.
+**OP: "There seems to be" is rather unconvential phrase.
+Perhaps use There was a positive trend between number of minimum gut content data and number of species (S) (Fig.
 \ref{fig:fig_rb} (a)), links (L) (Fig.
@@
 
-## Why incomplete gut content data can be used to infer trophic interactions?
+**OP: Focus on this... ## Why incomplete gut content data can be used to infer trophic interactions?
 
@@
 
-## There is uncertainty in gut content data and needs to be propagated into model's predictions
+**OP Focus on this, at least in the context of further work that could be done. ## There is uncertainty in gut content data and needs to be propagated into model's predictions
 
@@
 
-## Comparing our study with other studies of predicting food webs using incomplete data
+**OP: Focus on this, and other studies that have looked at the importance of quantity and quality of food web data ## Comparing our study with other studies of predicting food webs using incomplete data
 
@@
 
-## What is the generalisability of our results?
+**OP: Focus on this.## What is the generalisability of our results?
 
@@
 
+**OP: I suggest to put this in the Methods section, where the general method should also be described (a bit like I suggest at the end of the Introduction.
 ## Assumption that the food web constructed with the total gut content data is the true food web and how can this be improved
@@
 
-## How can we include other food web data type?
+**OP: Focus on this ## How can we include other food web data type?
 
@@
 ## Gut content data simulation
+
+**OP: It needs to be very clear in the main text, and here, why this is being described. It is currently unclear, not least because the main text does not, I think, refer to the information here.
 
@@
 \ref{fig:fig_r0}).
-The TSS of the predicted food webs estimated using the complete individual gut data had shorter prediction intervals resulting in less uncertainty, and higher mean TSS than that using the partial individual gut data.
+The TSS of the predicted food webs estimated using the complete individual gut data had narrower prediction intervals resulting in less uncertainty, and higher mean TSS than that using the partial individual gut data.
 The maximum limit of the prediction interval of TSS estimated using the complete gut data and the partial gut data were almost equal, with the minimum limit of the prediction interval of TSS using partial gut data being lower than that from the complete gut data.

### 2022-02-07 manuscript/ms_C2/ms_C2.Rmd
Updated ms_C2.Rmd and ms_C2.pdf files

@@
 ---
-title: "Optimal amount of gut content data required to predict trophic interactions using a food web model"
+title: Optimal amount of gut content data required to predict trophic interactions using a food web model
 authors:
@@
   name: Owen L. Petchey
-bibliography: bibliography.bib
-output:
-  rticles::arxiv_article:
-    keep_tex: yes
-  pdf_document: default
+geometry: margin=1in
+abstract: |
+
+  1)  Presence absence data of species interactions such as gut content data is used to parameterise food web models such as allometric diet  breadth model (ADBM), thereby predicting interactions.
+And collecting and analysing these data from the field is an expensive and time consuming task.
+Therefore, it is crucial to know how much gut content data is required to parameterise the ADBM with high accuracy and high precision for a given food web with minimum sampling effort.
+  2)  The novelty of our current approach is that we use approximate Bayesian computation to parameterise the ADBM, and true skill statistics to measure the goodness of fit for different amount of predators' gut content data.
+  3)  We estimated the minimum number of gut content data required for seven different food webs that resulted in 95% of the maximum true skill statistics achieved by the ADBM for total gut content data.
+We found that incomplete gut content data can be used to parameterise the ADBM with the lowest amount of gut content data being 28% of the total gut content data.
+  4)  These results suggest that one need not collect a large quantity of gut content data to predict a food web structure using a food web model, thereby reducing sampling effort considerably.
+
+keywords:
+  - gut content data
+  - ADBM
+  - food web accuracy
+  - food web prediction
 header-includes:
@@
    - \usepackage{setspace}\doublespacing
-# - \usepackage{setspace}\doublespacing
-keywords:
-- gut content data
-- ADBM
-- food web accuracy
-- food web prediction
+# indent: true
 mainfont: Times New Roman
-geometry: margin=1in
-abstract: "1) \n2)  \n3)  \n4)  \n"
+bibliography: bibliography.bib
+biblio-style: biblatex
+output:
+  # word_document:
+  #   fig_caption: yes
+  #   number_sections: yes
+  rticles::arxiv_article:
+    keep_tex: true
 ---
 
-**OP: For my comments, please search for "**OP:"
+\*\*AG: My comment starts with "**AG:"
 
@@
 For example, @petcheySizeForagingFood2008 used presence-absence information about trophic interactions to parameterise the allometric diet breadth model and thereby predict species interactions.
-Empirical information about interactions can be inferred from diverse set of methods such as gut content analysis [@peralta-maraverStructureDynamicsStability2017], stable isotope ratio analysis of tissues [@laymanCanStableIsotope2007], experimentation [@warrenSpatialTemporalVariation1989], DNA metabarcoding [@roslinUseDNABarcodes2016] and literature research [@grayJoiningDotsAutomated2015; @cohenSoilInvertebratesChemistry2014; @goldwasserConstructionAnalysisLarge1993a].
+These empirical information about interactions can be inferred from diverse set of methods such as gut content analysis [@peralta-maraverStructureDynamicsStability2017], stable isotope ratio analysis of tissues [@laymanCanStableIsotope2007], experimentation [@warrenSpatialTemporalVariation1989], DNA metabarcoding [@roslinUseDNABarcodes2016] and literature research [@grayJoiningDotsAutomated2015; @cohenSoilInvertebratesChemistry2014; @goldwasserConstructionAnalysisLarge1993a].
 
-**OP: The following three sentences may not be necessary here, or could perhaps go elsewhere.** All of these methods can provide information useful to infer the diet of a consumer, however different methods can result in different levels of uncertainty in the inferred diet (citreqd).
+<!-- **OP: The following three sentences may not be necessary here, or could perhaps go elsewhere.** All of these methods can provide information useful to infer the diet of a consumer, however different methods can result in different levels of uncertainty in the inferred diet (citreqd).
 A single gut content of a predator describes what that individual has consumed recently which can be used to infer the diet of the predator [@eitzingerTestingValidityFunctional2018; @omalleyEffectsFoodWeb2017; @dixonAssessingDietNorth2017; @mcclain-countsTrophicStructureMesopelagic2017b; @peralta-maraverStructureDynamicsStability2017].
 Stable isotope data when combined with mixing models can be used to determine which prey items are most likely fed upon by a predator [@kadoyaIsoWebBayesianIsotope2012; @crawfordApplicationsStableIsotope2008].
+-->
 
-**There should be I think, a paragraph that transition from the many methods mentioned just above, to the focus on the gut content method, which should mention, for example, some of the advantages (and possibly disadvantages) of the gut content method.
+Food web methods mentioned above have multiple shortcomings.
+Stable isotope ratio analysis of the organism's tissue does not give a direct information of the diet of that organism but rather approximate trophic position of that species in the food web.
+Although mixing models can be used to determine what prey items are most likely fed upon by a predator but this results in uncertainty in the estimates [@kadoyaIsoWebBayesianIsotope2012; @crawfordApplicationsStableIsotope2008].
+Experimentation (e.g.
+feeding trials) may create unrealistic conditions where a predator is confined in a small space with a potential "prey" and is effectively "forced" into eating it (citreqd).
+DNA metabarcoding could have many issues such as failure to relate OTUs to species, or inability to distinguish secondary predation, i.e.
+the DNA signature of the prey consumed by the prey consumed by the primary item found in the predator's gut.
+Another approach to infer missing links is literature research which involves assuming that a link will occur because another author described it in some other system, or for related predator/prey species, e.g.
+from the same genus or family [@grayJoiningDotsAutomated2015; @cohen2014; @goldwasser1993].
+This typically results in a food web that will be very oversampled with false positives in the presence of links (citreqd).
+@nielsen2018 have shown that gut content analysis method has a better match with real diet when compared to other methods.
+\*\*AG: Working on this paragraph.
 
@@
 
-Therefore, the key question we are interested in answering is how much presence-absence information, in the form of gut content data, is required to infer food web structure from a food web model with high accuracy and high precision.
-In other words, in case of gut content data how many samples of gut content should one collect from the field to parameterise a food web model?
-To answer this question, we use the presence-absence information from gut content data, and allometric diet breadth model (ADBM) to predict trophic interactions.
-We parameterise the model using approximate Bayesian computation/rejection Monte Carlo sampling.
-**OP: A more complete, though still very brief description of what we do, is important to add here.**
+Therefore, the key question we are interested in answering is how much presence-absence information, in the form of gut content data, is required to infer food web structure from a food web model specifically the ADBM with high accuracy and high precision.
+In other words, how many samples of gut content should one collect from the field to parameterise a food web model?
+To answer this question, we use the presence-absence information from gut content data to parameterise the allometric diet breadth model (ADBM) thereby predicting trophic interactions in seven different food webs using rejection approximate Bayesian computation, where the fitness of the model was measured using true skill statistics.
+We computed the true skill statistics of the predicted food webs for different number of predator guts to calculate the minimum number of gut content data to infer food web structure.
+Our study provides a guideline on how many gut content data is required to predict food web structure using a food web model.
 
@@
 
-In the upcoming sections, we present the allometric diet breadth model (ADBM) and the gut content data used to infer trophic interactions.
-We also give a detailed account of using partial gut content data to parameterise the ADBM using approximate Bayesian computation (ABC).
+In the upcoming sections, we present the food webs, the allometric diet breadth model (ADBM) and the gut content data used to infer the trophic interactions in the presented food webs using the ADBM.
+We also give a detailed account of using partial gut content data to parameterise the ADBM using rejection approximate Bayesian computation (ABC).
 We assessed model predictions using the true skill statistic and various structural food web properties for comparison across food webs.
@@
 
-*OP: Here state what criteria were used to select the empirical food webs that are used in this study.
-
+In our study, we used food webs for which gut content data is available at an individual level and, is FAIR.
 Presence and absence interactions of food web data can be aggregated in different ways [@gilljamSeeingDouble2011].
@@
 Here, a feeding link occurs between two size classes if at least one prey item within a size class was found in the gut of another size class, irrespective of their taxonomy.
-In our study, we aggregate the food web on the basis of size class **OP: state why!
-In general here and in any methods section, when we state what we did, we must state why...
-i.e.
-we must justify our choices.**
 
-### Broadstone Stream
+In our study, we aggregate the gut content data on the basis of size class because the food webs constructed using this approach were better predicted by the ADBM compared to the taxonomic approach [@woodward2010], and this is because the ADBM is based on foraging rules defined using the body sizes of organisms [@petcheySizeForagingFood2008].
 
-Broadstone Stream (51$^\circ$ 05' N 0$^\circ$ 03' E; 120 m above sea-level) is a second-order tributary of the River Medway in south-east England.
+Our study is based on the assumption that the food web constructed using the complete gut content data is the true food web.
+However, this might not be the case because the links are still under-sampled for many nodes [@woodwardIndividualBasedFoodWebs2010].
+This could result in a lower TSS of the predicted food web from the ADBM which can result in a biased estimate of the number of gut content data.
+
+```{r echo=FALSE, warning=FALSE}
+library(readxl)
+library(knitr)
+library(kableExtra)
+fw_table <- read_excel("../table/fw_table.xlsx")
+kable(fw_table, format = "latex",
+      caption = "\\label{fig:tab_1}Information about the empirical food webs. **AG: Working on this.", escape = FALSE, align = "l") %>%
+  kable_styling(font_size = 7, latex_options="scale_down", row_label_position = 1) %>%
+  landscape(margin = "1cm") %>%
+  column_spec(1, width = "3cm") %>%
+  column_spec(2, width = "8em") %>%
+  column_spec(7, width = "8em") %>%
+  column_spec(8, width = "8em") %>%
+  column_spec(9, width = "8em")
+
+```
+
+<!-- ### Broadstone Stream -->
+
+<!-- Broadstone Stream (51$^\circ$ 05' N 0$^\circ$ 03' E; 120 m above sea-level) is a second-order tributary of the River Medway in south-east England.
 It is dominated by invertebrates as the acidity of the stream (pH 4.7-6.6) excludes fish.
@@
 Broadstone Stream food web is one of the most completely described food webs available for any system [@schmid-arayaImportanceMeiofaunaFood2002; @hildrewChapterSustainedResearch2009; @layerFoodWebStructure2010; and @woodwardQuantificationResolutionComplex2005a].
+-->
 
-### Celtic Sea
+<!-- ### Celtic Sea -->
 
-The Celtic Sea is an area of continental shelf bordered by Ireland, the UK and the Bay of Biscay.
+<!-- The Celtic Sea is an area of continental shelf bordered by Ireland, the UK and the Bay of Biscay.
 Precise sampling locations and dates were not given in the Barnes et al.
@@
 Only vertebrate prey were identified and measured, with the vast majority being identified to species.
+-->
 
-### Afon Hirnant
+<!-- ### Afon Hirnant -->
 
-The Afon Hirnant is a tributary of the Welsh Dee in North Wales, U.K.
+<!-- The Afon Hirnant is a tributary of the Welsh Dee in North Wales, U.K.
 (52$^\circ$ 52'N 03$^\circ$ 34) with the study being conducted at three sites.
@@
 Prey items were identified using a combination of taxonomic keys and reference slides of previously identified species, after @schmid-arayaConnectanceStreamFood2002; @schmid-arayaImportanceMeiofaunaFood2002.
+-->
 
-### Tadnoll Brook
+<!-- ### Tadnoll Brook -->
 
-Description of Tadnoll Brook here
+<!-- Description of Tadnoll Brook here -->
 
-### Coilaco
+<!-- ### Coilaco -->
 
-Description of Coilaco here
+<!-- Description of Coilaco here -->
 
-### Guampoe
+<!-- ### Guampoe -->
 
-Description of Guampoe here
+<!-- Description of Guampoe here -->
 
-### Trancura
+<!-- ### Trancura -->
 
-Description of Trancura here
-
-## Food web construction
+<!-- Description of Trancura here -->
 
@@
 
-**OP: In this section there must be justification of why this food web model in particular was used, and why not others.**
-
 The allometric diet breadth model (ADBM) is based on optimal foraging theory, specifically the contingency foraging model [@macarthurOptimalUsePatchy1966].
+We chose this model because it uses the body size of organisms as input to predict feeding interactions.
 The ADBM predicts the set of prey species a consumer should feed upon to maximise its rate of energy intake [@petcheySizeForagingFood2008].
 The foraging variables in the model are: energy content of the resources, handling times of the prey, space clearance rate and prey densities are allometrically scaled to the body sizes of the species.
-**OP: please complete -> Further details can be found...
+Further details on the foraging rules defined in the ADBM and ADBM's predictive power across different food webs can be found in @petcheySizeForagingFood2008.
 
@@
 
-To fit the ADBM to a gut content dataset (be it complete or partial), we used the method we previously developed (**OP: citation).
-rejection ABC to accept a parameter value from a prior distribution which would have resulted in the minimum distance, where distance = 1 - True skill statistic.
+To fit the ADBM to a gut content dataset (be it complete or partial), we used the rejection ABC method we previously developed in @gupta2021 to accept a parameter value from a prior distribution which would have resulted in the minimum distance, where distance = 1 - True skill statistic.
 The true skill statistic was computed between the predators' diet predicted from the ADBM, and that from the sampled gut content data.
@@
 
-We first present how the accuracy of the food web model vary in predicting trophic interactions when we increase the amount the gut content data provided to the food web model.
-Then, we calculate the number of gut content data for each food webs corresponding to which the accuracy results in 90% of the maximum true skill statistics predicted by the food web model.
+We first present how the accuracy of the food web model i.e ADBM vary in predicting trophic interactions with increasing amount of gut content data provided to the food web model.
+Then, we calculate the number of gut content data for each food webs that results in accuracy equal to 95% of the maximum true skill statistics predicted by the food web model.
 We also compute the goodness of the food web model in predicting structural properties from incomplete gut content data.
@@
 \ref{fig:fig_ra}) (a, c, e, g, i, k, m).
-The prediction interval of the true skill statistics reduced with the increasing number of predator guts with the mean TSS asymptoting to the maximum mean TSS achieved by the ADBM when all the gut content data was used.
+The prediction interval of the true skill statistics decreased with increasing number of predator guts with the mean TSS asymptoting to the maximum mean TSS achieved by the ADBM when all the gut content data was used.
 Although the maximum TSS varied among the food webs, the qualitative increase in the TSS was the same.
 
-For a low number of predator guts, the TSS of the model predicted food web was higher compared to the TSS of the food web constructed from gut content data (Fig.
-\ref{fig:fig_ra} (b, d, f, h, j, l, n)) **OP: leave the following type of content for the Discussion section: recommending when a model can be used to compensate for undersampled links.
+For Broadstone Stream food web, with only 381 number of gut content data which is 38% of the total gut content data, the ADBM predicted the food web with the TSS of 0.74 which was 95% of the mean TSS (0.78) achieved using complete gut content data by the ADBM (Fig.
+\ref{fig:fig_ra}(a)).
+In case of the Celtic Sea food web, only 171 gut content data which is 35% of the total gut content data was required by the ADBM to predict food web with TSS equal to 95% of the mean TSS (0.68) achieved using complete gut content data by the ADBM (Fig.
+\ref{fig:fig_ra}(c)).
+
+## TSS(Model)/TSS(Data) for different food webs
+
+For a low number of predator guts, the TSS of the model predicted food web was higher than the TSS of the food web constructed from gut content data only (Fig.
+\ref{fig:fig_ra} (b, d, f, h, j, l, n)).
 After a certain increase in the number of predator guts, the ratio TSS(Model)/TSS(data) reduced to less than one, and reduced further gradually.
 
-For Broadstone Stream food web, with only 381 number of gut content data which is 38% of the total gut content data, the ADBM predicted the food web with TSS of 0.74 which was 95% of the mean TSS (0.78) achieved using complete gut content data by the ADBM  (Fig.
-\ref{fig:fig_ra}(a)).
-In the case of the Celtic Sea food web, only 171 gut content data (**OP: state what percentage this is) was required by the ADBM to predict food web with TSS equal to 95% of the mean TSS (0.68) achieved using complete gut content data by the ADBM (Fig.
-\ref{fig:fig_ra}(c)).
+## Mean standardised error in structural properties with respect to the number of gut content data
+
+Mean standardised error in structural properties of afon hirnant, broadstone stream, celtic sea and tadnoll brook food web reduced drastically with increasing number of predator gut content data at low number of predator gut content data (Fig.
+\ref{fig:fig_rab}).
+In case of Broadstone Stream food web, the 95% prediction interval reduced as well with increasing number of predator gut content data.
+
+\*\*AG: Working on this paragraph.
+
+```{r, echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_rab} Mean standardised error in structural properties of different food webs with respect to the number of gut content data."}
+knitr::include_graphics("../../results/misc/plot_mse_ngut_all.png")
+```
 
@@
 
-**OP: "There seems to be" is rather unconvential phrase.
-Perhaps use There was a positive trend between number of minimum gut content data and number of species (S) (Fig.
+There was a positive trend between number of minimum gut content data and number of species (S) (Fig.
 \ref{fig:fig_rb} (a)), links (L) (Fig.
@@
 
-```{r echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_rc} True skill statistics of the food web constructed using gut content data plotted against number of gut content data."}
-knitr::include_graphics("../../results/misc/plot_empTSS_ngut.png")
+```{r echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_rc} Link accumulation curve of the food web constructed using gut content data plotted against number of gut content data."}
+knitr::include_graphics("../../results/misc/plot_emplinks_ngut.png")
 ```
@@
 
-<!-- We have demonstrated how a food web model can be used to predict food web in the availability of incomplete data.
+We have demonstrated how a food web model can be used to predict food web in the availability of incomplete data.
 At lower amount of gut content data, ADBM is quite better at predicting trophic interactions.
-We also compute the upper limit of amount of gut content data till when it is advantageous to use the ADBM.
+We have computed the upper limit of amount of gut content data till when it can be used to compensate for undersampling.
 This can help us decide how much gut content data to actually collect when we are using a food web model to infer trophic interactions.
--->
+A future development could be to use this our approach on other food web models, and to also use food web data other than gut content data to parameterise those models.
+
+## Why incomplete gut content data can be used to infer trophic interactions?
+
+In all of the seven food webs, the ADBM was able to infer the trophic interactions using incomplete gut content data because the presence absence information from the gut content data was used to narrow down the possible model parameter values of the ADBM that best explained the predators' diets.
+Although in theory the ADBM can predict trophic interactions using only body sizes of organisms as it is based on set of foraging rule, it still requires some presence absence data to constrain the posterior parameter space thereby making more accurate predictions.
+
+## Why does the minimum gut data differ among food webs?
+
+We found the minimum number of gut content data to vary across food webs and this could be due to the possibility that the food webs are sampled differently i.e.
+some food webs are well sampled than others (Fig.
+\ref{fig:fig_rc}).
+Since some food webs are more size-structured than others, they are well predicted by the ADBM and therefore might require a lower number of gut content data for model parameterisation.
+\*\*:AG: I would need to add information about the interactions in these food webs.
+
+## Model fills up missing interactions and guide sampling direction
+
+When only few presence absence data is available, model can be used to fill up the missing interactions that has not been observed in the gut content data.
+Also model's predictions can be used as a guide to sample predator guts that might be significant in the food web.
+
+## Why is model's TSS less than one?
+
+Due to limitations of the ADBM as to not able to completely explain the interactions in a food webs using the foraging rules based on the body size and also possible undersampling in the observed data because of missing rare links, the ADBM's maximum predicted true skill statistics is always less than one.
+
+The maximum predictive power of a model is constrained by the rules it is based on.
+In the case of ADBM, that limits the predictive power of the ADBM is that it can only predict diets that are contiguous with respect to the size of prey.
+I.e.
+it cannot predict that a predator with consume prey of size 1 and 3, and not prey of size 2.
+Also, it is important to note that if the observed diets are not contiguous when prey are ordered by their size, the estimation process could lead to a lower value of the TSS.
+
+## TSS(Model)/TSS(Data) for different food webs
+
+\*\*AG: Working on this.
 
@@
 
-**OP: Focus on this... ## Why incomplete gut content data can be used to infer trophic interactions?
+\*\*AG: Working on this, not sure if this paragraph is needed.
 
--   Model fills up the missing interactions
+## Propagating uncertainty from gut content data to model's predictions
 
--   Partial data helps to constrain the parameter space
-
-<!-- Food web model is set of rules based on ecological theory which defines trophic interactions in a food web.
-A food web model does better in predicting trophic interactions provided the trophic interactions in an ecosystem is governed by these rules.
--->
-
-**OP Focus on this, at least in the context of further work that could be done. ## There is uncertainty in gut content data and needs to be propagated into model's predictions
+\*\*OP Focus on this, at least in the context of further work that could be done. ## There is uncertainty in gut content data and needs to be propagated into model's predictions
 
@@
 
-**OP: Focus on this, and other studies that have looked at the importance of quantity and quality of food web data ## Comparing our study with other studies of predicting food webs using incomplete data
+## Comparing our study with other studies of predicting food webs using incomplete data
+
+\*\*OP: Focus on this, and other studies that have looked at the importance of quantity and quality of food web data ## Comparing our study with other studies of predicting food webs using incomplete data
 
 Some studies have presented how the accuracy of food web prediction change when we vary the amount of food web data [@grayJoiningDotsAutomated2015]. 
+\*\*AG: Working on this paragraph.
 
-**OP: Focus on this.## What is the generalisability of our results?
+## What is the generalisability of our results?
 
--   Dependent on how size structured a food web is, how the food web is aggregated, the type of interactions
+\*\*OP: Focus on this.
 
-<!-- The model correctly predicted a greater proportion of links when the trophic interactions were more strongly dependent on size [@petcheySizeForagingFood2008].
-Indeed, constructing a food web based only on body size (i.e.
-ignoring taxonomy) resulted in almost twice the number of correctly predicted links, i.e.
-83%, in contrast to taxonomy [@woodwardChapterIndividualBasedFood2010].
-The goodness of fit of the ADBM's predictions depends on the types of interactions in the food webs [@petcheySizeForagingFood2008], because some of the interactions are more size structured than other interactions.
-For instance, predacious and aquatic herbivore interations were predicted better than parasitoid and herbivory ones [@petcheySizeForagingFood2008].
--->
+In our study, we have implemented the approach to only the ADBM.
+However, in principle, this approach could be extended to other food web models.
+A future prospect could be to study how good different food web models' prediction accuracy vary for different amount of gut content data.
+This can also help in making decision as to which food web model to chose from given set of gut content data.
 
-**OP: I suggest to put this in the Methods section, where the general method should also be described (a bit like I suggest at the end of the Introduction.
+A future study could be to use our approach of estimating the minimum gut content data for different food web models.
+An efficient model would be the one that uses minimum available gut content data to predict species interactions with high accuracy and high precision.
+
 ## Assumption that the food web constructed with the total gut content data is the true food web and how can this be improved
 
-Our study is based on the assumption that the food web constructed using the complete gut content data is the true food web.
-However, it might not be the case as the links are still under-sampled for many nodes [@woodwardIndividualBasedFoodWebs2010].
-This could result in a lower TSS of the predicted food web from the model which can lead to a higher upper limit on the amount of gut content data.
+Some of the food webs are not very well predicted using the ADBM.
+And with the assumption that the food web constructed from the complete gut content data is the true food web might result in not so accurate estimates of the minimum gut content data.
+As it might be the case that the links are still under-sampled for many nodes [@woodwardIndividualBasedFoodWebs2010].
 
-## Limitation of the model
+## How can we include other types of food web data?
 
-The maximum predictive power of a model is constrained by the rules it is based on.
+\*\*OP: Focus on this ## How can we include other food web data type?
 
-**OP: Focus on this ## How can we include other food web data type?
-
-A future prospect would be to include other types of food web data
-
--   experimentation (feeding trials)
-
--   DNA Metabarcoding
-
-## Extending the approach to other food web models
-
--   Current approach could be implemented with other food web models
-
-<!-- We have used rejection ABC to make use of incomplete gut content data to parameterise the ADBM.
-In theory, the ADBM could be replaced with any other food web models that predicts presence and absence interactions.
--->
+A future prospect would be to include other types of food web data along with gut content simultaneously to parameterise the ADBM.
+For example, one could use the approximate trophic position inferred from stable isotope ratio data from a tissue of an individual and gut content data of a different predator simultaneously to parameterise the ADBM.
+In this case, trophic position would be an additional summary statistics required in the parameterisation method.
+This is useful when only limited amount of diet information can be extracted by using a single method.
 
 # Conclusion
+
+\*\*OP: Working on this.
 
@@
 
-**OP: It needs to be very clear in the main text, and here, why this is being described. It is currently unclear, not least because the main text does not, I think, refer to the information here.
+\*\*OP: It needs to be very clear in the main text, and here, why this is being described. It is currently unclear, not least because the main text does not, I think, refer to the information here.
 

### 2022-02-28 manuscript/ms_C2/ms_C2.Rmd
Very minor
Update ms_C2.Rmd

@@
 ---
-title: Optimal amount of gut content data required to predict trophic interactions using a food web model
+title: How much gut content data is required to predict trophic interactions?
 authors:
@@
 
-  1)  Presence absence data of species interactions such as gut content data is used to parameterise food web models such as allometric diet  breadth model (ADBM), thereby predicting interactions.
-And collecting and analysing these data from the field is an expensive and time consuming task.
-Therefore, it is crucial to know how much gut content data is required to parameterise the ADBM with high accuracy and high precision for a given food web with minimum sampling effort.
-  2)  The novelty of our current approach is that we use approximate Bayesian computation to parameterise the ADBM, and true skill statistics to measure the goodness of fit for different amount of predators' gut content data.
-  3)  We estimated the minimum number of gut content data required for seven different food webs that resulted in 95% of the maximum true skill statistics achieved by the ADBM for total gut content data.
-We found that incomplete gut content data can be used to parameterise the ADBM with the lowest amount of gut content data being 28% of the total gut content data.
-  4)  These results suggest that one need not collect a large quantity of gut content data to predict a food web structure using a food web model, thereby reducing sampling effort considerably.
+  1)  Presence absence data of species interactions such as gut content data is used to parameterise food web models such as the allometric diet  breadth model (ADBM), thereby predicting interactions.
+Collecting and analysing these data from the field is, however, an expensive and time consuming task.
+Therefore, it is crucial to know how much gut content data is required to parameterise food web models with high accuracy and high precision.
+  2)  We apply to this problem a recently developed approach, namely Bayesian computation to parameterise the ADBM, and true skill statistics to measure the goodness of fit, and do so while varying the amount of gut content data is used in the parameterisation.
+  3)  We estimated the minimum number of gut content data required for seven different food webs that resulted in 95% of the maximum true skill statistics achieved by the ADBM when all available gut content data was used.
+We found that incomplete gut content data can be used to parameterise the ADBM with the lowest amount of gut content data being 28% of the available gut content data.
+  4)  These results suggest that one need not collect such a large quantity of gut content data to predict a food web structure using a food web model, thereby reducing sampling effort considerably, while having little effect on precision or accuracy of predictions.
 
@@
 For example, @petcheySizeForagingFood2008 used presence-absence information about trophic interactions to parameterise the allometric diet breadth model and thereby predict species interactions.
-These empirical information about interactions can be inferred from diverse set of methods such as gut content analysis [@peralta-maraverStructureDynamicsStability2017], stable isotope ratio analysis of tissues [@laymanCanStableIsotope2007], experimentation [@warrenSpatialTemporalVariation1989], DNA metabarcoding [@roslinUseDNABarcodes2016] and literature research [@grayJoiningDotsAutomated2015; @cohenSoilInvertebratesChemistry2014; @goldwasserConstructionAnalysisLarge1993a].
+These empirical information about interactions can come from diverse set of methods such as gut content analysis [@peralta-maraverStructureDynamicsStability2017], stable isotope ratio analysis of tissues [@laymanCanStableIsotope2007], experimentation [@warrenSpatialTemporalVariation1989], DNA metabarcoding of gut contents or faeces [@roslinUseDNABarcodes2016] and literature research [@grayJoiningDotsAutomated2015; @cohenSoilInvertebratesChemistry2014; @goldwasserConstructionAnalysisLarge1993a].
 
@@
 
-Food web methods mentioned above have multiple shortcomings.
-Stable isotope ratio analysis of the organism's tissue does not give a direct information of the diet of that organism but rather approximate trophic position of that species in the food web.
-Although mixing models can be used to determine what prey items are most likely fed upon by a predator but this results in uncertainty in the estimates [@kadoyaIsoWebBayesianIsotope2012; @crawfordApplicationsStableIsotope2008].
+Each of these sources of information about trophic interactions has shortcomings.
+Stable isotope ratio analysis of the organism's tissue does gives indirect information of the diet of that organism via revealing approximate trophic position of that species in the food web.
+Although mixing models can be used to determine what prey items are most likely fed upon by a predator, this results in uncertainty in the estimates [@kadoyaIsoWebBayesianIsotope2012; @crawfordApplicationsStableIsotope2008].
 Experimentation (e.g.
@@
 DNA metabarcoding could have many issues such as failure to relate OTUs to species, or inability to distinguish secondary predation, i.e.
-the DNA signature of the prey consumed by the prey consumed by the primary item found in the predator's gut.
+the DNA signature of the prey consumed by the prey consumed by the primary item found in the predator gut.
 Another approach to infer missing links is literature research which involves assuming that a link will occur because another author described it in some other system, or for related predator/prey species, e.g.
 from the same genus or family [@grayJoiningDotsAutomated2015; @cohen2014; @goldwasser1993].
-This typically results in a food web that will be very oversampled with false positives in the presence of links (citreqd).
+This typically results in a food web that has false positives--links included when in reality no link would occur (citreqd).
 @nielsen2018 have shown that gut content analysis method has a better match with real diet when compared to other methods.
@@
 Acquiring food web data from gut content analysis is time consuming and expensive (reference).
-In part this is due to the need for many gut contents to be collected and analysed in order to be confident that the majority of possible trophic links have been observed.
+In part this is due to the perception that many gut contents must be collected and analysed in order to be confident that the majority of possible trophic links among species have been observed.
 Furthermore, considerable time, resource investment, and expertise is required to process the collected samples.
@@
 
-Therefore, the key question we are interested in answering is how much presence-absence information, in the form of gut content data, is required to infer food web structure from a food web model specifically the ADBM with high accuracy and high precision.
+Therefore, the key question we are interested in answering is how much presence-absence information, in the form of gut content data, is required to infer food web structure from a food web model with high accuracy and high precision.
 In other words, how many samples of gut content should one collect from the field to parameterise a food web model?
-To answer this question, we use the presence-absence information from gut content data to parameterise the allometric diet breadth model (ADBM) thereby predicting trophic interactions in seven different food webs using rejection approximate Bayesian computation, where the fitness of the model was measured using true skill statistics.
+To answer this question, we use the presence-absence information from gut content data to parameterise the allometric diet breadth model (ADBM) thereby predicting trophic interactions in seven different food webs using rejection approximate Bayesian computation, where the fit of the model was measured using true skill statistics.
 We computed the true skill statistics of the predicted food webs for different number of predator guts to calculate the minimum number of gut content data to infer food web structure.
@@
 
-In the upcoming sections, we present the food webs, the allometric diet breadth model (ADBM) and the gut content data used to infer the trophic interactions in the presented food webs using the ADBM.
+In the upcoming sections, we present the empirical food webs, the allometric diet breadth model (ADBM), and the gut content data used to infer the trophic interactions.
 We also give a detailed account of using partial gut content data to parameterise the ADBM using rejection approximate Bayesian computation (ABC).
@@
 
-In our study, we used food webs for which gut content data is available at an individual level and, is FAIR.
+In our study, we used food webs for which gut content data is available at an individual level and data that is or that we could make FAIR [OP: cite this https://www.go-fair.org/fair-principles/].
 Presence and absence interactions of food web data can be aggregated in different ways [@gilljamSeeingDouble2011].
 A common way of aggregating food web data is the taxonomic approach, in which nodes in the food web are taxa (e.g.
-species) and one species is said to feed on another species if at least one individual of the latter is found in at least one gut of the former.
+species), or life stages of taxa, and one species is said to feed on another species if at least one individual of the latter is found in at least one gut of the former.
 Another approach is based on size, rather than taxonomy, and in this the nodes in the food web are size classes.
@@
 However, this might not be the case because the links are still under-sampled for many nodes [@woodwardIndividualBasedFoodWebs2010].
-This could result in a lower TSS of the predicted food web from the ADBM which can result in a biased estimate of the number of gut content data.
+This could result in a lower true skill statistic (TSS) of the predicted food web from the ADBM, which can result in a biased estimate of the number of gut content data [OP: this is unclear].
 
@@
 <!-- ### Broadstone Stream -->
+
+[OP: I like these sections and suggest to include them for other food webs also.]
 
@@
 The allometric diet breadth model (ADBM) is based on optimal foraging theory, specifically the contingency foraging model [@macarthurOptimalUsePatchy1966].
-We chose this model because it uses the body size of organisms as input to predict feeding interactions.
-The ADBM predicts the set of prey species a consumer should feed upon to maximise its rate of energy intake [@petcheySizeForagingFood2008].
-The foraging variables in the model are: energy content of the resources, handling times of the prey, space clearance rate and prey densities are allometrically scaled to the body sizes of the species.
+We chose this model for various reasons, including because it uses the body size of organisms as input to predict feeding interactions, and because of our familiarity with it.
+The ADBM predicts the set of prey types (e.g.
+species or sizes classes) a consumer should feed upon to maximise its rate of energy intake [@petcheySizeForagingFood2008].
+The foraging variables in the model are: energy content of the resources, handling times of the prey, space clearance rate, and prey densities.
+These are allometrically scaled to the body sizes of the species.
 Further details on the foraging rules defined in the ADBM and ADBM's predictive power across different food webs can be found in @petcheySizeForagingFood2008.
@@
 
-The accuracy of the predicted diet of the predators was defined using true skill statistic (TSS) which takes into account the true and false predictions of both the presence and absence of links defined as:
+The accuracy of the predicted diet of the predators was measured using true skill statistic (TSS) which takes into account the true and false predictions of both the presence and absence of links defined as:
 
 $$ \text{TSS} = \frac{ad-bc}{(a+c)(b+d)} $$ where $a$ is the number of observed links that are predicted by the model (true positives), $d$ is the number of observed absences of links that are correctly predicted (true negatives), $b$ is the number of false positives, and $c$ is the number of false negatives.
-
-The $TSS$ ranges from $-1$ to $1$, where +1 indicates a perfect prediction. A $TSS$ value of zero or less indicates a performance no better than random [@alloucheAssessingAccuracySpecies2006].
+The $TSS$ ranges from $-1$ to $1$, where +1 indicates a perfect prediction.
+A $TSS$ value of zero or less indicates a performance no better than random [@alloucheAssessingAccuracySpecies2006].
 
@@
 
-From an empirical dataset of gut content data, we draw a set of gut contents data randomly to create a partial gut content dataset. We then fit the ADBM to this partial dataset.
+From an empirical dataset of gut content data, we take a random sample of gut contents of specific size (see below) to create a partial gut content dataset.
+We then fit the ADBM to this partial dataset.
 
 To fit the ADBM to a gut content dataset (be it complete or partial), we used the rejection ABC method we previously developed in @gupta2021 to accept a parameter value from a prior distribution which would have resulted in the minimum distance, where distance = 1 - True skill statistic.
-The true skill statistic was computed between the predators' diet predicted from the ADBM, and that from the sampled gut content data.
-We repeated this process for $n~(= 100)$ number of times for every $i$ number of guts, where $i$ lies between 1 and total number of gut content data in the pool.
+The true skill statistic was computed between the diets predicted from the ADBM, and those observed in the sampled gut content data.
+We repeated this process $n~(= 100)$ times for every $i$ number of guts, where $i$ lies between 1 and total number of gut content data in the pool.
 
@@
 
--   A pool of gut content data $G: G = \{g_1, g_2, \dots, g_n\}$, where $g_{n}$ is a one-dimensional matrix containing ones and zeros.
+-   A pool of gut content data $G: G = \{g_1, g_2, \dots, g_n\}$, where $g_{n}$ is the observed diet matrix containing ones and zeros. [OP: I made some edits here, which I'm not sure if are correct.]
 
--   A model prediction $model(\theta): ADBM(\theta) = \{d_{p_1}, d_{p_1}, \dots, d_{p_k}\}$, where $d_{p_k}$ is a one-dimensional diet matrix of predator $k$ containing ones and zeros.
+-   A model prediction $model(\theta): ADBM(\theta) = \{d_{p_1}, d_{p_1}, \dots, d_{p_k}\}$, where $d_{p_k}$ is the predicted diet matrix of predator $k$ containing ones and zeros.
 
--   A summary statistic $s(x): s(x) \subseteq model(\theta)$
+-   A summary statistic $s(x): s(x) \subseteq model(\theta)$ [OP: a short explanation would be good.]
 
--   A distance function $d(x_i, y) : d(x_i,y) = 1 - TSS(x_i, y)$
+-   A distance function $d(x_i, y) : d(x_i,y) = 1 - TSS(x_i, y)$  [OP: a short explanation would be good.]
 
--   An observed food web $Y: Y = \{d_{p_1}', d_{p_1}', \dots, d_{p_k}'\}$
+-   An observed food web $Y: Y = \{d_{p_1}', d_{p_1}', \dots, d_{p_k}'\}$  [OP: a short explanation would be good.]
 
@@
 
-The $TSS$ between observed and predicted food webs for every $i$ number of gut content data drawn from the pool of gut content data.
+The $TSS$ between observed and predicted food webs, and the posterior parameter distributions for every $i$ number of gut content data drawn from the pool of gut content data.
 
@@
 
-We first present how the accuracy of the food web model i.e ADBM vary in predicting trophic interactions with increasing amount of gut content data provided to the food web model.
+We first present how the accuracy of the food web model in predicting trophic interactions varies with increasing amount of gut content data provided to the food web model.
 Then, we calculate the number of gut content data for each food webs that results in accuracy equal to 95% of the maximum true skill statistics predicted by the food web model.
-We also compute the goodness of the food web model in predicting structural properties from incomplete gut content data.
-We did that by computing mean standardised error in food web properties.
+We also compute how well  the food web model predicts structural properties from incomplete gut content data.
+by computing mean standardised error in food web properties.
 
@@
 \ref{fig:fig_ra}) (a, c, e, g, i, k, m).
-The prediction interval of the true skill statistics decreased with increasing number of predator guts with the mean TSS asymptoting to the maximum mean TSS achieved by the ADBM when all the gut content data was used.
+Furthermore, the prediction interval of the true skill statistics decreased with increasing number of predator guts with the mean TSS asymptoting to the maximum mean TSS achieved by the ADBM when all the gut content data was used.
 Although the maximum TSS varied among the food webs, the qualitative increase in the TSS was the same.
 
-For Broadstone Stream food web, with only 381 number of gut content data which is 38% of the total gut content data, the ADBM predicted the food web with the TSS of 0.74 which was 95% of the mean TSS (0.78) achieved using complete gut content data by the ADBM (Fig.
+For Broadstone Stream food web, with only 381 gut contents, which is 38% of the total gut content data, the ADBM predicted the food web with the TSS of 0.74 which was 95% of the mean TSS (0.78) achieved using complete gut content data (Fig.
 \ref{fig:fig_ra}(a)).
-In case of the Celtic Sea food web, only 171 gut content data which is 35% of the total gut content data was required by the ADBM to predict food web with TSS equal to 95% of the mean TSS (0.68) achieved using complete gut content data by the ADBM (Fig.
+In case of the Celtic Sea food web, only 171 gut content data which is 35% of the total gut content data was required by the ADBM to predict food web with TSS equal to 95% of the mean TSS (0.68) achieved using complete gut content data (Fig.
 \ref{fig:fig_ra}(c)).
-
-## TSS(Model)/TSS(Data) for different food webs
 
@@
 \ref{fig:fig_ra} (b, d, f, h, j, l, n)).
-After a certain increase in the number of predator guts, the ratio TSS(Model)/TSS(data) reduced to less than one, and reduced further gradually.
+An increase in the number of predator guts did reduce the ratio TSS(Model)/TSS(data) reduced to less than one, and reduced further gradually.
+This shows that with less data available it is better to use the model, while if more data is available then it is better to use the data itself.
 
@@
 
-Mean standardised error in structural properties of afon hirnant, broadstone stream, celtic sea and tadnoll brook food web reduced drastically with increasing number of predator gut content data at low number of predator gut content data (Fig.
+Mean standardised error in structural properties of Afon Hirnant, Broadstone Stream, Celtic Sea and Tadnoll Brook food web reduced drastically with increasing number of predator gut content data at low number of predator gut content data (Fig.
 \ref{fig:fig_rab}).
@@
 
-## Dependence of minimum gut content data on number of species, links and connectance
+## Dependence of the minimum gut content data on number of species, links and connectance
 
-There was a positive trend between number of minimum gut content data and number of species (S) (Fig.
+There was a positive trend between minimum gut content data [OP: minimum that could be used in order to ensure 95% of maximum TSS???] and number of species (S) (Fig.
 \ref{fig:fig_rb} (a)), links (L) (Fig.
@@
 \ref{fig:fig_rb} (a, c, e).
-The number of minimum gut content data increases with number of maximum gut content data sampled (Fig.
+The minimum gut content data increases with number of gut content data sampled (Fig.
 \ref{fig:fig_rb} (b)).
-There seems to be a negative relationship between proportion of minimum gut (= Number of minimum gut / Number of maximum guts sampled) and number of species (S) (Fig.
+Furthermore, there seems to be a negative relationship between proportion of minimum gut (= Number of minimum gut / Number of maximum guts sampled) and number of species (S) (Fig.
 \ref{fig:fig_rb} (f)), links (L) (Fig.
@@
 
-We have demonstrated how a food web model can be used to predict food web in the availability of incomplete data.
-At lower amount of gut content data, ADBM is quite better at predicting trophic interactions.
-We have computed the upper limit of amount of gut content data till when it can be used to compensate for undersampling.
-This can help us decide how much gut content data to actually collect when we are using a food web model to infer trophic interactions.
-A future development could be to use this our approach on other food web models, and to also use food web data other than gut content data to parameterise those models.
+We have demonstrated how a food web model can be used to predict food webs reasonably well even when incomplete data about trophic interactions is available.
+At lower amount of gut content data, predicting with the model is better than using the data itself, while at higher amounts of gut content data, it is better to only use the data.
+We computed the upper limit of amount of gut content data till when it can be used to compensate for undersampling [OP: reword this sentence, it is unclear.].
+This can help inform how much gut content data to actually collect when we are using a food web model to infer trophic interactions.
+A future development could be to make the same assessment using other food web models, and to also use food web data other than gut content data to parameterise those models.
 
@@
 
-In all of the seven food webs, the ADBM was able to infer the trophic interactions using incomplete gut content data because the presence absence information from the gut content data was used to narrow down the possible model parameter values of the ADBM that best explained the predators' diets.
+In all of the seven food webs, the ADBM was able to infer the trophic interactions using incomplete gut content data because the presence absence information from the gut content data was still sufficient to constrain the possible model parameter values of the ADBM that best explained the predators' diets.
 Although in theory the ADBM can predict trophic interactions using only body sizes of organisms as it is based on set of foraging rule, it still requires some presence absence data to constrain the posterior parameter space thereby making more accurate predictions.
@@
 
-We found the minimum number of gut content data to vary across food webs and this could be due to the possibility that the food webs are sampled differently i.e.
-some food webs are well sampled than others (Fig.
+We found the minimum amount of gut content data to vary across food webs and this could be due to the possibility that the food webs are sampled differently, i.e.
+some food webs are more extensively sampled than others (Fig.
 \ref{fig:fig_rc}).
-Since some food webs are more size-structured than others, they are well predicted by the ADBM and therefore might require a lower number of gut content data for model parameterisation.
+Furthermore, it is possible that interactions in some of the food webs are are more size-structured than others, and are therefore better predicted by the ADBM and consequently require a lower number of gut content data for model parameterisation.
+
 \*\*:AG: I would need to add information about the interactions in these food webs.
 
-## Model fills up missing interactions and guide sampling direction
+## Model fills up missing interactions and guides sampling direction
 
-When only few presence absence data is available, model can be used to fill up the missing interactions that has not been observed in the gut content data.
-Also model's predictions can be used as a guide to sample predator guts that might be significant in the food web.
+When little data about trophic interactions is available, the model can be used to add data about interactions for which data is missing.
+Furthermore, the model predictions can be used as a guide to sample predator guts that might be significant in the food web [OP: how?
+I suggest to explain this in more detail.]
 
@@
 
-Due to limitations of the ADBM as to not able to completely explain the interactions in a food webs using the foraging rules based on the body size and also possible undersampling in the observed data because of missing rare links, the ADBM's maximum predicted true skill statistics is always less than one.
+The food web model used (the ADBM) cannot explain all the interactions in any observed food web that it has been fit to.
+The foraging rules it encodes are based on the body size and have particular structure and assumptions; not all of these are met by all observed interactions.
+For example, the ADBM can only predict diets that are contiguous with respect to the size of prey.
+I.e.
+it cannot predict that a predator will consume taxa of size 1 and 3, and not taxa of size 2.
+Hence, if the observed diets are not contiguous when prey are ordered by their size, the estimation process could lead to a lower value of the TSS.
 
-The maximum predictive power of a model is constrained by the rules it is based on.
-In the case of ADBM, that limits the predictive power of the ADBM is that it can only predict diets that are contiguous with respect to the size of prey.
-I.e.
-it cannot predict that a predator with consume prey of size 1 and 3, and not prey of size 2.
-Also, it is important to note that if the observed diets are not contiguous when prey are ordered by their size, the estimation process could lead to a lower value of the TSS.
+Furthermore, the observed data may be missing links, e.g.
+links that rarely occur.
+Hence the ADBM's maximum predicted true skill statistics is less than one for all food webs it has so far been fit to.
 
@@
 
+[OP: This one I already shared with you: https://onlinelibrary.wiley.com/doi/10.1111/ele.13966
+
 \*\*OP: Focus on this, and other studies that have looked at the importance of quantity and quality of food web data ## Comparing our study with other studies of predicting food webs using incomplete data
@@
 
-In our study, we have implemented the approach to only the ADBM.
-However, in principle, this approach could be extended to other food web models.
-A future prospect could be to study how good different food web models' prediction accuracy vary for different amount of gut content data.
-This can also help in making decision as to which food web model to chose from given set of gut content data.
+In our study, we have implemented the approach only with the ADBM.
+However, in principle, this approach could be extended to other food web models [OP: such as???].
+A future prospect could be to study how well different food web models' prediction accuracy varies for different amount of gut content data.
+This can also help in making decision as to which food web model to chose from given a set of gut content data.
 
-A future study could be to use our approach of estimating the minimum gut content data for different food web models.
+[OP: seems to not add much relative to the previous paragraph.] A future study could be to use our approach of estimating the minimum gut content data for different food web models.
 An efficient model would be the one that uses minimum available gut content data to predict species interactions with high accuracy and high precision.
 
+[OP: comment if and why one might expect other food web models to show different efficiency.]
+
 ## Assumption that the food web constructed with the total gut content data is the true food web and how can this be improved
+
+[OP: this paragraph / section needs further development]
 
@@
 A future prospect would be to include other types of food web data along with gut content simultaneously to parameterise the ADBM.
-For example, one could use the approximate trophic position inferred from stable isotope ratio data from a tissue of an individual and gut content data of a different predator simultaneously to parameterise the ADBM.
-In this case, trophic position would be an additional summary statistics required in the parameterisation method.
-This is useful when only limited amount of diet information can be extracted by using a single method.
+For example, one could use the approximate trophic position inferred from stable isotope ratio data from a tissue of an individual and gut content data of a different predator simultaneously to parameterise a food web model such as the ADBM.
+In this case, trophic position would be an additional summary statistic required in the parameterisation method.
+This combination of different types of data about trophic interactions could be particularly useful when only a limited amount of diet information can be extracted by using a single method.
 
@@
 
-\*\*OP: Working on this.
+\*\*AG: Working on this.
 
@@
 
-\*\*OP: It needs to be very clear in the main text, and here, why this is being described. It is currently unclear, not least because the main text does not, I think, refer to the information here.
+\*\*OP: It needs to be very clear in the main text, and here, why this is being described.
+It is currently unclear, not least because the main text does not, I think, refer to the information here.
+[OP: I'm not sure my comment has been addressed.
+We should discuss this.] [OP: I don't see this Supplement being referred to anywhere in the main text.
+I would expect it to be.] [OP: I advise to integrate the content of this supplement into the main article.
+There is not so much of it, and it is insightful.]
 
@@
 
-## Prediction using simulated gut content data from a simulated food web
+## Prediction using gut content data from a simulated food web
 
@@
 
-The true skill statistics (TSS) between the predicted food web and observed food web saturated with an increasing number of distinct predator guts in a sample (Fig.
+The true skill statistics (TSS) between the predicted food web and simulated observed food web saturated with an increasing number of distinct predator guts in a sample (Fig.
 \ref{fig:fig_r0}).
@@
 The maximum limit of the prediction interval of TSS estimated using the complete gut data and the partial gut data were almost equal, with the minimum limit of the prediction interval of TSS using partial gut data being lower than that from the complete gut data.
-Eventually, the gap between the mean TSS using the partial gut data and the complete gut data reduced with an increasing number of distinct predator guts suggesting when we have enough predator species' gut data, the achieved TSS was almost constant and hence independent of the amount of gut data.
+Eventually, the gap between the mean TSS using the partial gut data and the complete gut data reduced with an increasing number of distinct predator guts.
+This suggests that when there is enough predator species' gut data, the achieved TSS was almost constant and hence independent of the amount of gut data.
 

### 2022-03-01 manuscript/ms_C2/ms_C2.Rmd
minor

--- 2022-02-07 manuscript/ms_C2/ms_C2.Rmd
@@
 
-  1)  Presence absence data of species interactions such as gut content data is used to parameterise food web models such as allometric diet  breadth model (ADBM), thereby predicting interactions.
+  1)  Presence absence data of species interactions such as gut content data is used to parameterise food web models such as allometric diet  breadth model (ADBM), thereby predicting the food web structure.
 And collecting and analysing these data from the field is an expensive and time consuming task.

### 2022-06-20 manuscript/ms_C2/ms_C2_v2.Rmd

---
title: How much predator guts are required to predict trophic interactions?
authors:
- affiliation: University of Zurich
  department: Department of Evolutionary Biology and Environmental Studies
  email: anubhav.gupta@ieu.uzh.ch
  location: 8057 Zurich, Switzerland
  name: Anubhav Gupta
  thanks: Corresponding author
- affiliation: University of Essex
  department: School of Life Sciences
  email: e.ogorman@essex.ac.uk
  location: CO4 3SQ Colchester, UK
  name: Eoin O' Gorman
- affiliation: Imperial College London
  department: Georgina Mace Centre for the Living Planet, Department of Life Sciences
  email: guy.woodward@imperial.ac.uk
  location: Ascot, Berkshire Sl5 7PY, UK
  name: Guy Woodward
- affiliation: XXX XXX
  department: XXX XXX
  email: XXX XXX
  location: XXX XXX
  name: Other authors
- affiliation: University of Zurich
  department: Department of Evolutionary Biology and Environmental Studies
  email: owen.petchey@ieu.uzh.ch
  location: 8057 Zurich, Switzerland
  name: Owen L. Petchey
geometry: margin=1in
abstract: |

  1)  One of the biggest obstacles in food web ecology is the time and effort required to adequately describe the structure of a food web using individual predator guts. Food web models such as the allometric diet breadth model (ADBM) can be used to circumvent this problem by predicting the interactions based on easily measured characteristics, such as the size of organisms. However, presence-absence data such as predator guts is required to parameterise these food web models, and collecting and analysing these data from the field is an expensive and time-consuming task. Therefore, it is crucial to know how much predator guts is required to parameterise food web models with high accuracy and high precision.
  2)  Here, we explore seven exceptionally well-characterised food webs in the literature and determine the minimum predator guts that would be needed to accurately predict their structure using the ADBM. We use Bayesian computation to parameterise the ADBM, and true skill statistics to measure the goodness of fit, and do so while varying the amount of predator guts used in the parameterisation to test the effect of sampling effort.
  3)  We found that incomplete predator guts can be used to parameterise the ADBM, with the lowest amount of predator guts being 28% of the available predator guts.
  4)  These results suggest that one need not collect such a large quantity of predator guts to predict the structure of a food web, thereby reducing sampling effort considerably, while having little effect on precision or accuracy of predictions.

keywords:
  - predator guts
  - ADBM
  - food web accuracy
  - food web prediction
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage {amsmath}
   - \setlength\parindent{24pt}
   - \usepackage{setspace}\doublespacing
indent: true
mainfont: Times New Roman
bibliography: bibliography.bib
biblio-style: biblatex
output:
  # word_document:
  #   fig_caption: yes
  #   number_sections: yes
  rticles::arxiv_article:
    keep_tex: true
---

# Introduction

Knowledge about the trophic interactions in a food web is crucial in ecology for purposes ranging from identifying keystone species [@jordanKeystoneSpeciesFood2009] to quantifying robustness of a food web to species extinctions [@dunneNetworkStructureBiodiversity2002]. This has led to the development of numerous food web models and associated theory [@allesinaGeneralModelFood2008; @cohenStochasticTheoryCommunity1985; @gravelInferringFoodWeb2013; @petcheySizeForagingFood2008; @tamaddoni-nezhadConstructionValidationFood2013]. Along with inferring missing links in an observed food web, such food web models are also increasingly used for ecological forecasting [@hattabForecastingFinescaleChanges2016; @lindegrenEcologicalForecastingClimate2010] and for understanding the underlying mechanism governing trophic interactions in the wild [@ogormanSimpleModelPredicts2019].

Although food web models are constructed using prior theory about the factors that determine trophic interactions, empirical data about interactions are required to parameterise a model. For example, @petcheySizeForagingFood2008 and @guptaSimultaneouslyEstimatingFood2022 used presence-absence information about trophic interactions to parameterise the allometric diet breadth model and thereby predict species interactions. Such empirical information about interactions can come from diverse set of methods such as gut content analysis [@peralta-maraverStructureDynamicsStability2017], stable isotope ratio analysis of tissues [@laymanCanStableIsotope2007], experimentation [@warrenSpatialTemporalVariation1989], DNA metabarcoding of gut contents or faeces [@roslinUseDNABarcodes2016] and literature research [@grayJoiningDotsAutomated2015; @cohenSoilInvertebratesChemistry2014; @goldwasserConstructionAnalysisLarge1993a] but each of these sources of information about trophic interactions has serious shortcomings, hindering the advancement of the field. For example: stable isotope ratio analysis of the organism's tissue does not give direct taxonomically resolved information of the diet of that organism, but rather it provides approximate trophic position of that species in the food web [@wadaUseStableIsotopes1991; @jenningsTrophicLevelsMarine2015] and although mixing models can be used to determine what prey items are most likely fed upon by a predator, this results in uncertainty in the estimates [@kadoyaIsoWebBayesianIsotope2012; @crawfordApplicationsStableIsotope2008]. Similarly, more recent approaches using DNA metabarcoding may give much higher taxonomic resolution but present other challenges, such as an inability to resolve secondary predation or cannibalism [@pompanonWhoEatingWhat2012; @nielsen2018] which are common in nature and also being prone to environmental contamination (e.g. DNA in the water swallowed along with DNA from an aquatic consumer's prey cannot be differentiated from actual prey) [@kellyUsingEnvironmentalDNA2014]. Furthermore, construction of food webs via literature review, which is one of the most common practices in food web research, can lead to false positives--links included when in reality no link would occur because it makes an assumption that the species interactions inferred from a system will occur in another system as well [@grayJoiningDotsAutomated2015; @cohen2014; @goldwasser1993]. It is unsurpsing given the limitations of these proxy or inferential approaches that authors such as @nielsen2018 have shown that gut content analysis method has a better match with real diet when compared to other methods.

Although gut content analysis is viewed as the "gold standard", acquiring such food web data from direct gut content analysis is extremely time consuming and expensive [@grayJoiningDotsAutomated2015a] and it also requires high skill levels in taxonomic identification, often involving dissection and microscopy techniques [@hyslopStomachContentsAnalysis1980]. The perception that this is unavoidably laborious and costly is also in part due to the assumption that many gut contents must be collected and analysed in order to be confident that the majority of possible trophic links among species have been observed. Most studies fail to quantify the effort needed, with yield-effort curves being the exception rather than the rule and those that have been done often point to the apparent need for hundreds or thousands of guts to be analysed to fully capture a food web's structure. Hence, it is of huge importance to know the minimum number of predator guts required to parameterise a food web model with high accuracy and high precision: this would enable researchers to allocate resources more effectively a priori, and even having a rough rule of thumb as to when is a good point to stop collecting any further empirical data on the food web is far better than the current common practice of simply taking a fixed set of samples with on yield-effort analyses being undertaken.

Therefore, the key question we are interested in answering is how much presence-absence information, in the form of predator guts, is required to infer food web structure from a food web model with high accuracy and high precision? In other words, how many samples of predator guts should one collect from the field to parameterise a food web model? To answer this question, we use different amount of predator guts to parameterise the allometric diet breadth model (ADBM) thereby predicting trophic interactions in seven different food webs using rejection approximate Bayesian computation, and calculate the minimum number of predator guts to infer food web structure. Our study provides a guideline on how many predator guts are required to predict food web structure using a food web model.

# Materials and Methods

We present the empirical food webs, the allometric diet breadth model (ADBM), and the predator guts used to infer the trophic interactions. We also give a detailed account of using partial predator guts to parameterise the ADBM using rejection approximate Bayesian computation (ABC). We assessed model predictions using the true skill statistic for comparison across the food webs.

## The Empirical Food Webs

In our study, we used food webs for which predator guts are available at an individual level and data that is or that we could make FAIR (Findable Accessible Interoperable Reusable; @wilkinsonFAIRGuidingPrinciples2016). In our study, first, we consider food webs where nodes are size classes i.e. individuals are aggregated into these size classes based on their body size. A feeding link occurs between two size classes if at least one prey item within a size class was found in the gut of another size class of predator, irrespective of the taxonomy of the individuals. We used this approach because of several reasons such as to take account the ontogenetic shift in the diet of a predator [@woodward2010], individual-based interaction based on body size which would not been considered if nodes were aggregated based on taxonomy as a taxonomic node can have a large variation in the body size. Food webs aggregated using size can be used to model the impacts of commercial exploitation on marine ecosystems [@jenningsPredictingEffectsClimate2010]. Second, we also consider food webs where nodes are aggregated based on the taxonomy of the individuals as this is the most common way of constructing food webs in food web ecology.

Our study food webs are freshwater food webs except the Celtic Sea food web which belongs to a marine ecosystem. Most of the food webs are dominated by invertebrates except Celtic Sea which is dominated by fishes and Tadnoll Brook which is dominated by fishes as well as invertebrates. The food webs vary in the number of nodes, trophic links, connectance and body sizes (Table 1).

Invertebrates in freshwater food webs were collected using Hess or Surber sampler, whereas fishes were caught with electrofisher, and anaesthetised using 2-phenoxyethanol in freshwater food webs. In case of the Celtic Sea, trawling was used to catch fishes.

The foreguts of the collected invertebrate predators were dissected and examined under the microscope. Regression equations were used to convert predator and prey lengths to the respective body masses. In case if the prey items were too highly digested for body lengths to be measured reliably, previously established regressions based on head capsule width were used as an alternative linear dimension. More detailed description of these food webs is present in @gilljamSeeingDouble2011.

```{r echo=FALSE, warning=FALSE}

library(readxl)

library(knitr)

library(kableExtra)

fw_table <- read_excel("../table/fw_table.xlsx")

kable(fw_table, format = "latex",

      caption = "\\label{fig:tab_1}Information about the empirical food webs. AG: Some information will be updated.", escape = FALSE, align = "l") %>%

  kable_styling(font_size = 7, latex_options="scale_down", row_label_position = 1) %>%

  landscape(margin = "1cm") %>%

  column_spec(1, width = "3cm") %>%

  column_spec(2, width = "8em") %>%

  column_spec(7, width = "8em") %>%

  column_spec(8, width = "8em") %>%

  column_spec(9, width = "8em")

```

## Allometric Diet Breadth Model (ADBM)

The allometric diet breadth model (ADBM) is based on optimal foraging theory, specifically the contingency foraging model [@macarthurOptimalUsePatchy1966]. We chose this model because it can predict species interactions based on an easily measurable trait body size. The ADBM predicts the set of prey types (e.g. species or sizes classes) a consumer should feed upon to maximise its rate of energy intake [@petcheySizeForagingFood2008]. The foraging variables in the model are: energy content of the resources, handling times of the prey, space clearance rate, and prey densities. These are allometrically scaled to the body sizes of the species. Further details on the foraging rules defined in the ADBM and ADBM's predictive power across different food webs can be found in @petcheySizeForagingFood2008.

## Assessment of prediction

The accuracy of the predicted diet of the predators was measured using a widely used accuracy measure in food web ecology namely true skill statistic (TSS) [@grayJoiningDotsAutomated2015; @gravelInferringFoodWeb2013; @guptaSimultaneouslyEstimatingFood2022]. We chose this metric because it takes into account the true and false predictions of both the presence and absence of links defined as:

$$ \text{TSS} = \frac{ad-bc}{(a+c)(b+d)} $$ where $a$ is the number of observed links that are predicted by the model (true positives), $d$ is the number of observed absences of links that are correctly predicted (true negatives), $b$ is the number of false positives, and $c$ is the number of false negatives. The $TSS$ ranges from $-1$ to $1$, where +1 indicates a perfect prediction. A $TSS$ value of zero or less indicates a performance no better than random [@alloucheAssessingAccuracySpecies2006].

## Inferring food web using partial predator guts

From an empirical dataset of predator guts, we take a random sample of gut contents of specific size (see below) to create a partial predator guts dataset. We then fit the ADBM to this partial dataset.

```{r, echo=FALSE, fig.align='center', out.width="350px", fig.cap="\\label{fig:fig_ra} Flowchart of the subsampling method implemented to predict the full food web from the food web model using the predator guts."}
knitr::include_graphics("../../manuscript/fig/ms_C2_flowchart.png")
```

To fit the ADBM to partial predator guts dataset, we used the rejection approximate Bayesian computation method we previously developed in @guptaSimultaneouslyEstimatingFood2022 to accept a parameter value from a prior distribution which would have resulted in the minimum distance, where distance = 1 - TSS. The true skill statistic was computed between the diets predicted from the ADBM, and those observed in the sampled predator guts. We repeated this process $n~(= 100)$ times for every $i$ number of guts, where $i$ lies between 1 and total number of predator guts in the pool.

*Input:*

-   Predators $P: P = \{p_1, p_2, \dots, p_k \}$

-   A pool of predator guts $G: G = \{g_1, g_2, \dots, g_n\}$, where $g_{n}$ is the observed diet matrix containing ones and zeros.

-   A model prediction $model(\theta): ADBM(\theta) = \{d_{p_1}, d_{p_1}, \dots, d_{p_k}\}$, where $d_{p_k}$ is the predicted diet matrix of predator $k$ containing ones and zeros.

-   A summary statistic $s(x): s(x) \subseteq model(\theta)$, where $s(x)$ is the diet of some or all of the predators.

-   A distance function $d(x_i, y) : d(x_i,y) = 1 - TSS(x_i, y)$, which quantifies how close the observed diet is to the predicted diet of some or all of the predators.

-   An observed food web $Y: Y = \{d_{p_1}', d_{p_1}', \dots, d_{p_k}'\}$, where $d_{p_k}'$ is the observed diet matrix of predator $k$ containing ones and zeros.

*Sampling:*

for $i = 1, \dots, tgut$ where $tgut$ is the total number of predator guts in the pool $G$

-   for $j = 1, \dots, nsample$ where $nsample$ is the number of independent samples to be drawn

    -   Subsample a set of predator guts $y = \{g_1, g_2, \dots, g_i\}$ from the pool of predator guts $G$

    -   for $k = 1, \dots, npar$ where $npar$ is the number of parameter values to be sampled

        -   Draw a set of parameter values $\theta_k$ from the prior distribution $\pi(\theta)$

        -   Compute the model result $x_k = model(\theta_k)$

        -   Compute $s(x_k)$ and $d(s(x_k), y)$

    -   Accept $\theta_j$, which results in the $min_k\{d(s(x_k), y)\}$

-   Compute $TSS_{i}(x, Y) = \{TSS(x_i, Y): x_i = ADBM(\theta_j), \theta_j \text{ computed from previous step}\}$ using the accepted $\theta_1, \dots, \theta_{nsample}$

*Output:*

The $TSS$ between observed and predicted food webs, and the posterior parameter distributions for every $i$ number of predator guts drawn from the pool of predator guts.

## Computing the minimum number of predator guts

Using TSS of the model predicted food webs for different number of predator guts, we computed the number of predator guts that results in the mean TSS equal to the 95% of the mean TSS achieved by the model using all the predator guts available in the pool for a food web. We call this number of predator guts as the minimum number of predator guts.

## Standardising sampling level of the food webs

Since the seven food webs have different levels of sampling effort, with Broadstone Stream being the most sampled among all, and every other food web being undersampled when compared to the Broadstone Stream food web (SI Fig. S2), we used the R *vegan* package to account for the undersampling with respect to the Broadstone Stream food web. We fitted the link accumulation curves using the fitspecaccum function to a set of nonlinear regression models suggested in @denglerWhichFunctionDescribes2009 and used the AIC criteria for model selection. We then extrapolated the link accumulation curves for all the food webs except the Broadstone Stream and computed the corrected number of predator guts that would have resulted in the gradient of the link accumulation curve equal to the gradient of that of the Broadstone Stream when all the predator guts were used. We also calculated the corrected number of trophic links corresponding to that corrected number of predator guts. For the food webs, we calculated the undersampling factor which is equal to the ratio of corrected number of predator guts to the number of predator guts in the pool. Using the undersampling factor, we further calculated the corrected minimum number of predator guts which is equal to the product of the undersampling factor and the minimum number of predator guts.

# Results

We first present how the accuracy of the food web model in predicting trophic interactions varies with increasing amount of predator guts provided to the food web model. We investigate how the minimum number of predator guts varied with number of trophic links and number of species.

```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_ra} Accuracy of the predicted food web measured using the true skill statistic, predicted by the ADBM parameterised using predator guts. Line and shaded grey region represents the mean and the prediction interval corresponding to 100 independent samples respectively. Red line represents the number of predator guts required to achieve a TSS of 95\\% of the maximum TSS."}
knitr::include_graphics("../../results/misc/plot_TSS_vs_ngut.png")
```

The true skill statistics of the food webs predicted by the ADBM using incomplete predator guts improved quickly for lower number of predator guts (Fig. \ref{fig:fig_ra}). Furthermore, the width of the prediction interval of the true skill statistics decreased with increasing number of predator guts with the mean TSS asymptoting to the maximum mean TSS achieved by the ADBM when all the predator guts was used. Although the maximum TSS varied among the food webs, the qualitative increase in the TSS was the same.

For Broadstone Stream food web, with only 381 predator guts, which is 38% of the total predator guts, the ADBM predicted the food web with the mean TSS of 0.74. This was equivalent to 95% of the mean TSS (0.78) achieved using complete predator guts (Fig. \ref{fig:fig_ra}(a)): i.e. the main characteristics of the food web could be captured with about 1/3 of the effort used in the original study. In case of the Celtic Sea food web, only 171 predator guts which is 35% of the total predator guts was required by the ADBM to predict food web with TSS equal to 95% of the mean TSS (0.68) achieved using complete predator guts (Fig. \ref{fig:fig_ra}(b)).

The minimum number of predator guts was not significantly related to number of trophic links (Fig. \ref{fig:fig_rb} (a)) and the number of species (Fig. \ref{fig:fig_rb} (b)). Similarly, the corrected minimum number of predator guts was not significantly related to corrected connectance, corrected number of trophic links and number of species respectively (Fig. \ref{fig:fig_rb} (c, d)). Correcting for the undersampling in the food webs improved the fit between the minimum number of predator guts and the number of trophic links from $R^2 = 0.13$ (Fig. \ref{fig:fig_rb} (a)) to $R^2 = 0.43$ (Fig. \ref{fig:fig_rb} (c)).

```{r echo=FALSE, fig.align='center', out.width="300px", fig.cap="\\label{fig:fig_rb} (a, b) Minimum number of predator guts (i.e the amount of predator guts used in order to ensure 95\\% of the maximum TSS) plotted against number of trophic links (L) and number of species respectively. (c, d) Corrected minimum number of predator guts (i.e. the minimum number of predator guts which takes into account the undersampling level of the food webs) plotted against corrected number of trophic links and number of species (S) respectively. Solid lines are linear regression ((a) t = 0.876, df = 5, P = 0.421; (c) t = 1.923, df = 5, P = 0.113; (d) t = 1.099, df = 5, P = 0.322) and grey region represents 95\\% confidence intervals."}
knitr::include_graphics("../../results/misc/plot_n_min_gut_vs_SL.png")
```

# Discussion

<!-- Eoin's comment: The discussion is a bit insular and focused on incremental improvements of the current model. Try to relate it better to the surrounding literature, think about applications of your findings, and expand some of those sections on other models and food web variables that have already been assessed or would be interesting to in the near future. -->

We have demonstrated how a food web model can be used to predict the full structure of a food web when incomplete data about trophic interactions is available, which is true in most of the real food webs. This can help inform how much predator guts to actually collect when we are using a food web model to infer trophic interactions for an ecosystem with a given number of species. A future development could be to make the same assessment using other food web models, and to also use food web data other than predator guts to parameterise those models.

Our study provides a ballpark figure of the minimum number of predator guts that need to be sampled to predict the structure of a food web using a food web model for an ecosystem with a given number of species. For instance, Fig. \ref{fig:fig_rb} (d) can be used as a rough estimate of how many predator guts needs to be collected to predict food web structure using a food web model for a given number of species. This would lead to a reduction in the hundreds of predator guts that would have to be collected in the first place [@ingsEcologicalNetworksFood2009], thereby saving considerable time and resources.

In our study, we have implemented the approach only with the ADBM, which is a model based on size rules. Therefore, we suspect to get a similar result (i.e. minimum number of predator guts for a food web) for a different food web model based on size rules such as the niche model by @gravelInferringFoodWeb2013. For a given food web, some food web models might do better job at predicting its structure as compared to other food web models, so we suggest to extend our approach to other food web models such as niche model [@williamsSimpleRulesYield2000; @gravelInferringFoodWeb2013; @allesinaGeneralModelFood2008] and nested hierarchical model [@cattinPhylogeneticConstraintsAdaptation2004]. A future prospect could be to study how well different food web models' prediction accuracy vary with different amount of predator guts. This can also help in making decision as to which food web model to chose from for a given a set of predator guts. We suspect the relationship (i.e shape of the curve) between the TSS of the predicted food web and the number of predator guts might vary within food web models because of the difference on the set of rules used to define those models and how well those rules explain the food web structure. For example: a food web model based on body size trait would require less amount of data to predict a size structured food web as compared to a food web model based on trait other than body size.

Some studies have presented how the accuracy of food web prediction change when the amount of food web data is varied [@grayJoiningDotsAutomated2015]. For example @desjardins-proulxEcologicalInteractionsNetflix2017 has used predictive machine learning models and @caronAddressingEltonianShortfall has used predictive traits-based models on partial knowledge of interactions to reconstruct a food web accurately, in contrast to our study where we used a mechanistic food web model.

In all of the seven food webs, the ADBM was able to infer the trophic interactions using incomplete predator guts because the presence absence information from the predator guts was still sufficient to constrain the possible model parameter values of the ADBM that best explained the predators' diets. Although in theory the ADBM can predict trophic interactions using only body sizes of organisms as it is based on set of foraging rules, it still requires some presence absence data to constrain the posterior parameter space thereby making more accurate predictions [@petcheySizeForagingFood2008].

To characterise trophic interactions which are rare in the nature one would require more predator guts to observe those interactions as compared to characterising trophic interactions which are more frequent in the nature. The model is perhaps able to infer these rare interactions using a relatively lower number of predator guts which one might have inferred directly from the predator guts only after collecting a large number of gut content samples.

Like any other food web models, the food web model used (the ADBM) cannot explain all the interactions in any observed food web that it has been fit to. The foraging rules it encodes are based on the body size and have particular structure and assumptions; not all of these are met by all observed interactions [@petcheySizeForagingFood2008]. For example, the ADBM can only predict diets that are contiguous with respect to the size of prey. I.e. it cannot predict that a predator will consume organism of size 1 and 3, and not organism of size 2. Hence, if the observed diets are not contiguous when prey are ordered by their size, the estimation process could lead to a lower value of the TSS [@guptaSimultaneouslyEstimatingFood2022].

Furthermore, the observed data may be missing links, e.g. links that rarely occur. Some of these food webs are undersampled (SI Fig. S2) suggesting those food webs might be missing these rare trophic links, and the false positives from a model might be a correctly predicted link. A future prospect could be to incorporate other sources of presence-absence data such as stable isotope ratio [@laymanCanStableIsotope2007], DNA metabarcoding [@roslinUseDNABarcodes2016], literature review [@grayJoiningDotsAutomated2015; @cohenSoilInvertebratesChemistry2014; @goldwasserConstructionAnalysisLarge1993a] and experimentation [@warrenSpatialTemporalVariation1989] to complement any trophic links that were missed by the gut content method.

We expected a positive relationship between the minimum number of predator guts and the number of trophic links and number of species respectively. However, we did not find such relation (Fig. \ref{fig:fig_rb} (a, b)). We suspect this is due to the possibility that the food webs are sampled at different level (SI Fig. S2), with Broadstone Stream being the most sampled among all the food webs. Taking into account the undersampling factor resulted in a better fit between the corrected minimum number of predator guts and corrected number of trophic links and number of species respectively (Fig. \ref{fig:fig_rb} (c, d)), however did not result in a relationship. This could be due to heterogenity in the predator guts across food webs and heterogenity among food webs. First, if less number of prey items are present in a predator gut then more number of predator guts would need to be collected on an average to quantify the diet of that predator. Second, a food web which has a high proportion of generalist species would require a high number of predator guts on average to characterise the food web structure as compared to characterising the structure of a food web which has a high proportion of specialist species.

In our study, we have not considered uncertainty which is involved in analysing the predator guts [@bakerFishGutContent2014]. For example, there are sometimes loose tissues that are not identifiable and cannot be assigned to a specific prey item with certainty. There are factors such as sample size of consumers, mechanical prey handling, differential digestion and evacuation rates of different prey types and volumes, and the ingestion order that in combination result in an unquantifiable error which is difficult to interpret in the predator diet [@hyslopStomachContentsAnalysis1980; @rindorfBiasEstimatingFood2004; @bakerFishGutContent2014]. Therefore, the next step could be to incorporate these different factors of uncertainty in parameterising the model and to understand how these affect the accuracy of the predicted food webs.

<!-- Some kinds of interactions are not possible to infer from analysing the predator guts. For example, suctorial predation cannot be inferred from gut content analysis. -->
<!-- A future prospect would be to include other types of food web data along with gut content simultaneously to parameterise the ADBM. For example, one could use the approximate trophic position inferred from stable isotope ratio data from a tissue of an individual and predator guts of a different predator simultaneously to parameterise a food web model such as the ADBM. In this case, trophic position would be an additional summary statistic required in the parameterisation method. This combination of different types of data about trophic interactions could be particularly useful when only a limited amount of diet information can be extracted by using a single method. -->

# Acknowledgements

This work was supported by the University Research Priority Program Global Change and Biodiversity (Grant number: U-704-04-11) of the University of Zurich. We thank the Petchey group members for their valuable suggestions in the manuscript.

# Author contributions

# Reference

### 2022-06-20 inst/report/sampling_standardization/sampling_standardisation_ngut.Rmd
Incorporated most comments from Guy, Eoin and David

---
title: "sampling_standardisation_ngut"
author: "Anubhav Gupta"
date: '2022-05-09'
output: 
  html_document:
    fig_caption: true
    number_sections: true
---

We standardise sampling across food webs.

## Link accumulation curve with respect to the number of predator guts

```{r echo = FALSE, fig.align='center', out.width="600px", fig.cap="Number of trophic links plotted against the number of gut content data for seven food webs."}
knitr::include_graphics("../../../results/misc/plot_emplinks_ngut.png")
```

## Rolling average of link accumulation curve with respect to the number of predator guts

```{r echo = FALSE, fig.align='center', out.width="600px", fig.cap="Rolling average (with window of 30 items) of number of trophic links plotted against the number of predator guts for seven food webs."}
knitr::include_graphics("../../../results/misc/plot_emplinks_ngut_ra.png")
```

## Slope of link accumulation curve with respect to the number of predator guts

```{r echo = FALSE, fig.align='center', out.width="600px", fig.cap="Slope of link accumulation curve plotted against the number of predator guts for seven food webs."}
knitr::include_graphics("../../../results/misc/plot_slope_emplinks_ngut.png")
```

## Rolling average of slope of link accumulation curve with respect to the number of predator guts

```{r echo = FALSE, fig.align='center', out.width="600px", fig.cap="Rolling average (with window of 10 items) of slope of link accumulation curve plotted against the number of predator guts for seven food webs."}
knitr::include_graphics("../../../results/misc/plot_slope_emplinks_ngut_ra.png")
```

## Rolling average of slope of link accumulation curve with respect to the number of predator guts for the Broadstone Stream food web

```{r echo = FALSE, fig.align='center', out.width="600px", fig.cap="Rolling average (with window of 100 items) of slope of link accumulation curve plotted against the number of predator guts for seven food webs."}
knitr::include_graphics("../../../results/misc/plot_slope_emplinks_ngut_ra_bs.png")
```

## Factor

```{r echo = FALSE}
factor_all <- readRDS("../../../results/misc/factor_all_ngut.RDS")
print(factor_all)
```

## Corrected minimum number of gut vs number of species

```{r echo = FALSE, fig.align='center', out.width="600px", fig.cap="Corrected minimum number of gut vs number of species (S) for seven food webs."}
knitr::include_graphics("../../../results/misc/plot_corrected_mingut_vs_S_ngut.png")
```

## Corrected minimum number of gut vs number of links

```{r echo = FALSE, fig.align='center', out.width="600px", fig.cap="Corrected minimum number of gut vs number of links (L) for seven food webs."}
knitr::include_graphics("../../../results/misc/plot_corrected_mingut_vs_L_ngut.png")
```

## Corrected minimum number of gut vs connectance

```{r echo = FALSE, fig.align='center', out.width="600px", fig.cap="Corrected minimum number of gut vs connectance (C) for seven food webs."}
knitr::include_graphics("../../../results/misc/plot_corrected_mingut_vs_C_ngut.png")
```

### 2022-06-20 inst/report/sampling_standardization/sampling_standardisation_nitems.Rmd
Incorporated most comments from Guy, Eoin and David

---
title: "sampling_standardisation_nitems"
author: "Anubhav Gupta"
date: '2022-05-09'
output: 
  html_document:
    fig_caption: true
    number_sections: true
---

We standardise sampling across food webs.

## Link accumulation curve with respect to the number of predator guts

```{r echo = FALSE, fig.align='center', out.width="600px", fig.cap="Number of trophic links plotted against the number of gut content data for seven food webs."}
knitr::include_graphics("../../../results/misc/plot_emplinks_ngut.png")
```

## Link accumulation curve with respect to the number of prey items

```{r echo = FALSE, fig.align='center', out.width="600px", fig.cap="Number of trophic links plotted against the number of prey items in the predator guts for seven food webs."}
knitr::include_graphics("../../../results/misc/plot_emplinks_nitems.png")
```

## Rolling average of link accumulation curve with respect to the number of prey items

```{r echo = FALSE, fig.align='center', out.width="600px", fig.cap="Rolling average (with window of 30 items) of number of trophic links plotted against the number of prey items in the predator guts for seven food webs."}
knitr::include_graphics("../../../results/misc/plot_emplinks_nitems_ra.png")
```

## Slope of link accumulation curve with respect to the number of prey items

```{r echo = FALSE, fig.align='center', out.width="600px", fig.cap="Slope of link accumulation curve plotted against the number of prey items in the predator guts for seven food webs."}
knitr::include_graphics("../../../results/misc/plot_slope_emplinks_nitems.png")
```

## Rolling average of slope of link accumulation curve with respect to the number of prey items

```{r echo = FALSE, fig.align='center', out.width="600px", fig.cap="Rolling average (with window of 20 items) of slope of link accumulation curve plotted against the number of prey items in the predator guts for seven food webs."}
knitr::include_graphics("../../../results/misc/plot_slope_emplinks_nitems_ra.png")
```

## Rolling average of slope of link accumulation curve with respect to the number of prey items for Broadstone Stream food web

```{r echo = FALSE, fig.align='center', out.width="600px", fig.cap="Rolling average (with window of 100 items) of slope of link accumulation curve plotted against the number of prey items in the predator guts for seven food webs."}
knitr::include_graphics("../../../results/misc/plot_slope_emplinks_nitems_ra_bs.png")
```

## Factor

```{r echo = FALSE}
factor_all <- readRDS("../../../results/misc/factor_all.RDS")
print(factor_all)
```

## Corrected minimum number of gut vs number of species

```{r echo = FALSE, fig.align='center', out.width="600px", fig.cap="Corrected minimum number of gut vs number of species (S) for seven food webs."}
knitr::include_graphics("../../../results/misc/plot_corrected_mingut_vs_S.png")
```

## Corrected minimum number of gut vs number of links

```{r echo = FALSE, fig.align='center', out.width="600px", fig.cap="Corrected minimum number of gut vs number of links (L) for seven food webs."}
knitr::include_graphics("../../../results/misc/plot_corrected_mingut_vs_L.png")
```

## Corrected minimum number of gut vs connectance

```{r echo = FALSE, fig.align='center', out.width="600px", fig.cap="Corrected minimum number of gut vs connectance (L) for seven food webs."}
knitr::include_graphics("../../../results/misc/plot_corrected_mingut_vs_C.png")
```

### 2022-06-20 manuscript/SI/SI.Rmd
Incorporated most comments from Guy, Eoin and David

--- 2022-03-01 manuscript/ms_C2/ms_C2.Rmd
@@
 ---
-title: Optimal amount of gut content data required to predict trophic interactions using a food web model
-authors:
-- affiliation: University of Zurich
-  department: Department of Evolutionary Biology and Environmental Studies
-  email: anubhav.gupta@ieu.uzh.ch
-  location: 8057 Zurich, Switzerland
-  name: Anubhav Gupta
-  thanks: Corresponding author
-- affiliation: University of Essex
-  department: School of Life Sciences
-  email: e.ogorman@essex.ac.uk
-  location: CO4 3SQ Colchester, UK
-  name: Eoin O' Gorman
-- affiliation: University of Zurich
-  department: Department of Evolutionary Biology and Environmental Studies
-  email: owen.petchey@ieu.uzh.ch
-  location: 8057 Zurich, Switzerland
-  name: Owen L. Petchey
-geometry: margin=1in
-abstract: |
-
-  1)  Presence absence data of species interactions such as gut content data is used to parameterise food web models such as allometric diet  breadth model (ADBM), thereby predicting the food web structure.
-And collecting and analysing these data from the field is an expensive and time consuming task.
-Therefore, it is crucial to know how much gut content data is required to parameterise the ADBM with high accuracy and high precision for a given food web with minimum sampling effort.
-  2)  The novelty of our current approach is that we use approximate Bayesian computation to parameterise the ADBM, and true skill statistics to measure the goodness of fit for different amount of predators' gut content data.
-  3)  We estimated the minimum number of gut content data required for seven different food webs that resulted in 95% of the maximum true skill statistics achieved by the ADBM for total gut content data.
-We found that incomplete gut content data can be used to parameterise the ADBM with the lowest amount of gut content data being 28% of the total gut content data.
-  4)  These results suggest that one need not collect a large quantity of gut content data to predict a food web structure using a food web model, thereby reducing sampling effort considerably.
-
-keywords:
-  - gut content data
-  - ADBM
-  - food web accuracy
-  - food web prediction
+title: "Supplementary Information:  \nHow much gut content data is required to predict trophic interactions?"
+author:
+  - Anubhav Gupta
+  - Eoin O' Gorman
+  - other authors
+  - Owen L. Petchey
+date: "`r format(Sys.time(), '%d %B %Y')`"
 header-includes:
    - \usepackage{lineno}
-   - \linenumbers
-   - \usepackage {amsmath}
-   - \setlength\parindent{24pt}
+   #- \linenumbers
+   - \renewcommand{\thefigure}{S\arabic{figure}}
+   - \setcounter{figure}{0}
    - \usepackage{setspace}\doublespacing
-# indent: true
-mainfont: Times New Roman
-bibliography: bibliography.bib
-biblio-style: biblatex
+   - \usepackage{float}
 output:
-  # word_document:
-  #   fig_caption: yes
-  #   number_sections: yes
-  rticles::arxiv_article:
-    keep_tex: true
+  pdf_document: 
+    number_sections: yes
+    latex_engine: pdflatex
+bibliography: bibliography_SI.bib
 ---
-
-\*\*AG: My comment starts with "**AG:"
-
-# Alternate titles
-
--   Predicting trophic interactions using incomplete gut content data
-
--   Effect of the amount of gut content data on the accuracy and precision of food web prediction
-
-# Introduction
-
-Knowledge about the trophic interactions in a food web is crucial in ecology for purposes ranging from identifying keystone species [@jordanKeystoneSpeciesFood2009] to quantifying robustness of a food web to species extinctions [@dunneNetworkStructureBiodiversity2002].
-This has led to the development of numerous food web models [@allesinaGeneralModelFood2008; @cohenStochasticTheoryCommunity1985; @gravelInferringFoodWeb2013; @petcheySizeForagingFood2008; @tamaddoni-nezhadConstructionValidationFood2013].
-Along with inferring missing links in an observed food web, the food web models are also used for ecological forecasting [@hattabForecastingFinescaleChanges2016; @lindegrenEcologicalForecastingClimate2010] and for understanding the underlying mechanism governing the interactions in a food web [@ogormanSimpleModelPredicts2019].
-
-Although food web models are constructed using prior theory about the factors that determine trophic interactions, empirical data about interactions is required to parameterise a model.
-For example, @petcheySizeForagingFood2008 used presence-absence information about trophic interactions to parameterise the allometric diet breadth model and thereby predict species interactions.
-These empirical information about interactions can be inferred from diverse set of methods such as gut content analysis [@peralta-maraverStructureDynamicsStability2017], stable isotope ratio analysis of tissues [@laymanCanStableIsotope2007], experimentation [@warrenSpatialTemporalVariation1989], DNA metabarcoding [@roslinUseDNABarcodes2016] and literature research [@grayJoiningDotsAutomated2015; @cohenSoilInvertebratesChemistry2014; @goldwasserConstructionAnalysisLarge1993a].
-
-<!-- **OP: The following three sentences may not be necessary here, or could perhaps go elsewhere.** All of these methods can provide information useful to infer the diet of a consumer, however different methods can result in different levels of uncertainty in the inferred diet (citreqd).
-A single gut content of a predator describes what that individual has consumed recently which can be used to infer the diet of the predator [@eitzingerTestingValidityFunctional2018; @omalleyEffectsFoodWeb2017; @dixonAssessingDietNorth2017; @mcclain-countsTrophicStructureMesopelagic2017b; @peralta-maraverStructureDynamicsStability2017].
-Stable isotope data when combined with mixing models can be used to determine which prey items are most likely fed upon by a predator [@kadoyaIsoWebBayesianIsotope2012; @crawfordApplicationsStableIsotope2008].
--->
-
-Food web methods mentioned above have multiple shortcomings.
-Stable isotope ratio analysis of the organism's tissue does not give a direct information of the diet of that organism but rather approximate trophic position of that species in the food web.
-Although mixing models can be used to determine what prey items are most likely fed upon by a predator but this results in uncertainty in the estimates [@kadoyaIsoWebBayesianIsotope2012; @crawfordApplicationsStableIsotope2008].
-Experimentation (e.g.
-feeding trials) may create unrealistic conditions where a predator is confined in a small space with a potential "prey" and is effectively "forced" into eating it (citreqd).
-DNA metabarcoding could have many issues such as failure to relate OTUs to species, or inability to distinguish secondary predation, i.e.
-the DNA signature of the prey consumed by the prey consumed by the primary item found in the predator's gut.
-Another approach to infer missing links is literature research which involves assuming that a link will occur because another author described it in some other system, or for related predator/prey species, e.g.
-from the same genus or family [@grayJoiningDotsAutomated2015; @cohen2014; @goldwasser1993].
-This typically results in a food web that will be very oversampled with false positives in the presence of links (citreqd).
-@nielsen2018 have shown that gut content analysis method has a better match with real diet when compared to other methods.
-\*\*AG: Working on this paragraph.
-
-Acquiring food web data from gut content analysis is time consuming and expensive (reference).
-In part this is due to the need for many gut contents to be collected and analysed in order to be confident that the majority of possible trophic links have been observed.
-Furthermore, considerable time, resource investment, and expertise is required to process the collected samples.
-Hence, there is of considerable importance to know the minimum number of gut contents and of which consumer species that are required to parameterise a food web model with high accuracy and high precision, so that one knows when is a good time to stop collecting any further empirical data on the food web.
-
-Therefore, the key question we are interested in answering is how much presence-absence information, in the form of gut content data, is required to infer food web structure from a food web model specifically the ADBM with high accuracy and high precision.
-In other words, how many samples of gut content should one collect from the field to parameterise a food web model?
-To answer this question, we use the presence-absence information from gut content data to parameterise the allometric diet breadth model (ADBM) thereby predicting trophic interactions in seven different food webs using rejection approximate Bayesian computation, where the fitness of the model was measured using true skill statistics.
-We computed the true skill statistics of the predicted food webs for different number of predator guts to calculate the minimum number of gut content data to infer food web structure.
-Our study provides a guideline on how many gut content data is required to predict food web structure using a food web model.
-
-```{r echo = FALSE, warning = FALSE}
-# options(knitr.kable.NA = '')
-# library(readxl)
-# library(knitr)
-# library(kableExtra)
-# fw_table <- read_excel("../table/data_summary_fil.xlsx")
-# 
-# kable(fw_table, format = "latex",
-#       caption = "\\label{fig:tab_1}Studies showing the type of data used to infer trophic interactions in a food web",
-#       escape = FALSE) %>%
-#     kable_styling(latex_options="scale_down")
-
-```
-
-# Materials and Methods
-
-In the upcoming sections, we present the food webs, the allometric diet breadth model (ADBM) and the gut content data used to infer the trophic interactions in the presented food webs using the ADBM.
-We also give a detailed account of using partial gut content data to parameterise the ADBM using rejection approximate Bayesian computation (ABC).
-We assessed model predictions using the true skill statistic and various structural food web properties for comparison across food webs.
-
-## The Empirical Food Webs
-
-In our study, we used food webs for which gut content data is available at an individual level and, is FAIR.
-Presence and absence interactions of food web data can be aggregated in different ways [@gilljamSeeingDouble2011].
-A common way of aggregating food web data is the taxonomic approach, in which nodes in the food web are taxa (e.g.
-species) and one species is said to feed on another species if at least one individual of the latter is found in at least one gut of the former.
-Another approach is based on size, rather than taxonomy, and in this the nodes in the food web are size classes.
-Here, a feeding link occurs between two size classes if at least one prey item within a size class was found in the gut of another size class, irrespective of their taxonomy.
-
-In our study, we aggregate the gut content data on the basis of size class because the food webs constructed using this approach were better predicted by the ADBM compared to the taxonomic approach [@woodward2010], and this is because the ADBM is based on foraging rules defined using the body sizes of organisms [@petcheySizeForagingFood2008].
-
-Our study is based on the assumption that the food web constructed using the complete gut content data is the true food web.
-However, this might not be the case because the links are still under-sampled for many nodes [@woodwardIndividualBasedFoodWebs2010].
-This could result in a lower TSS of the predicted food web from the ADBM which can result in a biased estimate of the number of gut content data.
-
-```{r echo=FALSE, warning=FALSE}
-library(readxl)
-library(knitr)
-library(kableExtra)
-fw_table <- read_excel("../table/fw_table.xlsx")
-kable(fw_table, format = "latex",
-      caption = "\\label{fig:tab_1}Information about the empirical food webs. **AG: Working on this.", escape = FALSE, align = "l") %>%
-  kable_styling(font_size = 7, latex_options="scale_down", row_label_position = 1) %>%
-  landscape(margin = "1cm") %>%
-  column_spec(1, width = "3cm") %>%
-  column_spec(2, width = "8em") %>%
-  column_spec(7, width = "8em") %>%
-  column_spec(8, width = "8em") %>%
-  column_spec(9, width = "8em")
-
-```
-
-<!-- ### Broadstone Stream -->
-
-<!-- Broadstone Stream (51$^\circ$ 05' N 0$^\circ$ 03' E; 120 m above sea-level) is a second-order tributary of the River Medway in south-east England.
-It is dominated by invertebrates as the acidity of the stream (pH 4.7-6.6) excludes fish.
-The stream consists of 25 common invertebrate species [@woodwardQuantificationResolutionComplex2005].
-Among the predators, the three large species are *Cordulegaster boltonii* Donovan, *Sialis fuliginosa* Pict.
-and *Plectrocnemia conspersa* [Curtis] and the three small species are the larvae of the tanypod midges *Macropelopia nebulosa* [Meigen], *Trissopelopia longimana* [Staeger], and *Zavrelimyia barbatipes* [Kieffer].
-Broadstone Stream food web is one of the most completely described food webs available for any system [@schmid-arayaImportanceMeiofaunaFood2002; @hildrewChapterSustainedResearch2009; @layerFoodWebStructure2010; and @woodwardQuantificationResolutionComplex2005a].
--->
-
-<!-- ### Celtic Sea -->
-
-<!-- The Celtic Sea is an area of continental shelf bordered by Ireland, the UK and the Bay of Biscay.
-Precise sampling locations and dates were not given in the Barnes et al.
-(2008) dataset, from where the data used in this chapter were extracted, so we pooled data over the whole time period and locations to capture general patterns.
-Only locations consistently sampled through the 1987--2001 time series were used (Blanchard et al., 2005).
-The feeding links of fishes in the Celtic Sea have been described in a published global dataset of individual predator and prey body sizes and taxonomy (Barnes et al., 2008): in total, 1988 feeding events from 29 predator species were included in the food web presented here.
-The original stomach contents data were collected from dissections carried out on board research vessels during the annual surveys carried out by the Centre for Environment, Fisheries and Aquaculture Science (Cefas) (Pinnegar et al., 2003).
-Predator and prey length were recorded and converted to body mass by Barnes et al.
-(2008) using published regression equations.
-Only vertebrate prey were identified and measured, with the vast majority being identified to species.
--->
-
-<!-- ### Afon Hirnant -->
-
-<!-- The Afon Hirnant is a tributary of the Welsh Dee in North Wales, U.K.
-(52$^\circ$ 52'N 03$^\circ$ 34) with the study being conducted at three sites.
-The pH within each site ranged from about 5.5 to 7 over the course of the year.
-A total of 180 invertebrate samples were collected for the whole sampling periods.
-All individuals within the benthic samples were counted and identified to the lowest possible taxonomic level (usually species).
-Prey items were identified using a combination of taxonomic keys and reference slides of previously identified species, after @schmid-arayaConnectanceStreamFood2002; @schmid-arayaImportanceMeiofaunaFood2002.
--->
-
-<!-- ### Tadnoll Brook -->
-
-<!-- Description of Tadnoll Brook here -->
-
-<!-- ### Coilaco -->
-
-<!-- Description of Coilaco here -->
-
-<!-- ### Guampoe -->
-
-<!-- Description of Guampoe here -->
-
-<!-- ### Trancura -->
-
-<!-- Description of Trancura here -->
-
-## Allometric Diet Breadth Model (ADBM)
-
-The allometric diet breadth model (ADBM) is based on optimal foraging theory, specifically the contingency foraging model [@macarthurOptimalUsePatchy1966].
-We chose this model because it uses the body size of organisms as input to predict feeding interactions.
-The ADBM predicts the set of prey species a consumer should feed upon to maximise its rate of energy intake [@petcheySizeForagingFood2008].
-The foraging variables in the model are: energy content of the resources, handling times of the prey, space clearance rate and prey densities are allometrically scaled to the body sizes of the species.
-Further details on the foraging rules defined in the ADBM and ADBM's predictive power across different food webs can be found in @petcheySizeForagingFood2008.
-
-## Assessment of prediction
-
-The accuracy of the predicted diet of the predators was defined using true skill statistic (TSS) which takes into account the true and false predictions of both the presence and absence of links defined as:
-
-$$ \text{TSS} = \frac{ad-bc}{(a+c)(b+d)} $$ where $a$ is the number of observed links that are predicted by the model (true positives), $d$ is the number of observed absences of links that are correctly predicted (true negatives), $b$ is the number of false positives, and $c$ is the number of false negatives.
-
-The $TSS$ ranges from $-1$ to $1$, where +1 indicates a perfect prediction. A $TSS$ value of zero or less indicates a performance no better than random [@alloucheAssessingAccuracySpecies2006].
-
-## Inferring food web using partial gut content data
-
-From an empirical dataset of gut content data, we draw a set of gut contents data randomly to create a partial gut content dataset. We then fit the ADBM to this partial dataset.
-
-To fit the ADBM to a gut content dataset (be it complete or partial), we used the rejection ABC method we previously developed in @gupta2021 to accept a parameter value from a prior distribution which would have resulted in the minimum distance, where distance = 1 - True skill statistic.
-The true skill statistic was computed between the predators' diet predicted from the ADBM, and that from the sampled gut content data.
-We repeated this process for $n~(= 100)$ number of times for every $i$ number of guts, where $i$ lies between 1 and total number of gut content data in the pool.
-
-*Input:*
-
--   Predators $P: P = \{p_1, p_2, \dots, p_k \}$
-
--   A pool of gut content data $G: G = \{g_1, g_2, \dots, g_n\}$, where $g_{n}$ is a one-dimensional matrix containing ones and zeros.
-
--   A model prediction $model(\theta): ADBM(\theta) = \{d_{p_1}, d_{p_1}, \dots, d_{p_k}\}$, where $d_{p_k}$ is a one-dimensional diet matrix of predator $k$ containing ones and zeros.
-
--   A summary statistic $s(x): s(x) \subseteq model(\theta)$
-
--   A distance function $d(x_i, y) : d(x_i,y) = 1 - TSS(x_i, y)$
-
--   An observed food web $Y: Y = \{d_{p_1}', d_{p_1}', \dots, d_{p_k}'\}$
-
-*Sampling:*
-
-for $i = 1, \dots, tgut$ where $tgut$ is the total number of gut content data in the pool $G$
-
--   for $j = 1, \dots, nsample$ where $nsample$ is the number of independent samples to be drawn
-
-    -   Draw a set of gut content data $y = \{g_1, g_2, \dots, g_i\}$ from the pool of gut content data $G$
-
-    -   for $k = 1, \dots, npar$ where $npar$ is the number of parameter values to be sampled
-
-        -   Draw a set of parameter values $\theta_k$ from the prior distribution $\pi(\theta)$
-
-        -   Compute the model result $x_i = model(\theta_k)$
-
-        -   Compute $s(x_i)$ and $d(s(x_i), y)$
-
-    -   Accept $\theta_j$, which results in the $min_i\{d(s(x_i), y)\}$
-
--   Compute $TSS_{i}(x, y) = \{TSS(x_i,y): x_i = ADBM(\theta_j), \theta_j \text{ computed from previous step}\}$ using the accepted $\theta_1, \dots, \theta_{nsample}$
-
-*Output:*
-
-The $TSS$ between observed and predicted food webs for every $i$ number of gut content data drawn from the pool of gut content data.
-
-# Results
-
-We first present how the accuracy of the food web model i.e ADBM vary in predicting trophic interactions with increasing amount of gut content data provided to the food web model.
-Then, we calculate the number of gut content data for each food webs that results in accuracy equal to 95% of the maximum true skill statistics predicted by the food web model.
-We also compute the goodness of the food web model in predicting structural properties from incomplete gut content data.
-We did that by computing mean standardised error in food web properties.
-
-## Inferring trophic interactions using ADBM and incomplete gut content data
-
-```{r, echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_ra} (a, c, e, g, i, k, m) Accuracy of the predicted food web measured using the true skill statistics, predicted by the ADBM parameterised using gut content data.
-Line and shaded grey region represents the mean and the prediction interval of 100 independent samples respectively.
-Red line represents the number of predator guts required to achieve a TSS of 95\\% of the maximum TSS.
-(b, d, f, h, j, l, n) Ratio of the true skill statistic of the predicted food web by the ADBM parameterised using gut content data to that of the predicted food web constructed using gut content data only.
-The dashed line shows where the ratio is one for reference."}
-knitr::include_graphics("../../results/misc/plot_TSS_ratio.png")
-```
-
-The true skill statistics of the food webs predicted by the ADBM using subsets of gut content data improved quickly for lower number of predator guts (Fig.
-\ref{fig:fig_ra}) (a, c, e, g, i, k, m).
-The prediction interval of the true skill statistics decreased with increasing number of predator guts with the mean TSS asymptoting to the maximum mean TSS achieved by the ADBM when all the gut content data was used.
-Although the maximum TSS varied among the food webs, the qualitative increase in the TSS was the same.
-
-For Broadstone Stream food web, with only 381 number of gut content data which is 38% of the total gut content data, the ADBM predicted the food web with the TSS of 0.74 which was 95% of the mean TSS (0.78) achieved using complete gut content data by the ADBM (Fig.
-\ref{fig:fig_ra}(a)).
-In case of the Celtic Sea food web, only 171 gut content data which is 35% of the total gut content data was required by the ADBM to predict food web with TSS equal to 95% of the mean TSS (0.68) achieved using complete gut content data by the ADBM (Fig.
-\ref{fig:fig_ra}(c)).
-
-## TSS(Model)/TSS(Data) for different food webs
-
-For a low number of predator guts, the TSS of the model predicted food web was higher than the TSS of the food web constructed from gut content data only (Fig.
-\ref{fig:fig_ra} (b, d, f, h, j, l, n)).
-After a certain increase in the number of predator guts, the ratio TSS(Model)/TSS(data) reduced to less than one, and reduced further gradually.
-
-## Mean standardised error in structural properties with respect to the number of gut content data
-
-Mean standardised error in structural properties of afon hirnant, broadstone stream, celtic sea and tadnoll brook food web reduced drastically with increasing number of predator gut content data at low number of predator gut content data (Fig.
-\ref{fig:fig_rab}).
-In case of Broadstone Stream food web, the 95% prediction interval reduced as well with increasing number of predator gut content data.
-
-\*\*AG: Working on this paragraph.
-
-```{r, echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_rab} Mean standardised error in structural properties of different food webs with respect to the number of gut content data."}
-knitr::include_graphics("../../results/misc/plot_mse_ngut_all.png")
-```
-
-## Dependence of minimum gut content data on number of species, links and connectance
-
-There was a positive trend between number of minimum gut content data and number of species (S) (Fig.
-\ref{fig:fig_rb} (a)), links (L) (Fig.
-\ref{fig:fig_rb} (c)), connectance (C) (Fig.
-\ref{fig:fig_rb} (d)) and number of predator nodes (Fig.
-\ref{fig:fig_rb} (e)), with Broadstone Stream being an outlier in Fig.
-\ref{fig:fig_rb} (a, c, e).
-The number of minimum gut content data increases with number of maximum gut content data sampled (Fig.
-\ref{fig:fig_rb} (b)).
-There seems to be a negative relationship between proportion of minimum gut (= Number of minimum gut / Number of maximum guts sampled) and number of species (S) (Fig.
-\ref{fig:fig_rb} (f)), links (L) (Fig.
-\ref{fig:fig_rb} (g)), connectance (C) (Fig.
-\ref{fig:fig_rb} (h)).
-
-```{r echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_rb} (a, b, c, d, e) Number of minimum gut content data plotted against number of species (S), number of maximum guts sampled, number of links (L), connectance (C) and number of predator nodes respectively.
-(f, g, h) Proportion of minimum gut content data plotted against number of species (S), number of links (L) and connectance (C) respectively."}
-knitr::include_graphics("../../results/misc/plot_min_gut_vs_X.png")
-```
-
-```{r echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_rc} Link accumulation curve of the food web constructed using gut content data plotted against number of gut content data."}
-knitr::include_graphics("../../results/misc/plot_emplinks_ngut.png")
-```
-
-# Discussion
-
-We have demonstrated how a food web model can be used to predict food web in the availability of incomplete data.
-At lower amount of gut content data, ADBM is quite better at predicting trophic interactions.
-We have computed the upper limit of amount of gut content data till when it can be used to compensate for undersampling.
-This can help us decide how much gut content data to actually collect when we are using a food web model to infer trophic interactions.
-A future development could be to use this our approach on other food web models, and to also use food web data other than gut content data to parameterise those models.
-
-## Why incomplete gut content data can be used to infer trophic interactions?
-
-In all of the seven food webs, the ADBM was able to infer the trophic interactions using incomplete gut content data because the presence absence information from the gut content data was used to narrow down the possible model parameter values of the ADBM that best explained the predators' diets.
-Although in theory the ADBM can predict trophic interactions using only body sizes of organisms as it is based on set of foraging rule, it still requires some presence absence data to constrain the posterior parameter space thereby making more accurate predictions.
-
-## Why does the minimum gut data differ among food webs?
-
-We found the minimum number of gut content data to vary across food webs and this could be due to the possibility that the food webs are sampled differently i.e.
-some food webs are well sampled than others (Fig.
-\ref{fig:fig_rc}).
-Since some food webs are more size-structured than others, they are well predicted by the ADBM and therefore might require a lower number of gut content data for model parameterisation.
-\*\*:AG: I would need to add information about the interactions in these food webs.
-
-## Model fills up missing interactions and guide sampling direction
-
-When only few presence absence data is available, model can be used to fill up the missing interactions that has not been observed in the gut content data.
-Also model's predictions can be used as a guide to sample predator guts that might be significant in the food web.
-
-## Why is model's TSS less than one?
-
-Due to limitations of the ADBM as to not able to completely explain the interactions in a food webs using the foraging rules based on the body size and also possible undersampling in the observed data because of missing rare links, the ADBM's maximum predicted true skill statistics is always less than one.
-
-The maximum predictive power of a model is constrained by the rules it is based on.
-In the case of ADBM, that limits the predictive power of the ADBM is that it can only predict diets that are contiguous with respect to the size of prey.
-I.e.
-it cannot predict that a predator with consume prey of size 1 and 3, and not prey of size 2.
-Also, it is important to note that if the observed diets are not contiguous when prey are ordered by their size, the estimation process could lead to a lower value of the TSS.
-
-## TSS(Model)/TSS(Data) for different food webs
-
-\*\*AG: Working on this.
-
-## Why Broadstone Stream is an outlier?
-
-Broadstone Stream is the most sampled food web compared to all the other food webs (Fig.
-\ref{fig:fig_rc}), which means the observed Broadstone Stream food web might be more accurate compared to others.
-
-\*\*AG: Working on this, not sure if this paragraph is needed.
-
-## Propagating uncertainty from gut content data to model's predictions
-
-\*\*OP Focus on this, at least in the context of further work that could be done. ## There is uncertainty in gut content data and needs to be propagated into model's predictions
-
-There is considerable uncertainty involved in gut content analysis [@bakerFishGutContent2014] such as in fish's guts, there are sometimes loose tissues that are not identifiable and cannot be assigned to a specific prey item with certainty.
-There are factors such as sample size of consumers, mechanical prey handling, differential digestion and evacuation rates of different prey types and volumes, and the ingestion order that in combination result in an unquantifiable error which is difficult to interpret in the predator diet [@hyslopStomachContentsAnalysis1980; @rindorfBiasEstimatingFood2004; @bakerFishGutContent2014].
-Therefore, a future development would be to consider how this uncertainty is propagated into food web prediction.
-
-## Comparing our study with other studies of predicting food webs using incomplete data
-
-\*\*OP: Focus on this, and other studies that have looked at the importance of quantity and quality of food web data ## Comparing our study with other studies of predicting food webs using incomplete data
-
-Some studies have presented how the accuracy of food web prediction change when we vary the amount of food web data [@grayJoiningDotsAutomated2015]. 
-\*\*AG: Working on this paragraph.
-
-## What is the generalisability of our results?
-
-\*\*OP: Focus on this.
-
-In our study, we have implemented the approach to only the ADBM.
-However, in principle, this approach could be extended to other food web models.
-A future prospect could be to study how good different food web models' prediction accuracy vary for different amount of gut content data.
-This can also help in making decision as to which food web model to chose from given set of gut content data.
-
-A future study could be to use our approach of estimating the minimum gut content data for different food web models.
-An efficient model would be the one that uses minimum available gut content data to predict species interactions with high accuracy and high precision.
-
-## Assumption that the food web constructed with the total gut content data is the true food web and how can this be improved
-
-Some of the food webs are not very well predicted using the ADBM.
-And with the assumption that the food web constructed from the complete gut content data is the true food web might result in not so accurate estimates of the minimum gut content data.
-As it might be the case that the links are still under-sampled for many nodes [@woodwardIndividualBasedFoodWebs2010].
-
-## How can we include other types of food web data?
-
-\*\*OP: Focus on this ## How can we include other food web data type?
-
-A future prospect would be to include other types of food web data along with gut content simultaneously to parameterise the ADBM.
-For example, one could use the approximate trophic position inferred from stable isotope ratio data from a tissue of an individual and gut content data of a different predator simultaneously to parameterise the ADBM.
-In this case, trophic position would be an additional summary statistics required in the parameterisation method.
-This is useful when only limited amount of diet information can be extracted by using a single method.
-
-# Conclusion
-
-\*\*AG: Working on this.
 
@@
 
-\*\*OP: It needs to be very clear in the main text, and here, why this is being described. It is currently unclear, not least because the main text does not, I think, refer to the information here.
+<!-- \*\*OP: It needs to be very clear in the main text, and here, why this is being described.
+It is currently unclear, not least because the main text does not, I think, refer to the information here.
+[OP: I'm not sure my comment has been addressed.
+We should discuss this.] [OP: I don't see this Supplement being referred to anywhere in the main text.
+I would expect it to be.] [OP: I advise to integrate the content of this supplement into the main article.
+There is not so much of it, and it is insightful.] -->
 
@@
 
-```{r fig_r3, echo=FALSE, fig.align='center', out.width="300px", fig.cap="\\label{fig:fig_r3} True skill statistics between predicted food web and observed food web estimated for different number of distinct predator guts.
-The estimation is done for three sets of gut data: gut content data of predators whose body sizes are smaller than the mean body size, larger than the mean body size, and all the gut content data."}
-knitr::include_graphics("../fig/TSS_with_n_pred_prop.png")
-```
+<!-- ```{r fig_r3, echo=FALSE, fig.align='center', out.width="300px", fig.cap="\\label{fig:fig_r3} True skill statistics between predicted food web and observed food web estimated for different number of distinct predator guts.
+The estimation is done for three sets of gut data: gut content data of predators whose body sizes are smaller than the mean body size, larger than the mean body size, and all the gut content data."} -->
+<!-- knitr::include_graphics("../fig/TSS_with_n_pred_prop.png") -->
+<!-- ``` -->
 
-```{r fig_r31, echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_r31} True skill statistic between predicted food web using ADBM and incomplete gut content data, and observed food web against the true skill statistic between food web constructed using incomplete gut content data, and observed food web.
+<!-- ```{r fig_r31, echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_r31} True skill statistic between predicted food web using ADBM and incomplete gut content data, and observed food web against the true skill statistic between food web constructed using incomplete gut content data, and observed food web.
 Error bars represent prediction intervals of 100 independent samples.
-Dashed line is 1:1 line for reference."}
-knitr::include_graphics("../../results/misc/TSS_model_vs_data.png")
-```
+Dashed line is 1:1 line for reference."} -->
+<!-- knitr::include_graphics("../../results/misc/TSS_model_vs_data.png") -->
+<!-- ``` -->
 
-```{r fig_r32, echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_r32} Mean standardised error in structural properties in the food web predicted using ADBM and incomplete gut content data against structural properties in the predicted food web constructed using incomplete gut content data.
+<!-- ```{r fig_r32, echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_r32} Mean standardised error in structural properties in the food web predicted using ADBM and incomplete gut content data against structural properties in the predicted food web constructed using incomplete gut content data.
 Error bars represent prediction intervals of 100 independent samples.
-Dashed line is 1:1 line for reference."}
-knitr::include_graphics("../../results/misc/mse_model_vs_data.png")
+Dashed line is 1:1 line for reference."} -->
+<!-- knitr::include_graphics("../../results/misc/mse_model_vs_data.png") -->
+<!-- ``` -->
+
+```{r echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_rc} Link accumulation curve of the food web constructed using gut content data plotted against number of gut content data."}
+knitr::include_graphics("../../results/misc/plot_emplinks_ngut.png")
 ```
@@
 
-# Acknowledgements
-
-# Author contributions
-
-# References
+<!-- # References -->
 

### 2022-06-20 manuscript/ms_C2/ms_C2.Rmd
Incorporated most comments from Guy, Eoin and David

--- 2022-02-28 manuscript/ms_C2/ms_C2.Rmd
@@
   name: Eoin O' Gorman
+- affiliation: XXX XXX
+  department: XXX XXX
+  email: XXX XXX
+  location: XXX XXX
+  name: Other authors
 - affiliation: University of Zurich
@@
 
-  1)  Presence absence data of species interactions such as gut content data is used to parameterise food web models such as the allometric diet  breadth model (ADBM), thereby predicting interactions.
-Collecting and analysing these data from the field is, however, an expensive and time consuming task.
+  1)  One of the biggest obstacles in food web ecology is the time and effort required to adequately describe the structure of a food web using gut content data.
+Food web models such as the ADBM can be used to circumvent this problem by predicting the interactions based on easily measured characteristics, such as the size of organisms.
+However, presence-absence data such as gut content data is required to parameterise these food web models.
+And collecting and analysing these data from the field is an expensive and time consuming task.
 Therefore, it is crucial to know how much gut content data is required to parameterise food web models with high accuracy and high precision.
-  2)  We apply to this problem a recently developed approach, namely Bayesian computation to parameterise the ADBM, and true skill statistics to measure the goodness of fit, and do so while varying the amount of gut content data is used in the parameterisation.
-  3)  We estimated the minimum number of gut content data required for seven different food webs that resulted in 95% of the maximum true skill statistics achieved by the ADBM when all available gut content data was used.
+  2)  Here, we explore seven food webs in the literature and determine how much gut content data would be needed to accurately predict their structure using the ADBM.
+We use Bayesian computation to parameterise the ADBM, and true skill statistics to measure the goodness of fit, and do so while varying the amount of gut content data used in the parameterisation.
+  3)  We estimated the minimum amount of gut content data required for seven different food webs that resulted in 95% of the maximum true skill statistics achieved by the ADBM when all available gut content data was used.
 We found that incomplete gut content data can be used to parameterise the ADBM with the lowest amount of gut content data being 28% of the available gut content data.
-  4)  These results suggest that one need not collect such a large quantity of gut content data to predict a food web structure using a food web model, thereby reducing sampling effort considerably, while having little effect on precision or accuracy of predictions.
+  4)  These results suggest that one need not collect such a large quantity of gut content data to predict the structure of a food web, thereby reducing sampling effort considerably, while having little effect on precision or accuracy of predictions.
 
@@
    - \usepackage{lineno}
-   - \linenumbers
+#   - \linenumbers
    - \usepackage {amsmath}
@@
 ---
-
-\*\*AG: My comment starts with "**AG:"
-
-# Alternate titles
-
--   Predicting trophic interactions using incomplete gut content data
-
--   Effect of the amount of gut content data on the accuracy and precision of food web prediction
 
@@
 Each of these sources of information about trophic interactions has shortcomings.
-Stable isotope ratio analysis of the organism's tissue does gives indirect information of the diet of that organism via revealing approximate trophic position of that species in the food web.
+For example: Stable isotope ratio analysis of the organism's tissue does not give direct information of the diet of that organism but rather gives approximate trophic position of that species in the food web [@wadaUseStableIsotopes1991; @jenningsTrophicLevelsMarine2015].
 Although mixing models can be used to determine what prey items are most likely fed upon by a predator, this results in uncertainty in the estimates [@kadoyaIsoWebBayesianIsotope2012; @crawfordApplicationsStableIsotope2008].
-Experimentation (e.g.
-feeding trials) may create unrealistic conditions where a predator is confined in a small space with a potential "prey" and is effectively "forced" into eating it (citreqd).
-DNA metabarcoding could have many issues such as failure to relate OTUs to species, or inability to distinguish secondary predation, i.e.
-the DNA signature of the prey consumed by the prey consumed by the primary item found in the predator gut.
-Another approach to infer missing links is literature research which involves assuming that a link will occur because another author described it in some other system, or for related predator/prey species, e.g.
-from the same genus or family [@grayJoiningDotsAutomated2015; @cohen2014; @goldwasser1993].
-This typically results in a food web that has false positives--links included when in reality no link would occur (citreqd).
+Similarly, DNA metabarcoding could have issues in detecting secondary predation or cannibalism [@pompanonWhoEatingWhat2012; @nielsen2018] and is prone to environmental contamination (e.g.
+DNA in the water swallowed along with DNA from an aquatic consumer's prey cannot be differentiated from actual prey) [@kellyUsingEnvironmentalDNA2014].
+Furthermore, construction of food webs via literature review can lead to false positives--links included when in reality no link would occur because it makes an assumption that the species interactions inferred from a system will occur in another system as well[@grayJoiningDotsAutomated2015; @cohen2014; @goldwasser1993].
+
  @nielsen2018 have shown that gut content analysis method has a better match with real diet when compared to other methods.
-\*\*AG: Working on this paragraph.
 
-Acquiring food web data from gut content analysis is time consuming and expensive (reference).
+Acquiring food web data from gut content analysis is time consuming and expensive (AG: Do we need a reference?
+Next sentence explains the reason.).
 In part this is due to the perception that many gut contents must be collected and analysed in order to be confident that the majority of possible trophic links among species have been observed.
@@
 
-```{r echo = FALSE, warning = FALSE}
-# options(knitr.kable.NA = '')
-# library(readxl)
-# library(knitr)
-# library(kableExtra)
-# fw_table <- read_excel("../table/data_summary_fil.xlsx")
-# 
-# kable(fw_table, format = "latex",
-#       caption = "\\label{fig:tab_1}Studies showing the type of data used to infer trophic interactions in a food web",
-#       escape = FALSE) %>%
-#     kable_styling(latex_options="scale_down")
-
-```
-
 # Materials and Methods
@@
 We also give a detailed account of using partial gut content data to parameterise the ADBM using rejection approximate Bayesian computation (ABC).
-We assessed model predictions using the true skill statistic and various structural food web properties for comparison across food webs.
+We assessed model predictions using the true skill statistic for comparison across food webs.
 
@@
 
-In our study, we used food webs for which gut content data is available at an individual level and data that is or that we could make FAIR [OP: cite this https://www.go-fair.org/fair-principles/].
+In our study, we used food webs for which gut content data is available at an individual level and data that is or that we could make FAIR [@wilkinsonFAIRGuidingPrinciples2016].
 Presence and absence interactions of food web data can be aggregated in different ways [@gilljamSeeingDouble2011].
@@
 However, this might not be the case because the links are still under-sampled for many nodes [@woodwardIndividualBasedFoodWebs2010].
-This could result in a lower true skill statistic (TSS) of the predicted food web from the ADBM, which can result in a biased estimate of the number of gut content data [OP: this is unclear].
+This could result in a lower true skill statistic (TSS) of the predicted food web from the ADBM, which can result in a biased estimate of the minimum number of gut content data required to achieve 95% of the TSS achieved using complete gut content data.
 
-```{r echo=FALSE, warning=FALSE}
-library(readxl)
-library(knitr)
-library(kableExtra)
-fw_table <- read_excel("../table/fw_table.xlsx")
-kable(fw_table, format = "latex",
-      caption = "\\label{fig:tab_1}Information about the empirical food webs. **AG: Working on this.", escape = FALSE, align = "l") %>%
-  kable_styling(font_size = 7, latex_options="scale_down", row_label_position = 1) %>%
-  landscape(margin = "1cm") %>%
-  column_spec(1, width = "3cm") %>%
-  column_spec(2, width = "8em") %>%
-  column_spec(7, width = "8em") %>%
-  column_spec(8, width = "8em") %>%
-  column_spec(9, width = "8em")
+In the following sections 2.1.1-2.1.5, we briefly explain seven empirical food webs used in our study. The text used in those sections are paraphrased from @gilljamSeeingDouble2011.
 
-```
+<!-- ```{r echo=FALSE, warning=FALSE} -->
 
-<!-- ### Broadstone Stream -->
+<!-- library(readxl) -->
 
-[OP: I like these sections and suggest to include them for other food webs also.]
+<!-- library(knitr) -->
 
-<!-- Broadstone Stream (51$^\circ$ 05' N 0$^\circ$ 03' E; 120 m above sea-level) is a second-order tributary of the River Medway in south-east England.
-It is dominated by invertebrates as the acidity of the stream (pH 4.7-6.6) excludes fish.
-The stream consists of 25 common invertebrate species [@woodwardQuantificationResolutionComplex2005].
-Among the predators, the three large species are *Cordulegaster boltonii* Donovan, *Sialis fuliginosa* Pict.
-and *Plectrocnemia conspersa* [Curtis] and the three small species are the larvae of the tanypod midges *Macropelopia nebulosa* [Meigen], *Trissopelopia longimana* [Staeger], and *Zavrelimyia barbatipes* [Kieffer].
-Broadstone Stream food web is one of the most completely described food webs available for any system [@schmid-arayaImportanceMeiofaunaFood2002; @hildrewChapterSustainedResearch2009; @layerFoodWebStructure2010; and @woodwardQuantificationResolutionComplex2005a].
--->
+<!-- library(kableExtra) -->
 
-<!-- ### Celtic Sea -->
+<!-- fw_table <- read_excel("../table/fw_table.xlsx") -->
 
-<!-- The Celtic Sea is an area of continental shelf bordered by Ireland, the UK and the Bay of Biscay.
-Precise sampling locations and dates were not given in the Barnes et al.
-(2008) dataset, from where the data used in this chapter were extracted, so we pooled data over the whole time period and locations to capture general patterns.
-Only locations consistently sampled through the 1987--2001 time series were used (Blanchard et al., 2005).
-The feeding links of fishes in the Celtic Sea have been described in a published global dataset of individual predator and prey body sizes and taxonomy (Barnes et al., 2008): in total, 1988 feeding events from 29 predator species were included in the food web presented here.
-The original stomach contents data were collected from dissections carried out on board research vessels during the annual surveys carried out by the Centre for Environment, Fisheries and Aquaculture Science (Cefas) (Pinnegar et al., 2003).
-Predator and prey length were recorded and converted to body mass by Barnes et al.
-(2008) using published regression equations.
-Only vertebrate prey were identified and measured, with the vast majority being identified to species.
--->
+<!-- kable(fw_table, format = "latex", -->
 
-<!-- ### Afon Hirnant -->
+<!--       caption = "\\label{fig:tab_1}Information about the empirical food webs. AG: Working on this.", escape = FALSE, align = "l") %>% -->
 
-<!-- The Afon Hirnant is a tributary of the Welsh Dee in North Wales, U.K.
-(52$^\circ$ 52'N 03$^\circ$ 34) with the study being conducted at three sites.
-The pH within each site ranged from about 5.5 to 7 over the course of the year.
-A total of 180 invertebrate samples were collected for the whole sampling periods.
-All individuals within the benthic samples were counted and identified to the lowest possible taxonomic level (usually species).
-Prey items were identified using a combination of taxonomic keys and reference slides of previously identified species, after @schmid-arayaConnectanceStreamFood2002; @schmid-arayaImportanceMeiofaunaFood2002.
--->
+<!--   kable_styling(font_size = 7, latex_options="scale_down", row_label_position = 1) %>% -->
 
-<!-- ### Tadnoll Brook -->
+<!--   landscape(margin = "1cm") %>% -->
 
-<!-- Description of Tadnoll Brook here -->
+<!--   column_spec(1, width = "3cm") %>% -->
 
-<!-- ### Coilaco -->
+<!--   column_spec(2, width = "8em") %>% -->
 
-<!-- Description of Coilaco here -->
+<!--   column_spec(7, width = "8em") %>% -->
 
-<!-- ### Guampoe -->
+<!--   column_spec(8, width = "8em") %>% -->
 
-<!-- Description of Guampoe here -->
+<!--   column_spec(9, width = "8em") -->
 
-<!-- ### Trancura -->
+<!-- ``` -->
 
-<!-- Description of Trancura here -->
+### Broadstone Stream
+
+Broadstone Stream (51$^\circ$ 05' N 0$^\circ$ 03' E; 120 m above sea-level) is a second-order tributary of the River Medway in south-east England.
+At the time of sampling in 1996--1997, the stream was acidic (pH 4.7--6.6) and fishless.
+About 31 common species make up the macroinvertebrate food web, including six major predators and detritivores like stoneflies and chironomids [@woodwardQuantificationResolutionComplex2005].
+
+Between June 1996 and April 1997, thirty randomly scattered benthic Surber sample-units (25cm $\times$ 25cm quadrat; mesh aperture 330mm) were taken every two months and kept in 5% formalin.
+All individuals retrieved from the benthos and identified in stomach contents had their linear body dimensions quantified and converted to dry mass using known regression formulae (listed in @woodwardBodysizeDeterminantsNiche2002).
+
+The predators' foreguts were dissected and analysed with 400 magnification in the Surber samples.
+The individual body masses of eaten prey were calculated using the same methods as for the benthic samples, using reference slides as a guide [@woodwardQuantificationResolutionComplex2005].
+Over the six sample instances, a single dataset was produced.
+Each predator and prey individual involved in a feeding relationship was measured and converted into their respective body masses, resulting in a total of 2893 individuals.
+
+### Celtic Sea
+
+The Celtic Sea is a continental shelf area that is bounded by Ireland, the United Kingdom, and the Bay of Biscay.
+Because the @barnesPredatorPreyBody2008 dataset, from which the data utilised in this chapter were taken, did not provide precise sampling sites and dates, the data was pooled throughout the whole time period and locations to capture broad tendencies.
+Only places that were sampled consistently from 1987 to 2001 were used [@blanchardClimateFishingInfluence2005].
+
+In a published global dataset of individual predator and prey body sizes and taxonomy (Barnes et al., 2008), the feeding linkages of fish in the Celtic Sea were described.
+The original stomach contents data were acquired during annual surveys conducted by the Centre for Environment, Fisheries, and Aquaculture Science (Cefas) on board research vessels during dissections [@pinnegarDoesDietCeltic2003].
+@barnesPredatorPreyBody2008 used known regression equations to measure predator and prey lengths and convert them to body mass.
+
+### Afon Hirnant
+
+Three sites in the Afon Hirnant, in North Wales, UK ($52^\circ$ 52' N $03^\circ$ 34' W), were used for the study.
+The average yearly discharge was 2.08 to 7.26 $m^3/s$, with a pH ranging from 5.5 to 7.
+(check @figueroaFoodWebDynamics2007 and @woodwardChapterIndividualBasedFood2010 for full details).
+Invertebrates were collected using a Hess sampler (sampling area: 0.028 $m^2$; mesh aperture 80 $\mu m$), with 15 sample-units obtained at random at each site and season, totaling 180 samples across the sampling period.
+The invertebrate fauna was promptly preserved in 100% ethanol and sorted in the lab.
+By removing predators' foreguts, which were mounted in Euparal media and viewed at 400 magnification, feeding interactions were determined.
+
+Every predator's linear dimensions (for example, body length) and individual prey items inside each predator's foregut were measured and then translated to body mass values using published regression equations for each taxon (presented in @woodwardChapterIndividualBasedFood2010).
+If the prey items were highly digested, the average body length of individuals in the same family (Ephemeroptera, Plecoptera, or Trichoptera) in the habitat was used.
+The body lengths of Chironomidae (Diptera) were calculated using previously established species-specific regressions between head capsule width and body length [@figueroaFoodWebDynamics2007].
+
+### Tadnoll Brook
+
+The Tadnoll Brook is a tributary of the River Frome in Southern England, UK, with a mean annual discharge of 0.35 $m^3/s$ and a pH of 6.9--7.7. (Edwards et al., 2009b).
+
+A 240-m reach was sampled every two months between February and December 2005 to create the summary food web.
+A Surber sampler was used to collect invertebrates every two months (0.06 m2; mesh aperture 300 mm).
+20 random samples were taken on each occasion, stored in the field in 4% (w/v) formalin, and then sorted for invertebrates.
+Fish were captured with an electrofisher, anaesthetized with 2-phenoxyethanol, recognised to species, measured, and weighed on each occasion (Woodward et al., 2010).
+The guts of trout (Salmo trutta L.) with fork lengths more than 70 mm were then flushed with a tiny manual water pump and stored in 4% formalin.
+For smaller trout and other fish species (*Cottus gobio*, *Anguilla anguilla*, *Phoxinus phoxinus*, *Barbatula barbatula*, *Gasterosteus aculeatus*), specimens were sacrificed and frozen for subsequent dissection.
+
+Gut contents analysis was performed on each sample occasion for the fish assemblage, whereas invertebrates had far less varied diets and were only characterised in May and October.
+Individuals of the benthos' numerically dominant or trophically important invertebrate taxa were taken from the Surber samples, dissected, and the contents of the foregut investigated for animal prey, which were recognised at $400\times$ magnification by comparison with reference specimens.
+The taxa used to examine stomach contents covered more than 95% of the individuals observed in the Benthos.
+Wherever possible, predators' gut contents were matched to species, and linear body dimensions were measured.
+Using established regression equations, the dry mass of prey items and invertebrate predators was calculated [@benkeLengthMassRelationshipsFreshwater1999; @ganiharBiomassEstimatesTerrestrial1997; @burgherrRegressionAnalysisLinear1997; @gonzalezSizemassRelationshipsStream; @smockRelationshipsBodySize1980; @edwardsRelationshipLengthMass2009; @meyerRelationshipBodyLength1989].
+
+### Guampoe, Coilaco and Trancura Rivers, Chile
+
+Three rivers (the Coilaco, Guampoe, and Trancura Rivers) in the catchment area of the Tolten River in south Chile, South America, were studied in a similar way.
+The Coilaco River (discharge 2.1--16.8 $m^3/s$), Guampoe River (output 1.8--7.5 $m^3/s$), and Trancura River (discharge 8.8--49.3 $m^3/s$) are all pH 6.7--7.6 circumneutral rivers [@figueroaFoodWebDynamics2007].
+
+In each river, eight benthic samples were taken in each season between 1984 and 1985, totaling 96 sample-units for the whole sampling period (Campos et al., 1985).
+Invertebrates were gathered using a Surber sampler (sampling area: 0.09 $m^2$; mesh aperture 250 $\mu m$) and stored in 70% ethanol before being transported to the lab for species identification and food web analysis.
+
+The feeding linkages were discovered by analysing the gut contents of all individuals observed in each sample.
+Large invertebrates had their guts removed and mounted in Euparal, whilst small specimens were mounted whole and studied with $400\times$ magnification.
+Following Schmid (1993) and [@schmid-arayaConnectanceStreamFood2002], species prey items detected on each gut were identified using previously mounted reference slides.
+Using known regression equations (mentioned in @reissExistingPlentyAbundance2008; @baumgartnerPredictiveLengthDry2003; @miserendinoRelacionesLongitudpesoPara2001; @woodwardIndividualBasedFoodWebs2010), all linear dimensions were translated to body mass estimates.
 
@@
 
+**Comment AG: Is it necessary to have the sections 1.1 and 1.2 of the supplementary information in the Supplementary information or shall the sections 1.1 and 1.2 be migrated to the main text (manuscript)?**
+
 From an empirical dataset of gut content data, we take a random sample of gut contents of specific size (see below) to create a partial gut content dataset.
@@
 
-To fit the ADBM to a gut content dataset (be it complete or partial), we used the rejection ABC method we previously developed in @gupta2021 to accept a parameter value from a prior distribution which would have resulted in the minimum distance, where distance = 1 - True skill statistic.
+```{r, echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_ra} (a, c, e, g, i, k, m) Accuracy of the predicted food web measured using the true skill statistics, predicted by the ADBM parameterised using gut content data.
+Line and shaded grey region represents the mean and the prediction interval of 100 independent samples respectively.
+Red line represents the number of predator guts required to achieve a TSS of 95\\% of the maximum TSS.
+(b, d, f, h, j, l, n) Ratio of the true skill statistic of the predicted food web by the ADBM parameterised using gut content data to that of the predicted food web constructed using gut content data only.
+The dashed line shows where the ratio is one for reference."}
+knitr::include_graphics("../../manuscript/fig/ms_C2(1).png")
+```
+
+To fit the ADBM to a gut content dataset (be it complete or partial), we used the rejection ABC method we previously developed in @guptaSimultaneouslyEstimatingFood2022 to accept a parameter value from a prior distribution which would have resulted in the minimum distance, where distance = 1 - True skill statistic.
 The true skill statistic was computed between the diets predicted from the ADBM, and those observed in the sampled gut content data.
@@
 
--   A pool of gut content data $G: G = \{g_1, g_2, \dots, g_n\}$, where $g_{n}$ is the observed diet matrix containing ones and zeros. [OP: I made some edits here, which I'm not sure if are correct.]
+-   A pool of gut content data $G: G = \{g_1, g_2, \dots, g_n\}$, where $g_{n}$ is the observed diet matrix containing ones and zeros.
 
@@
 
--   A summary statistic $s(x): s(x) \subseteq model(\theta)$ [OP: a short explanation would be good.]
+-   A summary statistic $s(x): s(x) \subseteq model(\theta)$, where $s(x)$ is the diet of some or all of the predators.
 
--   A distance function $d(x_i, y) : d(x_i,y) = 1 - TSS(x_i, y)$  [OP: a short explanation would be good.]
+-   A distance function $d(x_i, y) : d(x_i,y) = 1 - TSS(x_i, y)$, which quantifies how close the observed diet is to the predicted diet of some or all of the predators.
 
--   An observed food web $Y: Y = \{d_{p_1}', d_{p_1}', \dots, d_{p_k}'\}$  [OP: a short explanation would be good.]
+-   An observed food web $Y: Y = \{d_{p_1}', d_{p_1}', \dots, d_{p_k}'\}$, where $d_{p_k}'$ is the observed diet matrix of predator $k$ containing ones and zeros.
 
@@
 
+## Computing the minimum gut content data
+
+Using TSS of the predicted food webs for different number of predator guts, we computed the number of gut content data that results in the mean TSS equal to the 95% of the mean TSS achieved by the model using all the predator guts for a food web.
+We call this number of gut content data as the minimum gut content data.
+
 # Results
@@
 Then, we calculate the number of gut content data for each food webs that results in accuracy equal to 95% of the maximum true skill statistics predicted by the food web model.
-We also compute how well  the food web model predicts structural properties from incomplete gut content data.
-by computing mean standardised error in food web properties.
 
@@
 \ref{fig:fig_ra}) (a, c, e, g, i, k, m).
-Furthermore, the prediction interval of the true skill statistics decreased with increasing number of predator guts with the mean TSS asymptoting to the maximum mean TSS achieved by the ADBM when all the gut content data was used.
+Furthermore, the width of the prediction interval of the true skill statistics decreased with increasing number of predator guts with the mean TSS asymptoting to the maximum mean TSS achieved by the ADBM when all the gut content data was used.
 Although the maximum TSS varied among the food webs, the qualitative increase in the TSS was the same.
 
-For Broadstone Stream food web, with only 381 gut contents, which is 38% of the total gut content data, the ADBM predicted the food web with the TSS of 0.74 which was 95% of the mean TSS (0.78) achieved using complete gut content data (Fig.
+For Broadstone Stream food web, with only 381 gut contents, which is 38% of the total gut content data, the ADBM predicted the food web with the mean TSS of 0.74 which was 95% of the mean TSS (0.78) achieved using complete gut content data (Fig.
 \ref{fig:fig_ra}(a)).
@@
 
-## Mean standardised error in structural properties with respect to the number of gut content data
+<!-- ## Mean standardised error in structural properties with respect to the number of gut content data -->
 
-Mean standardised error in structural properties of Afon Hirnant, Broadstone Stream, Celtic Sea and Tadnoll Brook food web reduced drastically with increasing number of predator gut content data at low number of predator gut content data (Fig.
+<!-- Mean standardised error in structural properties of Afon Hirnant, Broadstone Stream, Celtic Sea and Tadnoll Brook food web reduced drastically with increasing number of predator gut content data at low number of predator gut content data (Fig.
 \ref{fig:fig_rab}).
 In case of Broadstone Stream food web, the 95% prediction interval reduced as well with increasing number of predator gut content data.
+-->
 
-\*\*AG: Working on this paragraph.
+<!-- \*\*AG: Working on this paragraph. -->
 
-```{r, echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_rab} Mean standardised error in structural properties of different food webs with respect to the number of gut content data."}
-knitr::include_graphics("../../results/misc/plot_mse_ngut_all.png")
-```
+<!-- ```{r, echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_rab} Mean standardised error in structural properties of different food webs with respect to the number of gut content data."} -->
 
-## Dependence of the minimum gut content data on number of species, links and connectance
+<!-- knitr::include_graphics("../../results/misc/plot_mse_ngut_all.png") -->
 
-There was a positive trend between minimum gut content data [OP: minimum that could be used in order to ensure 95% of maximum TSS???] and number of species (S) (Fig.
-\ref{fig:fig_rb} (a)), links (L) (Fig.
-\ref{fig:fig_rb} (c)), connectance (C) (Fig.
-\ref{fig:fig_rb} (d)) and number of predator nodes (Fig.
-\ref{fig:fig_rb} (e)), with Broadstone Stream being an outlier in Fig.
-\ref{fig:fig_rb} (a, c, e).
-The minimum gut content data increases with number of gut content data sampled (Fig.
+<!-- ``` -->
+
+## Dependence of the minimum gut content data on number of links and connectance
+
+There was a significant positive relationship between the minimum number of gut content data (i.e the amount of gut content data used in order to ensure 95% of the maximum TSS) and the connectance of the food webs (Fig.
+\ref{fig:fig_rb} (a)).
+Similarly, we also observed a positive relationship between the minimum number of gut content data and the number of trophic links (L) in the food webs, however this relationship was not significant (Fig.
 \ref{fig:fig_rb} (b)).
-Furthermore, there seems to be a negative relationship between proportion of minimum gut (= Number of minimum gut / Number of maximum guts sampled) and number of species (S) (Fig.
-\ref{fig:fig_rb} (f)), links (L) (Fig.
-\ref{fig:fig_rb} (g)), connectance (C) (Fig.
-\ref{fig:fig_rb} (h)).
+Furthermore, there was a significant positive relationship between the number of minimum gut content data and the the number of maximum gut content data sampled (Fig.
+\ref{fig:fig_rb} (c)) for food webs.
 
-```{r echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_rb} (a, b, c, d, e) Number of minimum gut content data plotted against number of species (S), number of maximum guts sampled, number of links (L), connectance (C) and number of predator nodes respectively.
-(f, g, h) Proportion of minimum gut content data plotted against number of species (S), number of links (L) and connectance (C) respectively."}
+```{r echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_rb} (a, b, c) Number of minimum gut content data (i.e the amount of gut content data used in order to ensure 95\\% of the maximum TSS) plotted against number of links (L), connectance (C) and number of maximum guts sampled respectively.
+Solid lines are linear regression ((a) t = 3.138, df = 5, P = 0.0257; (b) t = 0.876, df = 5, P = 0.421; (c) t = 9.571, df = 5, P = 0.0002) and grey region represents 95\\% confidence intervals."}
 knitr::include_graphics("../../results/misc/plot_min_gut_vs_X.png")
-```
-
-```{r echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_rc} Link accumulation curve of the food web constructed using gut content data plotted against number of gut content data."}
-knitr::include_graphics("../../results/misc/plot_emplinks_ngut.png")
 ```
@@
 At lower amount of gut content data, predicting with the model is better than using the data itself, while at higher amounts of gut content data, it is better to only use the data.
-We computed the upper limit of amount of gut content data till when it can be used to compensate for undersampling [OP: reword this sentence, it is unclear.].
 This can help inform how much gut content data to actually collect when we are using a food web model to infer trophic interactions.
@@
 We found the minimum amount of gut content data to vary across food webs and this could be due to the possibility that the food webs are sampled differently, i.e.
-some food webs are more extensively sampled than others (Fig.
-\ref{fig:fig_rc}).
+some food webs are more extensively sampled than others (SI Fig.
+S2).
 Furthermore, it is possible that interactions in some of the food webs are are more size-structured than others, and are therefore better predicted by the ADBM and consequently require a lower number of gut content data for model parameterisation.
-
-\*\*:AG: I would need to add information about the interactions in these food webs.
 
@@
 When little data about trophic interactions is available, the model can be used to add data about interactions for which data is missing.
-Furthermore, the model predictions can be used as a guide to sample predator guts that might be significant in the food web [OP: how?
-I suggest to explain this in more detail.]
+Furthermore, the model predictions can be used as a guide to sample those predator guts for which we do not have enough information on the presence of interactions from the empirical gut content samples but the model suggests there are interactions.
+Therefore, with enough number of predator guts sampled one might possibly observe those missed interactions.
+
+<!-- [OP: how? I suggest to explain this in more detail.] -->
 
@@
 
-\*\*AG: Working on this.
+In all the food webs, the ratio TSS(Model)/TSS(Data) decreased with increasing number of predator guts (Fig.
+\ref{fig:fig_ra} (b, d, f, h, j, l, n)).
+This suggests when less data is available it is better to use the model and when more data is available it is better to only use the data to predict trophic interactions.
+At lower number of predator guts the model fills up the missing interactions that were not observed in the gut content data, therefore resulting in model performing better as compared to data alone.
+Wile at higher number of predator guts the model is probably predicting some presence or absence of links i.e.
+false positives and false negatives resulting in a lower TSS as compared to that of data alone.
 
-## Why Broadstone Stream is an outlier?
+<!-- ## Why Broadstone Stream is an outlier? -->
 
-Broadstone Stream is the most sampled food web compared to all the other food webs (Fig.
-\ref{fig:fig_rc}), which means the observed Broadstone Stream food web might be more accurate compared to others.
+<!-- In most of the plots, Broadstone Stream food web was an outlier (Fig.
+\ref{fig:fig_rc})).
+This can be attributed to the fact that the Broadstone Stream food web was the most sampled food web (Fig.
+SI XXX).
+Since the Broadstone Stream food web has the highest number of predator gut content data as compared to other food webs so the chances of missing links is lower in the Broadstone Stream food web as compared to others.
+-->
 
-\*\*AG: Working on this, not sure if this paragraph is needed.
+<!-- \*\*AG: Working on this, not sure if this paragraph is needed. -->
 
@@
 
-\*\*OP Focus on this, at least in the context of further work that could be done. ## There is uncertainty in gut content data and needs to be propagated into model's predictions
+<!-- \*\*OP Focus on this, at least in the context of further work that could be done. ## There is uncertainty in gut content data and needs to be propagated into model's predictions -->
 
@@
 
-[OP: This one I already shared with you: https://onlinelibrary.wiley.com/doi/10.1111/ele.13966
+<!-- [OP: This one I already shared with you: https://onlinelibrary.wiley.com/doi/10.1111/ele.13966 -->
 
-\*\*OP: Focus on this, and other studies that have looked at the importance of quantity and quality of food web data ## Comparing our study with other studies of predicting food webs using incomplete data
+<!-- \*\*OP: Focus on this, and other studies that have looked at the importance of quantity and quality of food web data ## Comparing our study with other studies of predicting food webs using incomplete data -->
 
 Some studies have presented how the accuracy of food web prediction change when we vary the amount of food web data [@grayJoiningDotsAutomated2015].
-\*\*AG: Working on this paragraph.
+For example: @desjardins-proulxEcologicalInteractionsNetflix2017 has used predictive machine learning models and @caronAddressingEltonianShortfall has used predictive traits-based models on partial knowledge of interactions to reconstruct a food web accurately, in contrast to our study where we used a mechanistic food web model.
+
+<!-- \*\*AG: Working on this paragraph. -->
 
@@
 
-\*\*OP: Focus on this.
+<!-- \*\*OP: Focus on this. -->
 
 In our study, we have implemented the approach only with the ADBM.
-However, in principle, this approach could be extended to other food web models [OP: such as???].
-A future prospect could be to study how well different food web models' prediction accuracy varies for different amount of gut content data.
-This can also help in making decision as to which food web model to chose from given a set of gut content data.
+However, in principle, this approach could be extended to other food web models such as [@williamsSimpleRulesYield2000; @gravelInferringFoodWeb2013; @allesinaGeneralModelFood2008].
+A future prospect could be to study how well different food web models' prediction accuracy vary with different amount of gut content data.
+This can also help in making decision as to which food web model to chose from for a given a set of gut content data.
+We suspect the relationship (i.e shape of the curve) between the TSS of the predicted food web and the number of predator guts might vary within food web models.
 
-[OP: seems to not add much relative to the previous paragraph.] A future study could be to use our approach of estimating the minimum gut content data for different food web models.
-An efficient model would be the one that uses minimum available gut content data to predict species interactions with high accuracy and high precision.
-
-[OP: comment if and why one might expect other food web models to show different efficiency.]
+<!-- [OP: comment if and why one might expect other food web models to show different efficiency.] -->
 
@@
 
-[OP: this paragraph / section needs further development]
+<!-- [OP: this paragraph / section needs further development] -->
 
 Some of the food webs are not very well predicted using the ADBM.
-And with the assumption that the food web constructed from the complete gut content data is the true food web might result in not so accurate estimates of the minimum gut content data.
-As it might be the case that the links are still under-sampled for many nodes [@woodwardIndividualBasedFoodWebs2010].
+And this could possibly result in a lower value of minimum gut content data that was used to achieve 95% of the maximum TSS.
+This could be because our study is based on the assumption that the true food webs is the one which was constructed using the total gut content data.
+However, if the total gut content does not contain sufficient information to construct the complete food web, then the food web will miss some links.
+This would therefore result in a lower TSS of the predicted food web, which can eventually lead to a lower estimate of the minimum gut content data.
+A future prospect could be to incorporate other sources of presence-absence data such as stable isotope ratio, metabarcoding to complement any links that were missed by the gut content method.
 
 ## How can we include other types of food web data?
-
-\*\*OP: Focus on this ## How can we include other food web data type?
 
@@
 
-# Conclusion
-
-\*\*AG: Working on this.
-
-# Supplementary Information
-
-<!-- ```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_s1} \\textit{In silico} approach for investigating the effect of quantity and composition of food web data in predicting food web structure using the ADBM."} -->
-
-<!-- knitr::include_graphics("../fig/flowchart.png") -->
-
-<!-- ``` -->
-
-## Gut content data simulation
-
-\*\*OP: It needs to be very clear in the main text, and here, why this is being described.
-It is currently unclear, not least because the main text does not, I think, refer to the information here.
-[OP: I'm not sure my comment has been addressed.
-We should discuss this.] [OP: I don't see this Supplement being referred to anywhere in the main text.
-I would expect it to be.] [OP: I advise to integrate the content of this supplement into the main article.
-There is not so much of it, and it is insightful.]
-
-We simulated a food web using the ADBM for a given set of parameters.
-For a given set of predators, we subset the diet from the simulated food web.
-Then using a probability mass function (distribution), we sampled the gut content data from predators' diet thereby incorporating the uncertainty in the gut content data.
-We repeated this process multiple number of times for every predator in the food web.
-
-*Input:*
-
--   Predators whose diet are to be simulated $P = \{p_1, \dots, p_n\}$
-
--   A simulated food web $ADBM(\theta_i) = \{d_{p_1}, d_{p_1}, \dots, d_{p_k}\}$, where $d_{p_k}$ is a one-dimensional diet matrix of predator $k$ containing ones and zeros.
-
--   A function which describes uncertainty in the diet $U(d)$
-
--   Number of independent guts to be simulated for a predator $p_i: ngut$
-
-*Sampling:*
-
--   for $p_i \in P$
-
-    -   for $j = 1, \dots, ngut$, where $ngut$ is the number of guts to be simulated
-
-        -   Simulate a single gut of a predator $p_i: g(p_i) = d_{p_i} * U(d_{p_i})$
-
-    -   Set of gut of a predator $p_i: G(p_i) = \{ g(p_i) : g(p_i) = d_{p_i}*U(d_{p_i}) \}$
-
-*Output:*
-
--   We simulated a pool of gut content data which contains simulated gut content data $G(p_i)$ for every predator $p_i$
-
-## Prediction using gut content data from a simulated food web
-
-```{r fig_r0, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r0} True skill statistics between predicted food web and observed food web for a simulated small reef food web estimated for distinct predator guts in a sample.
-The observed simulated food web consists of 50 species and \\dots links.
-The vertical bars correspond to the prediction intervals of the true skill statistics with filled circles representing the corresponding mean.
-A prediction interval of the TSS is formed using a set of 100 accepted TSS values using the ABC method."}
-knitr::include_graphics("../fig/TSS_with_n_pred_prop_simulated.png")
-```
-
-The true skill statistics (TSS) between the predicted food web and simulated observed food web saturated with an increasing number of distinct predator guts in a sample (Fig.
-\ref{fig:fig_r0}).
-The TSS of the predicted food webs estimated using the complete individual gut data had narrower prediction intervals resulting in less uncertainty, and higher mean TSS than that using the partial individual gut data.
-The maximum limit of the prediction interval of TSS estimated using the complete gut data and the partial gut data were almost equal, with the minimum limit of the prediction interval of TSS using partial gut data being lower than that from the complete gut data.
-Eventually, the gap between the mean TSS using the partial gut data and the complete gut data reduced with an increasing number of distinct predator guts.
-This suggests that when there is enough predator species' gut data, the achieved TSS was almost constant and hence independent of the amount of gut data.
-
-The maximum TSS estimated using the complete gut data was very close to one and almost remained constant with an increasing number of different predator species sampled.
-With the gut data sample of only five distinct predator species, 95% of the maximum mean TSS was achieved when complete individual gut data was used, while the same was achieved with 15 predator species for partial gut data.
-This shows that one does not need to know the gut data of all the species to predict the food web and the accuracy is dependent on the completeness of an individual gut data.
-
-```{r fig_r3, echo=FALSE, fig.align='center', out.width="300px", fig.cap="\\label{fig:fig_r3} True skill statistics between predicted food web and observed food web estimated for different number of distinct predator guts.
-The estimation is done for three sets of gut data: gut content data of predators whose body sizes are smaller than the mean body size, larger than the mean body size, and all the gut content data."}
-knitr::include_graphics("../fig/TSS_with_n_pred_prop.png")
-```
-
-```{r fig_r31, echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_r31} True skill statistic between predicted food web using ADBM and incomplete gut content data, and observed food web against the true skill statistic between food web constructed using incomplete gut content data, and observed food web.
-Error bars represent prediction intervals of 100 independent samples.
-Dashed line is 1:1 line for reference."}
-knitr::include_graphics("../../results/misc/TSS_model_vs_data.png")
-```
-
-```{r fig_r32, echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_r32} Mean standardised error in structural properties in the food web predicted using ADBM and incomplete gut content data against structural properties in the predicted food web constructed using incomplete gut content data.
-Error bars represent prediction intervals of 100 independent samples.
-Dashed line is 1:1 line for reference."}
-knitr::include_graphics("../../results/misc/mse_model_vs_data.png")
-```
-
-<!-- # Notes: -->
-
-<!-- ## Stable isotope ratios -->
-
-<!-- * Isotope ratios are reported in parts per thousand  relative to standards, and atmospheric N for nitrogen, and defined in delta notation as -->
-
-<!-- * $\delta^{15}N$ or $\delta^{13}C = (\frac{R_{sample}}{R_{standard}} - 1) * 10^3 $ -->
-
-<!-- * Most commonly a fixed $\Delta^{15}N$ value of 3.4 ppt is used to estimate relative species TP -->
-
-<!-- # Other notes: -->
-
-<!-- * Audience: Researchers who are interested in food web data collection -->
-
 # Acknowledgements
@@
 
-# References
-
-<!-- ## Why knowing trophic interactions is important? -->
-
-<!-- Knowledge about the trophic interactions in a food web can be used to answer crucial ecological questions: Which species is a keystone species in a food web [@jordanKeystoneSpeciesFood2009]?
-How would a food web respond if the top predators are removed [@knightTrophicCascadesEcosystems2005]?
-Which species should be given priority when conservation efforts are implemented [@mcdonald-maddenUsingFoodwebTheory2016]?
-How robust is a food web to extinctions [@dunneNetworkStructureBiodiversity2002]?
--->
-
-<!-- ## What are the methods for knowing interactions? -->
-
-<!-- Species interactions can be directly or indirectly inferred from different types of methods such as gut content analysis [@peralta-maraverStructureDynamicsStability2017], stable isotope ratio analysis of tissues [@laymanCanStableIsotope2007], experimentation [@warrenSpatialTemporalVariation1989], DNA metabarcoding [@roslinUseDNABarcodes2016], food web model [@gravelInferringFoodWeb2013; @petcheySizeForagingFood2008; @williamsSimpleRulesYield2000] and literature research [@grayJoiningDotsAutomated2015; @cohenSoilInvertebratesChemistry2014; @goldwasserConstructionAnalysisLarge1993a].
--->
-
-<!-- ## What are the shortcomings of the methods mentioned above? -->
-
-<!-- These food web methods mentioned above have multiple shortcomings.
-Stable isotope ratio analysis of the organism's tissue does not give a direct information of the diet of that organism but rather approximate trophic position of that species in the food web.
-Although mixing models can be used to determine what prey items are most likely fed upon by a predator but this results in uncertainty in the estimates [@kadoyaIsoWebBayesianIsotope2012; @crawfordApplicationsStableIsotope2008].
-Experimentation (e.g.
-feeding trials) may create unrealistic conditions where a predator is confined in a small space with a potential "prey" and is effectively "forced" into eating it (citreqd).
-DNA metabarcoding could have many issues such as failure to relate OTUs to species, or inability to distinguish secondary predation, i.e.
-the DNA signature of the prey consumed by the prey consumed by the primary item found in the predator's gut.
-Another approach to infer missing links is literature research which involves assuming that a link will occur because another author described it in some other system, or for related predator/prey species, e.g.
-from the same genus or family  [@grayJoiningDotsAutomated2015; @cohenSoilInvertebratesChemistry2014; @goldwasserConstructionAnalysisLarge1993a] (citreqd).
-This typically results in a food web that will be very oversampled with false positives in the presence of links (citreqd).
--->
-
-<!-- ## Food web model -->
-
-<!-- Food web models are set of rules governed by ecological theory which defines trophic interactions in a food web.
-Along with inferring missing links in a food web, they can be used for understanding the mechanistic of the food web and ecological forecasting.
-Observed food web data can be used to parameterise the food web model.
--->
-
-<!-- ## Parameterising a food web model using food web data -->
-
-<!-- One of the common method of knowing presence-absence information of trophic links in food web is by gut content analysis of predator guts, which can be used to parameterise a food web model.
-Gut content data have been used to predict the diet of a predator in a food web [@eitzingerTestingValidityFunctional2018; @omalleyEffectsFoodWeb2017; @dixonAssessingDietNorth2017; @mcclain-countsTrophicStructureMesopelagic2017b; @peralta-maraverStructureDynamicsStability2017].
-A single gut content data of a predator gives the information what the predator has consumed recently.
-The diet of that individual can be inferred from the items in the stomach.
--->
-
-<!-- ## Why inferring interactions is not easy? -->
-
-<!-- As a food web can be quite complex with many species and trophic interactions [@williamsSimpleRulesYield2000;@berlowSimplePredictionInteraction2009], inferring these trophic interactions with high accuracy and low uncertainty would require a large amount of food web data (citreqd).
-E.g.
-One would need to sample many individuals for gut content data, and processing these guts require a large amount of effort and time as well.
--->
-
-<!-- A single gut content of a predator provides information of the prey individuals that have been consumed by the predator in a small temporal and spatial scale (citreqd).
-Therfore, given a spatial and temporal scale of a food web, the sampling of the gut content data needs to be carried out.
-This means that for a food web constructed on a large spatial and temporal scale large number of gut content data needs to be collected.
-There is also a possibility that some of the information provided by these types of food web data are redundant i.e.
-taking into account any further food web data does not necessarily increase the food web prediction significantly.
-E.g.
-This can happen if the guts of two predator individuals give the same information about the prey the predator has consumed.
-This issue can be resolved by using a yield-effort curve which suggests when sampling of new predator guts can be stopped [@hernandezParasitesAlterTopology2008].
--->
-
-<!-- ## Undersampled food web -->
-
-<!-- When it is difficult to obtain food web data, this can result in missing links in the food web thereby resulting in an undersampled food web.
-Limitations of resources and time can also lead to an undersampled food web because collecting and analysing gut content data is tedious and expensive task (citreqd).
-It is crucial to have well sampled food web because food web properties are highly sensitive to varying levels of sampling effort [@goldwasserSamplingEffectsEstimation1997].
-So, it is important to predict food web properties with high accuracy and high precision.
--->
-
-<!-- ## What is a food web model and how can it be used to compensate for undersampling? -->
-
-<!-- When we have an undersampled food web, food web models can be used to predict which trophic interactions are feasible and which are not [@allesinaGeneralModelFood2008; @cohenStochasticTheoryCommunity1985; @gravelInferringFoodWeb2013; @petcheySizeForagingFood2008; @tamaddoni-nezhadConstructionValidationFood2013].
-Food web model are set of rules governed by ecological theory which defines trophic interactions in a food web.
-For example, @petcheySizeForagingFood2008 based on foraging traits allometrically scaled using body size data of species predicted trophic interactions where the model was parameterised using known presence and absence of trophic interactions.
--->
-
-<!-- ## Research question -->
-
-<!-- How much gut content data is required when a food web model is used to predict trophic interactions?
-We are interested in maximizing the accuracy and precision of the predicted food web and simultaneously minimizing the amount of gut content data used, because we do not want to spend a lot of resources in sampling gut content data.
--->
+# Reference

### 2022-06-20 manuscript/ms_C2/ms_C2.tex
Incorporated most comments from Guy, Eoin and David

@@
 \usepackage{microtype}      % microtypography
-\usepackage{lipsum}
 \usepackage{graphicx}
 
-\title{Optimal amount of gut content data required to predict trophic
-interactions using a food web model}
+\title{How much gut content data is required to predict trophic
+interactions?}
 
@@
    \And
+    Other authors
+   \\
+    XXX XXX \\
+    XXX XXX \\
+  XXX XXX \\
+  \texttt{XXX XXX} \\
+   \And
     Owen L. Petchey
@@
 
+% tightlist command for lists without linebreak
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
 % Pandoc citation processing
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
 \newlength{\csllabelwidth}
 \setlength{\csllabelwidth}{3em}
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
 % for Pandoc 2.8 to 2.10.1
@@
 % For Pandoc 2.11+
-\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
  {% don't indent paragraphs
@@
   % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
   % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
+  \setlength{\parskip}{#2\cslentryspacingunit}
  }%
  {}
-\usepackage{calc} % for calculating minipage widths
+\usepackage{calc}
 \newcommand{\CSLBlock}[1]{#1\hfill\break}
 \newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
@@
 \usepackage{lineno}
-\linenumbers
 \usepackage {amsmath}
@@
 \usepackage{setspace}\doublespacing
-
 \begin{document}
 \maketitle
-
-\def\tightlist{}
 
@@
 \item
-\item
-\item
-\item
+  One of the biggest obstacles in food web ecology is the time and
+  effort required to adequately describe the structure of a food web
+  using gut content data. Food web models such as the ADBM can be used
+  to circumvent this problem by predicting the interactions based on
+  easily measured characteristics, such as the size of organisms.
+  However, presence-absence data such as gut content data is required to
+  parameterise these food web models. And collecting and analysing these
+  data from the field is an expensive and time consuming task.
+  Therefore, it is crucial to know how much gut content data is required
+  to parameterise food web models with high accuracy and high precision.
+\item
+  Here, we explore seven food webs in the literature and determine how
+  much gut content data would be needed to accurately predict their
+  structure using the ADBM. We use Bayesian computation to parameterise
+  the ADBM, and true skill statistics to measure the goodness of fit,
+  and do so while varying the amount of gut content data used in the
+  parameterisation.
+\item
+  We estimated the minimum amount of gut content data required for seven
+  different food webs that resulted in 95\% of the maximum true skill
+  statistics achieved by the ADBM when all available gut content data
+  was used. We found that incomplete gut content data can be used to
+  parameterise the ADBM with the lowest amount of gut content data being
+  28\% of the available gut content data.
+\item
+  These results suggest that one need not collect such a large quantity
+  of gut content data to predict the structure of a food web, thereby
+  reducing sampling effort considerably, while having little effect on
+  precision or accuracy of predictions.
 \end{enumerate}
@@
 
-\hypertarget{alternate-titles}{%
-\section{Alternate titles}\label{alternate-titles}}
-
-\begin{itemize}
-\item
-  Predicting trophic interactions using incomplete gut content data
-\item
-  Effect of the amount of gut content data on the accuracy and precision
-  of food web prediction
-\end{itemize}
-
 \hypertarget{introduction}{%
@@
 Knowledge about the trophic interactions in a food web is crucial in
-ecology from identifying keystone species (Jord'an 2009) to quantifying
-robustness of a food web to species extinctions (Dunne, Williams, and
-Martinez 2002). This has led to the development of numerous food web
-models (Allesina, Alonso, and Pascual 2008; Cohen, Newman, and Steele
-1985; Gravel et al. 2013; Petchey et al. 2008; Tamaddoni-Nezhad et al.
-2013). Along with inferring missing links in an observed food web, the
-food web models are also used for ecological forecasting (Hattab et al.
-2016; Lindegren et al. 2010) and understanding the underlying mechanism
-governing the interactions in a food web (O'NAGorman et al. 2019).
-
-Although food web models are constructed using prior theory governing
-the food webs, interaction data is required to parameterise a model. For
-example, Petchey et al. (2008) used presence-absence information about
-trophic interactions to parameterise the allometric diet breadth model
-and thereby predict species interactions. These information can be
-inferred from diverse set of methods such as gut content analysis
-(Peralta-Maraver, Lopez-Rodriguez, and de Figueroa 2017), stable isotope
-ratio analysis of tissues (Layman et al. 2007), experimentation (Warren
-1989), DNA metabarcoding (Roslin and Majaneva 2016) and literature
-research (Gray et al. 2015; Cohen and Mulder 2014; Goldwasser and
-Roughgarden 1993). All of these methods can infer the diet of a
-consumer, however different methods measure different consumed
-components, thereby resulting in different levels of uncertainty in the
-inferred diet (citreqd). A single gut content of a predator describes
-what that individual has consumed recently which can be used to infer
-the diet of the predator (Eitzinger et al. 2018; O'NAMalley et al. 2017;
-Dixon et al. 2017; McClain-Counts, Demopoulos, and Ross 2017;
-Peralta-Maraver, Lopez-Rodriguez, and de Figueroa 2017). Stable isotope
-data when combined with mixing models can be used to determine which
-prey items are most likely fed upon by a predator (Kadoya, Osada, and
-Takimoto 2012; Crawford, Mcdonald, and Bearhop 2008).
-
-Acquiring food web data from these methods is time consuming and
-expensive (reference). For example, many gut content data needs to be
-collected to infer the complete presence-absence information of a food
-web structure with high accuracy and precision. Also further time and
-resource investment is required to process the collected samples. Hence,
-there is an utmost demand to know the minimum number of presence-absence
-information of a food web to parameterise a food web model with high
-accuracy and high precision, so that one knows when to stop collecting
-any further data on the food web.
-
-The key question we are interested in answering is how much
-presence-absence information is required to infer food web structure
-from a food web model with high accuracy and high precision. In other
-words, in case of gut content data how many samples of gut content
-should one collect from the field to parameterise a food web model? To
-answer this question, we use the presence-absence information from gut
-content data, and allometric diet breadth model (ADBM) to predict
-trophic interactions. We parameterise the model using approximate
-Bayesian computation/rejection Monte Carlo sampling.
+ecology for purposes ranging from identifying keystone species (Jord'an
+2009) to quantifying robustness of a food web to species extinctions
+(Dunne, Williams, and Martinez 2002). This has led to the development of
+numerous food web models (Allesina, Alonso, and Pascual 2008; Cohen,
+Newman, and Steele 1985; Gravel et al. 2013; Petchey et al. 2008;
+Tamaddoni-Nezhad et al. 2013). Along with inferring missing links in an
+observed food web, the food web models are also used for ecological
+forecasting (Hattab et al. 2016; Lindegren et al. 2010) and for
+understanding the underlying mechanism governing the interactions in a
+food web (Gorman et al. 2019).
+
+Although food web models are constructed using prior theory about the
+factors that determine trophic interactions, empirical data about
+interactions is required to parameterise a model. For example, Petchey
+et al. (2008) used presence-absence information about trophic
+interactions to parameterise the allometric diet breadth model and
+thereby predict species interactions. These empirical information about
+interactions can come from diverse set of methods such as gut content
+analysis (Peralta-Maraver, Lopez-Rodriguez, and de Figueroa 2017),
+stable isotope ratio analysis of tissues (Layman et al. 2007),
+experimentation (Warren 1989), DNA metabarcoding of gut contents or
+faeces (Roslin and Majaneva 2016) and literature research (Gray et al.
+2015; Cohen and Mulder 2014a; Goldwasser and Roughgarden 1993a).
+
+Each of these sources of information about trophic interactions has
+shortcomings. For example: Stable isotope ratio analysis of the
+organism's tissue does not give direct information of the diet of that
+organism but rather gives approximate trophic position of that species
+in the food web (Wada, Mizutani, and Minagawa 1991; Jennings and van der
+Molen 2015). Although mixing models can be used to determine what prey
+items are most likely fed upon by a predator, this results in
+uncertainty in the estimates (Kadoya, Osada, and Takimoto 2012;
+Crawford, Mcdonald, and Bearhop 2008). Similarly, DNA metabarcoding
+could have issues in detecting secondary predation or cannibalism
+(Pompanon et al. 2012; Nielsen et al. 2018) and is prone to
+environmental contamination (e.g.~DNA in the water swallowed along with
+DNA from an aquatic consumer's prey cannot be differentiated from actual
+prey) (Kelly et al. 2014). Furthermore, construction of food webs via
+literature review can lead to false positives--links included when in
+reality no link would occur because it makes an assumption that the
+species interactions inferred from a system will occur in another system
+as well(Gray et al. 2015; Cohen and Mulder 2014b; Goldwasser and
+Roughgarden 1993b).
+
+Nielsen et al. (2018) have shown that gut content analysis method has a
+better match with real diet when compared to other methods.
+
+Acquiring food web data from gut content analysis is time consuming and
+expensive (AG: Do we need a reference? Next sentence explains the
+reason.). In part this is due to the perception that many gut contents
+must be collected and analysed in order to be confident that the
+majority of possible trophic links among species have been observed.
+Furthermore, considerable time, resource investment, and expertise is
+required to process the collected samples. Hence, there is of
+considerable importance to know the minimum number of gut contents and
+of which consumer species that are required to parameterise a food web
+model with high accuracy and high precision, so that one knows when is a
+good time to stop collecting any further empirical data on the food web.
+
+Therefore, the key question we are interested in answering is how much
+presence-absence information, in the form of gut content data, is
+required to infer food web structure from a food web model with high
+accuracy and high precision. In other words, how many samples of gut
+content should one collect from the field to parameterise a food web
+model? To answer this question, we use the presence-absence information
+from gut content data to parameterise the allometric diet breadth model
+(ADBM) thereby predicting trophic interactions in seven different food
+webs using rejection approximate Bayesian computation, where the fit of
+the model was measured using true skill statistics. We computed the true
+skill statistics of the predicted food webs for different number of
+predator guts to calculate the minimum number of gut content data to
+infer food web structure. Our study provides a guideline on how many gut
+content data is required to predict food web structure using a food web
+model.
 
@@
 
-In the upcoming sections, we present the allometric diet breadth model
-(ADBM) and the gut content data used to infer trophic interactions. We
-also give a detailed account of using partial gut content data to
-parameterise the ADBM using approximate Bayesian computation (ABC). We
-assessed model predictions using true skill statistic and various
-structural food web properties for comparison across food webs.
+In the upcoming sections, we present the empirical food webs, the
+allometric diet breadth model (ADBM), and the gut content data used to
+infer the trophic interactions. We also give a detailed account of using
+partial gut content data to parameterise the ADBM using rejection
+approximate Bayesian computation (ABC). We assessed model predictions
+using the true skill statistic for comparison across food webs.
+
+\hypertarget{the-empirical-food-webs}{%
+\subsection{The Empirical Food Webs}\label{the-empirical-food-webs}}
+
+In our study, we used food webs for which gut content data is available
+at an individual level and data that is or that we could make FAIR
+(Wilkinson et al. 2016). Presence and absence interactions of food web
+data can be aggregated in different ways (Gilljam et al. 2011). A common
+way of aggregating food web data is the taxonomic approach, in which
+nodes in the food web are taxa (e.g.~species), or life stages of taxa,
+and one species is said to feed on another species if at least one
+individual of the latter is found in at least one gut of the former.
+Another approach is based on size, rather than taxonomy, and in this the
+nodes in the food web are size classes. Here, a feeding link occurs
+between two size classes if at least one prey item within a size class
+was found in the gut of another size class, irrespective of their
+taxonomy.
+
+In our study, we aggregate the gut content data on the basis of size
+class because the food webs constructed using this approach were better
+predicted by the ADBM compared to the taxonomic approach (Woodward et
+al. 2010a), and this is because the ADBM is based on foraging rules
+defined using the body sizes of organisms (Petchey et al. 2008).
+
+Our study is based on the assumption that the food web constructed using
+the complete gut content data is the true food web. However, this might
+not be the case because the links are still under-sampled for many nodes
+(Woodward et al. 2010b). This could result in a lower true skill
+statistic (TSS) of the predicted food web from the ADBM, which can
+result in a biased estimate of the minimum number of gut content data
+required to achieve 95\% of the TSS achieved using complete gut content
+data.
+
+In the following sections 2.1.1-2.1.5, we briefly explain seven
+empirical food webs used in our study. The text used in those sections
+are paraphrased from Gilljam et al. (2011).
+
+\hypertarget{broadstone-stream}{%
+\subsubsection{Broadstone Stream}\label{broadstone-stream}}
+
+Broadstone Stream (51\(^\circ\) 05' N 0\(^\circ\) 03' E; 120 m above
+sea-level) is a second-order tributary of the River Medway in south-east
+England. At the time of sampling in 1996--1997, the stream was acidic
+(pH 4.7--6.6) and fishless. About 31 common species make up the
+macroinvertebrate food web, including six major predators and
+detritivores like stoneflies and chironomids (Woodward, Speirs, and
+Hildrew 2005).
+
+Between June 1996 and April 1997, thirty randomly scattered benthic
+Surber sample-units (25cm \(\times\) 25cm quadrat; mesh aperture 330mm)
+were taken every two months and kept in 5\% formalin. All individuals
+retrieved from the benthos and identified in stomach contents had their
+linear body dimensions quantified and converted to dry mass using known
+regression formulae (listed in Woodward and Hildrew (2002)).
+
+The predators' foreguts were dissected and analysed with 400
+magnification in the Surber samples. The individual body masses of eaten
+prey were calculated using the same methods as for the benthic samples,
+using reference slides as a guide (Woodward, Speirs, and Hildrew 2005).
+Over the six sample instances, a single dataset was produced. Each
+predator and prey individual involved in a feeding relationship was
+measured and converted into their respective body masses, resulting in a
+total of 2893 individuals.
+
+\hypertarget{celtic-sea}{%
+\subsubsection{Celtic Sea}\label{celtic-sea}}
+
+The Celtic Sea is a continental shelf area that is bounded by Ireland,
+the United Kingdom, and the Bay of Biscay. Because the Barnes et al.
+(2008) dataset, from which the data utilised in this chapter were taken,
+did not provide precise sampling sites and dates, the data was pooled
+throughout the whole time period and locations to capture broad
+tendencies. Only places that were sampled consistently from 1987 to 2001
+were used (Blanchard et al. 2005).
+
+In a published global dataset of individual predator and prey body sizes
+and taxonomy (Barnes et al., 2008), the feeding linkages of fish in the
+Celtic Sea were described. The original stomach contents data were
+acquired during annual surveys conducted by the Centre for Environment,
+Fisheries, and Aquaculture Science (Cefas) on board research vessels
+during dissections (Pinnegar et al. 2003). Barnes et al. (2008) used
+known regression equations to measure predator and prey lengths and
+convert them to body mass.
+
+\hypertarget{afon-hirnant}{%
+\subsubsection{Afon Hirnant}\label{afon-hirnant}}
+
+Three sites in the Afon Hirnant, in North Wales, UK (\(52^\circ\) 52' N
+\(03^\circ\) 34' W), were used for the study. The average yearly
+discharge was 2.08 to 7.26 \(m^3/s\), with a pH ranging from 5.5 to 7.
+(check Figueroa (2007) and Woodward et al. (2010c) for full details).
+Invertebrates were collected using a Hess sampler (sampling area: 0.028
+\(m^2\); mesh aperture 80 \(\mu m\)), with 15 sample-units obtained at
+random at each site and season, totaling 180 samples across the sampling
+period. The invertebrate fauna was promptly preserved in 100\% ethanol
+and sorted in the lab. By removing predators' foreguts, which were
+mounted in Euparal media and viewed at 400 magnification, feeding
+interactions were determined.
+
+Every predator's linear dimensions (for example, body length) and
+individual prey items inside each predator's foregut were measured and
+then translated to body mass values using published regression equations
+for each taxon (presented in Woodward et al. (2010c)). If the prey items
+were highly digested, the average body length of individuals in the same
+family (Ephemeroptera, Plecoptera, or Trichoptera) in the habitat was
+used. The body lengths of Chironomidae (Diptera) were calculated using
+previously established species-specific regressions between head capsule
+width and body length (Figueroa 2007).
+
+\hypertarget{tadnoll-brook}{%
+\subsubsection{Tadnoll Brook}\label{tadnoll-brook}}
+
+The Tadnoll Brook is a tributary of the River Frome in Southern England,
+UK, with a mean annual discharge of 0.35 \(m^3/s\) and a pH of 6.9--7.7.
+(Edwards et al., 2009b).
+
+A 240-m reach was sampled every two months between February and December
+2005 to create the summary food web. A Surber sampler was used to
+collect invertebrates every two months (0.06 m2; mesh aperture 300 mm).
+20 random samples were taken on each occasion, stored in the field in
+4\% (w/v) formalin, and then sorted for invertebrates. Fish were
+captured with an electrofisher, anaesthetized with 2-phenoxyethanol,
+recognised to species, measured, and weighed on each occasion (Woodward
+et al., 2010). The guts of trout (Salmo trutta L.) with fork lengths
+more than 70 mm were then flushed with a tiny manual water pump and
+stored in 4\% formalin. For smaller trout and other fish species
+(\emph{Cottus gobio}, \emph{Anguilla anguilla}, \emph{Phoxinus
+phoxinus}, \emph{Barbatula barbatula}, \emph{Gasterosteus aculeatus}),
+specimens were sacrificed and frozen for subsequent dissection.
+
+Gut contents analysis was performed on each sample occasion for the fish
+assemblage, whereas invertebrates had far less varied diets and were
+only characterised in May and October. Individuals of the benthos'
+numerically dominant or trophically important invertebrate taxa were
+taken from the Surber samples, dissected, and the contents of the
+foregut investigated for animal prey, which were recognised at
+\(400\times\) magnification by comparison with reference specimens. The
+taxa used to examine stomach contents covered more than 95\% of the
+individuals observed in the Benthos. Wherever possible, predators' gut
+contents were matched to species, and linear body dimensions were
+measured. Using established regression equations, the dry mass of prey
+items and invertebrate predators was calculated (Benke et al. 1999;
+Ganihar 1997; Burgherr and Meyer 1997; Gonzalez, Basaguren, and Pozo
+2002; Smock 1980; Edwards et al. 2009; MEYER 1989).
+
+\hypertarget{guampoe-coilaco-and-trancura-rivers-chile}{%
+\subsubsection{Guampoe, Coilaco and Trancura Rivers,
+Chile}\label{guampoe-coilaco-and-trancura-rivers-chile}}
+
+Three rivers (the Coilaco, Guampoe, and Trancura Rivers) in the
+catchment area of the Tolten River in south Chile, South America, were
+studied in a similar way. The Coilaco River (discharge 2.1--16.8
+\(m^3/s\)), Guampoe River (output 1.8--7.5 \(m^3/s\)), and Trancura
+River (discharge 8.8--49.3 \(m^3/s\)) are all pH 6.7--7.6 circumneutral
+rivers (Figueroa 2007).
+
+In each river, eight benthic samples were taken in each season between
+1984 and 1985, totaling 96 sample-units for the whole sampling period
+(Campos et al., 1985). Invertebrates were gathered using a Surber
+sampler (sampling area: 0.09 \(m^2\); mesh aperture 250 \(\mu m\)) and
+stored in 70\% ethanol before being transported to the lab for species
+identification and food web analysis.
+
+The feeding linkages were discovered by analysing the gut contents of
+all individuals observed in each sample. Large invertebrates had their
+guts removed and mounted in Euparal, whilst small specimens were mounted
+whole and studied with \(400\times\) magnification. Following Schmid
+(1993) and (Schmid-Araya et al. 2002), species prey items detected on
+each gut were identified using previously mounted reference slides.
+Using known regression equations (mentioned in Reiss and Schmid-Araya
+(2008); Baumgärtner and Rothhaupt (2003); Miserendino (2001); Woodward
+et al. (2010b)), all linear dimensions were translated to body mass
+estimates.
 
@@
 theory, specifically the contingency foraging model (MacArthur and
-Pianka 1966). The ADBM predicts the set of prey species a consumer
-should feed upon to maximise its rate of energy intake (Petchey et al.
-2008). The foraging variables in the model: energy content of the
-resources, handling times of the prey, space clearance rate and prey
-densities are allometrically scaled to the body sizes of the species.
-
-\hypertarget{broadstone-stream}{%
-\subsection{Broadstone Stream}\label{broadstone-stream}}
-
-Broadstone Stream (51\(^\circ\) 05' N 0\(^\circ\) 03' E; 120 m above
-sea-level) is a second-order tributary of the River Medway in south-east
-England. It is dominated by invertebrates as the acidity of the stream
-(pH 4.7-6.6) excludes fish. The stream consists of 25 common
-invertebrate species (Woodward, Speirs, and Hildrew 2005a). Among the
-predators, the three large species are \emph{Cordulegaster boltonii}
-Donovan, \emph{Sialis fuliginosa} Pict. and \emph{Plectrocnemia
-conspersa} {[}Curtis{]} and the three small species are the larvae of
-the tanypod midges \emph{Macropelopia nebulosa} {[}Meigen{]},
-\emph{Trissopelopia longimana} {[}Staeger{]}, and \emph{Zavrelimyia
-barbatipes} {[}Kieffer{]}. Broadstone Stream food web is one of the most
-completely described food webs available for any system (J. M.
-Schmid-Araya et al. 2002; Hildrew 2009; Layer et al. 2010; and Woodward,
-Speirs, and Hildrew 2005b).
-
-\hypertarget{celtic-sea}{%
-\subsection{Celtic Sea}\label{celtic-sea}}
-
-The Celtic Sea is an area of continental shelf bordered by Ireland, the
-UK and the Bay of Biscay. Precise sampling locations and dates were not
-given in the Barnes et al.~(2008) dataset, from where the data used in
-this chapter were extracted, so we pooled data over the whole time
-period and locations to capture general patterns. Only locations
-consistently sampled through the 1987--2001 time series were used
-(Blanchard et al., 2005).
-
-The feeding links of fishes in the Celtic Sea have been described in a
-published global dataset of individual predator and prey body sizes and
-taxonomy (Barnes et al., 2008): in total, 1988 feeding events from 29
-predator species were included in the food web presented here. The
-original stomach contents data were collected from dissections carried
-out on board research vessels during the annual surveys carried out by
-the Centre for Environment, Fisheries and Aquaculture Science (Cefas)
-(Pinnegar et al., 2003). Predator and prey length were recorded and
-converted to body mass by Barnes et al.~(2008) using published
-regression equations. Only vertebrate prey were identified and measured,
-with the vast majority being identified to species.
-
-\hypertarget{afon-hirnant}{%
-\subsection{Afon Hirnant}\label{afon-hirnant}}
-
-The Afon Hirnant is a tributary of the Welsh Dee in North Wales, U.K.
-(52\(^\circ\) 52'N 03\(^\circ\) 34) with the study being conducted at
-three sites. The pH within each site ranged from about 5.5 to 7 over the
-course of the year.
-
-A total of 180 invertebrate samples were collected for the whole
-sampling periods. All individuals within the benthic samples were
-counted and identified to the lowest possible taxonomic level (usually
-species). Prey items were identified using a combination of taxonomic
-keys and reference slides of previously identified species, after Jenny
-M. Schmid-Araya et al. (2002); J. M. Schmid-Araya et al. (2002).
-
-\hypertarget{tadnoll-brook}{%
-\subsection{Tadnoll Brook}\label{tadnoll-brook}}
-
-Description of Tadnoll Brook here
-
-\hypertarget{coilaco}{%
-\subsection{Coilaco}\label{coilaco}}
-
-Description of Coilaco here
-
-\hypertarget{guampoe}{%
-\subsection{Guampoe}\label{guampoe}}
-
-Description of Guampoe here
-
-\hypertarget{trancura}{%
-\subsection{Trancura}\label{trancura}}
-
-Description of Trancura here
-
-\hypertarget{food-web-construction}{%
-\subsection{Food web construction}\label{food-web-construction}}
-
-Presence and absence interactions of food web data can be aggregated in
-different ways (Gilljam et al. 2011). A common way of aggregating food
-web data is the taxonomic approach, where a species is defined as
-predating on another if at least one prey species individual was found
-in the gut of a predator species individual. Whereas in size-class food
-web, a feeding link was assigned if at least one prey item within a size
-class was found in the gut of a predator of another size class,
-irrespective of their taxonomy. In our study, we aggregate the food web
-on the basis of size class.
+Pianka 1966). We chose this model for various reasons, including because
+it uses the body size of organisms as input to predict feeding
+interactions, and because of our familiarity with it. The ADBM predicts
+the set of prey types (e.g.~species or sizes classes) a consumer should
+feed upon to maximise its rate of energy intake (Petchey et al. 2008).
+The foraging variables in the model are: energy content of the
+resources, handling times of the prey, space clearance rate, and prey
+densities. These are allometrically scaled to the body sizes of the
+species. Further details on the foraging rules defined in the ADBM and
+ADBM's predictive power across different food webs can be found in
+Petchey et al. (2008).
 
@@
 
-The accuracy of the predicted diet of the predators was defined using
+The accuracy of the predicted diet of the predators was measured using
 true skill statistic (TSS) which takes into account the true and false
@@
 (true negatives), \(b\) is the number of false positives, and \(c\) is
-the number of false negatives.
-
-The \(TSS\) ranges from \(-1\) to \(1\), where +1 indicates a perfect
-prediction. A \(TSS\) value of zero or less indicates a performance no
-better than random (Allouche, Tsoar, and Kadmon 2006).
+the number of false negatives. The \(TSS\) ranges from \(-1\) to \(1\),
+where +1 indicates a perfect prediction. A \(TSS\) value of zero or less
+indicates a performance no better than random (Allouche, Tsoar, and
+Kadmon 2006).
 
@@
 
-From a pool of gut content data, we draw a set of gut content data
-randomly. Then we used the rejection ABC to accept a parameter value
-from a prior distribution which would have resulted in the minimum
-distance, where distance = 1 - True skill statistic. The true skill
-statistic was computed between the predators' diet predicted from the
-ADBM, and that from the sampled gut content data. We repeated this
-process for \(n~(= 100)\) number of times for every \(i\) number of
-guts, where \(i\) lies between 1 and total number of gut content data in
-the pool.
+\textbf{Comment AG: Is it necessary to have the sections 1.1 and 1.2 of
+the supplementary information in the Supplementary information or shall
+the sections 1.1 and 1.2 be migrated to the main text (manuscript)?}
+
+From an empirical dataset of gut content data, we take a random sample
+of gut contents of specific size (see below) to create a partial gut
+content dataset. We then fit the ADBM to this partial dataset.
+
+\begin{figure}
+
+{\centering \includegraphics[width=500px]{../../manuscript/fig/ms_C2(1)}
+
+}
+
+\caption{\label{fig:fig_ra} (a, c, e, g, i, k, m) Accuracy of the predicted food web measured using the true skill statistics, predicted by the ADBM parameterised using gut content data.
+Line and shaded grey region represents the mean and the prediction interval of 100 independent samples respectively.
+Red line represents the number of predator guts required to achieve a TSS of 95\% of the maximum TSS.
+(b, d, f, h, j, l, n) Ratio of the true skill statistic of the predicted food web by the ADBM parameterised using gut content data to that of the predicted food web constructed using gut content data only.
+The dashed line shows where the ratio is one for reference.}\label{fig:unnamed-chunk-1}
+\end{figure}
+
+To fit the ADBM to a gut content dataset (be it complete or partial), we
+used the rejection ABC method we previously developed in Gupta, Furrer,
+and Petchey (2022) to accept a parameter value from a prior distribution
+which would have resulted in the minimum distance, where distance = 1 -
+True skill statistic. The true skill statistic was computed between the
+diets predicted from the ADBM, and those observed in the sampled gut
+content data. We repeated this process \(n~(= 100)\) times for every
+\(i\) number of guts, where \(i\) lies between 1 and total number of gut
+content data in the pool.
 
@@
   A pool of gut content data \(G: G = \{g_1, g_2, \dots, g_n\}\), where
-  \(g_{n}\) is a one-dimensional matrix containing ones and zeros.
+  \(g_{n}\) is the observed diet matrix containing ones and zeros.
 \item
@@
   \(model(\theta): ADBM(\theta) = \{d_{p_1}, d_{p_1}, \dots, d_{p_k}\}\),
-  where \(d_{p_k}\) is a one-dimensional diet matrix of predator \(k\)
+  where \(d_{p_k}\) is the predicted diet matrix of predator \(k\)
   containing ones and zeros.
 \item
-  A summary statistic \(s(x): s(x) \subseteq model(\theta)\)
-\item
-  A distance function \(d(x_i, y) : d(x_i,y) = 1 - TSS(x_i, y)\)
+  A summary statistic \(s(x): s(x) \subseteq model(\theta)\), where
+  \(s(x)\) is the diet of some or all of the predators.
+\item
+  A distance function \(d(x_i, y) : d(x_i,y) = 1 - TSS(x_i, y)\), which
+  quantifies how close the observed diet is to the predicted diet of
+  some or all of the predators.
 \item
   An observed food web
-  \(Y: Y = \{d_{p_1}', d_{p_1}', \dots, d_{p_k}'\}\)
+  \(Y: Y = \{d_{p_1}', d_{p_1}', \dots, d_{p_k}'\}\), where \(d_{p_k}'\)
+  is the observed diet matrix of predator \(k\) containing ones and
+  zeros.
 \end{itemize}
@@
 
-A prediction interval containing \(TSS\) between observed and predicted
-food webs for every \(i\) number of gut content data drawn from the pool
-of gut content data.
+The \(TSS\) between observed and predicted food webs, and the posterior
+parameter distributions for every \(i\) number of gut content data drawn
+from the pool of gut content data.
+
+\hypertarget{computing-the-minimum-gut-content-data}{%
+\subsection{Computing the minimum gut content
+data}\label{computing-the-minimum-gut-content-data}}
+
+Using TSS of the predicted food webs for different number of predator
+guts, we computed the number of gut content data that results in the
+mean TSS equal to the 95\% of the mean TSS achieved by the model using
+all the predator guts for a food web. We call this number of gut content
+data as the minimum gut content data.
 
@@
 
-We first present how the accuracy of the food web model vary in
-predicting trophic interactions when we increase the amount the gut
-content data provided to the food web model. Then, we calculate the
-number of gut content data for each food webs corresponding to which the
-accuracy results in 90\% of the maximum true skill statistics predicted
-by the food web model. We also compute the goodness of the food web
-model in predicting structural properties from incomplete gut content
-data. We did that by computing mean standardised error in food web
-properties.
+We first present how the accuracy of the food web model in predicting
+trophic interactions varies with increasing amount of gut content data
+provided to the food web model. Then, we calculate the number of gut
+content data for each food webs that results in accuracy equal to 95\%
+of the maximum true skill statistics predicted by the food web model.
 
@@
 subsets of gut content data improved quickly for lower number of
-predator guts (Fig. \ref{fig:fig_ra}) (a, c, e, g, i, k, m). The
-prediction interval of the true skill statistics reduced with the
-increasing number of predator guts with the mean TSS asymptoting to the
-maximum mean TSS achieved by the ADBM when all the gut content data was
-used. Although the maximum TSS varied among the food webs, the
-qualitative increase in the TSS was the same.
+predator guts (Fig. \ref{fig:fig_ra}) (a, c, e, g, i, k, m).
+Furthermore, the width of the prediction interval of the true skill
+statistics decreased with increasing number of predator guts with the
+mean TSS asymptoting to the maximum mean TSS achieved by the ADBM when
+all the gut content data was used. Although the maximum TSS varied among
+the food webs, the qualitative increase in the TSS was the same.
+
+For Broadstone Stream food web, with only 381 gut contents, which is
+38\% of the total gut content data, the ADBM predicted the food web with
+the mean TSS of 0.74 which was 95\% of the mean TSS (0.78) achieved
+using complete gut content data (Fig. \ref{fig:fig_ra}(a)). In case of
+the Celtic Sea food web, only 171 gut content data which is 35\% of the
+total gut content data was required by the ADBM to predict food web with
+TSS equal to 95\% of the mean TSS (0.68) achieved using complete gut
+content data (Fig. \ref{fig:fig_ra}(c)).
 
 For a low number of predator guts, the TSS of the model predicted food
-web was higher compared to the TSS of the food web constructed from gut
-content data (Fig. \ref{fig:fig_ra} (b, d, f, h, j, l, n)), recommending
-when a model can be used to compensate for undersampled links. After a
-certain increase in the number of predator guts, the ratio
-TSS(Model)/TSS(data) reduced to less than one, and reduced further
-gradually.
-
-With only 381 number of gut content data which is 38\% of the total gut
-content data, the ADBM predicted the food web with TSS of 0.74 which was
-95\% of the mean TSS (0.78) achieved using complete gut content data by
-the ADBM for Broadstone Stream food web (Fig. \ref{fig:fig_ra}(a)). In
-the case of the Celtic Sea food web, only 171 gut content data was
-required by the ADBM to predict food web with TSS equal to 95\% of the
-mean TSS (0.68) achieved using complete gut content data by the ADBM
-(Fig. \ref{fig:fig_ra}(c)).
-
-\hypertarget{dependence-of-minimum-gut-content-data-on-number-of-species-links-and-connectance}{%
-\subsection{Dependence of minimum gut content data on number of species,
+web was higher than the TSS of the food web constructed from gut content
+data only (Fig. \ref{fig:fig_ra} (b, d, f, h, j, l, n)). An increase in
+the number of predator guts did reduce the ratio TSS(Model)/TSS(data)
+reduced to less than one, and reduced further gradually. This shows that
+with less data available it is better to use the model, while if more
+data is available then it is better to use the data itself.
+
+\hypertarget{dependence-of-the-minimum-gut-content-data-on-number-of-links-and-connectance}{%
+\subsection{Dependence of the minimum gut content data on number of
 links and
-connectance}\label{dependence-of-minimum-gut-content-data-on-number-of-species-links-and-connectance}}
-
-There seems to be a positive relationship between number of minimum gut
-content data and number of species (S) (Fig. \ref{fig:fig_rb} (a)),
-links (L) (Fig. \ref{fig:fig_rb} (c)), connectance (C) (Fig.
-\ref{fig:fig_rb} (d)) and number of predator nodes (Fig.
-\ref{fig:fig_rb} (e)), with Broadstone Stream being an outlier in Fig.
-\ref{fig:fig_rb} (a, c, e). The number of minimum gut content data
-increases with number of maximum gut content data sampled (Fig.
-\ref{fig:fig_rb} (b)). There seems to be a negative relationship between
-proportion of minimum gut (= Number of minimum gut / Number of maximum
-guts sampled) and number of species (S) (Fig. \ref{fig:fig_rb} (f)),
-links (L) (Fig. \ref{fig:fig_rb} (g)), connectance (C) (Fig.
-\ref{fig:fig_rb} (h)).
+connectance}\label{dependence-of-the-minimum-gut-content-data-on-number-of-links-and-connectance}}
+
+There was a significant positive relationship between the minimum number
+of gut content data (i.e the amount of gut content data used in order to
+ensure 95\% of the maximum TSS) and the connectance of the food webs
+(Fig. \ref{fig:fig_rb} (a)). Similarly, we also observed a positive
+relationship between the minimum number of gut content data and the
+number of trophic links (L) in the food webs, however this relationship
+was not significant (Fig. \ref{fig:fig_rb} (b)). Furthermore, there was
+a significant positive relationship between the number of minimum gut
+content data and the the number of maximum gut content data sampled
+(Fig. \ref{fig:fig_rb} (c)) for food webs.
 
@@
 
-{\centering \includegraphics[width=500px]{../../results/misc/plot_min_gut_vs_X}
+{\centering \includegraphics[width=400px]{../../results/misc/plot_min_gut_vs_X}
 
@@
 
-\caption{\label{fig:fig_rb} (a, b, c, d, e) Number of minimum gut content data plotted against number of species (S), number of maximum guts sampled, number of links (L), connectance (C) and number of predator nodes respectively.
-(f, g, h) Proportion of minimum gut content data plotted against number of species (S), number of links (L) and connectance (C) respectively.}\label{fig:unnamed-chunk-3}
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics[width=500px]{../../results/misc/plot_empTSS_ngut}
-
-}
-
-\caption{\label{fig:fig_rc} True skill statistics of the food web constructed using gut content data plotted against number of gut content data.}\label{fig:unnamed-chunk-4}
+\caption{\label{fig:fig_rb} (a, b, c) Number of minimum gut content data (i.e the amount of gut content data used in order to ensure 95\% of the maximum TSS) plotted against number of links (L), connectance (C) and number of maximum guts sampled respectively.
+Solid lines are linear regression ((a) t = 3.138, df = 5, P = 0.0257; (b) t = 0.876, df = 5, P = 0.421; (c) t = 9.571, df = 5, P = 0.0002) and grey region represents 95\% confidence intervals.}\label{fig:unnamed-chunk-3}
 \end{figure}
@@
 
-\hypertarget{why-broadstone-stream-is-an-outlier}{%
-\subsection{Why Broadstone Stream is an
-outlier?}\label{why-broadstone-stream-is-an-outlier}}
-
-Broadstone Stream is the most sampled food web compared to all the other
-food webs (Fig. \ref{fig:fig_rc}), which means the observed Broadstone
-Stream food web might be more accurate compared to others.
+We have demonstrated how a food web model can be used to predict food
+webs reasonably well even when incomplete data about trophic
+interactions is available. At lower amount of gut content data,
+predicting with the model is better than using the data itself, while at
+higher amounts of gut content data, it is better to only use the data.
+This can help inform how much gut content data to actually collect when
+we are using a food web model to infer trophic interactions. A future
+development could be to make the same assessment using other food web
+models, and to also use food web data other than gut content data to
+parameterise those models.
 
@@
 
-\begin{itemize}
-\item
-  Model fills up the missing interactions
-\item
-  Partial data helps to constrain the parameter space
-\end{itemize}
-
-\hypertarget{there-is-uncertainty-in-gut-content-data-and-needs-to-be-propagated-into-models-predictions}{%
-\subsection{There is uncertainty in gut content data and needs to be
-propagated into model's
-predictions}\label{there-is-uncertainty-in-gut-content-data-and-needs-to-be-propagated-into-models-predictions}}
+In all of the seven food webs, the ADBM was able to infer the trophic
+interactions using incomplete gut content data because the presence
+absence information from the gut content data was still sufficient to
+constrain the possible model parameter values of the ADBM that best
+explained the predators' diets. Although in theory the ADBM can predict
+trophic interactions using only body sizes of organisms as it is based
+on set of foraging rule, it still requires some presence absence data to
+constrain the posterior parameter space thereby making more accurate
+predictions.
+
+\hypertarget{why-does-the-minimum-gut-data-differ-among-food-webs}{%
+\subsection{Why does the minimum gut data differ among food
+webs?}\label{why-does-the-minimum-gut-data-differ-among-food-webs}}
+
+We found the minimum amount of gut content data to vary across food webs
+and this could be due to the possibility that the food webs are sampled
+differently, i.e.~some food webs are more extensively sampled than
+others (SI Fig. S2). Furthermore, it is possible that interactions in
+some of the food webs are are more size-structured than others, and are
+therefore better predicted by the ADBM and consequently require a lower
+number of gut content data for model parameterisation.
+
+\hypertarget{model-fills-up-missing-interactions-and-guides-sampling-direction}{%
+\subsection{Model fills up missing interactions and guides sampling
+direction}\label{model-fills-up-missing-interactions-and-guides-sampling-direction}}
+
+When little data about trophic interactions is available, the model can
+be used to add data about interactions for which data is missing.
+Furthermore, the model predictions can be used as a guide to sample
+those predator guts for which we do not have enough information on the
+presence of interactions from the empirical gut content samples but the
+model suggests there are interactions. Therefore, with enough number of
+predator guts sampled one might possibly observe those missed
+interactions.
+
+\hypertarget{why-is-models-tss-less-than-one}{%
+\subsection{Why is model's TSS less than
+one?}\label{why-is-models-tss-less-than-one}}
+
+The food web model used (the ADBM) cannot explain all the interactions
+in any observed food web that it has been fit to. The foraging rules it
+encodes are based on the body size and have particular structure and
+assumptions; not all of these are met by all observed interactions. For
+example, the ADBM can only predict diets that are contiguous with
+respect to the size of prey. I.e. it cannot predict that a predator will
+consume taxa of size 1 and 3, and not taxa of size 2. Hence, if the
+observed diets are not contiguous when prey are ordered by their size,
+the estimation process could lead to a lower value of the TSS.
+
+Furthermore, the observed data may be missing links, e.g.~links that
+rarely occur. Hence the ADBM's maximum predicted true skill statistics
+is less than one for all food webs it has so far been fit to.
+
+\hypertarget{tssmodeltssdata-for-different-food-webs}{%
+\subsection{TSS(Model)/TSS(Data) for different food
+webs}\label{tssmodeltssdata-for-different-food-webs}}
+
+In all the food webs, the ratio TSS(Model)/TSS(Data) decreased with
+increasing number of predator guts (Fig. \ref{fig:fig_ra} (b, d, f, h,
+j, l, n)). This suggests when less data is available it is better to use
+the model and when more data is available it is better to only use the
+data to predict trophic interactions. At lower number of predator guts
+the model fills up the missing interactions that were not observed in
+the gut content data, therefore resulting in model performing better as
+compared to data alone. Wile at higher number of predator guts the model
+is probably predicting some presence or absence of links i.e.~false
+positives and false negatives resulting in a lower TSS as compared to
+that of data alone.
+
+\hypertarget{propagating-uncertainty-from-gut-content-data-to-models-predictions}{%
+\subsection{Propagating uncertainty from gut content data to model's
+predictions}\label{propagating-uncertainty-from-gut-content-data-to-models-predictions}}
 
@@
 Some studies have presented how the accuracy of food web prediction
-change when we vary the amount of food web data (Gray et al. 2015).
+change when we vary the amount of food web data (Gray et al. 2015). For
+example: Desjardins-Proulx et al. (2017) has used predictive machine
+learning models and Caron et al. (2022) has used predictive traits-based
+models on partial knowledge of interactions to reconstruct a food web
+accurately, in contrast to our study where we used a mechanistic food
+web model.
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  Dependent on how size structured a food web is, how the food web is
-  aggregated, the type of interactions
-\end{itemize}
+In our study, we have implemented the approach only with the ADBM.
+However, in principle, this approach could be extended to other food web
+models such as (Williams and Martinez 2000; Gravel et al. 2013;
+Allesina, Alonso, and Pascual 2008). A future prospect could be to study
+how well different food web models' prediction accuracy vary with
+different amount of gut content data. This can also help in making
+decision as to which food web model to chose from for a given a set of
+gut content data. We suspect the relationship (i.e shape of the curve)
+between the TSS of the predicted food web and the number of predator
+guts might vary within food web models.
 
@@
 
-Our study is based on the assumption that the food web constructed using
-the complete gut content data is the true food web. However, it might
-not be the case as the links are still under-sampled for many nodes
-(Woodward et al. 2010). This could result in a lower TSS of the
-predicted food web from the model which can lead to a higher upper limit
-on the amount of gut content data.
-
-\hypertarget{limitation-of-the-model}{%
-\subsection{Limitation of the model}\label{limitation-of-the-model}}
-
-The maximum predictive power of a model is constrained by the rules it
-is based on.
-
-\hypertarget{how-can-we-include-other-food-web-data-type}{%
-\subsection{How can we include other food web data
-type?}\label{how-can-we-include-other-food-web-data-type}}
-
-A future prospect would be to include other types of food web data
-
-\begin{itemize}
-\item
-  experimentation (feeding trials)
-\item
-  DNA Metabarcoding
-\end{itemize}
-
-\hypertarget{extending-the-approach-to-other-food-web-models}{%
-\subsection{Extending the approach to other food web
-models}\label{extending-the-approach-to-other-food-web-models}}
-
-\begin{itemize}
-\tightlist
-\item
-  Current approach could be implemented with other food web models
-\end{itemize}
-
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
-
-\hypertarget{supplementary-information}{%
-\section{Supplementary Information}\label{supplementary-information}}
-
-\hypertarget{gut-content-data-simulation}{%
-\subsection{Gut content data
-simulation}\label{gut-content-data-simulation}}
-
-We simulated a food web using the ADBM for a given set of parameters.
-For a given set of predators, we subset the diet from the simulated food
-web. Then using a probability mass function (distribution), we sampled
-the gut content data from predators' diet thereby incorporating the
-uncertainty in the gut content data. We repeated this process multiple
-number of times for every predator in the food web.
-
-\emph{Input:}
-
-\begin{itemize}
-\item
-  Predators whose diet are to be simulated \(P = \{p_1, \dots, p_n\}\)
-\item
-  A simulated food web
-  \(ADBM(\theta_i) = \{d_{p_1}, d_{p_1}, \dots, d_{p_k}\}\), where
-  \(d_{p_k}\) is a one-dimensional diet matrix of predator \(k\)
-  containing ones and zeros.
-\item
-  A function which describes uncertainty in the diet \(U(d)\)
-\item
-  Number of independent guts to be simulated for a predator
-  \(p_i: ngut\)
-\end{itemize}
-
-\emph{Sampling:}
-
-\begin{itemize}
-\item
-  for \(p_i \in P\)
-
-  \begin{itemize}
-  \item
-    for \(j = 1, \dots, ngut\), where \(ngut\) is the number of guts to
-    be simulated
-
-    \begin{itemize}
-    \tightlist
-    \item
-      Simulate a single gut of a predator
-      \(p_i: g(p_i) = d_{p_i} * U(d_{p_i})\)
-    \end{itemize}
-  \item
-    Set of gut of a predator
-    \(p_i: G(p_i) = \{ g(p_i) : g(p_i) = d_{p_i}*U(d_{p_i}) \}\)
-  \end{itemize}
-\end{itemize}
-
-\emph{Output:}
-
-\begin{itemize}
-\tightlist
-\item
-  We simulated a pool of gut content data which contains simulated gut
-  content data \(G(p_i)\) for every predator \(p_i\)
-\end{itemize}
-
-\hypertarget{prediction-using-simulated-gut-content-data-from-a-simulated-food-web}{%
-\subsection{Prediction using simulated gut content data from a simulated
-food
-web}\label{prediction-using-simulated-gut-content-data-from-a-simulated-food-web}}
-
-\begin{figure}
-
-{\centering \includegraphics[width=400px]{../fig/TSS_with_n_pred_prop_simulated}
-
-}
-
-\caption{\label{fig:fig_r0} True skill statistics between predicted food web and observed food web for a simulated small reef food web estimated for distinct predator guts in a sample.
-The observed simulated food web consists of 50 species and \dots links.
-The vertical bars correspond to the prediction intervals of the true skill statistics with filled circles representing the corresponding mean.
-A prediction interval of the TSS is formed using a set of 100 accepted TSS values using the ABC method.}\label{fig:fig_r0}
-\end{figure}
-
-The true skill statistics (TSS) between the predicted food web and
-observed food web saturated with an increasing number of distinct
-predator guts in a sample (Fig. \ref{fig:fig_r0}). The TSS of the
-predicted food webs estimated using the complete individual gut data had
-shorter prediction intervals resulting in less uncertainty, and higher
-mean TSS than that using the partial individual gut data. The maximum
-limit of the prediction interval of TSS estimated using the complete gut
-data and the partial gut data were almost equal, with the minimum limit
-of the prediction interval of TSS using partial gut data being lower
-than that from the complete gut data. Eventually, the gap between the
-mean TSS using the partial gut data and the complete gut data reduced
-with an increasing number of distinct predator guts suggesting when we
-have enough predator species' gut data, the achieved TSS was almost
-constant and hence independent of the amount of gut data.
-
-The maximum TSS estimated using the complete gut data was very close to
-one and almost remained constant with an increasing number of different
-predator species sampled. With the gut data sample of only five distinct
-predator species, 95\% of the maximum mean TSS was achieved when
-complete individual gut data was used, while the same was achieved with
-15 predator species for partial gut data. This shows that one does not
-need to know the gut data of all the species to predict the food web and
-the accuracy is dependent on the completeness of an individual gut data.
-
-\begin{figure}
-
-{\centering \includegraphics[width=300px]{../fig/TSS_with_n_pred_prop}
-
-}
-
-\caption{\label{fig:fig_r3} True skill statistics between predicted food web and observed food web estimated for different number of distinct predator guts.
-The estimation is done for three sets of gut data: gut content data of predators whose body sizes are smaller than the mean body size, larger than the mean body size, and all the gut content data.}\label{fig:fig_r3}
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics[width=500px]{../../results/misc/TSS_model_vs_data}
-
-}
-
-\caption{\label{fig:fig_r31} True skill statistic between predicted food web using ADBM and incomplete gut content data, and observed food web against the true skill statistic between food web constructed using incomplete gut content data, and observed food web.
-Error bars represent prediction intervals of 100 independent samples.
-Dashed line is 1:1 line for reference.}\label{fig:fig_r31}
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics[width=500px]{../../results/misc/mse_model_vs_data}
-
-}
-
-\caption{\label{fig:fig_r32} Mean standardised error in structural properties in the food web predicted using ADBM and incomplete gut content data against structural properties in the predicted food web constructed using incomplete gut content data.
-Error bars represent prediction intervals of 100 independent samples.
-Dashed line is 1:1 line for reference.}\label{fig:fig_r32}
-\end{figure}
+Some of the food webs are not very well predicted using the ADBM. And
+this could possibly result in a lower value of minimum gut content data
+that was used to achieve 95\% of the maximum TSS. This could be because
+our study is based on the assumption that the true food webs is the one
+which was constructed using the total gut content data. However, if the
+total gut content does not contain sufficient information to construct
+the complete food web, then the food web will miss some links. This
+would therefore result in a lower TSS of the predicted food web, which
+can eventually lead to a lower estimate of the minimum gut content data.
+A future prospect could be to incorporate other sources of
+presence-absence data such as stable isotope ratio, metabarcoding to
+complement any links that were missed by the gut content method.
+
+\hypertarget{how-can-we-include-other-types-of-food-web-data}{%
+\subsection{How can we include other types of food web
+data?}\label{how-can-we-include-other-types-of-food-web-data}}
+
+A future prospect would be to include other types of food web data along
+with gut content simultaneously to parameterise the ADBM. For example,
+one could use the approximate trophic position inferred from stable
+isotope ratio data from a tissue of an individual and gut content data
+of a different predator simultaneously to parameterise a food web model
+such as the ADBM. In this case, trophic position would be an additional
+summary statistic required in the parameterisation method. This
+combination of different types of data about trophic interactions could
+be particularly useful when only a limited amount of diet information
+can be extracted by using a single method.
 
@@
 
-\hypertarget{references}{%
-\section{References}\label{references}}
+\hypertarget{reference}{%
+\section*{Reference}\label{reference}}
+\addcontentsline{toc}{section}{Reference}
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-allesinaGeneralModelFood2008}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-allesinaGeneralModelFood2008}{}}%
 Allesina, Stefano, David Alonso, and Mercedes Pascual. 2008. {``A
@@
 
-\leavevmode\hypertarget{ref-alloucheAssessingAccuracySpecies2006}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-alloucheAssessingAccuracySpecies2006}{}}%
 Allouche, Omri, Asaf Tsoar, and Ronen Kadmon. 2006. {``Assessing the
@@
 
-\leavevmode\hypertarget{ref-bakerFishGutContent2014}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bakerFishGutContent2014}{}}%
 Baker, Ronald, Amanda Buckland, and Marcus Sheaves. 2014. {``Fish Gut
@@
 
-\leavevmode\hypertarget{ref-cohenSoilInvertebratesChemistry2014}{}%
-Cohen, Joel E., and Christian Mulder. 2014. {``Soil Invertebrates,
+\leavevmode\vadjust pre{\hypertarget{ref-barnesPredatorPreyBody2008}{}}%
+Barnes, C., D. M. Bethea, R. D. Brodeur, J. Spitz, V. Ridoux, C.
+Pusineri, B. C. Chase, et al. 2008. {``Predator and {Prey Body Sizes} in
+{Marine Food Webs}.''} \emph{Ecology} 89 (3): 881--81.
+\url{https://doi.org/10.1890/07-1551.1}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-baumgartnerPredictiveLengthDry2003}{}}%
+Baumgärtner, Daniel, and Karl-Otto Rothhaupt. 2003. {``Predictive
+{Length}--{Dry Mass Regressions} for {Freshwater Invertebrates} in a
+{Pre-Alpine Lake Littoral}.''} \emph{International Review of
+Hydrobiology} 88 (5): 453--63.
+\url{https://doi.org/10.1002/iroh.200310632}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-benkeLengthMassRelationshipsFreshwater1999}{}}%
+Benke, Arthur C., Alexander D. Huryn, Leonard A. Smock, and J. Bruce
+Wallace. 1999. {``Length-{Mass Relationships} for {Freshwater
+Macroinvertebrates} in {North America} with {Particular Reference} to
+the {Southeastern United States}.''} \emph{Journal of the North American
+Benthological Society} 18 (3): 308--43.
+\url{https://doi.org/10.2307/1468447}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-blanchardClimateFishingInfluence2005}{}}%
+Blanchard, Julia L., Nicholas K. Dulvy, Simon Jennings, James R. Ellis,
+John K. Pinnegar, Alex Tidd, and Laurence T. Kell. 2005. {``Do Climate
+and Fishing Influence Size-Based Indicators of {Celtic Sea} Fish
+Community Structure?''} \emph{ICES Journal of Marine Science} 62 (3):
+405--11. \url{https://doi.org/10.1016/j.icesjms.2005.01.006}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-burgherrRegressionAnalysisLinear1997}{}}%
+Burgherr, Peter, and Elisabeth I. Meyer. 1997. {``Regression Analysis of
+Linear Body Dimensions Vs. Dry Mass in Stream Macroinvertebrates.''}
+\emph{Archiv Für Hydrobiologie}, April, 101--12.
+\url{https://doi.org/10.1127/archiv-hydrobiol/139/1997/101}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-caronAddressingEltonianShortfall}{}}%
+Caron, Dominique, Luigi Maiorano, Wilfried Thuiller, and Laura J.
+Pollock. 2022. {``Addressing the {Eltonian} Shortfall with Trait-Based
+Interaction Models.''} \emph{Ecology Letters} n/a (n/a).
+\url{https://doi.org/10.1111/ele.13966}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cohenSoilInvertebratesChemistry2014}{}}%
+Cohen, Joel E., and Christian Mulder. 2014a. {``Soil Invertebrates,
 Chemistry, Weather, Human Management, and Edaphic Food Webs at 135 Sites
@@
 
-\leavevmode\hypertarget{ref-cohenStochasticTheoryCommunity1985}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-cohen2014}{}}%
+---------. 2014b. {``Soil Invertebrates, Chemistry, Weather, Human
+Management, and Edaphic Food Webs at 135 Sites in The Netherlands:
+SIZEWEB.''} \emph{Ecology} 95 (2): 578--78.
+\url{https://doi.org/10.1890/13-1337.1}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cohenStochasticTheoryCommunity1985}{}}%
 Cohen, Joel E., C. M. Newman, and John Hyslop Steele. 1985. {``A
@@
 
-\leavevmode\hypertarget{ref-crawfordApplicationsStableIsotope2008}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-crawfordApplicationsStableIsotope2008}{}}%
 Crawford, Kerry, Robbie A. Mcdonald, and Stuart Bearhop. 2008.
@@
 
-\leavevmode\hypertarget{ref-dixonAssessingDietNorth2017}{}%
-Dixon, Heather J., J. Brian Dempson, Timothy F. Sheehan, Mark D.
-Renkawitz, and Michael Power. 2017. {``Assessing the Diet of {North
-American Atlantic} Salmon ({Salmo} Salar {L}.) Off the {West Greenland}
-Coast Using Gut Content and Stable Isotope Analyses.''} \emph{Fisheries
-Oceanography} 26 (5): 555--68. \url{https://doi.org/10.1111/fog.12216}.
-
-\leavevmode\hypertarget{ref-dunneNetworkStructureBiodiversity2002}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-desjardins-proulxEcologicalInteractionsNetflix2017}{}}%
+Desjardins-Proulx, Philippe, Idaline Laigle, Timoth'ee Poisot, and
+Dominique Gravel. 2017. {``Ecological Interactions and the {Netflix}
+Problem.''} \emph{PeerJ} 5 (August): e3644.
+\url{https://doi.org/10.7717/peerj.3644}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-dunneNetworkStructureBiodiversity2002}{}}%
 Dunne, Jennifer A., Richard J. Williams, and Neo D. Martinez. 2002.
@@
 
-\leavevmode\hypertarget{ref-eitzingerTestingValidityFunctional2018}{}%
-Eitzinger, Bernhard, Björn C. Rall, Michael Traugott, and Stefan Scheu.
-2018. {``Testing the Validity of Functional Response Models Using
-Molecular Gut Content Analysis for Prey Choice in Soil Predators.''}
-\emph{Oikos} 127 (7): 915--26. \url{https://doi.org/10.1111/oik.04885}.
-
-\leavevmode\hypertarget{ref-gilljamSeeingDouble2011}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-edwardsRelationshipLengthMass2009}{}}%
+Edwards, François K. Lauridsen, Lucie Armand, Helen M. Vincent, and Iwan
+J. Jones. 2009. {``The Relationship Between Length, Mass and
+Preservation Time for Three Species of Freshwater Leeches
+({Hirudinea}).''} \emph{Fundamental and Applied Limnology} 173 (4):
+321--27. \url{https://doi.org/10.1127/1863-9135/2009/0173-0321}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-figueroaFoodWebDynamics2007}{}}%
+Figueroa, David. 2007. {``Food Web Dynamics : New Patterns from Southern
+{South America} and {North Wales UK}, and the Role of Basal Species
+Structuring Food Webs.''} PhD thesis, {University of London}.
+\url{https://ethos.bl.uk/OrderDetails.do?uin=uk.bl.ethos.582554}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-ganiharBiomassEstimatesTerrestrial1997}{}}%
+Ganihar, S. R. 1997. {``Biomass Estimates of Terrestrial Arthropods
+Based on Body Length.''} \emph{Journal of Biosciences} 22 (2): 219--24.
+\url{https://doi.org/10.1007/BF02704734}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-gilljamSeeingDouble2011}{}}%
 Gilljam, David, Aaron Thierry, Francois K. Edwards, David Figueroa,
@@
 
-\leavevmode\hypertarget{ref-goldwasserConstructionAnalysisLarge1993a}{}%
-Goldwasser, Lloyd, and Jonathan Roughgarden. 1993. {``Construction and
+\leavevmode\vadjust pre{\hypertarget{ref-goldwasserConstructionAnalysisLarge1993a}{}}%
+Goldwasser, Lloyd, and Jonathan Roughgarden. 1993a. {``Construction and
 {Analysis} of a {Large Caribbean Food Web}.''} \emph{Ecology} 74 (4):
@@
 
-\leavevmode\hypertarget{ref-gravelInferringFoodWeb2013}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-goldwasser1993}{}}%
+---------. 1993b. {``Construction and Analysis of a Large Caribbean Food
+Web.''} \emph{Ecology} 74 (4): 1216--33.
+\url{https://doi.org/10.2307/1940492}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-gonzalezSizemassRelationshipsStream}{}}%
+Gonzalez, Jose M, Ana Basaguren, and Jesus Pozo. 2002. {``Size-Mass
+Relationships of Stream Invertebrates in a Northern {Spain} Stream,''}
+7.
+
+\leavevmode\vadjust pre{\hypertarget{ref-ogormanSimpleModelPredicts2019}{}}%
+Gorman, Eoin J. O', Owen L. Petchey, Katy J. Faulkner, Bruno Gallo,
+Timothy A. C. Gordon, Joana Neto-Cerejeira, J'on S. 'Olafsson, Doris E.
+Pichler, Murray S. A. Thompson, and Guy Woodwar. 2019. {``A Simple Model
+Predicts How Warming Simplifies Wild Food Webs.''} \emph{Nature Climate
+Change} 9 (8, 8): 611--16.
+\url{https://doi.org/10.1038/s41558-019-0513-x}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-gravelInferringFoodWeb2013}{}}%
 Gravel, Dominique, Timoth'ee Poisot, Camille Albouy, Laure Velez, and
@@
 
-\leavevmode\hypertarget{ref-grayJoiningDotsAutomated2015}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-grayJoiningDotsAutomated2015}{}}%
 Gray, Clare, David H. Figueroa, Lawrence N. Hudson, Athen Ma, Dan
@@
 
-\leavevmode\hypertarget{ref-hattabForecastingFinescaleChanges2016}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-guptaSimultaneouslyEstimatingFood2022}{}}%
+Gupta, Anubhav, Reinhard Furrer, and Owen L. Petchey. 2022.
+{``Simultaneously Estimating Food Web Connectance and Structure with
+Uncertainty.''} \emph{Ecology and Evolution} 12 (3): e8643.
+\url{https://doi.org/10.1002/ece3.8643}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hattabForecastingFinescaleChanges2016}{}}%
 Hattab, Tarek, Fabien Leprieur, Frida Ben Rais Lasram, Dominique Gravel,
@@
 
-\leavevmode\hypertarget{ref-hildrewChapterSustainedResearch2009}{}%
-Hildrew, Alan G. 2009. {``Chapter 4 {Sustained Research} on {Stream
-Communities}.''} In \emph{Advances in {Ecological Research}},
-41:175--312. {Elsevier}.
-\url{https://doi.org/10.1016/S0065-2504(09)00404-8}.
-
-\leavevmode\hypertarget{ref-hyslopStomachContentsAnalysis1980}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-hyslopStomachContentsAnalysis1980}{}}%
 Hyslop, E. J. 1980. {``Stomach Contents Analysis---a Review of Methods
@@
 
-\leavevmode\hypertarget{ref-jordanKeystoneSpeciesFood2009}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-jenningsTrophicLevelsMarine2015}{}}%
+Jennings, Simon, and Johan van der Molen. 2015. {``Trophic Levels of
+Marine Consumers from Nitrogen Stable Isotope Analysis: Estimation and
+Uncertainty.''} \emph{ICES Journal of Marine Science} 72 (8):
+2289--2300. \url{https://doi.org/10.1093/icesjms/fsv120}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-jordanKeystoneSpeciesFood2009}{}}%
 Jord'an, Ferenc. 2009. {``Keystone Species and Food Webs.''}
@@
 
-\leavevmode\hypertarget{ref-kadoyaIsoWebBayesianIsotope2012}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-kadoyaIsoWebBayesianIsotope2012}{}}%
 Kadoya, Taku, Yutaka Osada, and Gaku Takimoto. 2012. {``{IsoWeb}: {A
@@
 
-\leavevmode\hypertarget{ref-layerFoodWebStructure2010}{}%
-Layer, Katrin, Jens O. Riede, Alan G. Hildrew, and Guy Woodward. 2010.
-{``Food {Web Structure} and {Stability} in 20 {Streams Across} a {Wide
-pH Gradient}.''} In \emph{Advances in {Ecological Research}},
-42:265--99. {Elsevier}.
-\url{https://doi.org/10.1016/B978-0-12-381363-3.00005-8}.
-
-\leavevmode\hypertarget{ref-laymanCanStableIsotope2007}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-kellyUsingEnvironmentalDNA2014}{}}%
+Kelly, Ryan P., Jesse A. Port, Kevan M. Yamahara, and Larry B. Crowder.
+2014. {``Using {Environmental DNA} to {Census Marine Fishes} in a {Large
+Mesocosm}.''} \emph{PLOS ONE} 9 (1): e86175.
+\url{https://doi.org/10.1371/journal.pone.0086175}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-laymanCanStableIsotope2007}{}}%
 Layman, Craig A., D. Albrey Arrington, Carmen G. Montaña, and David M.
@@
 
-\leavevmode\hypertarget{ref-lindegrenEcologicalForecastingClimate2010}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-lindegrenEcologicalForecastingClimate2010}{}}%
 Lindegren, Martin, Christian Möllmann, Anders Nielsen, Keith Brander,
@@
 
-\leavevmode\hypertarget{ref-macarthurOptimalUsePatchy1966}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-macarthurOptimalUsePatchy1966}{}}%
 MacArthur, Robert H., and Eric R. Pianka. 1966. {``On {Optimal Use} of a
 {Patchy Environment}.''} \emph{The American Naturalist} 100 (916):
-603--9. \url{http://www.jstor.org/stable/2459298}.
-
-\leavevmode\hypertarget{ref-mcclain-countsTrophicStructureMesopelagic2017b}{}%
-McClain-Counts, Jennifer P., Amanda W. J. Demopoulos, and Steve W. Ross.
-2017. {``Trophic Structure of Mesopelagic Fishes in the {Gulf} of
-{Mexico} Revealed by Gut Content and Stable Isotope Analyses.''} Journal
-Article. \emph{Marine Ecology} 38 (4).
-\url{https://doi.org/10.1111/maec.12449}.
-
-\leavevmode\hypertarget{ref-ogormanSimpleModelPredicts2019}{}%
-O'NAGorman, Eoin J., Owen L. Petchey, Katy J. Faulkner, Bruno Gallo,
-Timothy A. C. Gordon, Joana Neto-Cerejeira, J'on S. 'Olafsson, Doris E.
-Pichler, Murray S. A. Thompson, and Guy Woodwar. 2019. {``A Simple Model
-Predicts How Warming Simplifies Wild Food Webs.''} \emph{Nature Climate
-Change} 9 (8, 8): 611--16.
-\url{https://doi.org/10.1038/s41558-019-0513-x}.
-
-\leavevmode\hypertarget{ref-omalleyEffectsFoodWeb2017}{}%
-O'NAMalley, Brian P., Lars G. Rudstam, James M. Watkins, Toby J. Holda,
-and Brian C. Weide. 2017. {``Effects of Food Web Changes on {Mysis}
-Diluviana Diet in {Lake Ontario}.''} \emph{Journal of Great Lakes
-Research}, Special {section} on {Lake Ontario CSMI} 2013, 43 (5):
-813--22. \url{https://doi.org/10.1016/j.jglr.2017.02.003}.
-
-\leavevmode\hypertarget{ref-peralta-maraverStructureDynamicsStability2017}{}%
+603--9. \url{https://www.jstor.org/stable/2459298}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-meyerRelationshipBodyLength1989}{}}%
+MEYER, E. 1989. {``The Relationship Between Body Length Parameters and
+Dry Mass in Running Water Invertebrates.''} \emph{Arch Hydrobiol} 117:
+191--203. \url{https://ci.nii.ac.jp/naid/10019557615/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-miserendinoRelacionesLongitudpesoPara2001}{}}%
+Miserendino, Mar'ıa L. 2001. {``Relaciones Longitud-Peso Para
+Macroinvertebrados de Ambientes Dulceacuícolas de {Patagonia}
+({Argentina}).''} \emph{Ecología Austral} 11 (1): 3--8.
+\url{http://www.scielo.org.ar/scielo.php?script=sci_abstract\&pid=S1667-782X2001000100002\&lng=es\&nrm=iso\&tlng=es}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-nielsen2018}{}}%
+Nielsen, Jens M., Elizabeth L. Clare, Brian Hayden, Michael T. Brett,
+and Pavel Kratina. 2018. {``Diet Tracing in Ecology: Method Comparison
+and Selection.''} Edited by M. Thomas P. Gilbert. \emph{Methods in
+Ecology and Evolution} 9 (2): 278--91.
+\url{https://doi.org/10.1111/2041-210X.12869}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-peralta-maraverStructureDynamicsStability2017}{}}%
 Peralta-Maraver, I., M. J. Lopez-Rodriguez, and J. M. Tierno de
@@
 
-\leavevmode\hypertarget{ref-petcheySizeForagingFood2008}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-petcheySizeForagingFood2008}{}}%
 Petchey, Owen L., Andrew P. Beckerman, Jens O. Riede, and Philip H.
@@
 
-\leavevmode\hypertarget{ref-rindorfBiasEstimatingFood2004}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-pinnegarDoesDietCeltic2003}{}}%
+Pinnegar, J. K., V. M. Trenkel, A. N. Tidd, W. A. Dawson, and M. H. Du
+buit. 2003. {``Does Diet in {Celtic Sea} Fishes Reflect Prey
+Availability?''} \emph{Journal of Fish Biology} 63 (s1): 197--212.
+\url{https://doi.org/10.1111/j.1095-8649.2003.00204.x}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-pompanonWhoEatingWhat2012}{}}%
+Pompanon, Francois, Bruce E. Deagle, William O. C. Symondson, David S.
+Brown, Simon N. Jarman, and Pierre Taberlet. 2012. {``Who Is Eating
+What: Diet Assessment Using Next Generation Sequencing.''}
+\emph{Molecular Ecology} 21 (8): 1931--50.
+\url{https://doi.org/10.1111/j.1365-294X.2011.05403.x}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-reissExistingPlentyAbundance2008}{}}%
+Reiss, Julia, and Jenny M. Schmid-Araya. 2008. {``Existing in Plenty:
+Abundance, Biomass and Diversity of Ciliates and Meiofauna in Small
+Streams.''} \emph{Freshwater Biology} 53 (4): 652--68.
+\url{https://doi.org/10.1111/j.1365-2427.2007.01907.x}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rindorfBiasEstimatingFood2004}{}}%
 Rindorf, A, and P Lewy. 2004. {``Bias in Estimating Food Consumption of
@@
 
-\leavevmode\hypertarget{ref-roslinUseDNABarcodes2016}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-roslinUseDNABarcodes2016}{}}%
 Roslin, Tomas, and Sanna Majaneva. 2016. {``The Use of {DNA} Barcodes in
@@
 
-\leavevmode\hypertarget{ref-schmid-arayaImportanceMeiofaunaFood2002}{}%
-Schmid-Araya, J. M., A. G. Hildrew, A. Robertson, P. E. Schmid, and J.
-Winterbottom. 2002. {``The {Importance} of {Meiofauna} in {Food Webs}:
-{Evidence} from an {Acid Stream}.''} \emph{Ecology} 83 (5): 1271--85.
-\url{https://doi.org/10.1890/0012-9658(2002)083\%5B1271:TIOMIF\%5D2.0.CO;2}.
-
-\leavevmode\hypertarget{ref-schmid-arayaConnectanceStreamFood2002}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-schmid-arayaConnectanceStreamFood2002}{}}%
 Schmid-Araya, Jenny M., Peter E. Schmid, Anne Robertson, Julie
@@
 {``Connectance in {Stream Food Webs}.''} \emph{Journal of Animal
-Ecology} 71 (6): 1056--62. \url{http://www.jstor.org/stable/1555780}.
-
-\leavevmode\hypertarget{ref-tamaddoni-nezhadConstructionValidationFood2013}{}%
+Ecology} 71 (6): 1056--62. \url{https://www.jstor.org/stable/1555780}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-smockRelationshipsBodySize1980}{}}%
+Smock, Leonard A. 1980. {``Relationships Between Body Size and Biomass
+of Aquatic Insects.''} \emph{Freshwater Biology} 10 (4): 375--83.
+\url{https://doi.org/10.1111/j.1365-2427.1980.tb01211.x}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-tamaddoni-nezhadConstructionValidationFood2013}{}}%
 Tamaddoni-Nezhad, Alireza, Ghazal Afroozi Milani, Alan Raybould, Stephen
@@
 
-\leavevmode\hypertarget{ref-warrenSpatialTemporalVariation1989}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-wadaUseStableIsotopes1991}{}}%
+Wada, E., H. Mizutani, and M. Minagawa. 1991. {``The Use of Stable
+Isotopes for Food Web Analysis.''} \emph{Critical Reviews in Food
+Science and Nutrition} 30 (4): 361--71.
+\url{https://doi.org/10.1080/10408399109527547}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-warrenSpatialTemporalVariation1989}{}}%
 Warren, Philip H. 1989. {``Spatial and {Temporal Variation} in the
@@
 
-\leavevmode\hypertarget{ref-woodwardIndividualBasedFoodWebs2010}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-wilkinsonFAIRGuidingPrinciples2016}{}}%
+Wilkinson, Mark D., Michel Dumontier, IJsbrand Jan Aalbersberg,
+Gabrielle Appleton, Myles Axton, Arie Baak, Niklas Blomberg, et al.
+2016. {``The {FAIR Guiding Principles} for Scientific Data Management
+and Stewardship.''} \emph{Scientific Data} 3 (1, 1): 160018.
+\url{https://doi.org/10.1038/sdata.2016.18}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-williamsSimpleRulesYield2000}{}}%
+Williams, Richard J., and Neo D. Martinez. 2000. {``Simple Rules Yield
+Complex Food Webs.''} \emph{Nature} 404 (6774, 6774): 180--83.
+\url{https://doi.org/10.1038/35004572}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-woodwardIndividualBasedFoodWebs2010}{}}%
 Woodward, Guy, Julia Blanchard, Rasmus B. Lauridsen, Francois K.
 Edwards, J. Iwan Jones, David Figueroa, Philip H. Warren, and Owen L.
-Petchey. 2010. {``Individual-{Based Food Webs}.''} In \emph{Advances in
+Petchey. 2010b. {``Individual-{Based Food Webs}.''} In \emph{Advances in
 {Ecological Research}}, 43:211--66. {Elsevier}.
@@
 
-\leavevmode\hypertarget{ref-woodwardQuantificationResolutionComplex2005}{}%
-Woodward, Guy, Dougie C. Speirs, and Alan G. Hildrew. 2005a.
+\leavevmode\vadjust pre{\hypertarget{ref-woodward2010}{}}%
+---------. 2010a. {``Individual-Based Food Webs.''} In, 43:211--66.
+Elsevier. \url{https://doi.org/10.1016/B978-0-12-385005-8.00006-X}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-woodwardChapterIndividualBasedFood2010}{}}%
+---------. 2010c. {``Chapter 6 - {Individual}-{Based Food Webs}:
+{Species Identity}, {Body Size} and {Sampling Effects}.''} In
+\emph{Advances in {Ecological Research}}, edited by Guy Woodward,
+43:211--66. Integrative {Ecology}: {From Molecules} to {Ecosystems}.
+{Academic Press}.
+\url{https://doi.org/10.1016/B978-0-12-385005-8.00006-X}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-woodwardBodysizeDeterminantsNiche2002}{}}%
+Woodward, Guy, and Alan G. Hildrew. 2002. {``Body-Size Determinants of
+Niche Overlap and Intraguild Predation Within a Complex Food Web.''}
+\emph{Journal of Animal Ecology} 71 (6): 1063--74.
+\url{https://doi.org/10.1046/j.1365-2656.2002.00669.x}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-woodwardQuantificationResolutionComplex2005}{}}%
+Woodward, Guy, Dougie C. Speirs, and Alan G. Hildrew. 2005.
 {``Quantification and {Resolution} of a {Complex}, {Size}-{Structured
@@
 
-\leavevmode\hypertarget{ref-woodwardQuantificationResolutionComplex2005a}{}%
----------. 2005b. {``Quantification and {Resolution} of a {Complex},
-{Size}-{Structured Food Web}.''} In \emph{Advances in {Ecological
-Research}}, 36:85--135. {Elsevier}.
-\url{https://doi.org/10.1016/S0065-2504(05)36002-8}.
-
 \end{CSLReferences}
 
-\bibliographystyle{unsrt}
+\bibliographystyle{biblatex}
 \bibliography{bibliography.bib}

### 2022-06-20 manuscript/ms_C2/ms_C2_v2.tex
Incorporated most comments from Guy, Eoin and David

--- 2022-06-20 manuscript/ms_C2/ms_C2.tex
@@
 
-\title{How much gut content data is required to predict trophic
+\title{How much predator guts are required to predict trophic
 interactions?}
@@
   \texttt{\href{mailto:e.ogorman@essex.ac.uk}{\nolinkurl{e.ogorman@essex.ac.uk}}} \\
+   \And
+    Guy Woodward
+   \\
+    Georgina Mace Centre for the Living Planet, Department of Life
+Sciences \\
+    Imperial College London \\
+  Ascot, Berkshire Sl5 7PY, UK \\
+  \texttt{\href{mailto:guy.woodward@imperial.ac.uk}{\nolinkurl{guy.woodward@imperial.ac.uk}}} \\
    \And
@@
 \usepackage{lineno}
+\linenumbers
 \usepackage {amsmath}
@@
 \usepackage{setspace}\doublespacing
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
 \begin{document}
@@
   effort required to adequately describe the structure of a food web
-  using gut content data. Food web models such as the ADBM can be used
-  to circumvent this problem by predicting the interactions based on
-  easily measured characteristics, such as the size of organisms.
-  However, presence-absence data such as gut content data is required to
-  parameterise these food web models. And collecting and analysing these
-  data from the field is an expensive and time consuming task.
-  Therefore, it is crucial to know how much gut content data is required
-  to parameterise food web models with high accuracy and high precision.
-\item
-  Here, we explore seven food webs in the literature and determine how
-  much gut content data would be needed to accurately predict their
-  structure using the ADBM. We use Bayesian computation to parameterise
-  the ADBM, and true skill statistics to measure the goodness of fit,
-  and do so while varying the amount of gut content data used in the
-  parameterisation.
-\item
-  We estimated the minimum amount of gut content data required for seven
-  different food webs that resulted in 95\% of the maximum true skill
-  statistics achieved by the ADBM when all available gut content data
-  was used. We found that incomplete gut content data can be used to
-  parameterise the ADBM with the lowest amount of gut content data being
-  28\% of the available gut content data.
+  using individual predator guts. Food web models such as the allometric
+  diet breadth model (ADBM) can be used to circumvent this problem by
+  predicting the interactions based on easily measured characteristics,
+  such as the size of organisms. However, presence-absence data such as
+  predator guts is required to parameterise these food web models, and
+  collecting and analysing these data from the field is an expensive and
+  time-consuming task. Therefore, it is crucial to know how much
+  predator guts is required to parameterise food web models with high
+  accuracy and high precision.
+\item
+  Here, we explore seven exceptionally well-characterised food webs in
+  the literature and determine the minimum predator guts that would be
+  needed to accurately predict their structure using the ADBM. We use
+  Bayesian computation to parameterise the ADBM, and true skill
+  statistics to measure the goodness of fit, and do so while varying the
+  amount of predator guts used in the parameterisation to test the
+  effect of sampling effort.
+\item
+  We found that incomplete predator guts can be used to parameterise the
+  ADBM, with the lowest amount of predator guts being 28\% of the
+  available predator guts.
 \item
   These results suggest that one need not collect such a large quantity
-  of gut content data to predict the structure of a food web, thereby
+  of predator guts to predict the structure of a food web, thereby
   reducing sampling effort considerably, while having little effect on
@@
 \keywords{
-    gut content data
+    predator guts
    \and
@@
 (Dunne, Williams, and Martinez 2002). This has led to the development of
-numerous food web models (Allesina, Alonso, and Pascual 2008; Cohen,
-Newman, and Steele 1985; Gravel et al. 2013; Petchey et al. 2008;
-Tamaddoni-Nezhad et al. 2013). Along with inferring missing links in an
-observed food web, the food web models are also used for ecological
-forecasting (Hattab et al. 2016; Lindegren et al. 2010) and for
-understanding the underlying mechanism governing the interactions in a
-food web (Gorman et al. 2019).
+numerous food web models and associated theory (Allesina, Alonso, and
+Pascual 2008; Cohen, Newman, and Steele 1985; Gravel et al. 2013;
+Petchey et al. 2008; Tamaddoni-Nezhad et al. 2013). Along with inferring
+missing links in an observed food web, such food web models are also
+increasingly used for ecological forecasting (Hattab et al. 2016;
+Lindegren et al. 2010) and for understanding the underlying mechanism
+governing trophic interactions in the wild (O'Gorman et al. 2019).
 
@@
 factors that determine trophic interactions, empirical data about
-interactions is required to parameterise a model. For example, Petchey
-et al. (2008) used presence-absence information about trophic
-interactions to parameterise the allometric diet breadth model and
-thereby predict species interactions. These empirical information about
-interactions can come from diverse set of methods such as gut content
-analysis (Peralta-Maraver, Lopez-Rodriguez, and de Figueroa 2017),
-stable isotope ratio analysis of tissues (Layman et al. 2007),
-experimentation (Warren 1989), DNA metabarcoding of gut contents or
-faeces (Roslin and Majaneva 2016) and literature research (Gray et al.
-2015; Cohen and Mulder 2014a; Goldwasser and Roughgarden 1993a).
-
-Each of these sources of information about trophic interactions has
-shortcomings. For example: Stable isotope ratio analysis of the
-organism's tissue does not give direct information of the diet of that
-organism but rather gives approximate trophic position of that species
-in the food web (Wada, Mizutani, and Minagawa 1991; Jennings and van der
-Molen 2015). Although mixing models can be used to determine what prey
+interactions are required to parameterise a model. For example, Petchey
+et al. (2008) and Gupta, Furrer, and Petchey (2022) used
+presence-absence information about trophic interactions to parameterise
+the allometric diet breadth model and thereby predict species
+interactions. Such empirical information about interactions can come
+from diverse set of methods such as gut content analysis
+(Peralta-Maraver, Lopez-Rodriguez, and de Figueroa 2017), stable isotope
+ratio analysis of tissues (Layman et al. 2007), experimentation (Warren
+1989), DNA metabarcoding of gut contents or faeces (Roslin and Majaneva
+2016) and literature research (Gray et al. 2015b; Cohen and Mulder
+2014a; Goldwasser and Roughgarden 1993a) but each of these sources of
+information about trophic interactions has serious shortcomings,
+hindering the advancement of the field. For example: stable isotope
+ratio analysis of the organism's tissue does not give direct
+taxonomically resolved information of the diet of that organism, but
+rather it provides approximate trophic position of that species in the
+food web (Wada, Mizutani, and Minagawa 1991; Jennings and van der Molen
+2015) and although mixing models can be used to determine what prey
 items are most likely fed upon by a predator, this results in
 uncertainty in the estimates (Kadoya, Osada, and Takimoto 2012;
-Crawford, Mcdonald, and Bearhop 2008). Similarly, DNA metabarcoding
-could have issues in detecting secondary predation or cannibalism
-(Pompanon et al. 2012; Nielsen et al. 2018) and is prone to
-environmental contamination (e.g.~DNA in the water swallowed along with
-DNA from an aquatic consumer's prey cannot be differentiated from actual
-prey) (Kelly et al. 2014). Furthermore, construction of food webs via
-literature review can lead to false positives--links included when in
-reality no link would occur because it makes an assumption that the
-species interactions inferred from a system will occur in another system
-as well(Gray et al. 2015; Cohen and Mulder 2014b; Goldwasser and
-Roughgarden 1993b).
-
-Nielsen et al. (2018) have shown that gut content analysis method has a
-better match with real diet when compared to other methods.
-
-Acquiring food web data from gut content analysis is time consuming and
-expensive (AG: Do we need a reference? Next sentence explains the
-reason.). In part this is due to the perception that many gut contents
-must be collected and analysed in order to be confident that the
-majority of possible trophic links among species have been observed.
-Furthermore, considerable time, resource investment, and expertise is
-required to process the collected samples. Hence, there is of
-considerable importance to know the minimum number of gut contents and
-of which consumer species that are required to parameterise a food web
-model with high accuracy and high precision, so that one knows when is a
-good time to stop collecting any further empirical data on the food web.
+Crawford, Mcdonald, and Bearhop 2008). Similarly, more recent approaches
+using DNA metabarcoding may give much higher taxonomic resolution but
+present other challenges, such as an inability to resolve secondary
+predation or cannibalism (Pompanon et al. 2012; Nielsen et al. 2018)
+which are common in nature and also being prone to environmental
+contamination (e.g.~DNA in the water swallowed along with DNA from an
+aquatic consumer's prey cannot be differentiated from actual prey)
+(Kelly et al. 2014). Furthermore, construction of food webs via
+literature review, which is one of the most common practices in food web
+research, can lead to false positives--links included when in reality no
+link would occur because it makes an assumption that the species
+interactions inferred from a system will occur in another system as well
+(Gray et al. 2015b; Cohen and Mulder 2014b; Goldwasser and Roughgarden
+1993b). It is unsurpsing given the limitations of these proxy or
+inferential approaches that authors such as Nielsen et al. (2018) have
+shown that gut content analysis method has a better match with real diet
+when compared to other methods.
+
+Although gut content analysis is viewed as the ``gold standard'',
+acquiring such food web data from direct gut content analysis is
+extremely time consuming and expensive (Gray et al. 2015b) and it also
+requires high skill levels in taxonomic identification, often involving
+dissection and microscopy techniques (Hyslop 1980). The perception that
+this is unavoidably laborious and costly is also in part due to the
+assumption that many gut contents must be collected and analysed in
+order to be confident that the majority of possible trophic links among
+species have been observed. Most studies fail to quantify the effort
+needed, with yield-effort curves being the exception rather than the
+rule and those that have been done often point to the apparent need for
+hundreds or thousands of guts to be analysed to fully capture a food
+web's structure. Hence, it is of huge importance to know the minimum
+number of predator guts required to parameterise a food web model with
+high accuracy and high precision: this would enable researchers to
+allocate resources more effectively a priori, and even having a rough
+rule of thumb as to when is a good point to stop collecting any further
+empirical data on the food web is far better than the current common
+practice of simply taking a fixed set of samples with on yield-effort
+analyses being undertaken.
 
 Therefore, the key question we are interested in answering is how much
-presence-absence information, in the form of gut content data, is
-required to infer food web structure from a food web model with high
-accuracy and high precision. In other words, how many samples of gut
-content should one collect from the field to parameterise a food web
-model? To answer this question, we use the presence-absence information
-from gut content data to parameterise the allometric diet breadth model
-(ADBM) thereby predicting trophic interactions in seven different food
-webs using rejection approximate Bayesian computation, where the fit of
-the model was measured using true skill statistics. We computed the true
-skill statistics of the predicted food webs for different number of
-predator guts to calculate the minimum number of gut content data to
-infer food web structure. Our study provides a guideline on how many gut
-content data is required to predict food web structure using a food web
-model.
+presence-absence information, in the form of predator guts, is required
+to infer food web structure from a food web model with high accuracy and
+high precision? In other words, how many samples of predator guts should
+one collect from the field to parameterise a food web model? To answer
+this question, we use different amount of predator guts to parameterise
+the allometric diet breadth model (ADBM) thereby predicting trophic
+interactions in seven different food webs using rejection approximate
+Bayesian computation, and calculate the minimum number of predator guts
+to infer food web structure. Our study provides a guideline on how many
+predator guts are required to predict food web structure using a food
+web model.
 
@@
 
-In the upcoming sections, we present the empirical food webs, the
-allometric diet breadth model (ADBM), and the gut content data used to
-infer the trophic interactions. We also give a detailed account of using
-partial gut content data to parameterise the ADBM using rejection
-approximate Bayesian computation (ABC). We assessed model predictions
-using the true skill statistic for comparison across food webs.
+We present the empirical food webs, the allometric diet breadth model
+(ADBM), and the predator guts used to infer the trophic interactions. We
+also give a detailed account of using partial predator guts to
+parameterise the ADBM using rejection approximate Bayesian computation
+(ABC). We assessed model predictions using the true skill statistic for
+comparison across the food webs.
 
@@
 
-In our study, we used food webs for which gut content data is available
-at an individual level and data that is or that we could make FAIR
-(Wilkinson et al. 2016). Presence and absence interactions of food web
-data can be aggregated in different ways (Gilljam et al. 2011). A common
-way of aggregating food web data is the taxonomic approach, in which
-nodes in the food web are taxa (e.g.~species), or life stages of taxa,
-and one species is said to feed on another species if at least one
-individual of the latter is found in at least one gut of the former.
-Another approach is based on size, rather than taxonomy, and in this the
-nodes in the food web are size classes. Here, a feeding link occurs
-between two size classes if at least one prey item within a size class
-was found in the gut of another size class, irrespective of their
-taxonomy.
-
-In our study, we aggregate the gut content data on the basis of size
-class because the food webs constructed using this approach were better
-predicted by the ADBM compared to the taxonomic approach (Woodward et
-al. 2010a), and this is because the ADBM is based on foraging rules
-defined using the body sizes of organisms (Petchey et al. 2008).
-
-Our study is based on the assumption that the food web constructed using
-the complete gut content data is the true food web. However, this might
-not be the case because the links are still under-sampled for many nodes
-(Woodward et al. 2010b). This could result in a lower true skill
-statistic (TSS) of the predicted food web from the ADBM, which can
-result in a biased estimate of the minimum number of gut content data
-required to achieve 95\% of the TSS achieved using complete gut content
-data.
-
-In the following sections 2.1.1-2.1.5, we briefly explain seven
-empirical food webs used in our study. The text used in those sections
-are paraphrased from Gilljam et al. (2011).
-
-\hypertarget{broadstone-stream}{%
-\subsubsection{Broadstone Stream}\label{broadstone-stream}}
-
-Broadstone Stream (51\(^\circ\) 05' N 0\(^\circ\) 03' E; 120 m above
-sea-level) is a second-order tributary of the River Medway in south-east
-England. At the time of sampling in 1996--1997, the stream was acidic
-(pH 4.7--6.6) and fishless. About 31 common species make up the
-macroinvertebrate food web, including six major predators and
-detritivores like stoneflies and chironomids (Woodward, Speirs, and
-Hildrew 2005).
-
-Between June 1996 and April 1997, thirty randomly scattered benthic
-Surber sample-units (25cm \(\times\) 25cm quadrat; mesh aperture 330mm)
-were taken every two months and kept in 5\% formalin. All individuals
-retrieved from the benthos and identified in stomach contents had their
-linear body dimensions quantified and converted to dry mass using known
-regression formulae (listed in Woodward and Hildrew (2002)).
-
-The predators' foreguts were dissected and analysed with 400
-magnification in the Surber samples. The individual body masses of eaten
-prey were calculated using the same methods as for the benthic samples,
-using reference slides as a guide (Woodward, Speirs, and Hildrew 2005).
-Over the six sample instances, a single dataset was produced. Each
-predator and prey individual involved in a feeding relationship was
-measured and converted into their respective body masses, resulting in a
-total of 2893 individuals.
-
-\hypertarget{celtic-sea}{%
-\subsubsection{Celtic Sea}\label{celtic-sea}}
-
-The Celtic Sea is a continental shelf area that is bounded by Ireland,
-the United Kingdom, and the Bay of Biscay. Because the Barnes et al.
-(2008) dataset, from which the data utilised in this chapter were taken,
-did not provide precise sampling sites and dates, the data was pooled
-throughout the whole time period and locations to capture broad
-tendencies. Only places that were sampled consistently from 1987 to 2001
-were used (Blanchard et al. 2005).
-
-In a published global dataset of individual predator and prey body sizes
-and taxonomy (Barnes et al., 2008), the feeding linkages of fish in the
-Celtic Sea were described. The original stomach contents data were
-acquired during annual surveys conducted by the Centre for Environment,
-Fisheries, and Aquaculture Science (Cefas) on board research vessels
-during dissections (Pinnegar et al. 2003). Barnes et al. (2008) used
-known regression equations to measure predator and prey lengths and
-convert them to body mass.
-
-\hypertarget{afon-hirnant}{%
-\subsubsection{Afon Hirnant}\label{afon-hirnant}}
-
-Three sites in the Afon Hirnant, in North Wales, UK (\(52^\circ\) 52' N
-\(03^\circ\) 34' W), were used for the study. The average yearly
-discharge was 2.08 to 7.26 \(m^3/s\), with a pH ranging from 5.5 to 7.
-(check Figueroa (2007) and Woodward et al. (2010c) for full details).
-Invertebrates were collected using a Hess sampler (sampling area: 0.028
-\(m^2\); mesh aperture 80 \(\mu m\)), with 15 sample-units obtained at
-random at each site and season, totaling 180 samples across the sampling
-period. The invertebrate fauna was promptly preserved in 100\% ethanol
-and sorted in the lab. By removing predators' foreguts, which were
-mounted in Euparal media and viewed at 400 magnification, feeding
-interactions were determined.
-
-Every predator's linear dimensions (for example, body length) and
-individual prey items inside each predator's foregut were measured and
-then translated to body mass values using published regression equations
-for each taxon (presented in Woodward et al. (2010c)). If the prey items
-were highly digested, the average body length of individuals in the same
-family (Ephemeroptera, Plecoptera, or Trichoptera) in the habitat was
-used. The body lengths of Chironomidae (Diptera) were calculated using
-previously established species-specific regressions between head capsule
-width and body length (Figueroa 2007).
-
-\hypertarget{tadnoll-brook}{%
-\subsubsection{Tadnoll Brook}\label{tadnoll-brook}}
-
-The Tadnoll Brook is a tributary of the River Frome in Southern England,
-UK, with a mean annual discharge of 0.35 \(m^3/s\) and a pH of 6.9--7.7.
-(Edwards et al., 2009b).
-
-A 240-m reach was sampled every two months between February and December
-2005 to create the summary food web. A Surber sampler was used to
-collect invertebrates every two months (0.06 m2; mesh aperture 300 mm).
-20 random samples were taken on each occasion, stored in the field in
-4\% (w/v) formalin, and then sorted for invertebrates. Fish were
-captured with an electrofisher, anaesthetized with 2-phenoxyethanol,
-recognised to species, measured, and weighed on each occasion (Woodward
-et al., 2010). The guts of trout (Salmo trutta L.) with fork lengths
-more than 70 mm were then flushed with a tiny manual water pump and
-stored in 4\% formalin. For smaller trout and other fish species
-(\emph{Cottus gobio}, \emph{Anguilla anguilla}, \emph{Phoxinus
-phoxinus}, \emph{Barbatula barbatula}, \emph{Gasterosteus aculeatus}),
-specimens were sacrificed and frozen for subsequent dissection.
-
-Gut contents analysis was performed on each sample occasion for the fish
-assemblage, whereas invertebrates had far less varied diets and were
-only characterised in May and October. Individuals of the benthos'
-numerically dominant or trophically important invertebrate taxa were
-taken from the Surber samples, dissected, and the contents of the
-foregut investigated for animal prey, which were recognised at
-\(400\times\) magnification by comparison with reference specimens. The
-taxa used to examine stomach contents covered more than 95\% of the
-individuals observed in the Benthos. Wherever possible, predators' gut
-contents were matched to species, and linear body dimensions were
-measured. Using established regression equations, the dry mass of prey
-items and invertebrate predators was calculated (Benke et al. 1999;
-Ganihar 1997; Burgherr and Meyer 1997; Gonzalez, Basaguren, and Pozo
-2002; Smock 1980; Edwards et al. 2009; MEYER 1989).
-
-\hypertarget{guampoe-coilaco-and-trancura-rivers-chile}{%
-\subsubsection{Guampoe, Coilaco and Trancura Rivers,
-Chile}\label{guampoe-coilaco-and-trancura-rivers-chile}}
-
-Three rivers (the Coilaco, Guampoe, and Trancura Rivers) in the
-catchment area of the Tolten River in south Chile, South America, were
-studied in a similar way. The Coilaco River (discharge 2.1--16.8
-\(m^3/s\)), Guampoe River (output 1.8--7.5 \(m^3/s\)), and Trancura
-River (discharge 8.8--49.3 \(m^3/s\)) are all pH 6.7--7.6 circumneutral
-rivers (Figueroa 2007).
-
-In each river, eight benthic samples were taken in each season between
-1984 and 1985, totaling 96 sample-units for the whole sampling period
-(Campos et al., 1985). Invertebrates were gathered using a Surber
-sampler (sampling area: 0.09 \(m^2\); mesh aperture 250 \(\mu m\)) and
-stored in 70\% ethanol before being transported to the lab for species
-identification and food web analysis.
-
-The feeding linkages were discovered by analysing the gut contents of
-all individuals observed in each sample. Large invertebrates had their
-guts removed and mounted in Euparal, whilst small specimens were mounted
-whole and studied with \(400\times\) magnification. Following Schmid
-(1993) and (Schmid-Araya et al. 2002), species prey items detected on
-each gut were identified using previously mounted reference slides.
-Using known regression equations (mentioned in Reiss and Schmid-Araya
-(2008); Baumgärtner and Rothhaupt (2003); Miserendino (2001); Woodward
-et al. (2010b)), all linear dimensions were translated to body mass
-estimates.
+In our study, we used food webs for which predator guts are available at
+an individual level and data that is or that we could make FAIR
+(Findable Accessible Interoperable Reusable; Wilkinson et al. (2016)).
+In our study, first, we consider food webs where nodes are size classes
+i.e.~individuals are aggregated into these size classes based on their
+body size. A feeding link occurs between two size classes if at least
+one prey item within a size class was found in the gut of another size
+class of predator, irrespective of the taxonomy of the individuals. We
+used this approach because of several reasons such as to take account
+the ontogenetic shift in the diet of a predator (Woodward et al. 2010),
+individual-based interaction based on body size which would not been
+considered if nodes were aggregated based on taxonomy as a taxonomic
+node can have a large variation in the body size. Food webs aggregated
+using size can be used to model the impacts of commercial exploitation
+on marine ecosystems (Jennings and Brander 2010). Second, we also
+consider food webs where nodes are aggregated based on the taxonomy of
+the individuals as this is the most common way of constructing food webs
+in food web ecology.
+
+Our study food webs are freshwater food webs except the Celtic Sea food
+web which belongs to a marine ecosystem. Most of the food webs are
+dominated by invertebrates except Celtic Sea which is dominated by
+fishes and Tadnoll Brook which is dominated by fishes as well as
+invertebrates. The food webs vary in the number of nodes, trophic links,
+connectance and body sizes (Table 1).
+
+Invertebrates in freshwater food webs were collected using Hess or
+Surber sampler, whereas fishes were caught with electrofisher, and
+anaesthetised using 2-phenoxyethanol in freshwater food webs. In case of
+the Celtic Sea, trawling was used to catch fishes.
+
+The foreguts of the collected invertebrate predators were dissected and
+examined under the microscope. Regression equations were used to convert
+predator and prey lengths to the respective body masses. In case if the
+prey items were too highly digested for body lengths to be measured
+reliably, previously established regressions based on head capsule width
+were used as an alternative linear dimension. More detailed description
+of these food webs is present in Gilljam et al. (2011).
+
+\newgeometry{margin=1cm}
+\begin{landscape}\begin{table}
+
+\caption{\label{tab:unnamed-chunk-1}\label{fig:tab_1}Information about the empirical food webs. AG: Some information will be updated.}
+\centering
+\resizebox{\linewidth}{!}{
+\fontsize{7}{9}\selectfont
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}|>{\raggedright\arraybackslash}p{8em}|l|l|l|l|>{\raggedright\arraybackslash}p{8em}|>{\raggedright\arraybackslash}p{8em}|>{\raggedright\arraybackslash}p{8em}}
+\hline
+Common food web name (Original Publication) & Location & Predation matrix source & Body size source & General ecosystem & Number of nodes & Number of links & Connectance & Body size range (mg) (approximate)\\
+\hline
+Broadstone Stream (Woodward
+et al. 2010) & England, UK 51$^{\circ}$05'N 0$^{\circ}$03'E & Guy Woodward 2021 & Guy Woodward 2021 & Freshwater & 29 & 185 & 0.24 & $10^{-7}$ to $10^2$\\
+\hline
+Celtic Sea (Barnes et al. 2016) & British Isles and French coastal shelf 50$^{\circ}$50'N 08$^{\circ}$00'W & Barnes et al. 2016 & Barnes et al. 2016 & Marine & 48 & 386 & 0.17 & $10^{-2}$ to $10^4$\\
+\hline
+Tadnoll Brook & England, UK 50$^{\circ}$41'N 02$^{\circ}$19'W & NA & NA & Freshwater & 59 & 485 & 0.14 & $10^{-6}$ to $10^5$\\
+\hline
+Afon Hirnant (Woodward
+et al. 2010) & Wales, UK, 50$^{\circ}$52'N 03$^{\circ}$34'E & David H. Figueora 2022a & David H. Figueora 2022a & Freshwater & 33 & 221 & 0.20 & $10^{-6}$ to $10^2$\\
+\hline
+Coilaco (Figueora 2007) & Chile 39$^{\circ}$17'S 71$^{\circ}$44'W & David H. Figueora 2022b & David H. Figueora 2022b & Freshwater & 45 & 123 & 0.06 & $10^{-6}$ to $10^2$\\
+\hline
+Guampoe (Figueora 2007) & Chile 39$^{\circ}$23'S 71$^{\circ}$410W & David H. Figueora 2022b & David H. Figueora 2022b & Freshwater & 44 & 139 & 0.07 & $10^{-6}$ to $10^3$\\
+\hline
+Trancura (Figueora 2007) & Chile 39$^{\circ}$26'S 71$^{\circ}$32'W & David H. Figueora 2022b & David H. Figueora 2022b & Freshwater & 35 & 78 & 0.06 & $10^{-6}$ to $10^1$\\
+\hline
+\end{tabular}}
+\end{table}
+\end{landscape}
+\restoregeometry
 
@@
 theory, specifically the contingency foraging model (MacArthur and
-Pianka 1966). We chose this model for various reasons, including because
-it uses the body size of organisms as input to predict feeding
-interactions, and because of our familiarity with it. The ADBM predicts
-the set of prey types (e.g.~species or sizes classes) a consumer should
-feed upon to maximise its rate of energy intake (Petchey et al. 2008).
-The foraging variables in the model are: energy content of the
-resources, handling times of the prey, space clearance rate, and prey
-densities. These are allometrically scaled to the body sizes of the
+Pianka 1966). We chose this model because it can predict species
+interactions based on an easily measurable trait body size. The ADBM
+predicts the set of prey types (e.g.~species or sizes classes) a
+consumer should feed upon to maximise its rate of energy intake (Petchey
+et al. 2008). The foraging variables in the model are: energy content of
+the resources, handling times of the prey, space clearance rate, and
+prey densities. These are allometrically scaled to the body sizes of the
 species. Further details on the foraging rules defined in the ADBM and
@@
 
-The accuracy of the predicted diet of the predators was measured using
-true skill statistic (TSS) which takes into account the true and false
-predictions of both the presence and absence of links defined as:
+The accuracy of the predicted diet of the predators was measured using a
+widely used accuracy measure in food web ecology namely true skill
+statistic (TSS) (Gray et al. 2015b; Gravel et al. 2013; Gupta, Furrer,
+and Petchey 2022). We chose this metric because it takes into account
+the true and false predictions of both the presence and absence of links
+defined as:
 
@@
 
-\hypertarget{inferring-food-web-using-partial-gut-content-data}{%
-\subsection{Inferring food web using partial gut content
-data}\label{inferring-food-web-using-partial-gut-content-data}}
-
-\textbf{Comment AG: Is it necessary to have the sections 1.1 and 1.2 of
-the supplementary information in the Supplementary information or shall
-the sections 1.1 and 1.2 be migrated to the main text (manuscript)?}
-
-From an empirical dataset of gut content data, we take a random sample
-of gut contents of specific size (see below) to create a partial gut
-content dataset. We then fit the ADBM to this partial dataset.
+\hypertarget{inferring-food-web-using-partial-predator-guts}{%
+\subsection{Inferring food web using partial predator
+guts}\label{inferring-food-web-using-partial-predator-guts}}
+
+From an empirical dataset of predator guts, we take a random sample of
+gut contents of specific size (see below) to create a partial predator
+guts dataset. We then fit the ADBM to this partial dataset.
 
@@
 
-{\centering \includegraphics[width=500px]{../../manuscript/fig/ms_C2(1)}
+{\centering \includegraphics[width=350px]{../../manuscript/fig/ms_C2_flowchart}
 
@@
 
-\caption{\label{fig:fig_ra} (a, c, e, g, i, k, m) Accuracy of the predicted food web measured using the true skill statistics, predicted by the ADBM parameterised using gut content data.
-Line and shaded grey region represents the mean and the prediction interval of 100 independent samples respectively.
-Red line represents the number of predator guts required to achieve a TSS of 95\% of the maximum TSS.
-(b, d, f, h, j, l, n) Ratio of the true skill statistic of the predicted food web by the ADBM parameterised using gut content data to that of the predicted food web constructed using gut content data only.
-The dashed line shows where the ratio is one for reference.}\label{fig:unnamed-chunk-1}
+\caption{\label{fig:fig_ra} Flowchart of the subsampling method implemented to predict the full food web from the food web model using the predator guts.}\label{fig:unnamed-chunk-2}
 \end{figure}
 
-To fit the ADBM to a gut content dataset (be it complete or partial), we
-used the rejection ABC method we previously developed in Gupta, Furrer,
-and Petchey (2022) to accept a parameter value from a prior distribution
-which would have resulted in the minimum distance, where distance = 1 -
-True skill statistic. The true skill statistic was computed between the
-diets predicted from the ADBM, and those observed in the sampled gut
-content data. We repeated this process \(n~(= 100)\) times for every
-\(i\) number of guts, where \(i\) lies between 1 and total number of gut
-content data in the pool.
+To fit the ADBM to partial predator guts dataset, we used the rejection
+approximate Bayesian computation method we previously developed in
+Gupta, Furrer, and Petchey (2022) to accept a parameter value from a
+prior distribution which would have resulted in the minimum distance,
+where distance = 1 - TSS. The true skill statistic was computed between
+the diets predicted from the ADBM, and those observed in the sampled
+predator guts. We repeated this process \(n~(= 100)\) times for every
+\(i\) number of guts, where \(i\) lies between 1 and total number of
+predator guts in the pool.
 
@@
 \item
-  A pool of gut content data \(G: G = \{g_1, g_2, \dots, g_n\}\), where
+  A pool of predator guts \(G: G = \{g_1, g_2, \dots, g_n\}\), where
   \(g_{n}\) is the observed diet matrix containing ones and zeros.
@@
 
-for \(i = 1, \dots, tgut\) where \(tgut\) is the total number of gut
-content data in the pool \(G\)
+for \(i = 1, \dots, tgut\) where \(tgut\) is the total number of
+predator guts in the pool \(G\)
 
@@
   \item
-    Draw a set of gut content data \(y = \{g_1, g_2, \dots, g_i\}\) from
-    the pool of gut content data \(G\)
+    Subsample a set of predator guts \(y = \{g_1, g_2, \dots, g_i\}\)
+    from the pool of predator guts \(G\)
   \item
@@
     \item
-      Compute the model result \(x_i = model(\theta_k)\)
-    \item
-      Compute \(s(x_i)\) and \(d(s(x_i), y)\)
+      Compute the model result \(x_k = model(\theta_k)\)
+    \item
+      Compute \(s(x_k)\) and \(d(s(x_k), y)\)
     \end{itemize}
   \item
-    Accept \(\theta_j\), which results in the \(min_i\{d(s(x_i), y)\}\)
+    Accept \(\theta_j\), which results in the \(min_k\{d(s(x_k), y)\}\)
   \end{itemize}
@@
   Compute
-  \(TSS_{i}(x, y) = \{TSS(x_i,y): x_i = ADBM(\theta_j), \theta_j \text{ computed from previous step}\}\)
+  \(TSS_{i}(x, Y) = \{TSS(x_i, Y): x_i = ADBM(\theta_j), \theta_j \text{ computed from previous step}\}\)
   using the accepted \(\theta_1, \dots, \theta_{nsample}\)
@@
 The \(TSS\) between observed and predicted food webs, and the posterior
-parameter distributions for every \(i\) number of gut content data drawn
-from the pool of gut content data.
-
-\hypertarget{computing-the-minimum-gut-content-data}{%
-\subsection{Computing the minimum gut content
-data}\label{computing-the-minimum-gut-content-data}}
-
-Using TSS of the predicted food webs for different number of predator
-guts, we computed the number of gut content data that results in the
-mean TSS equal to the 95\% of the mean TSS achieved by the model using
-all the predator guts for a food web. We call this number of gut content
-data as the minimum gut content data.
+parameter distributions for every \(i\) number of predator guts drawn
+from the pool of predator guts.
+
+\hypertarget{computing-the-minimum-number-of-predator-guts}{%
+\subsection{Computing the minimum number of predator
+guts}\label{computing-the-minimum-number-of-predator-guts}}
+
+Using TSS of the model predicted food webs for different number of
+predator guts, we computed the number of predator guts that results in
+the mean TSS equal to the 95\% of the mean TSS achieved by the model
+using all the predator guts available in the pool for a food web. We
+call this number of predator guts as the minimum number of predator
+guts.
+
+\hypertarget{standardising-sampling-level-of-the-food-webs}{%
+\subsection{Standardising sampling level of the food
+webs}\label{standardising-sampling-level-of-the-food-webs}}
+
+Since the seven food webs have different levels of sampling effort, with
+Broadstone Stream being the most sampled among all, and every other food
+web being undersampled when compared to the Broadstone Stream food web
+(SI Fig. S2), we used the R \emph{vegan} package to account for the
+undersampling with respect to the Broadstone Stream food web. We fitted
+the link accumulation curves using the fitspecaccum function to a set of
+nonlinear regression models suggested in Dengler (2009) and used the AIC
+criteria for model selection. We then extrapolated the link accumulation
+curves for all the food webs except the Broadstone Stream and computed
+the corrected number of predator guts that would have resulted in the
+gradient of the link accumulation curve equal to the gradient of that of
+the Broadstone Stream when all the predator guts were used. We also
+calculated the corrected number of trophic links corresponding to that
+corrected number of predator guts. For the food webs, we calculated the
+undersampling factor which is equal to the ratio of corrected number of
+predator guts to the number of predator guts in the pool. Using the
+undersampling factor, we further calculated the corrected minimum number
+of predator guts which is equal to the product of the undersampling
+factor and the minimum number of predator guts.
 
@@
 We first present how the accuracy of the food web model in predicting
-trophic interactions varies with increasing amount of gut content data
-provided to the food web model. Then, we calculate the number of gut
-content data for each food webs that results in accuracy equal to 95\%
-of the maximum true skill statistics predicted by the food web model.
-
-\hypertarget{inferring-trophic-interactions-using-adbm-and-incomplete-gut-content-data}{%
-\subsection{Inferring trophic interactions using ADBM and incomplete gut
-content
-data}\label{inferring-trophic-interactions-using-adbm-and-incomplete-gut-content-data}}
+trophic interactions varies with increasing amount of predator guts
+provided to the food web model. We investigate how the minimum number of
+predator guts varied with number of trophic links and number of species.
 
@@
 
-{\centering \includegraphics[width=500px]{../../results/misc/plot_TSS_ratio}
+{\centering \includegraphics[width=400px]{../../results/misc/plot_TSS_vs_ngut}
 
@@
 
-\caption{\label{fig:fig_ra} (a, c, e, g, i, k, m) Accuracy of the predicted food web measured using the true skill statistics, predicted by the ADBM parameterised using gut content data.
-Line and shaded grey region represents the mean and the prediction interval of 100 independent samples respectively.
-Red line represents the number of predator guts required to achieve a TSS of 95\% of the maximum TSS.
-(b, d, f, h, j, l, n) Ratio of the true skill statistic of the predicted food web by the ADBM parameterised using gut content data to that of the predicted food web constructed using gut content data only.
-The dashed line shows where the ratio is one for reference.}\label{fig:unnamed-chunk-2}
+\caption{\label{fig:fig_ra} Accuracy of the predicted food web measured using the true skill statistic, predicted by the ADBM parameterised using predator guts.
+Line and shaded grey region represents the mean and the prediction interval corresponding to 100 independent samples respectively.
+Red line represents the number of predator guts required to achieve a TSS of 95\% of the maximum TSS.}\label{fig:unnamed-chunk-3}
 \end{figure}
@@
 The true skill statistics of the food webs predicted by the ADBM using
-subsets of gut content data improved quickly for lower number of
-predator guts (Fig. \ref{fig:fig_ra}) (a, c, e, g, i, k, m).
-Furthermore, the width of the prediction interval of the true skill
-statistics decreased with increasing number of predator guts with the
-mean TSS asymptoting to the maximum mean TSS achieved by the ADBM when
-all the gut content data was used. Although the maximum TSS varied among
-the food webs, the qualitative increase in the TSS was the same.
-
-For Broadstone Stream food web, with only 381 gut contents, which is
-38\% of the total gut content data, the ADBM predicted the food web with
-the mean TSS of 0.74 which was 95\% of the mean TSS (0.78) achieved
-using complete gut content data (Fig. \ref{fig:fig_ra}(a)). In case of
-the Celtic Sea food web, only 171 gut content data which is 35\% of the
-total gut content data was required by the ADBM to predict food web with
-TSS equal to 95\% of the mean TSS (0.68) achieved using complete gut
-content data (Fig. \ref{fig:fig_ra}(c)).
-
-For a low number of predator guts, the TSS of the model predicted food
-web was higher than the TSS of the food web constructed from gut content
-data only (Fig. \ref{fig:fig_ra} (b, d, f, h, j, l, n)). An increase in
-the number of predator guts did reduce the ratio TSS(Model)/TSS(data)
-reduced to less than one, and reduced further gradually. This shows that
-with less data available it is better to use the model, while if more
-data is available then it is better to use the data itself.
-
-\hypertarget{dependence-of-the-minimum-gut-content-data-on-number-of-links-and-connectance}{%
-\subsection{Dependence of the minimum gut content data on number of
-links and
-connectance}\label{dependence-of-the-minimum-gut-content-data-on-number-of-links-and-connectance}}
-
-There was a significant positive relationship between the minimum number
-of gut content data (i.e the amount of gut content data used in order to
-ensure 95\% of the maximum TSS) and the connectance of the food webs
-(Fig. \ref{fig:fig_rb} (a)). Similarly, we also observed a positive
-relationship between the minimum number of gut content data and the
-number of trophic links (L) in the food webs, however this relationship
-was not significant (Fig. \ref{fig:fig_rb} (b)). Furthermore, there was
-a significant positive relationship between the number of minimum gut
-content data and the the number of maximum gut content data sampled
-(Fig. \ref{fig:fig_rb} (c)) for food webs.
+incomplete predator guts improved quickly for lower number of predator
+guts (Fig. \ref{fig:fig_ra}). Furthermore, the width of the prediction
+interval of the true skill statistics decreased with increasing number
+of predator guts with the mean TSS asymptoting to the maximum mean TSS
+achieved by the ADBM when all the predator guts was used. Although the
+maximum TSS varied among the food webs, the qualitative increase in the
+TSS was the same.
+
+For Broadstone Stream food web, with only 381 predator guts, which is
+38\% of the total predator guts, the ADBM predicted the food web with
+the mean TSS of 0.74. This was equivalent to 95\% of the mean TSS (0.78)
+achieved using complete predator guts (Fig. \ref{fig:fig_ra}(a)):
+i.e.~the main characteristics of the food web could be captured with
+about 1/3 of the effort used in the original study. In case of the
+Celtic Sea food web, only 171 predator guts which is 35\% of the total
+predator guts was required by the ADBM to predict food web with TSS
+equal to 95\% of the mean TSS (0.68) achieved using complete predator
+guts (Fig. \ref{fig:fig_ra}(b)).
+
+The minimum number of predator guts was not significantly related to
+number of trophic links (Fig. \ref{fig:fig_rb} (a)) and the number of
+species (Fig. \ref{fig:fig_rb} (b)). Similarly, the corrected minimum
+number of predator guts was not significantly related to corrected
+connectance, corrected number of trophic links and number of species
+respectively (Fig. \ref{fig:fig_rb} (c, d)). Correcting for the
+undersampling in the food webs improved the fit between the minimum
+number of predator guts and the number of trophic links from
+\(R^2 = 0.13\) (Fig. \ref{fig:fig_rb} (a)) to \(R^2 = 0.43\) (Fig.
+\ref{fig:fig_rb} (c)).
 
@@
 
-{\centering \includegraphics[width=400px]{../../results/misc/plot_min_gut_vs_X}
+{\centering \includegraphics[width=300px]{../../results/misc/plot_n_min_gut_vs_SL}
 
@@
 
-\caption{\label{fig:fig_rb} (a, b, c) Number of minimum gut content data (i.e the amount of gut content data used in order to ensure 95\% of the maximum TSS) plotted against number of links (L), connectance (C) and number of maximum guts sampled respectively.
-Solid lines are linear regression ((a) t = 3.138, df = 5, P = 0.0257; (b) t = 0.876, df = 5, P = 0.421; (c) t = 9.571, df = 5, P = 0.0002) and grey region represents 95\% confidence intervals.}\label{fig:unnamed-chunk-3}
+\caption{\label{fig:fig_rb} (a, b) Minimum number of predator guts (i.e the amount of predator guts used in order to ensure 95\% of the maximum TSS) plotted against number of trophic links (L) and number of species respectively.
+(c, d) Corrected minimum number of predator guts (i.e.
+the minimum number of predator guts which takes into account the undersampling level of the food webs) plotted against corrected number of trophic links and number of species (S) respectively.
+Solid lines are linear regression ((a) t = 0.876, df = 5, P = 0.421; (c) t = 1.923, df = 5, P = 0.113; (d) t = 1.099, df = 5, P = 0.322) and grey region represents 95\% confidence intervals.}\label{fig:unnamed-chunk-4}
 \end{figure}
@@
 
-We have demonstrated how a food web model can be used to predict food
-webs reasonably well even when incomplete data about trophic
-interactions is available. At lower amount of gut content data,
-predicting with the model is better than using the data itself, while at
-higher amounts of gut content data, it is better to only use the data.
-This can help inform how much gut content data to actually collect when
-we are using a food web model to infer trophic interactions. A future
-development could be to make the same assessment using other food web
-models, and to also use food web data other than gut content data to
-parameterise those models.
-
-\hypertarget{why-incomplete-gut-content-data-can-be-used-to-infer-trophic-interactions}{%
-\subsection{Why incomplete gut content data can be used to infer trophic
-interactions?}\label{why-incomplete-gut-content-data-can-be-used-to-infer-trophic-interactions}}
-
-In all of the seven food webs, the ADBM was able to infer the trophic
-interactions using incomplete gut content data because the presence
-absence information from the gut content data was still sufficient to
-constrain the possible model parameter values of the ADBM that best
-explained the predators' diets. Although in theory the ADBM can predict
-trophic interactions using only body sizes of organisms as it is based
-on set of foraging rule, it still requires some presence absence data to
-constrain the posterior parameter space thereby making more accurate
-predictions.
-
-\hypertarget{why-does-the-minimum-gut-data-differ-among-food-webs}{%
-\subsection{Why does the minimum gut data differ among food
-webs?}\label{why-does-the-minimum-gut-data-differ-among-food-webs}}
-
-We found the minimum amount of gut content data to vary across food webs
-and this could be due to the possibility that the food webs are sampled
-differently, i.e.~some food webs are more extensively sampled than
-others (SI Fig. S2). Furthermore, it is possible that interactions in
-some of the food webs are are more size-structured than others, and are
-therefore better predicted by the ADBM and consequently require a lower
-number of gut content data for model parameterisation.
-
-\hypertarget{model-fills-up-missing-interactions-and-guides-sampling-direction}{%
-\subsection{Model fills up missing interactions and guides sampling
-direction}\label{model-fills-up-missing-interactions-and-guides-sampling-direction}}
-
-When little data about trophic interactions is available, the model can
-be used to add data about interactions for which data is missing.
-Furthermore, the model predictions can be used as a guide to sample
-those predator guts for which we do not have enough information on the
-presence of interactions from the empirical gut content samples but the
-model suggests there are interactions. Therefore, with enough number of
-predator guts sampled one might possibly observe those missed
-interactions.
-
-\hypertarget{why-is-models-tss-less-than-one}{%
-\subsection{Why is model's TSS less than
-one?}\label{why-is-models-tss-less-than-one}}
-
-The food web model used (the ADBM) cannot explain all the interactions
-in any observed food web that it has been fit to. The foraging rules it
-encodes are based on the body size and have particular structure and
-assumptions; not all of these are met by all observed interactions. For
-example, the ADBM can only predict diets that are contiguous with
-respect to the size of prey. I.e. it cannot predict that a predator will
-consume taxa of size 1 and 3, and not taxa of size 2. Hence, if the
-observed diets are not contiguous when prey are ordered by their size,
-the estimation process could lead to a lower value of the TSS.
-
-Furthermore, the observed data may be missing links, e.g.~links that
-rarely occur. Hence the ADBM's maximum predicted true skill statistics
-is less than one for all food webs it has so far been fit to.
-
-\hypertarget{tssmodeltssdata-for-different-food-webs}{%
-\subsection{TSS(Model)/TSS(Data) for different food
-webs}\label{tssmodeltssdata-for-different-food-webs}}
-
-In all the food webs, the ratio TSS(Model)/TSS(Data) decreased with
-increasing number of predator guts (Fig. \ref{fig:fig_ra} (b, d, f, h,
-j, l, n)). This suggests when less data is available it is better to use
-the model and when more data is available it is better to only use the
-data to predict trophic interactions. At lower number of predator guts
-the model fills up the missing interactions that were not observed in
-the gut content data, therefore resulting in model performing better as
-compared to data alone. Wile at higher number of predator guts the model
-is probably predicting some presence or absence of links i.e.~false
-positives and false negatives resulting in a lower TSS as compared to
-that of data alone.
-
-\hypertarget{propagating-uncertainty-from-gut-content-data-to-models-predictions}{%
-\subsection{Propagating uncertainty from gut content data to model's
-predictions}\label{propagating-uncertainty-from-gut-content-data-to-models-predictions}}
-
-There is considerable uncertainty involved in gut content analysis
-(Baker, Buckland, and Sheaves 2014) such as in fish's guts, there are
-sometimes loose tissues that are not identifiable and cannot be assigned
-to a specific prey item with certainty. There are factors such as sample
-size of consumers, mechanical prey handling, differential digestion and
-evacuation rates of different prey types and volumes, and the ingestion
-order that in combination result in an unquantifiable error which is
-difficult to interpret in the predator diet (Hyslop 1980; Rindorf and
-Lewy 2004; Baker, Buckland, and Sheaves 2014). Therefore, a future
-development would be to consider how this uncertainty is propagated into
-food web prediction.
-
-\hypertarget{comparing-our-study-with-other-studies-of-predicting-food-webs-using-incomplete-data}{%
-\subsection{Comparing our study with other studies of predicting food
-webs using incomplete
-data}\label{comparing-our-study-with-other-studies-of-predicting-food-webs-using-incomplete-data}}
+We have demonstrated how a food web model can be used to predict the
+full structure of a food web when incomplete data about trophic
+interactions is available, which is true in most of the real food webs.
+This can help inform how much predator guts to actually collect when we
+are using a food web model to infer trophic interactions for an
+ecosystem with a given number of species. A future development could be
+to make the same assessment using other food web models, and to also use
+food web data other than predator guts to parameterise those models.
+
+Our study provides a ballpark figure of the minimum number of predator
+guts that need to be sampled to predict the structure of a food web
+using a food web model for an ecosystem with a given number of species.
+For instance, Fig. \ref{fig:fig_rb} (d) can be used as a rough estimate
+of how many predator guts needs to be collected to predict food web
+structure using a food web model for a given number of species. This
+would lead to a reduction in the hundreds of predator guts that would
+have to be collected in the first place (Ings et al. 2009), thereby
+saving considerable time and resources.
+
+In our study, we have implemented the approach only with the ADBM, which
+is a model based on size rules. Therefore, we suspect to get a similar
+result (i.e.~minimum number of predator guts for a food web) for a
+different food web model based on size rules such as the niche model by
+Gravel et al. (2013). For a given food web, some food web models might
+do better job at predicting its structure as compared to other food web
+models, so we suggest to extend our approach to other food web models
+such as niche model (Williams and Martinez 2000; Gravel et al. 2013;
+Allesina, Alonso, and Pascual 2008) and nested hierarchical model
+(Cattin et al. 2004). A future prospect could be to study how well
+different food web models' prediction accuracy vary with different
+amount of predator guts. This can also help in making decision as to
+which food web model to chose from for a given a set of predator guts.
+We suspect the relationship (i.e shape of the curve) between the TSS of
+the predicted food web and the number of predator guts might vary within
+food web models because of the difference on the set of rules used to
+define those models and how well those rules explain the food web
+structure. For example: a food web model based on body size trait would
+require less amount of data to predict a size structured food web as
+compared to a food web model based on trait other than body size.
 
 Some studies have presented how the accuracy of food web prediction
-change when we vary the amount of food web data (Gray et al. 2015). For
-example: Desjardins-Proulx et al. (2017) has used predictive machine
+change when the amount of food web data is varied (Gray et al. 2015b).
+For example Desjardins-Proulx et al. (2017) has used predictive machine
 learning models and Caron et al. (2022) has used predictive traits-based
@@
 
-\hypertarget{what-is-the-generalisability-of-our-results}{%
-\subsection{What is the generalisability of our
-results?}\label{what-is-the-generalisability-of-our-results}}
-
-In our study, we have implemented the approach only with the ADBM.
-However, in principle, this approach could be extended to other food web
-models such as (Williams and Martinez 2000; Gravel et al. 2013;
-Allesina, Alonso, and Pascual 2008). A future prospect could be to study
-how well different food web models' prediction accuracy vary with
-different amount of gut content data. This can also help in making
-decision as to which food web model to chose from for a given a set of
-gut content data. We suspect the relationship (i.e shape of the curve)
-between the TSS of the predicted food web and the number of predator
-guts might vary within food web models.
-
-\hypertarget{assumption-that-the-food-web-constructed-with-the-total-gut-content-data-is-the-true-food-web-and-how-can-this-be-improved}{%
-\subsection{Assumption that the food web constructed with the total gut
-content data is the true food web and how can this be
-improved}\label{assumption-that-the-food-web-constructed-with-the-total-gut-content-data-is-the-true-food-web-and-how-can-this-be-improved}}
-
-Some of the food webs are not very well predicted using the ADBM. And
-this could possibly result in a lower value of minimum gut content data
-that was used to achieve 95\% of the maximum TSS. This could be because
-our study is based on the assumption that the true food webs is the one
-which was constructed using the total gut content data. However, if the
-total gut content does not contain sufficient information to construct
-the complete food web, then the food web will miss some links. This
-would therefore result in a lower TSS of the predicted food web, which
-can eventually lead to a lower estimate of the minimum gut content data.
-A future prospect could be to incorporate other sources of
-presence-absence data such as stable isotope ratio, metabarcoding to
-complement any links that were missed by the gut content method.
-
-\hypertarget{how-can-we-include-other-types-of-food-web-data}{%
-\subsection{How can we include other types of food web
-data?}\label{how-can-we-include-other-types-of-food-web-data}}
-
-A future prospect would be to include other types of food web data along
-with gut content simultaneously to parameterise the ADBM. For example,
-one could use the approximate trophic position inferred from stable
-isotope ratio data from a tissue of an individual and gut content data
-of a different predator simultaneously to parameterise a food web model
-such as the ADBM. In this case, trophic position would be an additional
-summary statistic required in the parameterisation method. This
-combination of different types of data about trophic interactions could
-be particularly useful when only a limited amount of diet information
-can be extracted by using a single method.
+In all of the seven food webs, the ADBM was able to infer the trophic
+interactions using incomplete predator guts because the presence absence
+information from the predator guts was still sufficient to constrain the
+possible model parameter values of the ADBM that best explained the
+predators' diets. Although in theory the ADBM can predict trophic
+interactions using only body sizes of organisms as it is based on set of
+foraging rules, it still requires some presence absence data to
+constrain the posterior parameter space thereby making more accurate
+predictions (Petchey et al. 2008).
+
+To characterise trophic interactions which are rare in the nature one
+would require more predator guts to observe those interactions as
+compared to characterising trophic interactions which are more frequent
+in the nature. The model is perhaps able to infer these rare
+interactions using a relatively lower number of predator guts which one
+might have inferred directly from the predator guts only after
+collecting a large number of gut content samples.
+
+Like any other food web models, the food web model used (the ADBM)
+cannot explain all the interactions in any observed food web that it has
+been fit to. The foraging rules it encodes are based on the body size
+and have particular structure and assumptions; not all of these are met
+by all observed interactions (Petchey et al. 2008). For example, the
+ADBM can only predict diets that are contiguous with respect to the size
+of prey. I.e. it cannot predict that a predator will consume organism of
+size 1 and 3, and not organism of size 2. Hence, if the observed diets
+are not contiguous when prey are ordered by their size, the estimation
+process could lead to a lower value of the TSS (Gupta, Furrer, and
+Petchey 2022).
+
+Furthermore, the observed data may be missing links, e.g.~links that
+rarely occur. Some of these food webs are undersampled (SI Fig. S2)
+suggesting those food webs might be missing these rare trophic links,
+and the false positives from a model might be a correctly predicted
+link. A future prospect could be to incorporate other sources of
+presence-absence data such as stable isotope ratio (Layman et al. 2007),
+DNA metabarcoding (Roslin and Majaneva 2016), literature review (Gray et
+al. 2015b; Cohen and Mulder 2014a; Goldwasser and Roughgarden 1993a) and
+experimentation (Warren 1989) to complement any trophic links that were
+missed by the gut content method.
+
+We expected a positive relationship between the minimum number of
+predator guts and the number of trophic links and number of species
+respectively. However, we did not find such relation (Fig.
+\ref{fig:fig_rb} (a, b)). We suspect this is due to the possibility that
+the food webs are sampled at different level (SI Fig. S2), with
+Broadstone Stream being the most sampled among all the food webs. Taking
+into account the undersampling factor resulted in a better fit between
+the corrected minimum number of predator guts and corrected number of
+trophic links and number of species respectively (Fig. \ref{fig:fig_rb}
+(c, d)), however did not result in a relationship. This could be due to
+heterogenity in the predator guts across food webs and heterogenity
+among food webs. First, if less number of prey items are present in a
+predator gut then more number of predator guts would need to be
+collected on an average to quantify the diet of that predator. Second, a
+food web which has a high proportion of generalist species would require
+a high number of predator guts on average to characterise the food web
+structure as compared to characterising the structure of a food web
+which has a high proportion of specialist species.
+
+In our study, we have not considered uncertainty which is involved in
+analysing the predator guts (Baker, Buckland, and Sheaves 2014). For
+example, there are sometimes loose tissues that are not identifiable and
+cannot be assigned to a specific prey item with certainty. There are
+factors such as sample size of consumers, mechanical prey handling,
+differential digestion and evacuation rates of different prey types and
+volumes, and the ingestion order that in combination result in an
+unquantifiable error which is difficult to interpret in the predator
+diet (Hyslop 1980; Rindorf and Lewy 2004; Baker, Buckland, and Sheaves
+2014). Therefore, the next step could be to incorporate these different
+factors of uncertainty in parameterising the model and to understand how
+these affect the accuracy of the predicted food webs.
 
@@
 \section{Acknowledgements}\label{acknowledgements}}
+
+This work was supported by the University Research Priority Program
+Global Change and Biodiversity (Grant number: U-704-04-11) of the
+University of Zurich. We thank the Petchey group members for their
+valuable suggestions in the manuscript.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-barnesPredatorPreyBody2008}{}}%
-Barnes, C., D. M. Bethea, R. D. Brodeur, J. Spitz, V. Ridoux, C.
-Pusineri, B. C. Chase, et al. 2008. {``Predator and {Prey Body Sizes} in
-{Marine Food Webs}.''} \emph{Ecology} 89 (3): 881--81.
-\url{https://doi.org/10.1890/07-1551.1}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-baumgartnerPredictiveLengthDry2003}{}}%
-Baumgärtner, Daniel, and Karl-Otto Rothhaupt. 2003. {``Predictive
-{Length}--{Dry Mass Regressions} for {Freshwater Invertebrates} in a
-{Pre-Alpine Lake Littoral}.''} \emph{International Review of
-Hydrobiology} 88 (5): 453--63.
-\url{https://doi.org/10.1002/iroh.200310632}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-benkeLengthMassRelationshipsFreshwater1999}{}}%
-Benke, Arthur C., Alexander D. Huryn, Leonard A. Smock, and J. Bruce
-Wallace. 1999. {``Length-{Mass Relationships} for {Freshwater
-Macroinvertebrates} in {North America} with {Particular Reference} to
-the {Southeastern United States}.''} \emph{Journal of the North American
-Benthological Society} 18 (3): 308--43.
-\url{https://doi.org/10.2307/1468447}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-blanchardClimateFishingInfluence2005}{}}%
-Blanchard, Julia L., Nicholas K. Dulvy, Simon Jennings, James R. Ellis,
-John K. Pinnegar, Alex Tidd, and Laurence T. Kell. 2005. {``Do Climate
-and Fishing Influence Size-Based Indicators of {Celtic Sea} Fish
-Community Structure?''} \emph{ICES Journal of Marine Science} 62 (3):
-405--11. \url{https://doi.org/10.1016/j.icesjms.2005.01.006}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-burgherrRegressionAnalysisLinear1997}{}}%
-Burgherr, Peter, and Elisabeth I. Meyer. 1997. {``Regression Analysis of
-Linear Body Dimensions Vs. Dry Mass in Stream Macroinvertebrates.''}
-\emph{Archiv Für Hydrobiologie}, April, 101--12.
-\url{https://doi.org/10.1127/archiv-hydrobiol/139/1997/101}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-caronAddressingEltonianShortfall}{}}%
@@
 \url{https://doi.org/10.1111/ele.13966}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cattinPhylogeneticConstraintsAdaptation2004}{}}%
+Cattin, Marie-France, Louis-F'elix Bersier, Carolin Banašek-Richter,
+Richard Baltensperger, and Jean-Pierre Gabriel. 2004. {``Phylogenetic
+Constraints and Adaptation Explain Food-Web Structure.''} \emph{Nature}
+427 (6977, 6977): 835--39. \url{https://doi.org/10.1038/nature02327}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-denglerWhichFunctionDescribes2009}{}}%
+Dengler, Jürgen. 2009. {``Which Function Describes the Species--Area
+Relationship Best? {A} Review and Empirical Evaluation.''} \emph{Journal
+of Biogeography} 36 (4): 728--44.
+\url{https://doi.org/10.1111/j.1365-2699.2008.02038.x}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-desjardins-proulxEcologicalInteractionsNetflix2017}{}}%
@@
 \url{https://doi.org/10.1046/j.1461-0248.2002.00354.x}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-edwardsRelationshipLengthMass2009}{}}%
-Edwards, François K. Lauridsen, Lucie Armand, Helen M. Vincent, and Iwan
-J. Jones. 2009. {``The Relationship Between Length, Mass and
-Preservation Time for Three Species of Freshwater Leeches
-({Hirudinea}).''} \emph{Fundamental and Applied Limnology} 173 (4):
-321--27. \url{https://doi.org/10.1127/1863-9135/2009/0173-0321}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-figueroaFoodWebDynamics2007}{}}%
-Figueroa, David. 2007. {``Food Web Dynamics : New Patterns from Southern
-{South America} and {North Wales UK}, and the Role of Basal Species
-Structuring Food Webs.''} PhD thesis, {University of London}.
-\url{https://ethos.bl.uk/OrderDetails.do?uin=uk.bl.ethos.582554}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ganiharBiomassEstimatesTerrestrial1997}{}}%
-Ganihar, S. R. 1997. {``Biomass Estimates of Terrestrial Arthropods
-Based on Body Length.''} \emph{Journal of Biosciences} 22 (2): 219--24.
-\url{https://doi.org/10.1007/BF02704734}.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-gonzalezSizemassRelationshipsStream}{}}%
-Gonzalez, Jose M, Ana Basaguren, and Jesus Pozo. 2002. {``Size-Mass
-Relationships of Stream Invertebrates in a Northern {Spain} Stream,''}
-7.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ogormanSimpleModelPredicts2019}{}}%
-Gorman, Eoin J. O', Owen L. Petchey, Katy J. Faulkner, Bruno Gallo,
-Timothy A. C. Gordon, Joana Neto-Cerejeira, J'on S. 'Olafsson, Doris E.
-Pichler, Murray S. A. Thompson, and Guy Woodwar. 2019. {``A Simple Model
-Predicts How Warming Simplifies Wild Food Webs.''} \emph{Nature Climate
-Change} 9 (8, 8): 611--16.
-\url{https://doi.org/10.1038/s41558-019-0513-x}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-gravelInferringFoodWeb2013}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-grayJoiningDotsAutomated2015}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-grayJoiningDotsAutomated2015a}{}}%
 Gray, Clare, David H. Figueroa, Lawrence N. Hudson, Athen Ma, Dan
-Perkins, and Guy Woodward. 2015. {``Joining the Dots: {An} Automated
+Perkins, and Guy Woodward. 2015a. {``Joining the Dots: {An} Automated
 Method for Constructing Food Webs from Compendia of Published
 Interactions.''} \emph{Food Webs} 5 (December): 11--20.
+\url{https://doi.org/10.1016/j.fooweb.2015.09.001}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-grayJoiningDotsAutomated2015}{}}%
+---------. 2015b. {``Joining the Dots: {An} Automated Method for
+Constructing Food Webs from Compendia of Published Interactions.''}
+\emph{Food Webs} 5 (December): 11--20.
 \url{https://doi.org/10.1016/j.fooweb.2015.09.001}.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-ingsEcologicalNetworksFood2009}{}}%
+Ings, Thomas C., Jos'e M. Montoya, Jordi Bascompte, Nico Blüthgen, Lee
+Brown, Carsten F. Dormann, François Edwards, et al. 2009. {``Ecological
+Networks--Beyond Food Webs.''} \emph{The Journal of Animal Ecology} 78
+(1): 253--69. \url{https://doi.org/10.1111/j.1365-2656.2008.01460.x}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-jenningsPredictingEffectsClimate2010}{}}%
+Jennings, Simon, and Keith Brander. 2010. {``Predicting the Effects of
+Climate Change on Marine Communities and the Consequences for
+Fisheries.''} \emph{Journal of Marine Systems} 79 (3-4): 418--26.
+\url{https://doi.org/10.1016/j.jmarsys.2008.12.016}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-jenningsTrophicLevelsMarine2015}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-meyerRelationshipBodyLength1989}{}}%
-MEYER, E. 1989. {``The Relationship Between Body Length Parameters and
-Dry Mass in Running Water Invertebrates.''} \emph{Arch Hydrobiol} 117:
-191--203. \url{https://ci.nii.ac.jp/naid/10019557615/}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-miserendinoRelacionesLongitudpesoPara2001}{}}%
-Miserendino, Mar'ıa L. 2001. {``Relaciones Longitud-Peso Para
-Macroinvertebrados de Ambientes Dulceacuícolas de {Patagonia}
-({Argentina}).''} \emph{Ecología Austral} 11 (1): 3--8.
-\url{http://www.scielo.org.ar/scielo.php?script=sci_abstract\&pid=S1667-782X2001000100002\&lng=es\&nrm=iso\&tlng=es}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-nielsen2018}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-ogormanSimpleModelPredicts2019}{}}%
+O'Gorman, Eoin J., Owen L. Petchey, Katy J. Faulkner, Bruno Gallo,
+Timothy A. C. Gordon, Joana Neto-Cerejeira, J'on S. 'Olafsson, Doris E.
+Pichler, Murray S. A. Thompson, and Guy Woodwar. 2019. {``A Simple Model
+Predicts How Warming Simplifies Wild Food Webs.''} \emph{Nature Climate
+Change} 9 (8, 8): 611--16.
+\url{https://doi.org/10.1038/s41558-019-0513-x}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-peralta-maraverStructureDynamicsStability2017}{}}%
@@
 \url{https://doi.org/10.1073/pnas.0710672105}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-pinnegarDoesDietCeltic2003}{}}%
-Pinnegar, J. K., V. M. Trenkel, A. N. Tidd, W. A. Dawson, and M. H. Du
-buit. 2003. {``Does Diet in {Celtic Sea} Fishes Reflect Prey
-Availability?''} \emph{Journal of Fish Biology} 63 (s1): 197--212.
-\url{https://doi.org/10.1111/j.1095-8649.2003.00204.x}.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-reissExistingPlentyAbundance2008}{}}%
-Reiss, Julia, and Jenny M. Schmid-Araya. 2008. {``Existing in Plenty:
-Abundance, Biomass and Diversity of Ciliates and Meiofauna in Small
-Streams.''} \emph{Freshwater Biology} 53 (4): 652--68.
-\url{https://doi.org/10.1111/j.1365-2427.2007.01907.x}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-rindorfBiasEstimatingFood2004}{}}%
@@
 \url{https://doi.org/10.1139/gen-2015-0229}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-schmid-arayaConnectanceStreamFood2002}{}}%
-Schmid-Araya, Jenny M., Peter E. Schmid, Anne Robertson, Julie
-Winterbottom, Charlotte Gjerløv, and Alan G. Hildrew. 2002.
-{``Connectance in {Stream Food Webs}.''} \emph{Journal of Animal
-Ecology} 71 (6): 1056--62. \url{https://www.jstor.org/stable/1555780}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-smockRelationshipsBodySize1980}{}}%
-Smock, Leonard A. 1980. {``Relationships Between Body Size and Biomass
-of Aquatic Insects.''} \emph{Freshwater Biology} 10 (4): 375--83.
-\url{https://doi.org/10.1111/j.1365-2427.1980.tb01211.x}.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-woodwardIndividualBasedFoodWebs2010}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-woodward2010}{}}%
 Woodward, Guy, Julia Blanchard, Rasmus B. Lauridsen, Francois K.
 Edwards, J. Iwan Jones, David Figueroa, Philip H. Warren, and Owen L.
-Petchey. 2010b. {``Individual-{Based Food Webs}.''} In \emph{Advances in
-{Ecological Research}}, 43:211--66. {Elsevier}.
-\url{https://doi.org/10.1016/B978-0-12-385005-8.00006-X}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-woodward2010}{}}%
----------. 2010a. {``Individual-Based Food Webs.''} In, 43:211--66.
+Petchey. 2010. {``Individual-Based Food Webs.''} In, 43:211--66.
 Elsevier. \url{https://doi.org/10.1016/B978-0-12-385005-8.00006-X}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-woodwardChapterIndividualBasedFood2010}{}}%
----------. 2010c. {``Chapter 6 - {Individual}-{Based Food Webs}:
-{Species Identity}, {Body Size} and {Sampling Effects}.''} In
-\emph{Advances in {Ecological Research}}, edited by Guy Woodward,
-43:211--66. Integrative {Ecology}: {From Molecules} to {Ecosystems}.
-{Academic Press}.
-\url{https://doi.org/10.1016/B978-0-12-385005-8.00006-X}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-woodwardBodysizeDeterminantsNiche2002}{}}%
-Woodward, Guy, and Alan G. Hildrew. 2002. {``Body-Size Determinants of
-Niche Overlap and Intraguild Predation Within a Complex Food Web.''}
-\emph{Journal of Animal Ecology} 71 (6): 1063--74.
-\url{https://doi.org/10.1046/j.1365-2656.2002.00669.x}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-woodwardQuantificationResolutionComplex2005}{}}%
-Woodward, Guy, Dougie C. Speirs, and Alan G. Hildrew. 2005.
-{``Quantification and {Resolution} of a {Complex}, {Size}-{Structured
-Food Web}.''} In \emph{Advances in {Ecological Research}}, 36:85--135.
-{Elsevier}. \url{https://doi.org/10.1016/S0065-2504(05)36002-8}.
 

### 2022-06-20 inst/main/best_estimates.R

@@ -2,11 +2,11 @@
 
 # We consider the best estimates of predicted food web using gut content data
 
-fw_name <- "Tadnoll Brook size_agg"
+fw_name <- "Trancura size_agg"
 dir_N <- 1e5
 dir_tol <- 2 #different for ind and rand
 n_gut_sample <- 100  
-propn <- c(seq(1, 688, 14), 688)
+propn <- seq(1, 47, by = 2)
 n_sel <- 1
 n <- length(propn)
 l_acc <- numeric(n)

### 2022-06-20 inst/main/extrapolating_ngut_Celtic_Sea.R

@@ -1,0 +1,64 @@
+### Let's try with Celtic Sea gut content data
+
+bs_pred <- readRDS("../C2_comp_qnty/data/Trancura size_agg.web.Rdata")$predation.matrix
+nspecies <- dim(bs_pred)[1]
+bs_gut <- readRDS("../C2_comp_qnty/data/gut_data/Trancura size_agg_ind_predator.gut.Rdata")
+
+ngut <- dim(bs_gut)[2]
+nlinks <- sum(bs_pred)
+
+link_mat <- matrix(data = 0, nrow = ngut, ncol = nlinks,  dimnames = list(1:ngut, 1:nlinks))
+
+### Renaming the column names of the link_mat matrix
+k <- 1
+for(pred_i in 1:nspecies){
+  for(prey_j in 1:nspecies){
+    if(bs_pred[prey_j, pred_i] == 1){
+      colnames(link_mat)[k] <- paste0("P", pred_i, "p", prey_j)
+      print(k)
+      k <- k + 1
+    }
+  }
+}
+
+
+#### Filling up the values in the link_mat matrix ####
+
+for(gut_index in 1:ngut){
+  for(prey_j in 1:nspecies){
+    gut_i_prey_j <- bs_gut[prey_j + 2, gut_index]
+    if(gut_i_prey_j == 1){
+      pred_index <-  bs_gut[, gut_index][2]
+      prey_index <- prey_j
+      gut_index <- gut_index
+      col_name_ind <- paste0("P", pred_index, "p", prey_index)
+      link_mat[,col_name_ind][gut_index] <- 1
+    }
+  }
+}
+
+
+link_acc_curve <- specaccum(link_mat)
+plot(link_acc_curve)
+
+pred <- poolaccum(link_mat)
+plot(pred, display = "chao")
+summary(pred, display = "chao")
+
+specpool(link_mat)
+estimateR(link_mat)
+specpool2vect(link_mat)
+
+
+sp1 <- specaccum(link_mat)
+plot(sp1, ci.type="poly", col="blue", lwd=2, ci.lty=0, ci.col="lightblue")
+
+mod1 <- fitspecaccum(sp1, "lomolino")
+plot(mod1, add = TRUE, col=2, lwd=2)
+
+
+estaccumR(link_mat, permutations = 100, parallel = getOption("mc.cores"))
+
+
+sp <- specpool(link_mat)
+estimateR(link_mat)

### 2022-06-20 inst/main/fig3_ms_mingut_vs_CSL.R

@@ -1,0 +1,139 @@
+# 2022.06.14
+# Plot how the minimum number of predator guts varied with food web summary: C, S and L
+
+library(ggplot2)
+library(ggpubr)
+library(dplyr)
+
+df_min_gut_vs_S <- readRDS("results/misc/df_min_gut_vs_S.RDS")
+
+
+#### Min gut vs C ####
+
+plot_n_min_gut_vs_C <- ggplot(df_min_gut_vs_S) +
+  geom_point(aes(x = C, y = n_min_gut), size = 5) +
+  geom_smooth(aes(x = C, y = n_min_gut), method = "lm", color = "black") +
+  theme_classic() +
+  scale_color_discrete(name = "Food web") +
+  xlab("Connectance (C)") +
+  labs(tag = "(a)") +
+  coord_cartesian(ylim = c(0, 450)) +
+  ylab("Minimum number of predator guts") +
+  theme(title = element_text(size = 15), text = element_text(size = 15))
+
+lm_n_min_gut_vs_C <- lm(n_min_gut ~ C, data = df_min_gut_vs_S)
+summary(lm_n_min_gut_vs_C)
+
+#### Min gut vs L ####
+
+plot_n_min_gut_vs_L <- ggplot(df_min_gut_vs_S) +
+  geom_point(aes(x = L, y = n_min_gut), size = 5) +
+  geom_smooth(aes(x = L, y = n_min_gut), method = "lm", color = "black") +
+  theme_classic() +
+  scale_color_discrete(name = "Food web") +
+  xlab("Number of trophic links (L)") +
+  labs(tag = "(a)") +
+  coord_cartesian(ylim = c(0, 450)) +
+  ylab("Minimum number of predator guts") +
+  theme(title = element_text(size = 15), text = element_text(size = 15))
+
+lm_n_min_gut_vs_L <- lm(n_min_gut ~ L, data = df_min_gut_vs_S)
+summary(lm_n_min_gut_vs_L)
+
+#### Min gut vs S ####
+
+plot_n_min_gut_vs_S <- ggplot(df_min_gut_vs_S) +
+  geom_point(aes(x = S, y = n_min_gut), size = 5) +
+  # geom_smooth(aes(x = S, y = n_min_gut), method = "lm", color = "black") +
+  theme_classic() +
+  scale_color_discrete(name = "Food web") +
+  xlab("Number of species (S)") +
+  labs(tag = "(b)") +
[…]

### 2022-06-20 inst/main/link_acc_vs_prey_items_curve.R

@@ -1,0 +1,283 @@
+# 2022.05.04
+# We plot the links accumulation curve wrt to the number of prey items
+
+library(ggplot2)
+library(dplyr)
+library(zoo)
+
+fw_list <- c("Broadstone Stream size_agg_v2",
+             "Celtic Sea size_agg",
+             "Tadnoll Brook size_agg",
+             "Afon Hirnant size_agg",
+             "Coilaco size_agg",
+             "Guampoe size_agg",
+             "Trancura size_agg")
+
+links_nitems <- data.frame(l_links = double(), u_links = double(), mean_links = double(),
+                           nitems = integer(), nsample = integer(), fw = character())
+for(fw_name in  fw_list){
+  fname_data <- paste("data/", fw_name, ".web.Rdata", sep="")
+  fw_data <- readRDS(fname_data)
+  nspecies <- dim(fw_data$predation.matrix)[1]
+  complete_pred_mat <- fw_data$predation.matrix
+  pred_nodes <- which(colSums(complete_pred_mat)>0)
+  
+  rule <- "ind_predator"
+  fname_gut <- paste("data/gut_data/", fw_name, "_", rule, ".gut.Rdata", sep="")
+  gut_data_main <- readRDS(file = fname_gut)
+  
+  desc_main <- "TSS_gut_ind"
+  
+  nitems <- sum(gut_data_main[-c(1,2),])
+  n_gut <- dim(gut_data_main[-c(1,2),])[2]
+  n_nodes <- dim(gut_data_main[-c(1,2),])[1]
+  items_data_main <- matrix(data = 0, nrow = n_nodes+2, ncol = nitems)
+  
+  k <- 1
+  for(ith_gut in 1:n_gut){
+    ith_gut_info <- gut_data_main[-c(1,2),ith_gut]
+    
+    item_ind <- which(ith_gut_info == 1)
+    for(ith_item in item_ind){
+      items_data_main[1,k] <-  gut_data_main[1,ith_gut]
+      items_data_main[2,k] <-  gut_data_main[2,ith_gut]
+      items_data_main[ith_item+2,k] <-  gut_data_main[2 + ith_item, ith_gut]
+      k <- k + 1
+    }
+  }
+  
+  
+  propn <- 1:length(items_data_main[1,])
+  n_gut_sample <- 100
+  
+  for(nitems in propn){
+    
+    links_array <- c()
+    for(n_sample in 1:n_gut_sample){
+      
[…]

### 2022-06-20 inst/main/model_TSS_vs_ngut.R

@@ -1,0 +1,289 @@
+# 2022.05.26
+# We plot the TSS of the predicted food webs wrt to number of predator guts
+
+library(ggplot2)
+library(ggpubr)
+
+df_min_gut_vs_S <- readRDS("../../../../../Volumes/SSD1/Secondary_storage/PhD_local/C2_files/Misc/df_min_gut_vs_S.RDS")
+
+#### Broadstone Stream #####
+
+####################################################################################################
+fw_name <- "Broadstone Stream size_agg_v2"
+
+dd_bs <- readRDS(paste0("../../../../../Volumes/SSD1/Secondary_storage/PhD_local/C2_files/", fw_name, "/rule_ind_predator/dd_bs.Rdata"))
+
+min_gut_bs <- df_min_gut_vs_S$n_min_gut[which(df_min_gut_vs_S$foodweb == "Broadstone Stream")]
+
+tsize <- 30
+
+### Black background ####
+# ggplot(dd_bs) +
+#   geom_vline(xintercept = min_gut_bs, color = "red", size = 2) +
+#   geom_line(aes(x = propn, y = mean_acc), size = 1, color = "white") +
+#   geom_ribbon(aes(x = propn, ymin = l_acc, ymax = r_acc), alpha = 0.5, show.legend = FALSE,
+#               position=position_dodge(width = 3), fill = "white") +
+#   xlab("Number of predator guts") +
+#   ylab("True skill statistic") +
+#   theme_classic() +
+#   scale_color_manual(name = "Gut content data", values = c("red", "blue")) +
+#   scale_x_continuous(breaks = as.integer(seq(1, 1008, length = 5))) +
+#   ggtitle("Broadstone Stream") +
+#   theme(text = element_text(size = 20, face = "bold", color = "white"), plot.title=element_text(hjust=0.5, size = 40, vjust = 3.5),
+#         panel.background = element_rect(fill = "black", colour = "black"),
+#         plot.background = element_rect(fill = "black", colour = "black"),
+#         axis.line = element_line(color  = "white"),
+#         axis.ticks = element_line(colour = "white"),
+#         axis.text = element_text(colour = "white"),
+#         axis.title.y = element_text(margin = margin(r = 10)),
+#         axis.title.x = element_text(margin = margin(t = 10)),
+#         plot.margin  = margin(t = 25))
+
+
+ggplot(dd_bs) +
[…]

### 2022-06-20 inst/main/mse_wrt_ngut.R

@@ -1,18 +1,32 @@
 # 04.05.2021
 # Computes mean standardised error in structural properties wrt ngut
 
-propn <- c(seq(481, 1008, by = 20), 1008)
+# 28.01.2022
+# Computes mean standardised error in structural properties wrt ngut for all food webs
+
+library(plotrix); library(ggplot2)
+library(cowplot); library(latex2exp); library(HDInterval)
+library(doParallel); library(foreach); library(raster)
+library(cheddar); library(dplyr); library(reshape2)
+library(psych); library(DirectedClustering); library(colorspace)
+library(R.utils)
+library(cheddar)
+library(bipartite)
+
+sourceDirectory("R", modifiedOnly=FALSE)
+prop_name <- c("connectance", "prop_basal", "prop_inter", "prop_top", "prop_herb",
+               "mean_omn", "clus_coeff", "sd_gen", "sd_vulner", "mean_max_trophic_sim", "mean_path_lt",
+               "nest_prop")
+
+
+#### For Broadstone Stream size_agg_v2 ####
+
+propn <- c(seq(1, 1008, by = 20), 1008)
 desc_main <- "TSS_gut_ind"
 rule <- "ind_predator"
 n_gut_sample <- 100
 dir_N <- 1e5
 dir_tol <- 2
-
-prop_name <- c("connectance", "prop_basal", "prop_inter", "prop_top", "prop_herb",
-               "mean_omn", "clus_coeff", "sd_gen", "sd_vulner", "mean_max_trophic_sim", "mean_path_lt",
-               "nest_prop")
-
-# prop_name <- c("sd_vulner")
 
 n_prop <- length(prop_name)
 plot_list <- list()
@@ -28,14 +42,14 @@ real_prop_org <- real_prop_predator(foodweb_data)
 
 SE_vs_ngut <- data.frame(l_SE = double(), u_SE = double(), mean_SE = double(),
                         ngut = integer(),
-                        foodweb = character())
+                        foodweb = character(), foodweb = character())
 
 for(ngut in propn){
   
   desc <- paste(desc_main, '_l', ngut, sep = '')
[…]

### 2022-06-20 inst/main/species_agg_gut_data_afon_hirnant.R

@@ -1,0 +1,14 @@
+# 15.06.2022
+# Compile individual predator guts in species aggregated way
+
+
+library(dplyr)
+library(ggplot2)
+
+bs_data <- read.csv("~/Google Drive/PhD (UZH)/tadnoll/AfonHirnantData_Gilljam_etal_AER_v45ch3.csv", comment.char="#")
+
+pred_species <- unique(bs_data$predID)
+prey_species <- unique(bs_data$preyID)
+
+species_name <- unique(union(pred_species, prey_species))
+

### 2022-06-20 inst/main/species_agg_gut_data_celtic_sea.R

@@ -1,0 +1,16 @@
+# 13.06.2022
+# Compile individual predator guts in species aggregated way
+
+library(dplyr)
+library(ggplot2)
+library(readr)
+
+
+bs_data <- read_delim("../../GitHub/Celtic Sea/data/Predator_and_prey_body_sizes_in_marine_food_webs_vsn4.txt", 
+                      "\t", escape_double = FALSE, trim_ws = TRUE)
+bs_data <- bs_data %>%
+  filter(!Prey %in% c("fish larvae", "fish unidentified", "flatfish") ) %>%
+  filter(!is.na(Prey) & !is.na(Predator)) %>%
+  filter(`Geographic location` == "Europe, Celtic Sea ecosystem")
+
+

### 2022-06-20 inst/main/standardising_link_acc_curve.R

@@ -1,0 +1,218 @@
+# 2022.05.16
+# We standardise link accumulation curves across the food webs i.e. we estimate the number of gut content data for all the 
+# food webs that would have resulted in a fully sampled food web
+
+library(dplyr)
+library(ggplot2)
+library(zoo)
+
+foodweb_list <- c("Broadstone Stream",
+             "Celtic Sea",
+             "Tadnoll Brook",
+             "Afon Hirnant",
+             "Coilaco",
+             "Guampoe",
+             "Trancura")
+
+links_ngut_bs <- readRDS("../../../../../Volumes/SSD1/Secondary_storage/PhD_local/C2_files/Broadstone Stream size_agg_v2/rule_ind_predator/empirical_links_ngut.Rdata")
+links_ngut_cs <- readRDS("../../../../../Volumes/SSD1/Secondary_storage/PhD_local/C2_files/Celtic Sea size_agg/rule_ind_predator/empirical_links_ngut.Rdata")
+links_ngut_tb <- readRDS("../../../../../Volumes/SSD1/Secondary_storage/PhD_local/C2_files/Tadnoll Brook size_agg/rule_ind_predator/empirical_links_ngut.Rdata")
+links_ngut_ah <- readRDS("../../../../../Volumes/SSD1/Secondary_storage/PhD_local/C2_files/Afon Hirnant size_agg/rule_ind_predator/empirical_links_ngut.Rdata")
+links_ngut_co <- readRDS("../../../../../Volumes/SSD1/Secondary_storage/PhD_local/C2_files/Coilaco size_agg/rule_ind_predator/empirical_links_ngut.Rdata")
+links_ngut_gu <- readRDS("../../../../../Volumes/SSD1/Secondary_storage/PhD_local/C2_files/Guampoe size_agg/rule_ind_predator/empirical_links_ngut.Rdata")
+links_ngut_tr <- readRDS("../../../../../Volumes/SSD1/Secondary_storage/PhD_local/C2_files/Trancura size_agg/rule_ind_predator/empirical_links_ngut.Rdata")
+
+links_ngut_bs_1 <- mutate(links_ngut_bs, foodweb = "Broadstone Stream")
+links_ngut_cs_1 <- mutate(links_ngut_cs, foodweb = "Celtic Sea")
+links_ngut_tb_1 <- mutate(links_ngut_tb, foodweb = "Tadnoll Brook")
[…]

### 2022-06-20 inst/main/standardising_link_acc_curve_vegan.R

@@ -1,0 +1,229 @@
+# 2022.05.23
+# We standardise the link accumulation curves across the food webs with the help of vegan package
+
+library(vegan)
+library(ggplot2)
+library(dplyr)
+library(zoo)
+
+fw_ngut <- data.frame(foodweb = character(), max_gut = integer())
+
+#### Broadstone Stream ####
+bs_pred <- readRDS("../C2_comp_qnty/data/Broadstone Stream size_agg_v2.web.Rdata")$predation.matrix
+nspecies_bs <- dim(bs_pred)[1]
+bs_gut <- readRDS("../C2_comp_qnty/data/gut_data/Broadstone Stream size_agg_v2_ind_predator.gut.Rdata")
+max_gut_bs <- dim(bs_gut)[2]
+nlinks_bs <- sum(bs_pred)
+link_mat_bs <- matrix(data = 0, nrow = max_gut_bs, ncol = nlinks_bs,  dimnames = list(1:max_gut_bs, 1:nlinks_bs))
+
+fw_ngut <- data.frame(foodweb = "Broadstone Stream", max_gut = max_gut_bs)
+
+#### Link mat matrix for Broadstone Stream ####
+
+k <- 1
+for(pred_i in 1:nspecies_bs){
+  for(prey_j in 1:nspecies_bs){
+    if(bs_pred[prey_j, pred_i] == 1){
+      colnames(link_mat_bs)[k] <- paste0("P", pred_i, "p", prey_j)
+      print(k)
+      k <- k + 1
+    }
+  }
+}
+
+
+#### Filling up the values in the link_mat matrix ####
+
+for(gut_index in 1:max_gut_bs){
+  for(prey_j in 1:nspecies_bs){
+    gut_i_prey_j <- bs_gut[prey_j + 2, gut_index]
+    if(gut_i_prey_j == 1){
+      pred_index <-  bs_gut[, gut_index][2]
+      prey_index <- prey_j
+      gut_index <- gut_index
+      col_name_ind <- paste0("P", pred_index, "p", prey_index)
+      link_mat_bs[,col_name_ind][gut_index] <- 1
+    }
+  }
+}
+
+#### the vegan package ####
+
+link_acc_curve_bs <- specaccum(link_mat_bs)
+plot(link_acc_curve_bs)
+
+link_acc_df <- data.frame(ngut = link_acc_curve_bs$sites,
+                          nlink = link_acc_curve_bs$richness,
+                          foodweb = "Broadstone Stream")
+
[…]

### 2022-06-20 inst/main/str_prop_v3.R

@@ -12,8 +12,8 @@ library(bipartite)
 ## Relative path from the project directory
 sourceDirectory("R", modifiedOnly=FALSE)
 
-fw_name <- "Broadstone Stream size_agg_v2"
-propn <- c(seq(1, 1008, by = 20), 1008)
+fw_name <- "Coilaco size_agg"
+propn <- c(73, 74)
 
 dir_N <- 1e5
 dir_tol <- 2 #different for ind and lbs and ubs
@@ -28,7 +28,7 @@ fw_data <- readRDS(fname_data)
 model_core_par <- ADBM_core_par(fw_data)
 
 par_accepted <- readRDS(paste("../../../../../Volumes/SSD1/Secondary_storage/PhD_local/C2_files/", fw_name, "/rule_", rule, 
-                              "/accepted_ones/accepted_par.Rdata",
+                              "/accepted_par/accepted_par.Rdata",
                               sep = ""))
 
 n_cores <- 4
@@ -58,7 +58,7 @@ foreach(k = 1:n_cores) %dopar%
       calc_prop <- fw_prop_predator(foodweb = prop_acc_accepted, other = model_core_par, all.web.info = fw_data)
       
       fname_prop <- paste0("../../../../../Volumes/SSD1/Secondary_storage/PhD_local/C2_files/", fw_name, "/rule_", rule, 
-                           "/accepted_ones/properties/", "/", fw_name,"_n_diet=", i, "_properties.Rdata")
+                           "/accepted_par/properties/", "/", fw_name,"_n_diet=", i, "_properties.Rdata")
       saveRDS(object = calc_prop, file = fname_prop)
       print(i)
     }

### 2022-06-20 inst/main/threshold.R

@@ -242,6 +242,9 @@ df_min_gut_vs_S <- rbind(df_min_gut_vs_S,
 
 
 # saveRDS(object = df_min_gut_vs_S, file = "results/misc/df_min_gut_vs_S.RDS")
+
+df_min_gut_vs_S <- readRDS("results/misc/df_min_gut_vs_S.RDS")
+
 ###############################
 
 
@@ -251,6 +254,66 @@ plot_n_min_gut_vs_S <- ggplot(df_min_gut_vs_S) +
   scale_color_discrete(name = "Food web") +
   xlab("Number of species (S)") +
   ylab("Number of minimum gut")
+
+df_min_gut_vs_S <- df_min_gut_vs_S %>%
+  mutate(S_sq = S^2)
+
+library(latex2exp)
+
+ggplot(df_min_gut_vs_S) +
+  geom_point(aes(x = S_sq, y = n_min_gut), size = 5) +
+  theme_classic() +
+  scale_color_discrete(name = "Food web") +
+  xlab(TeX("$(Number~of~species)^2$")) +
+  ylab("Minimum number of predator guts") +
+  scale_y_continuous(breaks = as.integer(seq(1, 400, length = 5))) +
+  # scale_x_continuous(breaks = as.integer(seq(25, 65, length = 3))) +
+  theme(text = element_text(size = 20), plot.title=element_text(hjust=0.5, size = 40, vjust = 3.5),
+        axis.title.y = element_text(margin = margin(r = 10)),
+        axis.title.x = element_text(margin = margin(t = 10)),
+        plot.margin  = margin(t = 25, l = 10, b = 10)) +
+  coord_cartesian(ylim = c(1, 400))
+
+# ggsave(filename = "results/misc/plot_n_min_gut_vs_S_sq.png", dpi = 500)
+
+#### Black background ####
+
+df_min_gut_vs_S <- df_min_gut_vs_S %>%
+  mutate(S_sq = S^2)
+  
+library(latex2exp)
+
+ggplot(df_min_gut_vs_S) +
+  geom_point(aes(x = S_sq, y = n_min_gut), color = "white", size = 5) +
+  theme_classic() +
+  scale_color_discrete(name = "Food web") +
+  xlab(TeX("$(Number~of~species)^2$")) +
+  ylab("Number of minimum predator gut") +
+  scale_y_continuous(breaks = as.integer(seq(1, 400, length = 5))) +
+  # scale_x_continuous(breaks = as.integer(seq(25, 65, length = 3))) +
[…]

### 2022-06-20 manuscript/ms_C2/ms_C2_v2.Rmd
Update ms_C2_v2.Rmd

@@
 
-  1)  One of the biggest obstacles in food web ecology is the time and effort required to adequately describe the structure of a food web using individual predator guts.
+  1)  A large obstacle in food web ecology is the time and effort required to adequately describe the structure of a food web using individual predator guts.
 Food web models such as the allometric diet breadth model (ADBM) can be used to circumvent this problem by predicting the interactions based on easily measured characteristics, such as the size of organisms.
-However, presence-absence data such as predator guts is required to parameterise these food web models, and collecting and analysing these data from the field is an expensive and time-consuming task.
-Therefore, it is crucial to know how much predator guts is required to parameterise food web models with high accuracy and high precision.
-  2)  Here, we explore seven exceptionally well-characterised food webs in the literature and determine the minimum predator guts that would be needed to accurately predict their structure using the ADBM.
-We use Bayesian computation to parameterise the ADBM, and true skill statistics to measure the goodness of fit, and do so while varying the amount of predator guts used in the parameterisation to test the effect of sampling effort.
-  3)  We found that incomplete predator guts can be used to parameterise the ADBM, with the lowest amount of predator guts being 28% of the available predator guts.
-  4)  These results suggest that one need not collect such a large quantity of predator guts to predict the structure of a food web, thereby reducing sampling effort considerably, while having little effect on precision or accuracy of predictions.
+However, diet data such as that which comes from analysis of  predator guts is still required to parameterise these food web models, and collecting and analysing these data from the field is an expensive and time-consuming task.
+Therefore, it is important to know how much predator guts is required to parameterise food web models to obtain high accuracy and high precision.
+  2)  Here, we explore seven exceptionally well-characterised food webs and determine the minimum number of predator guts needed to accurately predict their structure using the ADBM.
+We use Bayesian computation to parameterise the ADBM, and true skill statistics to measure the goodness of fit, and do so while varying the number of predator guts used in the parameterisation to test the effect of sampling effort.
+  3)  We found that relatively few, and many fewer than were actually collected, predator guts can be used to parameterise the ADBM.
+The lowest number of predator guts was 28% of the number of available predator guts.
+  4)  These results suggest that one need not collect and analyse such a large quantity of predator guts in order to adequately predict the structure of a food web, thereby reducing sampling effort considerably, while having little effect on precision or accuracy of predictions.
 
@@
 
-Knowledge about the trophic interactions in a food web is crucial in ecology for purposes ranging from identifying keystone species [@jordanKeystoneSpeciesFood2009] to quantifying robustness of a food web to species extinctions [@dunneNetworkStructureBiodiversity2002].
+Knowledge about the trophic interactions in a food web is crucial in ecology for purposes ranging from identifying keystone species [@jordanKeystoneSpeciesFood2009], to quantifying robustness of a food web, and to predicting species extinctions [@dunneNetworkStructureBiodiversity2002].
 This has led to the development of numerous food web models and associated theory [@allesinaGeneralModelFood2008; @cohenStochasticTheoryCommunity1985; @gravelInferringFoodWeb2013; @petcheySizeForagingFood2008; @tamaddoni-nezhadConstructionValidationFood2013].
@@
 
-Although food web models are constructed using prior theory about the factors that determine trophic interactions, empirical data about interactions are required to parameterise a model.
+Although food web models are constructed using prior theory and hypotheses about the factors that determine trophic interactions, empirical data about interactions are required to parameterise them.
 For example, @petcheySizeForagingFood2008 and @guptaSimultaneouslyEstimatingFood2022 used presence-absence information about trophic interactions to parameterise the allometric diet breadth model and thereby predict species interactions.
-Such empirical information about interactions can come from diverse set of methods such as gut content analysis [@peralta-maraverStructureDynamicsStability2017], stable isotope ratio analysis of tissues [@laymanCanStableIsotope2007], experimentation [@warrenSpatialTemporalVariation1989], DNA metabarcoding of gut contents or faeces [@roslinUseDNABarcodes2016] and literature research [@grayJoiningDotsAutomated2015; @cohenSoilInvertebratesChemistry2014; @goldwasserConstructionAnalysisLarge1993a] but each of these sources of information about trophic interactions has serious shortcomings, hindering the advancement of the field.
+Such empirical information about interactions can come from diverse set of methods such as gut content analysis [@peralta-maraverStructureDynamicsStability2017], stable isotope ratio analysis of tissues [@laymanCanStableIsotope2007], experimentation [@warrenSpatialTemporalVariation1989], DNA metabarcoding of gut contents or faeces [@roslinUseDNABarcodes2016] and literature research [@grayJoiningDotsAutomated2015; @cohenSoilInvertebratesChemistry2014; @goldwasserConstructionAnalysisLarge1993a].
+Nevertheless, each of these sources of information about trophic interactions has shortcomings that hinder the advancement of the field.
 For example: stable isotope ratio analysis of the organism's tissue does not give direct taxonomically resolved information of the diet of that organism, but rather it provides approximate trophic position of that species in the food web [@wadaUseStableIsotopes1991; @jenningsTrophicLevelsMarine2015] and although mixing models can be used to determine what prey items are most likely fed upon by a predator, this results in uncertainty in the estimates [@kadoyaIsoWebBayesianIsotope2012; @crawfordApplicationsStableIsotope2008].
-Similarly, more recent approaches using DNA metabarcoding may give much higher taxonomic resolution but present other challenges, such as an inability to resolve secondary predation or cannibalism [@pompanonWhoEatingWhat2012; @nielsen2018] which are common in nature and also being prone to environmental contamination (e.g.
+Similarly, more recent approaches using DNA metabarcoding may give much higher taxonomic resolution but present other challenges, such as not providing trait information (e.g.
+body sizes of prey) and an inability to resolve secondary predation or cannibalism [@pompanonWhoEatingWhat2012; @nielsen2018] which are common in nature.
+Furthermore, DNA approaches are prone to environmental contamination (e.g.
 DNA in the water swallowed along with DNA from an aquatic consumer's prey cannot be differentiated from actual prey) [@kellyUsingEnvironmentalDNA2014].
-Furthermore, construction of food webs via literature review, which is one of the most common practices in food web research, can lead to false positives--links included when in reality no link would occur because it makes an assumption that the species interactions inferred from a system will occur in another system as well [@grayJoiningDotsAutomated2015; @cohen2014; @goldwasser1993].
-It is unsurpsing given the limitations of these proxy or inferential approaches that authors such as @nielsen2018 have shown that gut content analysis method has a better match with real diet when compared to other methods.
+Construction of food webs via literature review, common practice in food web research, can lead to false positives--links included when in reality no link would occur because it makes an assumption that the species interactions inferred from a system will occur in another system as well [@grayJoiningDotsAutomated2015; @cohen2014; @goldwasser1993].
+It is unsurpising given the limitations of these proxy or inferential approaches that authors such as @nielsen2018 have shown that gut content analysis based method have a better match with real diet when compared to other methods.
 
-Although gut content analysis is viewed as the "gold standard", acquiring such food web data from direct gut content analysis is extremely time consuming and expensive [@grayJoiningDotsAutomated2015a] and it also requires high skill levels in taxonomic identification, often involving dissection and microscopy techniques [@hyslopStomachContentsAnalysis1980].
+Although gut content analysis is viewed as the "gold standard", acquiring food web data from direct gut content analysis is extremely time consuming and expensive [@grayJoiningDotsAutomated2015a].
+It also requires high skill levels in taxonomic identification, often involving dissection and microscopy techniques [@hyslopStomachContentsAnalysis1980].
 The perception that this is unavoidably laborious and costly is also in part due to the assumption that many gut contents must be collected and analysed in order to be confident that the majority of possible trophic links among species have been observed.
-Most studies fail to quantify the effort needed, with yield-effort curves being the exception rather than the rule and those that have been done often point to the apparent need for hundreds or thousands of guts to be analysed to fully capture a food web's structure.
-Hence, it is of huge importance to know the minimum number of predator guts required to parameterise a food web model with high accuracy and high precision: this would enable researchers to allocate resources more effectively a priori, and even having a rough rule of thumb as to when is a good point to stop collecting any further empirical data on the food web is far better than the current common practice of simply taking a fixed set of samples with on yield-effort analyses being undertaken.
+Some studies fail to quantify the effort needed, with yield-effort curves being the exception rather than the rule and those that have been quantified often point to the apparent need for hundreds or thousands of guts to be analysed to fully capture a food web's structure.
+Hence, it is ofconsiderable importance to know the minimum number of predator guts required to parameterise a food web model with high accuracy and high precision: this would enable researchers to allocate resources more effectively a priori.
+Moreover, a rough rule of thumb of when to stop collecting data from gut contents would provide an method to adapt the amount of sampling/analysis during the sampling/analysis process itself.
 
-Therefore, the key question we are interested in answering is how much presence-absence information, in the form of predator guts, is required to infer food web structure from a food web model with high accuracy and high precision?
-In other words, how many samples of predator guts should one collect from the field to parameterise a food web model?
-To answer this question, we use different amount of predator guts to parameterise the allometric diet breadth model (ADBM) thereby predicting trophic interactions in seven different food webs using rejection approximate Bayesian computation, and calculate the minimum number of predator guts to infer food web structure.
+Therefore, the key question we wish to answer is how much diet information, coming from predator guts, is required to infer food web structure from a food web model with adequate accuracy and precision?
+In other words, how many samples of predator guts should one collect and analyse from the field to parameterise a food web model?
+To answer this question, we vary the  amount of predator gut data that is used to parameterise the allometric diet breadth model (ADBM) and record how well the model can then predict the food web produced when all available gut content data is used.
+We do this separately for seven different food webs, for each calculating the minimum number of predator guts required to adequately infer food web structure.
 Our study provides a guideline on how many predator guts are required to predict food web structure using a food web model.
@@
 
-We present the empirical food webs, the allometric diet breadth model (ADBM), and the predator guts used to infer the trophic interactions.
+Here we present the empirical food webs, the allometric diet breadth model (ADBM), and the predator guts used to infer the trophic interactions.
 We also give a detailed account of using partial predator guts to parameterise the ADBM using rejection approximate Bayesian computation (ABC).
@@
 
-In our study, we used food webs for which predator guts are available at an individual level and data that is or that we could make FAIR (Findable Accessible Interoperable Reusable; @wilkinsonFAIRGuidingPrinciples2016).
-In our study, first, we consider food webs where nodes are size classes i.e.
+In our study,  @wilkinsonFAIRGuidingPrinciples2016).
+
+Traditionally, food webs describe the trophic links among species (i.e.
+each of the species is a node in the food web, and links occur when one species preys on another).
+However, we consider food webs where nodes are size classes, i.e.
 individuals are aggregated into these size classes based on their body size.
 A feeding link occurs between two size classes if at least one prey item within a size class was found in the gut of another size class of predator, irrespective of the taxonomy of the individuals.
-We used this approach because of several reasons such as to take account the ontogenetic shift in the diet of a predator [@woodward2010], individual-based interaction based on body size which would not been considered if nodes were aggregated based on taxonomy as a taxonomic node can have a large variation in the body size.
-Food webs aggregated using size can be used to model the impacts of commercial exploitation on marine ecosystems [@jenningsPredictingEffectsClimate2010].
-Second, we also consider food webs where nodes are aggregated based on the taxonomy of the individuals as this is the most common way of constructing food webs in food web ecology.
+We used this approach for several reasons, such as to take account the ontogenetic shifts in the diet of a predator [@woodward2010], and to account for individual-based interactions which would not been considered if nodes were aggregated based on taxonomy, because a taxonomic group can have a large variation in the body size.
+This size-based approach has often been used in strongly size structured ecosystems that also have considerable intraspecific sze variation and has been instrumental in understanding commercial exploitation of marine ecosystems [@jenningsPredictingEffectsClimate2010].
+Second, we also consider more traditional food webs where nodes are aggregated based on the taxonomy of the individuals.
 
-Our study food webs are freshwater food webs except the Celtic Sea food web which belongs to a marine ecosystem.
+We analysed food webs for which predator guts are available at an individual level, with body size data, and with data that is or that we could make FAIR (Findable Accessible Interoperable Reusable;Our study food webs are freshwater food webs except the Celtic Sea food web which belongs to a marine ecosystem.
 Most of the food webs are dominated by invertebrates except Celtic Sea which is dominated by fishes and Tadnoll Brook which is dominated by fishes as well as invertebrates.
@@
 Regression equations were used to convert predator and prey lengths to the respective body masses.
-In case if the prey items were too highly digested for body lengths to be measured reliably, previously established regressions based on head capsule width were used as an alternative linear dimension.
+In case highly digested prey, previously established regressions based on head capsule width were used as an alternative linear dimension.
 More detailed description of these food webs is present in @gilljamSeeingDouble2011.
@@
 species or sizes classes) a consumer should feed upon to maximise its rate of energy intake [@petcheySizeForagingFood2008].
-The foraging variables in the model are: energy content of the resources, handling times of the prey, space clearance rate, and prey densities.
-These are allometrically scaled to the body sizes of the species.
+The foraging variables in the model are: energy content of the prey, handling times of the predator on a prey, space clearance rate (how fast a predator searches space), and prey densities.
+Each of these are predicted from allometric scaling relationship, thus the model requires body sizes and the allometric constants and exponents in order to make predictions.
 Further details on the foraging rules defined in the ADBM and ADBM's predictive power across different food webs can be found in @petcheySizeForagingFood2008.
@@
 
-The accuracy of the predicted diet of the predators was measured using a widely used accuracy measure in food web ecology namely true skill statistic (TSS) [@grayJoiningDotsAutomated2015; @gravelInferringFoodWeb2013; @guptaSimultaneouslyEstimatingFood2022].
-We chose this metric because it takes into account the true and false predictions of both the presence and absence of links defined as:
+The accuracy of the predicted diet of the predators was measured using a widely used accuracy measure in food web ecology, namely the true skill statistic (TSS) [@grayJoiningDotsAutomated2015; @gravelInferringFoodWeb2013; @guptaSimultaneouslyEstimatingFood2022].
+We chose this metric because it takes into account the true and false predictions of both the presence and absence of links.
+It is defined as:
 
-$$ \text{TSS} = \frac{ad-bc}{(a+c)(b+d)} $$ where $a$ is the number of observed links that are predicted by the model (true positives), $d$ is the number of observed absences of links that are correctly predicted (true negatives), $b$ is the number of false positives, and $c$ is the number of false negatives.
+$$ \text{TSS} = \frac{ad-bc}{(a+c)(b+d)} $$
+
+where $a$ is the number of observed links that are predicted by the model (true positives), $d$ is the number of observed absences of links that are correctly predicted (true negatives), $b$ is the number of false positives, and $c$ is the number of false negatives.
 The $TSS$ ranges from $-1$ to $1$, where +1 indicates a perfect prediction.
-A $TSS$ value of zero or less indicates a performance no better than random [@alloucheAssessingAccuracySpecies2006].
+A $TSS$ value of zero  indicates a performance no better than random, and less than zero indicates performance worse than random [@alloucheAssessingAccuracySpecies2006].
 
-## Inferring food web using partial predator guts
+## Parameterisation using partial predator gut information
 
@@
 We then fit the ADBM to this partial dataset.
+
+**OP: please ensure that this figure is cited in the text.
 
@@
 
-To fit the ADBM to partial predator guts dataset, we used the rejection approximate Bayesian computation method we previously developed in @guptaSimultaneouslyEstimatingFood2022 to accept a parameter value from a prior distribution which would have resulted in the minimum distance, where distance = 1 - TSS.
+To fit the ADBM to partial predator guts dataset, we used the rejection approximate Bayesian computation method we previously developed in @guptaSimultaneouslyEstimatingFood2022.
+In brief, we accept a parameter value from a prior distribution which would have resulted in a predicted food that has sufficient similarity to the observed food web.
 The true skill statistic was computed between the diets predicted from the ADBM, and those observed in the sampled predator guts.
 We repeated this process $n~(= 100)$ times for every $i$ number of guts, where $i$ lies between 1 and total number of predator guts in the pool.
+Pseudo-code for the procedure follows:
 
@@
 
--   A model prediction $model(\theta): ADBM(\theta) = \{d_{p_1}, d_{p_1}, \dots, d_{p_k}\}$, where $d_{p_k}$ is the predicted diet matrix of predator $k$ containing ones and zeros.
+-   A model prediction $model(\theta): ADBM(\theta) = \{d_{p_1}, d_{p_2}, \dots, d_{p_k}\}$, where $d_{p_k}$ is the predicted diet matrix of predator $k$ containing ones and zeros.
 
@@
 
+**OP: should the meaning of x_i and y be specified?
+
 -   An observed food web $Y: Y = \{d_{p_1}', d_{p_1}', \dots, d_{p_k}'\}$, where $d_{p_k}'$ is the observed diet matrix of predator $k$ containing ones and zeros.
@@
 
-for $i = 1, \dots, tgut$ where $tgut$ is the total number of predator guts in the pool $G$
+for $i = 1, \dots, totalgut$ where $totalgut$ is the total number of predator guts in the pool $G$
 
@@
 
-Using TSS of the model predicted food webs for different number of predator guts, we computed the number of predator guts that results in the mean TSS equal to the 95% of the mean TSS achieved by the model using all the predator guts available in the pool for a food web.
-We call this number of predator guts as the minimum number of predator guts.
+Using the TSS of the model predicted food webs for different number of predator guts, we computed the number of predator guts that results in the mean TSS equal to the 95% of the mean TSS achieved by the model using all the predator guts available in the pool for a food web.
+We term this number of predator guts the "minimum number of predator guts".
 
@@
 
-Since the seven food webs have different levels of sampling effort, with Broadstone Stream being the most sampled among all, and every other food web being undersampled when compared to the Broadstone Stream food web (SI Fig.
-S2), we used the R *vegan* package to account for the undersampling with respect to the Broadstone Stream food web.
-We fitted the link accumulation curves using the fitspecaccum function to a set of nonlinear regression models suggested in @denglerWhichFunctionDescribes2009 and used the AIC criteria for model selection.
-We then extrapolated the link accumulation curves for all the food webs except the Broadstone Stream and computed the corrected number of predator guts that would have resulted in the gradient of the link accumulation curve equal to the gradient of that of the Broadstone Stream when all the predator guts were used.
+Since the seven food webs have different levels of sampling effort, with Broadstone Stream being the most sampled among all, and every other food web being considerably less well sampled (SI Fig.
+S2), we wished to attempt to compensate for this in our analyses.
+To do this we used the R *vegan* package to account for the undersampling with respect to the Broadstone Stream food web.
+We fitted the link accumulation curves using the *fitspecaccum* function to a set of nonlinear regression models suggested in @denglerWhichFunctionDescribes2009 and used the AIC criteria for model selection.
+We then extrapolated the link accumulation curves for all the food webs except the Broadstone Stream and computed the  number of predator guts that would have resulted in the gradient of the link accumulation curve equal to the gradient of that of the Broadstone Stream when all the predator guts were used.
 We also calculated the corrected number of trophic links corresponding to that corrected number of predator guts.
-For the food webs, we calculated the undersampling factor which is equal to the ratio of corrected number of predator guts to the number of predator guts in the pool.
-Using the undersampling factor, we further calculated the corrected minimum number of predator guts which is equal to the product of the undersampling factor and the minimum number of predator guts.
+For each food web, we then calculated an undersampling factor, equal to the ratio of corrected number of predator guts to the number of predator guts in the pool.
+Using the undersampling factor, we further calculated the corrected minimum number of predator guts, which was the product of the undersampling factor and the minimum number of predator guts.
 
@@
 We first present how the accuracy of the food web model in predicting trophic interactions varies with increasing amount of predator guts provided to the food web model.
-We investigate how the minimum number of predator guts varied with number of trophic links and number of species.
+We then show how the minimum number of predator guts varied with number of trophic links and number of species.
 
 ```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_ra} Accuracy of the predicted food web measured using the true skill statistic, predicted by the ADBM parameterised using predator guts.
-Line and shaded grey region represents the mean and the prediction interval corresponding to 100 independent samples respectively.
-Red line represents the number of predator guts required to achieve a TSS of 95\\% of the maximum TSS."}
+The line and the shaded grey region represents the mean and the prediction interval corresponding to 100 independent samples respectively.
+The red line represents the number of predator guts required to achieve a TSS of 95\\% of the maximum TSS."}
 knitr::include_graphics("../../results/misc/plot_TSS_vs_ngut.png")
@@
 \ref{fig:fig_ra}).
-Furthermore, the width of the prediction interval of the true skill statistics decreased with increasing number of predator guts with the mean TSS asymptoting to the maximum mean TSS achieved by the ADBM when all the predator guts was used.
-Although the maximum TSS varied among the food webs, the qualitative increase in the TSS was the same.
+Furthermore, the width of the prediction interval of the true skill statistics decreased with increasing number of predator guts, with the mean TSS asymptoting to the maximum mean TSS achieved by the ADBM when all the predator guts was used.
+Although the maximum TSS varied among the food webs, the qualitative increase in the TSS was the same for all.
 
@@
 This was equivalent to 95% of the mean TSS (0.78) achieved using complete predator guts (Fig.
-\ref{fig:fig_ra}(a)): i.e.
+\ref{fig:fig_ra}(a)).
+I.e.
 the main characteristics of the food web could be captured with about 1/3 of the effort used in the original study.
-In case of the Celtic Sea food web, only 171 predator guts which is 35% of the total predator guts was required by the ADBM to predict food web with TSS equal to 95% of the mean TSS (0.68) achieved using complete predator guts (Fig.
+In case of the Celtic Sea food web, only 171 predator guts, which is 35% of the total predator guts sampled and analysed, was required by the ADBM to predict food web with TSS equal to 95% of the mean TSS (0.68) achieved using complete predator guts (Fig.
 \ref{fig:fig_ra}(b)).
+
+**OP: for contrast, how about describing the pattern in Trancura, since it is quite different?
+
+**OP: Its important to add to the Introduction some rationale / justification for the following analysis. What was the goal and reason for doing it?
 
@@
 \ref{fig:fig_rb} (c, d)).
-Correcting for the undersampling in the food webs improved the fit between the minimum number of predator guts and the number of trophic links from $R^2 = 0.13$ (Fig.
+However, correcting for the undersampling in the food webs improved the fit between the minimum number of predator guts and the number of trophic links from $R^2 = 0.13$ (Fig.
 \ref{fig:fig_rb} (a)) to $R^2 = 0.43$ (Fig.
@@
 
-We have demonstrated how a food web model can be used to predict the full structure of a food web when incomplete data about trophic interactions is available, which is true in most of the real food webs.
-This can help inform how much predator guts to actually collect when we are using a food web model to infer trophic interactions for an ecosystem with a given number of species.
+We have demonstrated how a food web model can be used to predict the full structure of a food web when incomplete data about trophic interactions is available, which is true in most real food webs.
+This can help inform how many predator guts to collect and analyse when we are using a food web model to infer trophic interactions for an ecosystem with a given number of species.
 A future development could be to make the same assessment using other food web models, and to also use food web data other than predator guts to parameterise those models.
@@
 \ref{fig:fig_rb} (d) can be used as a rough estimate of how many predator guts needs to be collected to predict food web structure using a food web model for a given number of species.
-This would lead to a reduction in the hundreds of predator guts that would have to be collected in the first place [@ingsEcologicalNetworksFood2009], thereby saving considerable time and resources.
+This could lead to a reduction in the number of predator guts that would be collected, [@ingsEcologicalNetworksFood2009], thereby saving considerable time and resources.
 
 In our study, we have implemented the approach only with the ADBM, which is a model based on size rules.
-Therefore, we suspect to get a similar result (i.e.
-minimum number of predator guts for a food web) for a different food web model based on size rules such as the niche model by @gravelInferringFoodWeb2013.
-For a given food web, some food web models might do better job at predicting its structure as compared to other food web models, so we suggest to extend our approach to other food web models such as niche model [@williamsSimpleRulesYield2000; @gravelInferringFoodWeb2013; @allesinaGeneralModelFood2008] and nested hierarchical model [@cattinPhylogeneticConstraintsAdaptation2004].
-A future prospect could be to study how well different food web models' prediction accuracy vary with different amount of predator guts.
-This can also help in making decision as to which food web model to chose from for a given a set of predator guts.
+We expect to get a similar result (i.e.
+minimum number of predator guts for a food web) for different food web models based on size rules such as the those by @gravelInferringFoodWeb2013.
+For a given food web, however, some food web models might be better at predicting structure compared to others, so we suggest to a range of models and their performance when parameterised with limited data [@williamsSimpleRulesYield2000; @gravelInferringFoodWeb2013; @allesinaGeneralModelFood2008; @cattinPhylogeneticConstraintsAdaptation2004].
+For example, future research could study how well different food web models' prediction accuracy vary with different amount of predator guts.
+This could also help in making decisions about which food web model to chose from for a given a set of predator guts.
 We suspect the relationship (i.e shape of the curve) between the TSS of the predicted food web and the number of predator guts might vary within food web models because of the difference on the set of rules used to define those models and how well those rules explain the food web structure.
@@
 
-Some studies have presented how the accuracy of food web prediction change when the amount of food web data is varied [@grayJoiningDotsAutomated2015].
+Some studies have presented how the accuracy of food web prediction changes when the amount of food web data is varied [@grayJoiningDotsAutomated2015].
 For example @desjardins-proulxEcologicalInteractionsNetflix2017 has used predictive machine learning models and @caronAddressingEltonianShortfall has used predictive traits-based models on partial knowledge of interactions to reconstruct a food web accurately, in contrast to our study where we used a mechanistic food web model.
+**OP: try to add some perspective here about this is interesting and or important.
+At present then question "so what" springs to mind.
 
-In all of the seven food webs, the ADBM was able to infer the trophic interactions using incomplete predator guts because the presence absence information from the predator guts was still sufficient to constrain the possible model parameter values of the ADBM that best explained the predators' diets.
-Although in theory the ADBM can predict trophic interactions using only body sizes of organisms as it is based on set of foraging rules, it still requires some presence absence data to constrain the posterior parameter space thereby making more accurate predictions [@petcheySizeForagingFood2008].
+In all of the seven food webs, the ADBM was able to infer the trophic interactions using incomplete predator guts because the diet information from the predator guts was still sufficient to constrain the possible model parameter values of the ADBM that best explained the predators' diets.
+Although in theory the ADBM can predict trophic interactions using only body sizes of organisms as it is based on set of foraging rules, it still requires some diet data to constrain the posterior parameter space thereby making more accurate predictions [@petcheySizeForagingFood2008].
+**OP: same as the comment I made on the previous paragraph.
 
 To characterise trophic interactions which are rare in the nature one would require more predator guts to observe those interactions as compared to characterising trophic interactions which are more frequent in the nature.
-The model is perhaps able to infer these rare interactions using a relatively lower number of predator guts which one might have inferred directly from the predator guts only after collecting a large number of gut content samples.
+The model is able to predict these rare interactions using a relatively lower number of predator guts which one might have inferred directly from the predator guts only after collecting a large number of gut content samples.
 
-Like any other food web models, the food web model used (the ADBM) cannot explain all the interactions in any observed food web that it has been fit to.
-The foraging rules it encodes are based on the body size and have particular structure and assumptions; not all of these are met by all observed interactions [@petcheySizeForagingFood2008].
+Like any other food web models, the food web model used (the ADBM) cannot explain all the interactions in any observed food web.
+The foraging rules it encodes are based on body size and have particular structure and assumptions; not all of these are met by all observed interactions [@petcheySizeForagingFood2008].
 For example, the ADBM can only predict diets that are contiguous with respect to the size of prey.
 I.e.
-it cannot predict that a predator will consume organism of size 1 and 3, and not organism of size 2.
+it cannot predict that a predator will consume an organism of size 1 and 3, and not organism of size 2.
 Hence, if the observed diets are not contiguous when prey are ordered by their size, the estimation process could lead to a lower value of the TSS [@guptaSimultaneouslyEstimatingFood2022].
@@
 S2) suggesting those food webs might be missing these rare trophic links, and the false positives from a model might be a correctly predicted link.
-A future prospect could be to incorporate other sources of presence-absence data such as stable isotope ratio [@laymanCanStableIsotope2007], DNA metabarcoding [@roslinUseDNABarcodes2016], literature review [@grayJoiningDotsAutomated2015; @cohenSoilInvertebratesChemistry2014; @goldwasserConstructionAnalysisLarge1993a] and experimentation [@warrenSpatialTemporalVariation1989] to complement any trophic links that were missed by the gut content method.
+A future prospect could be to incorporate other sources of presence-absence data such as stable isotope ratio [@laymanCanStableIsotope2007], DNA metabarcoding [@roslinUseDNABarcodes2016], literature review [@grayJoiningDotsAutomated2015; @cohenSoilInvertebratesChemistry2014; @goldwasserConstructionAnalysisLarge1993a] and experimentation [@warrenSpatialTemporalVariation1989] to complement trophic links that may have been missed by the gut content method.
 
 We expected a positive relationship between the minimum number of predator guts and the number of trophic links and number of species respectively.
+**OP: this expectation / hypothesis should be added to the Introduction, as I mentioned already in a slightly different way.
+Also why it is expected should be included.
 However, we did not find such relation (Fig.
 \ref{fig:fig_rb} (a, b)).
-We suspect this is due to the possibility that the food webs are sampled at different level (SI Fig.
+We suspect this is due to the possibility that the seven food webs have very different amounts of samples (SI Fig.
 S2), with Broadstone Stream being the most sampled among all the food webs.
-Taking into account the undersampling factor resulted in a better fit between the corrected minimum number of predator guts and corrected number of trophic links and number of species respectively (Fig.
-\ref{fig:fig_rb} (c, d)), however did not result in a relationship.
+Taking into account the undersampling resulted in a better fit between the corrected minimum number of predator guts and corrected number of trophic links and number of species respectively (Fig.
+\ref{fig:fig_rb} (c, d)).
+It did not however result in a statisticaly significant relationship.
 This could be due to heterogenity in the predator guts across food webs and heterogenity among food webs.
-First, if less number of prey items are present in a predator gut then more number of predator guts would need to be collected on an average to quantify the diet of that predator.
+First, if a fewer number of prey items are present in a predator gut, then more number of predator guts would need to be collected on an average to quantify the diet of that predator.
 Second, a food web which has a high proportion of generalist species would require a high number of predator guts on average to characterise the food web structure as compared to characterising the structure of a food web which has a high proportion of specialist species.
 
-In our study, we have not considered uncertainty which is involved in analysing the predator guts [@bakerFishGutContent2014].
+In our study, we have not considered any uncertainty involved in analysing the predator guts [@bakerFishGutContent2014].
 For example, there are sometimes loose tissues that are not identifiable and cannot be assigned to a specific prey item with certainty.
@@
 Therefore, the next step could be to incorporate these different factors of uncertainty in parameterising the model and to understand how these affect the accuracy of the predicted food webs.
+
+**OP: A short concluding paragraph would be good, to close with.
 
